### 2023-07-12 template.tex
Add latex template and bib file

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Master Thesis Template by Fabian Schär %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Packages and Document Settings %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt,a4paper,titlepage,oneside,english]{article}

%%% Main Packages %%%
\usepackage[english]{babel}
%\usepackage[ngerman]{babel} % Use this option for German settings.
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

%%% Additional Packages %%%
\usepackage{cite}
\usepackage{framed}
\usepackage{graphicx}
%\usepackage[german]{fancyref}
\usepackage[german,hidelinks]{hyperref} %hidelinks
\usepackage{multirow}
\usepackage[round]{natbib}
\usepackage{setspace}
\usepackage{geometry}
\usepackage{pst-all} % Not working with Sweave!!!

%%% Math Packages %%%
\usepackage{amsmath}
\usepackage{amstext}
\usepackage{amssymb}
\usepackage{theorem}
\usepackage{epsfig}
\usepackage{longtable}

%%% Layout Specifications %%%
\geometry{a4paper, top=35mm, left=40mm, right=40mm, bottom=45mm,
headsep=10mm, footskip=12mm}

%%% Parskip Settings %%%
\setlength{\parskip}{3mm}
\setlength{\parindent}{0mm}

%%% Document Specifications %%%
\title{Template Master's Thesis}
\author{John Doe}

%%%%%%%%%%%%%%%%%%
%%% Title Page %%%
%%%%%%%%%%%%%%%%%%

\begin{document}
%\begin{titlepage}
\begin{center}
\vspace{1em}
\large{Master Thesis}\\
\huge Developing Address Clustering Heuristics for Account-Based Blockchain Networks:\\ An Analysis based on a Specific Address Set \\
\Large \vspace{1em}
Dario Thürkauf
\end{center}

\vspace{1em}
\normalsize
\begin{flushleft}
Supervised by:\\ 
Prof. Dr. Fabian Schär \\
Credit Suisse Asset Management (Schweiz) Professor for \\ 
Distributed Ledger Technologies and Fintech \\
Center for Innovative Finance, University of Basel
\end{flushleft}

\vspace{1em}
\onehalfspacing
\begin{center}
\section*{Abstract}
\end{center}
Assentiar consuetae ha opinionum mentemque ob ii. Ne conflantur de intelligat et me cohibendam. Imaginandi ob to at agnoscerem et mutationum. In methodum ob ii at quicquid lectorum. Procuravi ha dependent ob evidenter tangantur concipere. Immortalem objectivus deo eae rei attingebam ita advertebam quamprimum. Typis patet prius qua nia mem ens. Suppono sim ita pendere nam agnosci quopiam vestiri spondeo dum. Tes illum mundo vetus signa fit talem res his.  \\
\vfill
\textbf{Keywords:} Keyword 1, Keyword 2, Keyword 3, Keyword 4.\\
\noindent\textbf{JEL:} X00, X00, X00
%\end{titlepage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Contents & Declaration%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pagenumbering{gobble}

\newpage
\pagenumbering{Roman}
\tableofcontents

\vfill
\begin{center}
\includegraphics[width=4cm]{../figures/logo_cif.png}
\end{center}
\newpage
\singlespacing
%\vspace{-1.5cm}
\section*{Declaration of Independent Authorship}
I attest with my signature that I have written this work independently and without outside help. I also attest that the information concerning the sources used in this work is true and complete in every respect. All sources that have been quoted or paraphrased have been marked accordingly. 
Additionally, I affirm that any text passages written with the help of AI-supported technology are marked as such, including a reference to the AI-supported program used. This paper may be checked for plagiarism and use of AI-supported technology using the appropriate software. I understand that unethical conduct may lead to a grade of 1 or ``fail`` or expulsion from the study program.\\

Dario Thürkauf

\begin{figure}[h!]
	\centering
	\hspace{-10cm}
	\includegraphics[width=3cm]{../figures/signature.jpeg}
\end{figure}
%%%%%%%%%%%%%%%%%%%%

\newpage
\onehalfspacing
\pagenumbering{arabic}

%%%%%%%%%%%%%%%%%%%
%%% Introduction%%%
%%%%%%%%%%%%%%%%%%%

\section{Introduction}
Propugnent solutiones id potentiale devenietur probabiles ii cognitione re. Si majestatis an sequuturum intelligat at im. Ulla ac de ausi vera vita meum tale. Tamen ullas ferre reddi aucta age vel aptum.\footnote{This is a footnote.} Communibus dulcedinem expectabam ima qui sequeretur objectivum. Age pla fal juncta somnis figura. Du caelum si natura quibus. Id omnis nulla fieri et video at falsa. Locusque et sentiens ei ac siquidem to. Istiusmodi ea ut voluntates formaliter. Admittere tantumdem at videlicet si. Ens aperte reddat imo altera quibus nemine. Priorem sternat dormire tes produci quosdam lapidem vel jam per. Mentemque abstinere aggredior percipior hic ita. Non aucupantur per ponderibus dulcedinem non.  \\

%%% Table
\begin{table}[h!]
  \center
  \begin{tabular}{lcc}
    \hline\hline
    Header & Header & Header \\ \hline
    Entry 1 & $0 \leq x<1$ & $\alpha$\\
    Entry 2 & $x=1$ & $\beta$\\
    Entry 3 & $x>1$ & $\gamma$\\
    \hline\hline
  \end{tabular}
  \caption{This is a table}
  \label{tbl:test}
\end{table}
%%%

As shown in table \ref{tbl:test}, deum sint fert suum cui voce tam jure. Cui mellis iisdem scient hic cumque vacabo necdum. Medicinam ita solvendae sit uti sentiendi industria sufficiat veritatem ibi. Si cera ea gi ausi vero data ii. Remotam futurus vix sentire cap est una. Certa reges ac dubie ii ab an talem cerae. Flexibile probandum geometras sic est non potestate admonitus vox. Ideoque una revolvo pla virorum mem lapidis nec. Simplex saeculi quidnam is ad. In somni ullam ideas solis ex sanae lapis ad.

%%%%%%%%%%%%%%%%%%%%%
%%% Preliminaries %%%
%%%%%%%%%%%%%%%%%%%%%

\section{Preliminaries}

%%%%%%%%%%%%
%%% Data %%%
%%%%%%%%%%%%

\section{Data Preparation}

%%%%%%%%%%%%%%%%%%%%%
%%% Data Analysis %%%
%%%%%%%%%%%%%%%%%%%%%

\section{Data Analysis}

%%%%%%%%%%%%%%%%%%
%%% Discussion %%%
%%%%%%%%%%%%%%%%%%

\section{Discussion}

%%%%%%%%%%%%%%%%%%
%%% Conclusion %%%
%%%%%%%%%%%%%%%%%%

\section{Conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Literaturverzeichnis %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\setcounter{page}{1}
\pagenumbering{roman}
\onehalfspacing
\addcontentsline{toc}{section}{References}
\bibliography{mybib}
\bibliographystyle{agsm}

%\section{Appendix}
\end{document}

### 2023-07-15 template.tex
Update .gitignore, update scripts, add latex

@@
 \section{Introduction}
-Propugnent solutiones id potentiale devenietur probabiles ii cognitione re.
-Si majestatis an sequuturum intelligat at im.
-Ulla ac de ausi vera vita meum tale.
-Tamen ullas ferre reddi aucta age vel aptum.\footnote{This is a footnote.} Communibus dulcedinem expectabam ima qui sequeretur objectivum.
-Age pla fal juncta somnis figura.
-Du caelum si natura quibus.
-Id omnis nulla fieri et video at falsa.
-Locusque et sentiens ei ac siquidem to.
-Istiusmodi ea ut voluntates formaliter.
-Admittere tantumdem at videlicet si.
-Ens aperte reddat imo altera quibus nemine.
-Priorem sternat dormire tes produci quosdam lapidem vel jam per.
-Mentemque abstinere aggredior percipior hic ita.
-Non aucupantur per ponderibus dulcedinem non.
-\\
-
-%%% Table
-\begin{table}[h!]
-  \center
-  \begin{tabular}{lcc}
-    \hline\hline
-    Header & Header & Header \\ \hline
-    Entry 1 & $0 \leq x<1$ & $\alpha$\\
-    Entry 2 & $x=1$ & $\beta$\\
-    Entry 3 & $x>1$ & $\gamma$\\
-    \hline\hline
-  \end{tabular}
-  \caption{This is a table}
-  \label{tbl:test}
-\end{table}
-%%%
-
-As shown in table \ref{tbl:test}, deum sint fert suum cui voce tam jure.
-Cui mellis iisdem scient hic cumque vacabo necdum.
-Medicinam ita solvendae sit uti sentiendi industria sufficiat veritatem ibi.
-Si cera ea gi ausi vero data ii.
-Remotam futurus vix sentire cap est una.
-Certa reges ac dubie ii ab an talem cerae.
-Flexibile probandum geometras sic est non potestate admonitus vox.
-Ideoque una revolvo pla virorum mem lapidis nec.
-Simplex saeculi quidnam is ad.
-In somni ullam ideas solis ex sanae lapis ad.
+Motivation \& Relevance of the topic \\
+Literarure Review: Still nascent field, First start with bitcoin/UTXO based, go over to account-based: Victor, Beres et al. \\
+Structure of the paper  \\
 
@@
 
+Similar to seminar thesis\\
+Account-based blockchains\\
+Ethereum, Polygon\\
+Smart Contracts, EOAs\\
+Transactions, Transfer Events \\
+Privacy-enhancing protocols, Tornado \\
+Metaverse, Decentraland \\
+Token Standards, shorter than in Seminar Thesis, comparable to Metaverse Retailing Paper \\
+
 %%%%%%%%%%%%
@@
 
-\section{Data Preparation}
+\section{Data Preparation and Retrieval}
+
+Transfer Events, adding Information (isInSet) \\
+Transactions \\
+Filtering, Intra-set transfers\\
+Data Structure, Fields \\
+Additional data \\
 
@@
 \section{Data Analysis}
+Existing clustering heuristics \\
+Graph-based network analysis\\
 
@@
 \end{document}
+
+%%% Table
+%\begin{table}[h!]
+%  \center
+%  \begin{tabular}{lcc}
+%    \hline\hline
+%    Header & Header & Header \\ \hline
+%    Entry 1 & $0 \leq x<1$ & $\alpha$\\
+%    Entry 2 & $x=1$ & $\beta$\\
+%    Entry 3 & $x>1$ & $\gamma$\\
+%    \hline\hline
+%  \end{tabular}
+%  \caption{This is a table}
+%  \label{tbl:test}
+%\end{table}
+%%%

### 2023-08-01 python/prepare-transfer-event-data.py
Reorganize folder

@@ -103,4 +103,4 @@ events_inSet['userAddress'] = events_inSet.apply(lambda row: row['from'] if row[
                                                  axis=1)
 
 # Save as csv
-events_inSet.to_csv('../data/transfer_events.csv')
+events_inSet.to_csv('../data/raw_transfer_events.csv')

### 2023-08-01 python/utils.py
Add Deepwalk to utils.py

@@ -1,6 +1,6 @@
 # Import packages
 import pandas as pd
-from karateclub import Diff2Vec, Role2Vec
+from karateclub import Diff2Vec, Role2Vec, DeepWalk
 import networkx as nx
 import matplotlib.pyplot as plt
 import numpy as np

### 2023-08-02 python/computeStatisticsDistributions.py
Add address stats and distributions
TimeOfDay and normalizedGas

@@ -1,0 +1,86 @@
+import pandas as pd
+import numpy as np
+from datetime import datetime
+
+
+def add_ToD(df):
+    df['timeStamp'] = pd.to_datetime(df['timeStamp'], unit='s')
+    df['ToD'] = df['timeStamp'].dt.hour * 3600 + df['timeStamp'].dt.minute * 60 + df['timeStamp'].dt.second
+    return df
+
+def compute_statistics(data):
+    """ Compute mean, median, standard deviation for each 'from' address """
+    stats = data.groupby('from').agg({'ToD': ['mean', 'median', np.std]})
+    stats.columns = ['_'.join(col).strip() for col in stats.columns.values]
+    return stats
+
+def compute_histogram(data, bins):
+    """ Compute histogram for ToD column with specified number of bins """
+    labels = [f"hist_bin_{i}" for i in range(1, bins+1)]
+    data['bin'] = pd.cut(data['ToD'], bins=bins, labels=labels)
+    hist_data = data.groupby(['from', 'bin']).size().unstack(fill_value=0)
+    return hist_data
+
+
+# Load data
+ethereum_trx = pd.read_csv('../data/raw_ethereum_transactions.csv', index_col=[0])
+polygon_trx = pd.read_csv('../data/raw_polygon_transactions.csv', index_col=[0])
+transaction_df = pd.concat([ethereum_trx, polygon_trx])
+
+
+
+#################
+### TimeOfDay ###
+#################
+
+# Add ToD column
+transaction_df = add_ToD(transaction_df)
+
+# Filter out addresses with less then 5 trx sent
+#counts = transaction_df.groupby('from').size()
+#addresses_to_keep = counts[counts >= 5].index
+#transaction_df_filtered = transaction_df[transaction_df['from'].isin(addresses_to_keep)]
+transaction_df_filtered = transaction_df[transaction_df.groupby('from')['from'].transform('size') >= 5]
+
+
+# Compute statistics and histogram
+hist_df = compute_histogram(transaction_df_filtered, bins=6)
+stats_df = compute_statistics(transaction_df_filtered)
+result_df = pd.merge(stats_df, hist_df, left_index=True, right_index=True)
+
+# Save to csv
+result_df.to_csv('../data/timeOfDay.csv')
+
+
+################
+### GasPrice ###
+################
+
+# Add date column
[…]

### 2023-08-02 python/utils.py
Update utils.py

@@ -8,13 +8,14 @@ import seaborn as sns
 
 
 # Functions
-def compute_weights(df): ### evtl direkt mit undirected graph arbeiten
+def compute_weights(df):  ### evtl direkt mit undirected graph arbeiten
     # Sort from and to addresses lexicographically
     df['from'], df['to'] = np.where(df['from'] > df['to'], [df['to'], df['from']], [df['from'], df['to']])
     # Group by 'from' and 'to', and count the number of interactions
     grouped_df = df.groupby(['from', 'to']).size().reset_index(name='weight')
-    #grouped_df = grouped_df.rename(columns={"from": "address1", "to": "address2"})
+    # grouped_df = grouped_df.rename(columns={"from": "address1", "to": "address2"})
     return grouped_df
+
 
 def clean_graph(G, k=None):
     """Convert to undirected graph and remove self loops"""
@@ -26,6 +27,7 @@ def clean_graph(G, k=None):
     if k is not None:
         G_tmp = nx.k_core(G_tmp, k=2)
     return G_tmp
+
 
 def recode_graph(G):
     """Rename nodes to work with Diff2Vec"""
@@ -57,33 +59,34 @@ def address_txs(address_str):
     transaction_df = pd.read_csv('../data/native_transfers.csv', index_col=[0])
     all_df = pd.concat([transaction_df, transfer_df], ignore_index=True)
     address = str(address_str).lower()
-    txs = all_df[(all_df["from"]==address) | (all_df["to"]==address)]
+    txs = all_df[(all_df["from"] == address) | (all_df["to"] == address)]
     return txs.sort_values("timeStamp")
 
 
-def show_patterns(events_df, addresses, hour_bins=24, figsize=(15,3), show_kde=False):
+def show_patterns(events_df, addresses, hour_bins=24, figsize=(15, 3), show_kde=False):
     """Show side channels distribution of the given addresses"""
     addresses = [addr.lower() for addr in addresses]
     events_df['timeStamp'] = pd.to_datetime(events_df['timeStamp'], unit='s')
-    events_df['hour'] = events_df['timeStamp'].dt.hour * 3600 + events_df['timeStamp'].dt.minute * 60 + events_df['timeStamp'].dt.second
+    events_df['hour'] = events_df['timeStamp'].dt.hour * 3600 + events_df['timeStamp'].dt.minute * 60 + events_df[
+        'timeStamp'].dt.second
[…]

### 2023-08-03 paper.tex
Add notes to paper

--- 2023-07-15 template.tex
@@
 	\hspace{-10cm}
-	\includegraphics[width=3cm]{../figures/signature.jpeg}
+	%\includegraphics[width=3cm]{../figures/signature.jpeg}
 \end{figure}
@@
 Motivation \& Relevance of the topic \\
-Literarure Review: Still nascent field, First start with bitcoin/UTXO based, go over to account-based: Victor, Beres et al. \\
+
+% Transaction data publicly available
+% Not really good to hide illicit business acitivities.
+% First, this was exploited in Bitcoin and Bitcoins UTXO model
+% Recently also account-based
+
+Literarure Review: Still nascent field, First start with bitcoin/UTXO based, go over to account-based: Victor, Beres et al., Tutela \\
 Structure of the paper  \\
@@
 
-Similar to seminar thesis\\
 Account-based blockchains\\
@@
 \section{Data Preparation and Retrieval}
+From our address set containing X addresses, we selected addresses that were active on either Ethereum or Polygon using blockscan.
+Using this list, we were able to significantly reduce the amount of API calls.
+We collected these addresses transactions and token transfer data.
 
@@
 Data Structure, Fields \\
-Additional data \\
+Additional data, ENS \\
 
@@
 Graph-based network analysis\\
+
+Self-authorization \\
+Transaction Graph Analysis \\
+The set of addresses used in interactions characterize a users.
+Users with multiple accounts might interact with the same addresses from most of them.
+Furthermore, as users move funds between their personal addresses, they may unintetionally reveal their address clusters.
+Clustering experiments conducted on a transaction/transfer graph with nodes as addresses and edges as transactions/transfers.
+Rozemberczki provides a library of node embedding methods to discover address pairs that might belong to the same user.
+Preprocessing steps: transfers as undirected edges, remove loops and multi-edges, exlcude nodes outside the largest connected component.
+Resulting graph.
+Applied 3 node embedding methods to this graph (Diff2Vec, Role2Vec and deep walk.
+
+Diff2Vec, Role2Vec, DeepWalk \\
+Time-of-day transaction activity \\
+Transaction timestamps reveal the daily activity patterns of the account owner -> example
+Given the set of timestamps, an account is represented by the vector including the mean, median and standard deviation, as well as the time-of-day activity histogram dividid into $b_{hour}$ bins.
+We chose 50 bins (from beres)
+Gas price distribution \\
+Gas price definition, often set by the wallet software (slow, medium, fast), given the changes in traffic volume we normalice the gas price bxy the daily network average in our dataset.
+Make example.
+Given the normalized gas prices of the transactions sent, an account is represented by the mean, median and standard deviation, as well as the normalized gas price histogram divided into $b_{gas}$ bins.
+We chose 6 bins (4 hour intervals) according to Beres.
 

### 2023-08-03 python/approvals.py
Update python scripts

@@ -1,7 +1,7 @@
 from pymongo import MongoClient
 import pandas as pd
 
-# Connect to db collections
+# Connect to db collection
 client = MongoClient('mongodb://localhost:27017/')
 db = client['address-clustering']
 transactions = db['transactions']
@@ -17,9 +17,11 @@ approvals['spender'] = approvals['spender'].apply(lambda x: '0x' + x)
 
 # Only keep spenders from set
 self_approvals = approvals[approvals['spender'].isin(users)]
+print(f'Approvals of set address: {len(self_approvals)}')
 
 # Only keep senders from set that approved another address
 filtered_self_approvals = self_approvals[self_approvals['from'] != self_approvals['spender']]
+print(f'Approvals of set address (other address): {len(filtered_self_approvals)}')
 
 # Remove unnecessary rows
 filtered_self_approvals = filtered_self_approvals[['hash','from', 'to', 'spender']].reset_index(drop=True)
@@ -27,3 +29,5 @@ filtered_self_approvals = filtered_self_approvals[['hash','from', 'to', 'spender
 # Group approvals by 'from' address
 grouped_df = filtered_self_approvals.groupby(['from']).size().reset_index(name='Number of Approvals given')
 print(grouped_df)
+print(filtered_self_approvals)
+

### 2023-08-03 python/computeStatisticsDistributions.py

@@ -8,16 +8,16 @@ def add_ToD(df):
     df['ToD'] = df['timeStamp'].dt.hour * 3600 + df['timeStamp'].dt.minute * 60 + df['timeStamp'].dt.second
     return df
 
-def compute_statistics(data):
+def compute_statistics(data, col_name='ToD'):
     """ Compute mean, median, standard deviation for each 'from' address """
-    stats = data.groupby('from').agg({'ToD': ['mean', 'median', np.std]})
+    stats = data.groupby('from').agg({col_name: ['mean', 'median', np.std]})
     stats.columns = ['_'.join(col).strip() for col in stats.columns.values]
     return stats
 
-def compute_histogram(data, bins):
-    """ Compute histogram for ToD column with specified number of bins """
-    labels = [f"hist_bin_{i}" for i in range(1, bins+1)]
-    data['bin'] = pd.cut(data['ToD'], bins=bins, labels=labels)
+def compute_histogram(data, bins, col_name='ToD'):
+    """ Compute histogram for specified column with number of bins """
+    labels = [f"{col_name}_hist_bin_{i}" for i in range(1, bins+1)]
+    data['bin'] = pd.cut(data[col_name], bins=bins, labels=labels)
     hist_data = data.groupby(['from', 'bin']).size().unstack(fill_value=0)
     return hist_data
 
@@ -28,7 +28,6 @@ polygon_trx = pd.read_csv('../data/raw_polygon_transactions.csv', index_col=[0])
 transaction_df = pd.concat([ethereum_trx, polygon_trx])
 
 
-
 #################
 ### TimeOfDay ###
 #################
@@ -37,19 +36,15 @@ transaction_df = pd.concat([ethereum_trx, polygon_trx])
 transaction_df = add_ToD(transaction_df)
 
 # Filter out addresses with less then 5 trx sent
-#counts = transaction_df.groupby('from').size()
-#addresses_to_keep = counts[counts >= 5].index
-#transaction_df_filtered = transaction_df[transaction_df['from'].isin(addresses_to_keep)]
 transaction_df_filtered = transaction_df[transaction_df.groupby('from')['from'].transform('size') >= 5]
 
-
 # Compute statistics and histogram
-hist_df = compute_histogram(transaction_df_filtered, bins=6)
-stats_df = compute_statistics(transaction_df_filtered)
[…]

### 2023-08-03 python/utils.py

@@ -149,9 +149,9 @@ class DistCalculation:
 
             if len(indices1) > 0 and query_idx2 in indices1 and len(indices2) > 0 and query_idx1 in indices2:
                 trg_idx1 = np.where(indices1 == query_idx2)[0]
-                print(trg_idx1)
+                #print(trg_idx1)
                 trg_idx2 = np.where(indices2 == query_idx1)[0]
-                print(trg_idx2)
+                #print(trg_idx2)
                 average_rank = (trg_idx1.item() + 1 + trg_idx2.item() + 1) / 2
                 average_distance = (distances1[trg_idx1].item() + distances2[trg_idx2].item()) / 2
                 return average_rank, average_distance

### 2023-08-04 paper.tex
Add intro and data collection draft

@@
 \begin{center}
-\includegraphics[width=4cm]{../figures/logo_cif.png}
+%\includegraphics[width=4cm]{../figures/logo_cif.png}
 \end{center}
@@
 \section{Introduction}
-Motivation \& Relevance of the topic \\
 
+In public permissionless blockchains such as Bitcoin \citep{nakamotoBitcoin2008} and Ethereum \citep{buterin2014ethereum}, individuals can participate with multiple pseudonymous addresses.
+Any user can create a large number of these addresses at virtually no cost.
+Also, contrary to popular belief, permissionless blockchains are completely transparent.
+All confirmed transactions are publicly observable and stored as part of the blockchain’s history.
+This has opened up a nascent scientific field dealing with entity identification within blockchain networks.
+By analyzing on-chain data and detecting usage patterns, researchers try to cluster addresses that are controlled by the same user.
+Most of these methods are heuristics, as the lack of a ground truth makes evaluation hard \newline
+On the one hand, knowing which addresses belong to the same real-world entity is advantageous, as it allows for a better assessment of network properties in terms of usage, wealth distribution, and fraudulent activity \citep{FV:17}.
+For example, a user could manipulate a seemingly fair on-chain voting process by splitting his voting power among multiple addresses.
+\newline
+On the other hand, the lack of privacy is also detrimental to most use cases, especially financial applications.
+In response to this/ as a countermeasure, several privacy-enhancing protocols and tools have been proposed to obfuscate transaction tracing.
+This reaction has, in turn, sparked the development of other clustering heuristics exploiting user behavior interacting with privacy-enhancing protocols.
+\newline
+
+%Identifying addresses that belong to the same entity is predominantly done through heuristics. These heuristics try to make sense
+
+\textbf{Related work}
+
+Previous work in this field can be broadly distinguished between heuristics developed for the unspent transaction output (UTXO) model (e.g Bitcoin, ZCash) and the account-based model (e.g.
+Ethereum, Polygon).
+While these models share the concept of addresses, the concept of accounts is not present in UTXO-based blockchains and the way in which transactions are processed is fundamentally different.
+In the UTXO model, each transaction has to reference an .
+When spending a Bitcoin, a user creates a UTXO.
+Each UTXO incorporates a spending condition, which can only be fulfilled by the .
+Transactions can thought of as large graphs of inputs and outputs and most wallet implementation use a new Bitcoin address/public key for each transaction.
+
+%Two architectures/models. Describe and compare.
+
+\textbf{UTXO-model clustering heuristics} %not the focus of this work and therefore not explained
+
+Meiklejohn
+
+In contrast to the UTXO-model, in account-based blockchains, native transactions can only move funds between a single sender and receiver (payment transaction), and the “change” remains in the sender account.
+Subsequent transactions necessarily use the same address again.
+The account-based model essentially relies on address reuse on the protocol level.
+(Citation)
+
+\textbf{Account-model clustering heuristics}
+
+\cite{FV:17} was the first to introduce clustering heuristics for account-based blockchains.
+He proposed and applied heuristics that exploit patterns related to deposit addresses, multiple participation in airdrops, and token authorization mechanisms.
+\newline
+\cite{Beres2020} argue that Victor’s heuristics, while powerful, assume participation in certain on-chain events and therefore propose more universally applicable methods.
+Their technique utilizes graph representation learning, a subset of machine learning interpreting transactions or token transfers as network graphs, with addresses as nodes and transactions or token transfers as edges.
+They further contribute to the field by proposing time-of-day activity and transaction fee-based user profiling techniques.
+Using ENS address pairs as ground truth, they test the methods rigorously and apply their findings to significantly reduce the privacy guarantees of Tornado Cash.
+They also provide a comprehensive overview and comparison of different node embedding algorithms.
+\newline
+\cite{wu2022tutela} adapt one of Beres et al.
+node embedding algorithms and apply it at scale.
+Further, they propose five clustering heuristics in the context of Tornado Cash.
+They build an application built on those heuristics to report the true anonymity of an Ethereum address.
+All methods will be discussed in greater detail in Section 3.
+Broadening the scope to entity identification, Friedhelm and Lüders (2020) undertook an analysis of the top 1000 Ethereum-ERC20 token networks from a graph perspective.
+Similarly, Casale-Brunet et al.
+extended the analysis to various NFT (ERC721) ecosystems.
+(Payette Schwager)
+
+Instead of on-chain data, \cite{yu2023} propose a new correlation method by utilizing nodes as entities, exploiting network information.
+This approach comes with a whole new set of limitations and problems, but one can possibly avoid the impact of privacy-enhancing technologies.
+This approach may be interesting once privacy-enhancing techniques are more widely used.
+
+%network level/off-chain data ->
+%transaction level/ on-chain data ->
+
+\textbf{Our contribution}\\
+Anwenden/discuss and evaluate existing heuristics to my specific address set.
+Anpassen, erweitern
+Eigene, spezifische Heuristiken ausdenken
+
+\textbf{Structure of the paper}
+The remainder of this paper is structured as follows: In Section 2, we provide a brief overview of the key concepts (basics, necessary for understanding the setup), including Ethereum accounts and the EVM, tokens, Decentraland and privacy-enhancing protocols.
+In Section 3, we describe our data collection methodology and the data preparation.
+Section 4  describes and different clustering heuristics in detail.
+Section 5 applies the clustering heuristics from 4.
+Finally we discuss the results of our analysis and summarize our findings in Sections 5 and 6.
+
+% Motivation \& Relevance of the topic \\
 % Transaction data publicly available
@@
 % Recently also account-based
-
-Literarure Review: Still nascent field, First start with bitcoin/UTXO based, go over to account-based: Victor, Beres et al., Tutela \\
-Structure of the paper  \\
+%Literarure Review: Still nascent field, First start with bitcoin/UTXO based, go over to account-based: Victor, Beres et al., Tutela \\
 
@@
 
-Account-based blockchains\\
-Ethereum, Polygon\\
-Smart Contracts, EOAs\\
-Transactions, Transfer Events \\
-Privacy-enhancing protocols, Tornado \\
-Metaverse, Decentraland \\
-Token Standards, shorter than in Seminar Thesis, comparable to Metaverse Retailing Paper \\
+\textbf{Account-based blockchains, Contract Accounts and EOAs}\\
+Account-based blockchains usually distinguish between \textit{externally owned accounts} (EOAs) and \textit{contract accounts} (smart contracts).
+EOAs are created and controlled by private keys and can be used to hold the native protocol asset, send and receive transactions, and interact with contract accounts.
+Contract accounts are controlled by the contract's code, their state can be modified through transactions sent to the contract and they cannot initiate transactions.
+\citep{buterin2014ethereum} \newline Each account has a 20-byte address encoded in hexadecimal.
+For EOAs, this address is based on the last 20 bytes of the Keccak-256 hash of the ECDSA public key.
+For contract accounts, it is defined as the last 20 bytes of the Keccak-256 hash of the RLP encoding of the sender address and account nonce.
+\citep{GW:14} \newline
+In addition, \cite{eip1014} introduces a new contract creation mechanism allowing for more predictable contract addresses.%EIP-1014
+
+\textbf{Ethereum, Polygon, EVM}\\
+
+\textbf{Transactions, Transfer Events}\\
+
+\textbf{Tokens and Token Standards}\\
+%shorter than in Seminar Thesis, comparable to Metaverse Retailing Paper
+
+\textbf{Metaverse, Decentraland} \\
+
+\textbf{Privacy-enhancing protocols, mixing, Tornado} \\
 
@@
 
-\section{Data Preparation and Retrieval}
-From our address set containing X addresses, we selected addresses that were active on either Ethereum or Polygon using blockscan.
-Using this list, we were able to significantly reduce the amount of API calls.
-We collected these addresses transactions and token transfer data.
+\section{Data Collection and Preparation}
 
-Transfer Events, adding Information (isInSet) \\
-Transactions \\
-Filtering, Intra-set transfers\\
-Data Structure, Fields \\
+The initial dataset contained 473,927 unique Web3 addresses.
+As we are only interested in clustering methods leveraging on-chain transaction or token transfer data, we omit addresses that were not recorded on either Ethereum or Polygon.
+This was achieved using data/information from Blockscan\footnote{\url{https://blockscan.com/}}.
+In total, 59,651 addresses were recorded on Ethereum, 129,988 addresses on Polygon and 52,095 on both networks simultanously.
+Therefore, the remaining address set comprises 137,544 addresses.
+Figure 1 visualizes the subsets in a VENN diagram.
+We used these addresses to gather/collect transaction and token transfer receipts from Ethereum Mainnet and Polygon PoS.
+Ethereum or Polygon data can be accessed directly through a node or an application programming interface (API) provider such as Infura or Etherscan.
+The absence of account indexing in Ethereum or Polygon makes queries of the type "Retrieve all past transactions and token transfers of address \texttt{0xABC}" challenging, as one would have to scan through every block and every token transfer event emitted by a specified set of token contracts.
+Fortunately, Etherscan offers/provides an API Endpoint Module for ``Accounts`` that facilitates the retrieval of transactions and token transfer events for a given address.
+Using our network specific address subsets, we were able to significantly reduce the amount of API calls.
+
+We gathered all transactions and token transfer data of the addresses until block 17,670,000 on Ethereum (July 11, 2023) and block 44,990,000 on Polygon (July 12, 2023).
+The results were stored in comma-separated value (CSV) files and loaded into a MongoDB database\footnote{\url{https://www.mongodb.com/}}.
+
+Statistics about data, how many transactions, how many transfers, size
+Transfer events = 30,689,978
+Transactions = 16,184,993, how many polygon/ethereum, table
+
+\begin{table}[h]
+\centering
+\begin{tabular}{lcc}
+\hline \hline
+  & Transactions & Transfers \\
+ \hline
+ Polygon & Cell 2 & Cell 3 \\
+ Ethereum & Cell 5 & Cell 6 \\
+ \hline
+ Total & 16,184,993 & 30,689,978 \\
+ \hline \hline
+\end{tabular}
+\caption{Size of raw data}
+\label{tab:data_size}
+\end{table}
+
+The transaction data fields contain the transaction hash, from and to address, the timestamp in seconds from UNIX epoch, a nonce, value, input (calldata), gasused, gasprice, functionname (from Etherscan), chainname.
+Token transfer receipts include the transactions hash, timestamp, from and to address, nonce, gas price, the amount of gas used, chain information, the token contract address and name, tokenType, and token standard specific fields: value, tokenDecimal for ERC-20, tokenID for ERC-721, and value/tokenID for ERC-1155.
+
+%Transfer Events, adding Information (isInSet) \\
+%Transactions \\
+%Filtering, Intra-set transfers\\
+%Data Structure, Fields \\
+%We reduced this set to addresses that were active/recorded on either Ethereum or Polygon using Blockscan\footnote{\url{https://blockscan.com/}}. This reduced the address set from to X.
+%Using Blockscan\footnote{\url{https://blockscan.com/}}, we were able to reduce the address set to addresses that were recorded on either Ethereum or Polygon.
+
+For detecting ground truth pairs in order to evaluate our node embedding methods, we gathered data from ENS contract...
 Additional data, ENS \\
 
-%%%%%%%%%%%%%%%%%%%%%
-%%% Data Analysis %%%
-%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%% Clustering Heuristics %%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Data Analysis}
-Existing clustering heuristics \\
-Graph-based network analysis\\
+\section{Clustering Heuristics}
+% Goal: explain each heuristic, categorize, and discuss applicability to our address set
 
 Self-authorization \\
-Transaction Graph Analysis \\
-The set of addresses used in interactions characterize a users.
+Deposit address reuse \\
+Airdrop multi participation \\
+
+Graph-based network analysis / Transaction Graph Analysis
+Token networks -> Victor, Casale Brunet
+
+%The set of addresses used in interactions characterize a users.
 Users with multiple accounts might interact with the same addresses from most of them.
@@
 We chose 6 bins (4 hour intervals) according to Beres.
+
+%%%%%%%%%%%%%%%%%%%%%
+%%% Data Analysis %%%
+%%%%%%%%%%%%%%%%%%%%%
+
+\section{Data Analysis}
 

### 2023-08-04 paper.tex
Update intro

@@
 \newline
-On the other hand, the lack of privacy is also detrimental to most use cases, especially financial applications.
-In response to this/ as a countermeasure, several privacy-enhancing protocols and tools have been proposed to obfuscate transaction tracing.
+On the other hand, the lack of privacy is also detrimental to most financial use cases(financial applications).
+In response to this, several privacy-enhancing protocols and tools have been proposed to obfuscate transaction tracing.
+The most prominent/widely used of which is Tornado cash.
 This reaction has, in turn, sparked the development of other clustering heuristics exploiting user behavior interacting with privacy-enhancing protocols.
@@
 
-%Identifying addresses that belong to the same entity is predominantly done through heuristics. These heuristics try to make sense
+%Privacy will be an important topic in the future.
 
-\textbf{Related work}
+%Identifying addresses that belong to the same entity is predominantly done through heuristics.
 
+\textbf{Related work}\\
 Previous work in this field can be broadly distinguished between heuristics developed for the unspent transaction output (UTXO) model (e.g Bitcoin, ZCash) and the account-based model (e.g.
 Ethereum, Polygon).
-While these models share the concept of addresses, the concept of accounts is not present in UTXO-based blockchains and the way in which transactions are processed is fundamentally different.
-In the UTXO model, each transaction has to reference an .
-When spending a Bitcoin, a user creates a UTXO.
-Each UTXO incorporates a spending condition, which can only be fulfilled by the .
-Transactions can thought of as large graphs of inputs and outputs and most wallet implementation use a new Bitcoin address/public key for each transaction.
+While both share the concept of addresses, the concept of accounts is not present in UTXO-based blockchains and the way in which transactions are processed is fundamentally different.
+Therefore, clustering heuristics are not applicable to account-model blockchains.
+Meiklejohn et al.
+proposes
 
-%Two architectures/models. Describe and compare.
-
-\textbf{UTXO-model clustering heuristics} %not the focus of this work and therefore not explained
-
-Meiklejohn
+\textbf{UTXO-model clustering heuristics} \\%not the focus of this work and therefore not explained
+A number of address clustering heuristics in the UTXO setup have been proposed Bitcoin (Meiklejohn), Litecoin, and ZCash.
+Satoshi proposed using a new address for each transaction and most wallets work this way.
 
@@
 
-\textbf{Account-model clustering heuristics}
-
+\textbf{Account-model clustering heuristics}\\
 \cite{FV:17} was the first to introduce clustering heuristics for account-based blockchains.
@@
 \newline
-\cite{wu2022tutela} adapt one of Beres et al.
-node embedding algorithms and apply it at scale.
+\cite{wu2022tutela} extend on one of \cite{Beres2020} node embedding algorithms and apply it at scale.
 Further, they propose five clustering heuristics in the context of Tornado Cash.
@@
 All methods will be discussed in greater detail in Section 3.
-Broadening the scope to entity identification, Friedhelm and Lüders (2020) undertook an analysis of the top 1000 Ethereum-ERC20 token networks from a graph perspective.
-Similarly, Casale-Brunet et al.
-extended the analysis to various NFT (ERC721) ecosystems.
-(Payette Schwager)
+Broadening the scope to entity identification, \cite{victorlüders2019} undertook an analysis of the top Ethereum-ERC20 token networks from a graph perspective.
+Similarly, \cite{casalebrunet2021} extend the analysis to various NFT (ERC721) ecosystems.
+Both find ...
+Payette schwager propose a segmentation of Ethereum address space into four distinct behaviour groups based on a broad range of address features (k-means).
 
@@
 %transaction level/ on-chain data ->
+%In the UTXO model, each transaction has to reference an output from a previous transaction.
+When spending a Bitcoin, a user creates a UTXO.
+Each UTXO incorporates a spending condition, which can only be fulfilled by the .
+Transactions can thought of as large graphs of inputs and outputs and most wallet implementation use a new Bitcoin address/public key for each transaction.
 
 \textbf{Our contribution}\\
-Anwenden/discuss and evaluate existing heuristics to my specific address set.
-Anpassen, erweitern
-Eigene, spezifische Heuristiken ausdenken
+In this work, we perform entity identification/address clustering on an address set containing 473,927 addresses. 
+These addresses were gathered in a separate project by collecting avatar activity snapshots over a 8 month time frame spanning from July, 2022 to April, 2023.
+Due to the blockchain-based architecture of Decentraland, each avatar contains information about a users' Web3 address.
 
-\textbf{Structure of the paper}
+We test the applicability of existing heuristics for our case and evaluate their success in detecting (given there is a ground truth).
+We estimate how many real-world entities are represented by these addresses.
+To achieve this, we adapt and extend existing methods to our specific situation/setting.
+
+Propose own heuristics approaches for detecting address clusters.
+
+%We apply several existing clustering heuristics in order to cluster a specific set containing 400k addresses.
+%Anwenden/discuss and evaluate existing heuristics to my specific address set.
+%Anpassen, erweitern
+%Eigene, spezifische Heuristiken ausdenken
+
+\textbf{Structure of the paper}\\
 The remainder of this paper is structured as follows: In Section 2, we provide a brief overview of the key concepts (basics, necessary for understanding the setup), including Ethereum accounts and the EVM, tokens, Decentraland and privacy-enhancing protocols.
@@
 
-\textbf{Account-based blockchains, Contract Accounts and EOAs}\\
+\textbf{Contract Accounts and EOAs}\\
 Account-based blockchains usually distinguish between \textit{externally owned accounts} (EOAs) and \textit{contract accounts} (smart contracts).

### 2023-08-05 python/utils.py
Update node embedding script

@@ -5,6 +5,7 @@ import networkx as nx
 import matplotlib.pyplot as plt
 import numpy as np
 import seaborn as sns
+from tqdm import tqdm
 
 
 # Functions
@@ -99,6 +100,7 @@ def format_x_axis(ax, hour_bins):
     ax.set_xticks(x_ticks)
     x_labels = [f'{int(tick / 3600)}' for tick in x_ticks]
     ax.set_xticklabels(x_labels)
+
 
 
 ############################

### 2023-08-05 paper.tex
Update introduction

@@
 
-In public permissionless blockchains such as Bitcoin \citep{nakamotoBitcoin2008} and Ethereum \citep{buterin2014ethereum}, individuals can participate with multiple pseudonymous addresses.
-Any user can create a large number of these addresses at virtually no cost.
-Also, contrary to popular belief, permissionless blockchains are completely transparent.
-All confirmed transactions are publicly observable and stored as part of the blockchain’s history.
+Public permissionless blockchains such as Bitcoin \citep{nakamotoBitcoin2008} and Ethereum \citep{buterin2014ethereum} allow users/individuals to participate with multiple pseudonymous addresses.
+The creation of these addresses is virtually cost free.
+Contrary to popular belief, these blockchains are entirely transparent.
+All transactions are stored as part of the blockchain's history and publicly observable.
 This has opened up a nascent scientific field dealing with entity identification within blockchain networks.
-By analyzing on-chain data and detecting usage patterns, researchers try to cluster addresses that are controlled by the same user.
-Most of these methods are heuristics, as the lack of a ground truth makes evaluation hard \newline
-On the one hand, knowing which addresses belong to the same real-world entity is advantageous, as it allows for a better assessment of network properties in terms of usage, wealth distribution, and fraudulent activity \citep{FV:17}.
-For example, a user could manipulate a seemingly fair on-chain voting process by splitting his voting power among multiple addresses.
+Researchers try to cluster addresses controlled by the same user by analyzing on-chain data and detecting usage patterns.
+The majority of these methods are heuristic which often makes them difficult to evaluate due to the absence of any ground truth.
 \newline
-On the other hand, the lack of privacy is also detrimental to most financial use cases(financial applications).
-In response to this, several privacy-enhancing protocols and tools have been proposed to obfuscate transaction tracing.
-The most prominent/widely used of which is Tornado cash.
-This reaction has, in turn, sparked the development of other clustering heuristics exploiting user behavior interacting with privacy-enhancing protocols.
+On one hand, identifying the addresses that belong to the same real-world entity is beneficial as it allows better evaluation of network properties with respect to usage, distribution of wealth and detecting fraudulent activities \citep{FV:17}.
+For instance, if a user distributes their voting power across various addresses, they might manipulate an on-chain voting process that seems fair at the outset.
 \newline
+Conversely, the lack of privacy is also detrimental to most financial use cases (DeFi).
+As a response, multiple privacy-enhancing tools and protocols have been proposed to obfuscate transaction tracing.
+Nonetheless, these protocols are not yet widely adopted and careless user behaviour can undermine the privacy guarantees they offer. \newline
+The topic of privacy, or lack thereof, will remain significant for future blockchain development and research.
 
-%Privacy will be an important topic in the future.
-
-%Identifying addresses that belong to the same entity is predominantly done through heuristics.
+%However, they are not widely used even cannot guarantee perfect privacy (factors: size of anonymity set, usage /user behaviour of protocol, privacy guarantees depend on other users).
+%The most prominent/widely used non-custodial mixer is Tornado cash (Schär, Tutela).
+%This reaction has, in turn, sparked the development of other clustering heuristics exploiting user behavior interacting with privacy-enhancing protocols.
 
@@
 Ethereum, Polygon).
-While both share the concept of addresses, the concept of accounts is not present in UTXO-based blockchains and the way in which transactions are processed is fundamentally different.
-Therefore, clustering heuristics are not applicable to account-model blockchains.
-Meiklejohn et al.
-proposes
-
-\textbf{UTXO-model clustering heuristics} \\%not the focus of this work and therefore not explained
-A number of address clustering heuristics in the UTXO setup have been proposed Bitcoin (Meiklejohn), Litecoin, and ZCash.
-Satoshi proposed using a new address for each transaction and most wallets work this way.
-
-In contrast to the UTXO-model, in account-based blockchains, native transactions can only move funds between a single sender and receiver (payment transaction), and the “change” remains in the sender account.
+While both models share the concept of addresses, the notion of accounts is not present in UTXO-based blockchains.
+The way in which transactions are processed is fundamentally different, and therefore, clustering heuristics are not applicable to both paradigms.
+%\textbf{UTXO-model clustering heuristics} 
+A number of address clustering heuristics in the UTXO setup have been proposed for Bitcoin and derivatives \citep{Androulaki2013, Meiklejohn2013, Haslhofer2016, jourdan2018, kappos2022}.
+All these methods will not be the focus of this work and therefore not discussed.
+As suggested by Nakamoto in the Bitcoin whitepaper, most Bitcoin wallet implementations use a new key pair for each transaction to keep them from being linked to a common owner.
+\newline
+In contrast to the UTXO-model, native transactions in account-based blockchains can only move funds between a single sender and receiver, and the ``change``remains in the sender account.
 Subsequent transactions necessarily use the same address again.
 The account-based model essentially relies on address reuse on the protocol level.
-(Citation)
-
-\textbf{Account-model clustering heuristics}\\
-\cite{FV:17} was the first to introduce clustering heuristics for account-based blockchains.
+\citep{Beres2020} \newline
+% Make an assumption that people only use a small set of addressesyy
+%\textbf{Account-model clustering heuristics}
+Clustering heuristics for account-based blockchains were first introduced by \cite{FV:17}.
 He proposed and applied heuristics that exploit patterns related to deposit addresses, multiple participation in airdrops, and token authorization mechanisms.
 \newline
-\cite{Beres2020} argue that Victor’s heuristics, while powerful, assume participation in certain on-chain events and therefore propose more universally applicable methods.
-Their technique utilizes graph representation learning, a subset of machine learning interpreting transactions or token transfers as network graphs, with addresses as nodes and transactions or token transfers as edges.
-They further contribute to the field by proposing time-of-day activity and transaction fee-based user profiling techniques.
-Using ENS address pairs as ground truth, they test the methods rigorously and apply their findings to significantly reduce the privacy guarantees of Tornado Cash.
-They also provide a comprehensive overview and comparison of different node embedding algorithms.
+\cite{Beres2020} propose more universally applicable methods, as they argue that Victor’s heuristics, while powerful, assume participation in certain on-chain events.
+Their technique interprets transactions or token transfers as network graphs, with addresses as nodes and asset transfers as edges.
+They quantitavely compare graph-representation learning algorithms (a subset of machine learning) and propose further user profiling techniques based on time-of-day activity and transaction fees.
+Using ENS address pairs as ground truth (quasi-identifiers), the authors rigorously test their methods and apply their findings to significantly reduce the privacy guarantees of Tornado Cash.
 \newline
-\cite{wu2022tutela} extend on one of \cite{Beres2020} node embedding algorithms and apply it at scale.
-Further, they propose five clustering heuristics in the context of Tornado Cash.
-They build an application built on those heuristics to report the true anonymity of an Ethereum address.
-All methods will be discussed in greater detail in Section 3.
-Broadening the scope to entity identification, \cite{victorlüders2019} undertook an analysis of the top Ethereum-ERC20 token networks from a graph perspective.
-Similarly, \cite{casalebrunet2021} extend the analysis to various NFT (ERC721) ecosystems.
-Both find ...
-Payette schwager propose a segmentation of Ethereum address space into four distinct behaviour groups based on a broad range of address features (k-means).
+\cite{wu2022tutela} extend on one of \cite{Beres2020} graph representation learning (node-embedding) algorithms and apply it at scale.
+Further, they also propose a set of new clustering heuristics targeting Tornado Cash, showing that careless user behavior can still reveal identity.
+They build an application built on those heuristics to measure the anonymity of an Ethereum address.
+\newline
+All of the methods mentioned will be discussed in greater detail in Section 3. \newline
+Broadening the scope of entity identification, \cite{victorlüders2019} analyzed the top Ethereum ERC-20 token networks from a graph perspective.
+Similarly, \cite{casalebrunet2021} apply a similar analysis to various non-fungible token (NFT) ecosystems.
+Both find similarities to interaction graphs in social networks (hub-and-spoke).
+\cite{Payette2017} propose a segmentation of Ethereum address space into four distinct behaviour groups sharing similar attributes using k-means clustering.
 
-Instead of on-chain data, \cite{yu2023} propose a new correlation method by utilizing nodes as entities, exploiting network information.
-This approach comes with a whole new set of limitations and problems, but one can possibly avoid the impact of privacy-enhancing technologies.
-This approach may be interesting once privacy-enhancing techniques are more widely used.
+\cite{yu2023} propose a novel approach for correlation analysis by exploiting network information, rather than treating users as entities and analyzing on-chain data.
+Although this approach has the potential to avoid the impact of privacy-enhancing technologies, it introduces a new set of limitations and problems.
+Thus, this approach may be of great interest for further research, particularly when privacy-enhancing techniques become more widely used.
 
@@
 Transactions can thought of as large graphs of inputs and outputs and most wallet implementation use a new Bitcoin address/public key for each transaction.
+%In addition, the authors provide a comprehensive overview and comparison of various node embedding algorithms.
 
@@
 To achieve this, we adapt and extend existing methods to our specific situation/setting.
-
 Propose own heuristics approaches for detecting address clusters.
@@
 
-\textbf{Structure of the paper}\\
 The remainder of this paper is structured as follows: In Section 2, we provide a brief overview of the key concepts (basics, necessary for understanding the setup), including Ethereum accounts and the EVM, tokens, Decentraland and privacy-enhancing protocols.
@@
 
-\textbf{Ethereum, Polygon, EVM}\\
+Ethereum Mainnet and Polygon PoS are both account-model blockchains and use the same execution logic, the Ethereum Virtual machine.
 
-\textbf{Transactions, Transfer Events}\\
+- Polygon PoS is a so-called sidechain, closely associated with Ethereum mainnet and used for scaling
+
+%\textbf{Ethereum, Polygon, EVM}\\
+
+\textbf{Transactions and Transfer Events}\\
 
@@
 
-\textbf{Metaverse, Decentraland} \\
+\textbf{Metaverse and Decentraland} \\
+- Much of the Decentraland infrastructure has been deployed on Ethereum Mainnet
 
-\textbf{Privacy-enhancing protocols, mixing, Tornado} \\
+\textbf{Privacy-enhancing protocols} \\
 
@@
 
-The initial dataset contained 473,927 unique Web3 addresses.
-As we are only interested in clustering methods leveraging on-chain transaction or token transfer data, we omit addresses that were not recorded on either Ethereum or Polygon.
-This was achieved using data/information from Blockscan\footnote{\url{https://blockscan.com/}}.
-In total, 59,651 addresses were recorded on Ethereum, 129,988 addresses on Polygon and 52,095 on both networks simultanously.
-Therefore, the remaining address set comprises 137,544 addresses.
-Figure 1 visualizes the subsets in a VENN diagram.
-We used these addresses to gather/collect transaction and token transfer receipts from Ethereum Mainnet and Polygon PoS.
-Ethereum or Polygon data can be accessed directly through a node or an application programming interface (API) provider such as Infura or Etherscan.
-The absence of account indexing in Ethereum or Polygon makes queries of the type "Retrieve all past transactions and token transfers of address \texttt{0xABC}" challenging, as one would have to scan through every block and every token transfer event emitted by a specified set of token contracts.
+The original dataset comprised 473,927 distinct (Web3) addresses.
+As we only focus on clustering methods using on-chain transaction or token transfer data, we exclude addresses that have not been recorded on either Ethereum or Polygon.
+To accomplish this, we used data from Blockscan\footnote{\url{https://blockscan.com/}}.
+Overall, 59,651 addresses were recorded on Ethereum, 129,988 on Polygon, with 52,095 addresses appearing on both networks simultaneously.
+The set of remaining addresses consists of 137,544 addresses.
+Subsets are visualized in a Venn diagram in Figure 1.
+These addresses were used to collect transactions and token transfer events from Ethereum Mainnet and Polygon PoS.
+Ethereum or Polygon data can be accessed directly through a node or an application programming interface (API) provider like Infura or Etherscan.
+The absence of account indexing in Ethereum or Polygon poses a challenge for retrieving all past transactions and token transfers of a specific address, as it requires scanning through all blocks and token transfer events emitted by designated token contracts.
 Fortunately, Etherscan offers/provides an API Endpoint Module for ``Accounts`` that facilitates the retrieval of transactions and token transfer events for a given address.
-Using our network specific address subsets, we were able to significantly reduce the amount of API calls.
-
-We gathered all transactions and token transfer data of the addresses until block 17,670,000 on Ethereum (July 11, 2023) and block 44,990,000 on Polygon (July 12, 2023).
-The results were stored in comma-separated value (CSV) files and loaded into a MongoDB database\footnote{\url{https://www.mongodb.com/}}.
+By using our network-specific address subsets, we were able to significantly decrease the number of required API calls.
+We gathered all transaction and token transfer data of the addresses up until block 17,670,000 on Ethereum (July 11, 2023) and block 44,990,000 on Polygon (July 12, 2023).
+The output was saved in comma-separated value (CSV) files and imported into a MongoDB database\footnote{\url{https://www.mongodb.com/}}.
 

### 2023-08-06 paper.tex
Update paper

@@
 
-Public permissionless blockchains such as Bitcoin \citep{nakamotoBitcoin2008} and Ethereum \citep{buterin2014ethereum} allow users/individuals to participate with multiple pseudonymous addresses.
+Public permissionless blockchains such as Bitcoin \citep{nakamotoBitcoin2008} and Ethereum \citep{buterin2014ethereum} allow users %individuals
+ to participate with multiple pseudonymous addresses.
 The creation of these addresses is virtually cost free.
@@
 \newline
-On one hand, identifying the addresses that belong to the same real-world entity is beneficial as it allows better evaluation of network properties with respect to usage, distribution of wealth and detecting fraudulent activities \citep{FV:17}.
+On one hand, identifying the addresses that belong to the same real-world entity is beneficial.
+According to \cite{FV:17} it allows better evaluation of network properties with respect to usage, distribution of wealth and detecting fraudulent activities.
 For instance, if a user distributes their voting power across various addresses, they might manipulate an on-chain voting process that seems fair at the outset.
@@
 Nonetheless, these protocols are not yet widely adopted and careless user behaviour can undermine the privacy guarantees they offer. \newline
+%As such/In conclusion
 The topic of privacy, or lack thereof, will remain significant for future blockchain development and research.
@@
 The account-based model essentially relies on address reuse on the protocol level.
+Therefore, privacy guarantees should be lower and most users likely use only a small number of addresses.
 \citep{Beres2020} \newline
@@
 All of the methods mentioned will be discussed in greater detail in Section 3. \newline
-Broadening the scope of entity identification, \cite{victorlüders2019} analyzed the top Ethereum ERC-20 token networks from a graph perspective.
+Broadening the scope of entity identification, \cite{victorlüders2019} analyzed the largest Ethereum ERC-20 token networks from a graph perspective.
 Similarly, \cite{casalebrunet2021} apply a similar analysis to various non-fungible token (NFT) ecosystems.
 Both find similarities to interaction graphs in social networks (hub-and-spoke).
-\cite{Payette2017} propose a segmentation of Ethereum address space into four distinct behaviour groups sharing similar attributes using k-means clustering.
+Further, \cite{Payette2017} propose a segmentation of Ethereum address space into four distinct behaviour groups sharing similar attributes using k-means clustering.
 
@@
 
-%network level/off-chain data ->
-%transaction level/ on-chain data ->
-%In the UTXO model, each transaction has to reference an output from a previous transaction.
-When spending a Bitcoin, a user creates a UTXO.
-Each UTXO incorporates a spending condition, which can only be fulfilled by the .
-Transactions can thought of as large graphs of inputs and outputs and most wallet implementation use a new Bitcoin address/public key for each transaction.
-%In addition, the authors provide a comprehensive overview and comparison of various node embedding algorithms.
-
 \textbf{Our contribution}\\
-In this work, we perform entity identification/address clustering on an address set containing 473,927 addresses. 
-These addresses were gathered in a separate project by collecting avatar activity snapshots over a 8 month time frame spanning from July, 2022 to April, 2023.
-Due to the blockchain-based architecture of Decentraland, each avatar contains information about a users' Web3 address.
-
-We test the applicability of existing heuristics for our case and evaluate their success in detecting (given there is a ground truth).
-We estimate how many real-world entities are represented by these addresses.
-To achieve this, we adapt and extend existing methods to our specific situation/setting.
-Propose own heuristics approaches for detecting address clusters.
-
-%We apply several existing clustering heuristics in order to cluster a specific set containing 400k addresses.
+Due to Decentraland's blockchain-based architecture, each avatar contains information about a user's Web3 address. 
+To obtain these addresses, a separate project collected snapshots of avatar activity over an ten-month period from July 2022 to April 2023. 
+In this work, we perform entity identification on this address set containing 473,927 addresses. 
+The applicability of existing heuristics is tested, and if feasible, their efficacy in detecting entities using multiple addresses is evaluated. 
+The objective is to estimate the number of real-world entities that are represented by these addresses.
+Our focus is on clustering addresses within this set alone, while disregarding possible clusters outside of it that were not active in Decentraland during the given timeframe.
+Furthermore, we introduce our own heuristics for identifying address clusters and evaluate their suitability for implementation in other contexts.
 %Anwenden/discuss and evaluate existing heuristics to my specific address set.
@@
 In Section 3, we describe our data collection methodology and the data preparation.
-Section 4  describes and different clustering heuristics in detail.
+Section 4  describes different clustering heuristics in detail.
 Section 5 applies the clustering heuristics from 4.
@@
 
-The transaction data fields contain the transaction hash, from and to address, the timestamp in seconds from UNIX epoch, a nonce, value, input (calldata), gasused, gasprice, functionname (from Etherscan), chainname.
+The transaction data fields contain the transaction hash, from and to address, the timestamp in seconds from the UNIX epoch, a nonce, value, input (often reffered to as calldata), the amount of gas used in the transaction, the specified gas price, the name of the function called (added by Etherscan) and the name of the blockchain.
 Token transfer receipts include the transactions hash, timestamp, from and to address, nonce, gas price, the amount of gas used, chain information, the token contract address and name, tokenType, and token standard specific fields: value, tokenDecimal for ERC-20, tokenID for ERC-721, and value/tokenID for ERC-1155.

### 2023-08-07 paper.tex
Update paper

@@
 
-%However, they are not widely used even cannot guarantee perfect privacy (factors: size of anonymity set, usage /user behaviour of protocol, privacy guarantees depend on other users).
 %The most prominent/widely used non-custodial mixer is Tornado cash (Schär, Tutela).
-%This reaction has, in turn, sparked the development of other clustering heuristics exploiting user behavior interacting with privacy-enhancing protocols.
+%If someone obtains information that allows them to link a blockchain address to an entity, they may effectively observe that entity’s entire transaction history and associated activity.
+Even if the entity uses multiple addresses, any link between these addresses may expose the fact that they belong to the same person.
 
 \textbf{Related work}\\
-Previous work in this field can be broadly distinguished between heuristics developed for the unspent transaction output (UTXO) model (e.g Bitcoin, ZCash) and the account-based model (e.g.
-Ethereum, Polygon).
+Previous work in this field can be broadly distinguished between heuristics developed for the unspent transaction output (UTXO) model (e.g, Bitcoin and ZCash) and the account-based model (e.g., Ethereum, Polygon).
 While both models share the concept of addresses, the notion of accounts is not present in UTXO-based blockchains.
 The way in which transactions are processed is fundamentally different, and therefore, clustering heuristics are not applicable to both paradigms.
-%\textbf{UTXO-model clustering heuristics} 
+
 A number of address clustering heuristics in the UTXO setup have been proposed for Bitcoin and derivatives \citep{Androulaki2013, Meiklejohn2013, Haslhofer2016, jourdan2018, kappos2022}.
@@
 \citep{Beres2020} \newline
-% Make an assumption that people only use a small set of addressesyy
-%\textbf{Account-model clustering heuristics}
+% Make an assumption that people only use a small set of addresses
 Clustering heuristics for account-based blockchains were first introduced by \cite{FV:17}.
@@
 They quantitavely compare graph-representation learning algorithms (a subset of machine learning) and propose further user profiling techniques based on time-of-day activity and transaction fees.
-Using ENS address pairs as ground truth (quasi-identifiers), the authors rigorously test their methods and apply their findings to significantly reduce the privacy guarantees of Tornado Cash.
+Using ENS address pairs as ground truth, the authors rigorously test their methods and apply their findings to significantly reduce the privacy guarantees of Tornado Cash.
 \newline
@@
 They build an application built on those heuristics to measure the anonymity of an Ethereum address.
+All of the methods mentioned will be discussed in greater detail in Section 3.
 \newline
-All of the methods mentioned will be discussed in greater detail in Section 3. \newline
-Broadening the scope of entity identification, \cite{victorlüders2019} analyzed the largest Ethereum ERC-20 token networks from a graph perspective.
+Broadening the scope of entity identification, \cite{victorlüders2019} study the largest Ethereum ERC-20 token networks from a graph perspective.
 Similarly, \cite{casalebrunet2021} apply a similar analysis to various non-fungible token (NFT) ecosystems.
-Both find similarities to interaction graphs in social networks (hub-and-spoke).
+Both find that many of the networks follow either a star or a hub-and-spoke pattern.
+These patterns are similar to interaction graphs in social networks.
 Further, \cite{Payette2017} propose a segmentation of Ethereum address space into four distinct behaviour groups sharing similar attributes using k-means clustering.
-
-\cite{yu2023} propose a novel approach for correlation analysis by exploiting network information, rather than treating users as entities and analyzing on-chain data.
+\newline
+Rather than treating users as entities and analyzing on-chain data, \cite{yu2023} propose a novel approach for correlation analysis by exploiting network information.
 Although this approach has the potential to avoid the impact of privacy-enhancing technologies, it introduces a new set of limitations and problems.
@@
 \textbf{Our contribution}\\
+In this work, we perform entity identification on an address set containing 473,927 addresses.
+To obtain these addresses, a separate project collected snapshots of avatar activity in Decentraland over an ten-month period from July 2022 to April 2023.
 Due to Decentraland's blockchain-based architecture, each avatar contains information about a user's Web3 address.
-To obtain these addresses, a separate project collected snapshots of avatar activity over an ten-month period from July 2022 to April 2023. 
-In this work, we perform entity identification on this address set containing 473,927 addresses. 
-The applicability of existing heuristics is tested, and if feasible, their efficacy in detecting entities using multiple addresses is evaluated. 
-The objective is to estimate the number of real-world entities that are represented by these addresses.
-Our focus is on clustering addresses within this set alone, while disregarding possible clusters outside of it that were not active in Decentraland during the given timeframe.
+We test the applicability of existing heuristics, and if feasible, their efficacy (in detecting entities using multiple addresses) is evaluated.
+The main objective is to estimate the number of real-world entities that these addresses represent.
+The clustering of addresses is limited to this set only, without considering any (clusters for) addresses that were not registered/active in Decentraland during the given time frame.
 Furthermore, we introduce our own heuristics for identifying address clusters and evaluate their suitability for implementation in other contexts.
@@
 %Anpassen, erweitern
-%Eigene, spezifische Heuristiken ausdenken
 
-The remainder of this paper is structured as follows: In Section 2, we provide a brief overview of the key concepts (basics, necessary for understanding the setup), including Ethereum accounts and the EVM, tokens, Decentraland and privacy-enhancing protocols.
-In Section 3, we describe our data collection methodology and the data preparation.
-Section 4  describes different clustering heuristics in detail.
+The remainder of this paper is structured as follows: In Section 2, we provide a brief overview of the basic concepts necessary to understand the setup.
+The include Ethereum accounts and the EVM, tokens, Decentraland, and privacy-enhancing protocols.
+Section 3 describes our methodology for data collection and preparation.
+The fourth section provides a detailed explanation of various clustering heuristics.
 Section 5 applies the clustering heuristics from 4.
-Finally we discuss the results of our analysis and summarize our findings in Sections 5 and 6.
-
-% Motivation \& Relevance of the topic \\
-% Transaction data publicly available
-% Not really good to hide illicit business acitivities.
-% First, this was exploited in Bitcoin and Bitcoins UTXO model
-% Recently also account-based
-%Literarure Review: Still nascent field, First start with bitcoin/UTXO based, go over to account-based: Victor, Beres et al., Tutela \\
+The fifth section applies the clustering heuristics described in section 4, after which we discuss the results of our analysis and summarize our findings in sections 5 and 6.
 
@@
 For EOAs, this address is based on the last 20 bytes of the Keccak-256 hash of the ECDSA public key.
-For contract accounts, it is defined as the last 20 bytes of the Keccak-256 hash of the RLP encoding of the sender address and account nonce.
-\citep{GW:14} \newline
-In addition, \cite{eip1014} introduces a new contract creation mechanism allowing for more predictable contract addresses.%EIP-1014
+For contract accounts, it is usually the last 20 bytes of the Keccak-256 hash of the RLP encoding of the sender address and account nonce.
+\citep{GW:14}
 
-Ethereum Mainnet and Polygon PoS are both account-model blockchains and use the same execution logic, the Ethereum Virtual machine.
-
-- Polygon PoS is a so-called sidechain, closely associated with Ethereum mainnet and used for scaling
-
-%\textbf{Ethereum, Polygon, EVM}\\
-
-\textbf{Transactions and Transfer Events}\\
+\textbf{Ethereum, Polygon and the EVM}\\
+Ethereum and Polygon are both smart contract based account-model blockchains. They share the same execution logic - the Ethereum Virtual machine (EVM).
+The EVM provides a standardized framework for contract execution, ensuring that smart contracts produce deterministic results across all nodes in the network \citep{GW:14}.
+The EVM is independent of the underlying blockchain protocol.
+This allows other blockchain implementations to adopt this standardized framework for contract execution.\newline
+Polygon is a so-called sidechain and aims to address the scalability limitations of Ethereum.
+The adoption of the EVM means that both blockchains share the same user address schemes.
+It further enables developers to deploy and execute Ethereum-based smart contracts on the Polygon network with minimal changes.
+\citep{matic_whitepaper}
+%A high-level programming language is typically used to write smart contracts, and a compiler to convert them into bytecode \citep{mastering_ethereum}.
+Solidity is currently the dominant smart contract language.
+%Polygon PoS is a so-called sidechain, closely associated with Ethereum mainnet and used for scaling.
+%Ethereum Mainnet is the chain on which much of the Decentraland infrastructure has been deployed.
+%In addition, \cite{eip1014} introduces a new contract creation mechanism allowing for more predictable contract addresses.%EIP-1014
+%This allows developers to calculate the address of a contract before it is deployed.
 
 \textbf{Tokens and Token Standards}\\
-%shorter than in Seminar Thesis, comparable to Metaverse Retailing Paper
+According to \cite{roth2019tokenization}, \textit{tokens} as rivalrous, digital units of value that represent ownership of an asset or utility.
+Smart contracts are the primary method of creating tokens on EVM-based blockchains.
+In essence, a smart-contract-based token is a mapping of accounts with token balances and a set of functions defining how these balances can be changed.
+Any smart contract containing these elements can be interpreted as a token contract.
+\citep{roth2019tokenization} \newline
+Token standards specify basic interfaces that allow for interoperability between contracts.
+These standards do not prescribe an implementation but set minimum requirements without restricting the design beyond that.
+The most common token standards are ERC-20\footnote{https://eips.ethereum.org/EIPS/eip-20} for fungible tokens (NFTs), ERC-721\footnote{https://eips.ethereum.org/EIPS/eip-721} for non-fungible tokens or ERC-1155\footnote{https://eips.ethereum.org/EIPS/eip-1155} for semi-fungible tokens.\newline
+When a (blockchain) transaction completes, it produces a transaction receipt that contains log entries providing information about the actions that occurred during its execution.
+The standarization of tokens allows us to listen for ``transfer events``, which are emitted whenever an asset/token changes ownership.\cite{mastering_ethereum}
+These transfer events include the \textit{sender} and \textit{recipient} address, along with a \textit{token ID} and/or \textit{amount}.
 
-\textbf{Metaverse and Decentraland} \\
-- Much of the Decentraland infrastructure has been deployed on Ethereum Mainnet
+%Token standards specify basic interfaces that allow for interoperability between contracts.
+These standards do not prescribe an implementation but set minimum requirements without restricting the design beyond that.
+ERC-20 (fungible), ERC-721 (non-fungible) or ERC-1155 (semi-fungible) are the most widely used token standards.
+\newline
 
-\textbf{Privacy-enhancing protocols} \\
+%Solidity high-level objects called \textit{Events} construct these logs, which can be queried from a full node and are stored separately from the state.
+
+%Token Definition
+%Implemented in a standardized way
+%Three most popular token standards
+%Transfer emits Events/Logs/Transaction receipts, we can listen for Events
+
+\textbf{Decentraland} \\
+
+%The term metaverse refers to Neal Stephenson’s 1992 novel Snow Crash and describes an immersive virtual world that is populated by humans-as-avatars.
+Decentraland is the first large-scale blockchain-based virtual world.
+Users can own various digital assets, e.g., monetary units, land parcels, avatar apparel, or user names.
+The ownership of these assets is tracked and managed by smart contracts on Ethereum and Polygon.
+\citep{goldbergschaer}
+
+ Why interesting? Business perspective
+
+LAND / MANA
+
+%If you choose to experience Decentraland Explorer without a wallet, the information will only be locally stored: you will be able to walk around, customize your Avatar and chat with others in-world, but you won’t have the chance to receive daily rewards, participate in events or log in with a different device using the same Guest ID and Avatar.
+
+\textbf{Non-custodial crypto asset mixers} \\
+
+-> intuition of how it works,  distinction between custodial and non-custodial, Tornado cash = SC based
+
+According to \cite{nadler2023tornado}, crypto-asset mixers are currently the most widely used approach to achieve privacy on public blockchains.
+On a high level, we can distinguish between two types of implementation.
+
+The simplest version is a custodial model.
+In this setup, users send their assets to a centralized service provider operating the pool.
+In return, the provider sends back the assets to a privately relayed recipient address.
+This approach is fully trust-based because the service provider has complete control over the assets and access to the identifying data.
+
+, where a centralized service provider operates the mixing service. Users send their funds to the mixing service’s public deposit address and specify a recipient address over a private channel.
+
+In contrast to that, non-custodial crypto asset mixers do not require trust.
+Instead, they rely on cryptographic schemes that allow anyone to prove and independently verify the validity of a withdrawal without disclosing the link to a specific deposit.
+
+Moreover, the user does not have to share the identifying information with anyone and there is no liquidity risk, since the funds are locked and cannot be used in any other way.
+As such, non-custodial mixers can be created as an immutable and independent infrastructure, where no centralized entity can unilaterally control, alter, or delete the information.
+
+Various entities deposit the same amount of a specific crypto asset to a mixer address.
+The mixer acts as a pool.
+Anyone who has contributed to the pool may then generate a new address and withdraw their funds without revealing the link between the depositor and withdrawal addresses.
+Third parties can still observe the addresses that have deposited to and withdrawn from the pool, but given a large enough anonymity set, those third parties cannot link a specific depositor address to a specific withdrawal address.
+
+The best known smart-contract based non-custodial mixer is Tornado Cash.
+
+%Crypto asset mixers can be implemented at various levels of technological sophistication.
 

### 2023-08-07 paper.tex
Update paper

@@
 On a high level, we can distinguish between two types of implementation.
-
 The simplest version is a custodial model.
@@
 
-, where a centralized service provider operates the mixing service. Users send their funds to the mixing service’s public deposit address and specify a recipient address over a private channel.
+In contrast to that, non-custodial crypto asset mixers replace the trusted mixing party with a publicly verifiable (transparent) smart contract.
+They rely on cryptographic schemes that allow anyone to prove and independently verify the validity of a withdrawal without disclosing the link to a specific deposit.
+This has the advantage that users do not have to share the identifying information with anyone and there is no liquidity risk since the funds are locked.
 
-In contrast to that, non-custodial crypto asset mixers do not require trust.
-Instead, they rely on cryptographic schemes that allow anyone to prove and independently verify the validity of a withdrawal without disclosing the link to a specific deposit.
-
-Moreover, the user does not have to share the identifying information with anyone and there is no liquidity risk, since the funds are locked and cannot be used in any other way.
-As such, non-custodial mixers can be created as an immutable and independent infrastructure, where no centralized entity can unilaterally control, alter, or delete the information.
+Brief explanation of how it works:
 
@@
 Third parties can still observe the addresses that have deposited to and withdrawn from the pool, but given a large enough anonymity set, those third parties cannot link a specific depositor address to a specific withdrawal address.
+
+Moreover, the user does not have to share the identifying information with anyone and there is no liquidity risk, since the funds are locked and cannot be used in any other way.
+As such, non-custodial mixers can be created as an immutable and independent infrastructure, where no centralized entity can unilaterally control, alter, or delete the information.
 

### 2023-08-07 paper.tex
Update non-custodial mixer section, Add info for heuristics

@@
 The most common token standards are ERC-20\footnote{https://eips.ethereum.org/EIPS/eip-20} for fungible tokens (NFTs), ERC-721\footnote{https://eips.ethereum.org/EIPS/eip-721} for non-fungible tokens or ERC-1155\footnote{https://eips.ethereum.org/EIPS/eip-1155} for semi-fungible tokens.\newline
-When a (blockchain) transaction completes, it produces a transaction receipt that contains log entries providing information about the actions that occurred during its execution.
-The standarization of tokens allows us to listen for ``transfer events``, which are emitted whenever an asset/token changes ownership.\cite{mastering_ethereum}
+When a (blockchain) transaction completes, it produces a transaction receipt that contains log entries providing information about the actions that occurred during its execution \citep{mastering_ethereum}.
+The standarization of tokens allows us to listen for ``transfer events``, which are emitted whenever an asset/token changes ownership.
 These transfer events include the \textit{sender} and \textit{recipient} address, along with a \textit{token ID} and/or \textit{amount}.
@@
 
-\textbf{Non-custodial crypto asset mixers} \\
+\textbf{Non-custodial crypto asset mixers and Tornado Cash} \\
+%intuition of how it works,  distinction between custodial and non-custodial, Tornado cash = SC based
+According to \cite{nadler2023tornado}, crypto-asset mixers are currently the most widely used approach to achieve privacy on public blockchains.
+At a high level, we can distinguish between custodial and non-custodial crypto-asset mixers.
+\newline
+In the custodial setup, users send their assets to a centralized service provider's public deposit address.
+In return, the provider sends the assets back to a privately relayed recipient address.
+This approach is fully trust-based, as the service provider has complete control over the assets and access to the identifying data.
+\newline
+In contrast, non-custodial crypto asset mixers (e.g., Tornado Cash) replace the trusted mixing party with a publicly verifiable smart contract.
+They rely on cryptographic schemes that allow anyone to prove and independently verify the validity of a withdrawal without disclosing the link to a specific deposit.
+This has the advantage that users do not have to share the identifying information with anyone and there is no liquidity risk as the funds are locked.
+\citep{nadler2023tornado} \newline
+In a nutshell, the mixer works in the following way: Various entities deposit the same amount of a specific crpyto asset to a mixer address acting as a pool.
+Anyone who has contributed to the pool may then generate a new address and withdraw their funds without revealing the link between the deposit and withdrawal addresses.
+This is achieved using zK-SNARKS.
+Each depositor inserts a hash value in a Merkle-tree.
+At the time of withdrawal, each legitimate withdrawer can prove unlinkably with a zero-knowledge proof that they know the pre-image of a previously inserted hash leaf in the Merkle-tree.
+%Subsequently, users can withdraw their asset from the mixer whenever they consider that the size of the anonymity set is satisfactory.
+ For a more detailed description of how Tornado Cash works, see \cite{nadler2023tornado} or \cite{Beres2020}.
+For a mathematical discussion of ZKSNARK, please refer to Petkus (2019), Thaler (2022) or Berentsen et al.
+(2022).
+\newline
+In the context of this work, it is sufficient to know that third parties can still observe the addresses that have deposited to and withdrawn from the pool.
+The number of addresses that have deposited in a particular pool is defined as the \textit{anonymity set}.
+Typically, a larger anonymity set will provide a higher level of privacy, as a larger number of deposit addresses can be associated with a given withdrawal address.
+\newline
+In theory, if the anonymity set is large enough, third parties will not be able to link a specific depositor address to a specific withdrawal address.
+However, this is not always the case.
+For example, some users withdraw from the pool with the same address as they deposited.
+According to \cite{nadler2023tornado}, careless use of the protocol, testing transactions or external incentive mechanisms might be reasons for this behaviour.
+\newline
+Furthermore, \cite{Beres2020} and \cite{wu2022tutela} have proposed approaches to de-anonymize Tornado cash transactions using various clustering heuristics.
+These methods are discussed in more detail in the next section.
+% making use of address re-use, transaction activity, transaction cost choice, or more complex transaction graph and network analyses.
 
--> intuition of how it works,  distinction between custodial and non-custodial, Tornado cash = SC based
-
-According to \cite{nadler2023tornado}, crypto-asset mixers are currently the most widely used approach to achieve privacy on public blockchains.
-On a high level, we can distinguish between two types of implementation.
-The simplest version is a custodial model.
-In this setup, users send their assets to a centralized service provider operating the pool.
-In return, the provider sends back the assets to a privately relayed recipient address.
-This approach is fully trust-based because the service provider has complete control over the assets and access to the identifying data.
-
-In contrast to that, non-custodial crypto asset mixers replace the trusted mixing party with a publicly verifiable (transparent) smart contract.
-They rely on cryptographic schemes that allow anyone to prove and independently verify the validity of a withdrawal without disclosing the link to a specific deposit.
-This has the advantage that users do not have to share the identifying information with anyone and there is no liquidity risk since the funds are locked.
-
-Brief explanation of how it works:
-
-Various entities deposit the same amount of a specific crypto asset to a mixer address.
-The mixer acts as a pool.
-Anyone who has contributed to the pool may then generate a new address and withdraw their funds without revealing the link between the depositor and withdrawal addresses.
-Third parties can still observe the addresses that have deposited to and withdrawn from the pool, but given a large enough anonymity set, those third parties cannot link a specific depositor address to a specific withdrawal address.
-
-Moreover, the user does not have to share the identifying information with anyone and there is no liquidity risk, since the funds are locked and cannot be used in any other way.
-As such, non-custodial mixers can be created as an immutable and independent infrastructure, where no centralized entity can unilaterally control, alter, or delete the information.
-
-The best known smart-contract based non-custodial mixer is Tornado Cash.
-
-%Crypto asset mixers can be implemented at various levels of technological sophistication.
+%The best known smart-contract based non-custodial mixer is Tornado Cash.
 
@@
 
-Self-authorization \\
-Deposit address reuse \\
-Airdrop multi participation \\
+\textbf{Self-authorization} \newline
+The \texttt{approve} function required in all three token standards allows another address to spend tokens on behalf of the actual owners.
+This functionality is mainly used in connection with smart contracts, but can also be applied for regular EOAs.
+Users could approve another address they own, a reason for this might be risk distribution over several addresses with partial accessibility.
+\citep{FV:17}
 
-Graph-based network analysis / Transaction Graph Analysis
+\textbf{Deposit address reuse} \newline
+This heuristic exploits the common practice of crypto exchanges creating so-called deposit addresses for each user, which forward funds to a main address.
+Multiple addresses that send funds to the same deposit address are highly likely controlled by the same entity.
+\citep{FV:17}
+
+\textbf{Airdrop multi participation} \newline
+Airdrops are popular token distribution mechanisms, and recipients are mostly chosen based on past protocol activity.
+A famous example is Uniswap's UNI airdrop, where each address that interacted with the protocol received a fixed amount of UNI tokens\footnote{\url{https://blog.uniswap.org/uni}}.
+These distribution mechanisms are often not Sybil-resistant, leading to people creating multiple addresses in anticipation of an airdrop.
+However, managing the tokens on all of these addresses is impractical, which is why they are often aggregated into one address.
+\citep{FV:17}
+
+\textbf{Graph-based network analysis/Transaction Graph Analysis}\newline
 Token networks -> Victor, Casale Brunet
@@
 Diff2Vec, Role2Vec, DeepWalk \\
-Time-of-day transaction activity \\
+
+\textbf{Time-of-day transaction activity} \\
 Transaction timestamps reveal the daily activity patterns of the account owner -> example
@@
 We chose 50 bins (from beres)
-Gas price distribution \\
+
+\textbf{Gas price distribution} \\
 Gas price definition, often set by the wallet software (slow, medium, fast), given the changes in traffic volume we normalice the gas price bxy the daily network average in our dataset.

### 2023-08-08 paper.tex
Update paper

@@
 \begin{center}
-%\includegraphics[width=4cm]{../figures/logo_cif.png}
+\includegraphics[width=4cm]{../figures/logo_cif.png}
 \end{center}
@@
 	\hspace{-10cm}
-	%\includegraphics[width=3cm]{../figures/signature.jpeg}
+	\includegraphics[width=3cm]{../figures/signature.jpeg}
 \end{figure}
@@
 Researchers try to cluster addresses controlled by the same user by analyzing on-chain data and detecting usage patterns.
-The majority of these methods are heuristic which often makes them difficult to evaluate due to the absence of any ground truth.
-\newline
-On one hand, identifying the addresses that belong to the same real-world entity is beneficial.
+The frequent lack of ground truth makes it difficult to evaluate different clustering methods.
+As a result, most methods are heuristic.
+%The majority of these methods are heuristic which often makes them difficult to evaluate due to the absence of any ground truth.
+\newline On one hand, identifying the addresses that belong to the same real-world entity is beneficial.
 According to \cite{FV:17} it allows better evaluation of network properties with respect to usage, distribution of wealth and detecting fraudulent activities.
@@
 \textbf{Related work}\\
-Previous work in this field can be broadly distinguished between heuristics developed for the unspent transaction output (UTXO) model (e.g, Bitcoin and ZCash) and the account-based model (e.g., Ethereum, Polygon).
+Previous work in this field can be broadly distinguished between methods%heuristics
+ developed for the unspent transaction output (UTXO) model (e.g, Bitcoin and ZCash) and the account-based model (e.g., Ethereum, Polygon).
 While both models share the concept of addresses, the notion of accounts is not present in UTXO-based blockchains.
@@
 All these methods will not be the focus of this work and therefore not discussed.
-As suggested by Nakamoto in the Bitcoin whitepaper, most Bitcoin wallet implementations use a new key pair for each transaction to keep them from being linked to a common owner.
+As suggested by \cite{nakamotoBitcoin2008} in the Bitcoin whitepaper, most Bitcoin wallet implementations use a new key pair for each transaction to keep them from being linked to a common owner.
 \newline
@@
 Subsequent transactions necessarily use the same address again.
-The account-based model essentially relies on address reuse on the protocol level.
+The account-based model essentially relies on address reuse on the protocol level \citep{Beres2020}.
 Therefore, privacy guarantees should be lower and most users likely use only a small number of addresses.
-\citep{Beres2020} \newline
+\newline
 % Make an assumption that people only use a small set of addresses
@@
 They quantitavely compare graph-representation learning algorithms (a subset of machine learning) and propose further user profiling techniques based on time-of-day activity and transaction fees.
-Using ENS address pairs as ground truth, the authors rigorously test their methods and apply their findings to significantly reduce the privacy guarantees of Tornado Cash.
+Using ENS address pairs as ground truth, the authors rigorously test their methods and apply their findings to significantly reduce the privacy guarantees of Tornado Cash, a non-custodial privacy-enhancing protocol on Ethereum.
 \newline
-\cite{wu2022tutela} extend on one of \cite{Beres2020} graph representation learning (node-embedding) algorithms and apply it at scale.
+\cite{wu2022tutela} extend on one of \cite{Beres2020} graph representation learning %node-embedding
+ algorithms and apply it at scale.
 Further, they also propose a set of new clustering heuristics targeting Tornado Cash,  showing that careless user behavior can still reveal identity.
@@
 Broadening the scope of entity identification, \cite{victorlüders2019} study the largest Ethereum ERC-20 token networks from a graph perspective.
-Similarly, \cite{casalebrunet2021} apply a similar analysis to various non-fungible token (NFT) ecosystems.
+Similarly, \cite{casalebrunet2021} apply network graph analysis to various non-fungible token (NFT) ecosystems.
 Both find that many of the networks follow either a star or a hub-and-spoke pattern.
-These patterns are similar to interaction graphs in social networks.
-Further, \cite{Payette2017} propose a segmentation of Ethereum address space into four distinct behaviour groups sharing similar attributes using k-means clustering.
+These patterns are common to interaction graphs in social networks.
+Further, \cite{Payette2017} propose a segmentation of the Ethereum address space into four distinct behaviour groups sharing similar attributes using k-means clustering.
 \newline
@@
 Due to Decentraland's blockchain-based architecture, each avatar contains information about a user's Web3 address.
-We test the applicability of existing heuristics, and if feasible, their efficacy (in detecting entities using multiple addresses) is evaluated.
-The main objective is to estimate the number of real-world entities that these addresses represent.
-The clustering of addresses is limited to this set only, without considering any (clusters for) addresses that were not registered/active in Decentraland during the given time frame.
+We test the applicability of existing heuristics, and if feasible, their efficacy in detecting entities using multiple addresses is evaluated.
+The main objective is to estimate the number of real-world entities that these addresses represent. The clustering of addresses is limited to this set only, without considering any %(clusters for)
+ addresses outside of it, e.g., that were not registered in Decentraland during the given time frame.
 Furthermore, we introduce our own heuristics for identifying address clusters and evaluate their suitability for implementation in other contexts.
@@
 Section 3 describes our methodology for data collection and preparation.
-The fourth section provides a detailed explanation of various clustering heuristics.
-Section 5 applies the clustering heuristics from 4.
-The fifth section applies the clustering heuristics described in section 4, after which we discuss the results of our analysis and summarize our findings in sections 5 and 6.
+The fourth section provides a detailed explanation of various clustering heuristics.The fifth section applies the clustering heuristics described in section 4, after which we discuss the results of our analysis and summarize our findings in sections 6 and 7.
 
@@
 \section{Preliminaries}
-
-\textbf{Contract Accounts and EOAs}\\
+% Introduce section
+\subsection{Contract Accounts and EOAs}
 Account-based blockchains usually distinguish between \textit{externally owned accounts} (EOAs) and \textit{contract accounts} (smart contracts).
@@
 
-\textbf{Ethereum, Polygon and the EVM}\\
+\subsection{Ethereum, Polygon and the EVM}
 Ethereum and Polygon are both smart contract based account-model blockchains. They share the same execution logic - the Ethereum Virtual machine (EVM).
@@
 
-\textbf{Tokens and Token Standards}\\
-According to \cite{roth2019tokenization}, \textit{tokens} as rivalrous, digital units of value that represent ownership of an asset or utility.
+\subsection{Tokens and Token Standards}
+\cite{roth2019tokenization} define \textit{tokens} as rivalrous, digital units of value that represent ownership of an asset or utility.
 Smart contracts are the primary method of creating tokens on EVM-based blockchains.
@@
 Token standards specify basic interfaces that allow for interoperability between contracts.
-These standards do not prescribe an implementation but set minimum requirements without restricting the design beyond that.
-The most common token standards are ERC-20\footnote{https://eips.ethereum.org/EIPS/eip-20} for fungible tokens (NFTs), ERC-721\footnote{https://eips.ethereum.org/EIPS/eip-721} for non-fungible tokens or ERC-1155\footnote{https://eips.ethereum.org/EIPS/eip-1155} for semi-fungible tokens.\newline
+These standards do not prescribe an implementation but set minimum requirements without restricting the design beyond that \citep{mastering_ethereum}.
+The most common token standards are ERC-20\footnote{https://eips.ethereum.org/EIPS/eip-20} for fungible tokens, ERC-721\footnote{https://eips.ethereum.org/EIPS/eip-721} for non-fungible tokens (NFTs) and ERC-1155\footnote{https://eips.ethereum.org/EIPS/eip-1155} for semi-fungible tokens.\newline
 When a (blockchain) transaction completes, it produces a transaction receipt that contains log entries providing information about the actions that occurred during its execution \citep{mastering_ethereum}.
-The standarization of tokens allows us to listen for ``transfer events``, which are emitted whenever an asset/token changes ownership.
+The standarization of tokens allows us to listen for ``transfer events``, which are emitted whenever an token changes ownership.
 These transfer events include the \textit{sender} and \textit{recipient} address, along with a \textit{token ID} and/or \textit{amount}.
@@
 
-\textbf{Decentraland} \\
+\subsection{Decentraland}
+\textit{Decentraland} is the first large-scale blockchain-based virtual world.
+It has attracted the attention of well-known companies like Tommy Hilfiger, Samsung, PepsiCo, Diesel, Adidas, and Netflix, who are actively engaged in it  \citep{metaverse-retailing2023}.\newline
+Decentraland is an ideal platform for empirical research for two main reasons.
+\textit{First}, its open architecture allows compiling snapshots of user activity, including the users' locations  within the metaverse.
+This was done by \cite{metaverse-retailing2023}, who captured snapshots of users/avatar locations over a period of 10 months.
+The addresses used in this paper are provided form this work.
+\textit{Second}, users who connect their Web3 account can own various digital assets, such as monetary units, land parcels, and avatar collectibles (e.g.
+wearables, emotes, and names).
+Smart contracts on Ethereum and Polygon track and manage the ownership of these assets \cite{goldbergschaer2023}.
+As a result, this allows us to analyze the entire transaction history and derive information about the avatars’/users' economic activity.
+\newline
+The Decentraland ecosystem has two main tokens.
+\textit{LAND}, an NFT compliant with ERC-721, manages the ownership of land parcels in Decentraland.
+\textit{MANA}, a fungible token compliant with ERC-20, is the in-world currency used to purchase digital goods and services.
+The majority of purchases and trades are settled in MANA.
+Furthermore, Decentraland %the foundation/DAO/developers
+operates/provides/hosts a virtual/smart-contract-based marketplace where its users may buy or exchange LAND or other in-game collectibles.
 
+%Owners of multiple adjacent land parcels can combine them into an ESTATE, which acts as a wrapper token for the land parcels.
 %The term metaverse refers to Neal Stephenson’s 1992 novel Snow Crash and describes an immersive virtual world that is populated by humans-as-avatars.
-Decentraland is the first large-scale blockchain-based virtual world.
-Users can own various digital assets, e.g., monetary units, land parcels, avatar apparel, or user names.
-The ownership of these assets is tracked and managed by smart contracts on Ethereum and Polygon.
-\citep{goldbergschaer}
+%Goods: in-world assets, such as avatar wearables, merchandise, or tickets, as well as tokenized vouchers that can be redeemed for real-world goods or services.
 
- Why interesting? Business perspective
-
-LAND / MANA
-
-%If you choose to experience Decentraland Explorer without a wallet, the information will only be locally stored: you will be able to walk around, customize your Avatar and chat with others in-world, but you won’t have the chance to receive daily rewards, participate in events or log in with a different device using the same Guest ID and Avatar.
-
-\textbf{Non-custodial crypto asset mixers and Tornado Cash} \\
+\subsection{Non-custodial crypto asset mixers}
 %intuition of how it works,  distinction between custodial and non-custodial, Tornado cash = SC based
@@
  For a more detailed description of how Tornado Cash works, see \cite{nadler2023tornado} or \cite{Beres2020}.
-For a mathematical discussion of ZKSNARK, please refer to Petkus (2019), Thaler (2022) or Berentsen et al.
+For a mathematical discussion of ZKSNARKs, please refer to Petkus (2019), Thaler (2022) or Berentsen et al.
 (2022).
@@
 The number of addresses that have deposited in a particular pool is defined as the \textit{anonymity set}.
-Typically, a larger anonymity set will provide a higher level of privacy, as a larger number of deposit addresses can be associated with a given withdrawal address.
+Typically, a larger anonymity set will provide a higher level of privacy, as a more deposit addresses can be associated with any given withdrawal address.
 \newline
@@
 \section{Data Collection and Preparation}
-
-The original dataset comprised 473,927 distinct (Web3) addresses.
-As we only focus on clustering methods using on-chain transaction or token transfer data, we exclude addresses that have not been recorded on either Ethereum or Polygon.
+% Introduction Satz - Ausgangslage 
+The starting point for our work was a dataset comprising 473,927 distinct (Web3) addresses. %The original dataset comprised 473,927 distinct (Web3) addresses.
+ As we focus on clustering methods using on-chain data, we exclude addresses that have not been recorded on either Ethereum or Polygon.
 To accomplish this, we used data from Blockscan\footnote{\url{https://blockscan.com/}}.
@@
 The set of remaining addresses consists of 137,544 addresses.
-Subsets are visualized in a Venn diagram in Figure 1.
-These addresses were used to collect transactions and token transfer events from Ethereum Mainnet and Polygon PoS.
+Subsets are visualized as a Venn diagram in \ref{fig:Venn}.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=0.6\textwidth]{../figures/venn_diagram.png}
+	\caption{Venn Diagram of address subsets}
+	\label{fig:Venn}
+\end{figure}
+
+\subsection{Transactions and Token Transfer Events}
+The address dataset was used to collect transaction and token transfer event data from Ethereum and Polygon.
 Ethereum or Polygon data can be accessed directly through a node or an application programming interface (API) provider like Infura or Etherscan.
 The absence of account indexing in Ethereum or Polygon poses a challenge for retrieving all past transactions and token transfers of a specific address, as it requires scanning through all blocks and token transfer events emitted by designated token contracts.
-Fortunately, Etherscan offers/provides an API Endpoint Module for ``Accounts`` that facilitates the retrieval of transactions and token transfer events for a given address.
+Fortunately, Etherscan offers an API Endpoint Module for ``Accounts`` that facilitates the retrieval of transactions and token transfer events for a given address.
 By using our network-specific address subsets, we were able to significantly decrease the number of required API calls.
-We gathered all transaction and token transfer data of the addresses up until block 17,670,000 on Ethereum (July 11, 2023) and block 44,990,000 on Polygon (July 12, 2023).
-The output was saved in comma-separated value (CSV) files and imported into a MongoDB database\footnote{\url{https://www.mongodb.com/}}.
+We gathered all transactions and token transfers up until block height \texttt{17,670,000} on Ethereum (July 11, 2023) and block \texttt{44,990,000} on Polygon (July 12, 2023).
+The output was saved in separate CSV files.
+We then imported this data into a MongoDB database\footnote{\url{https://www.mongodb.com/}}.
+In total, we collected 30,689,978 token transfers and 16,092,531 normal transactions. Figure X visualizes the number of daily transactions and token transfers for each chain. Can see activity.
 
-Statistics about data, how many transactions, how many transfers, size
-Transfer events = 30,689,978
-Transactions = 16,184,993, how many polygon/ethereum, table
+Transfer Events: 30,689,978
+Transfer Events Ethereum: 7,832,778
+Transfer Events Polygon: 22,857,200
 
-\begin{table}[h]
-\centering
-\begin{tabular}{lcc}
-\hline \hline
-  & Transactions & Transfers \\
- \hline
- Polygon & Cell 2 & Cell 3 \\
- Ethereum & Cell 5 & Cell 6 \\
- \hline
- Total & 16,184,993 & 30,689,978 \\
- \hline \hline
-\end{tabular}
-\caption{Size of raw data}
-\label{tab:data_size}
-\end{table}
+Statistics about data, how many transactions on Polygon, how many on Ethereum, how many transfers on Polygon, how many on Ethereum -> Show in Figure
 
-The transaction data fields contain the transaction hash, from and to address, the timestamp in seconds from the UNIX epoch, a nonce, value, input (often reffered to as calldata), the amount of gas used in the transaction, the specified gas price, the name of the function called (added by Etherscan) and the name of the blockchain.
-Token transfer receipts include the transactions hash, timestamp, from and to address, nonce, gas price, the amount of gas used, chain information, the token contract address and name, tokenType, and token standard specific fields: value, tokenDecimal for ERC-20, tokenID for ERC-721, and value/tokenID for ERC-1155.
+Transactions = 16,092,531
+Transactions Ethereum = 8,448,584
+Transactions Polygon = 7,643,947
+
+%\begin{table}[h]
+%\centering
+%\begin{tabular}{lcc}
+%\hline \hline
+%  & Transactions & Transfers \\
+% \hline
+% Polygon & Cell 2 & Cell 3 \\
+% Ethereum & Cell 5 & Cell 6 \\
+% \hline
+% Total & 16,184,993 & 30,689,978 \\
+% \hline \hline
+%\end{tabular}
+%\caption{Size of raw data}
+%\label{tab:data_size}
+%\end{table}
+
+Transaction hash, timestamp in seconds from the UNIX epoch, gas used in the transaction, specified gas price, nonce
+
+The transaction data fields contain the transaction hash, from and to address, the timestamp in seconds from the UNIX epoch, a nonce, value, input (often referred to as calldata), the amount of gas used in the transaction, the specified gas price, the name of the function called (added by Etherscan) and the name of the blockchain.
+
+Token transfer receipts include the transaction hash, UNIX timestamp, sender and recipient address, nonce, gas price, the amount of gas, chain information, the token contract address and name, tokenType, and token standard specific fields: value, tokenDecimal for ERC-20, tokenID for ERC-721, and value/tokenID for ERC-1155.
 
@@
 %Using Blockscan\footnote{\url{https://blockscan.com/}}, we were able to reduce the address set to addresses that were recorded on either Ethereum or Polygon.
+
+\subsection{ENS Names}
 
@@
 \section{Clustering Heuristics}
+In this section, we provide a overview of clustering heuristics in the context of account-based blockchains and on-chain data.
+We will give a detailed explanation of the intuition/rationale behind the heuristic, the workings and discuss the applicability for our case.
+In Section 5 we will then apply and, if possible, evaluate the heuristics deemed suited for us.
+
+%detailed explanation
 % Goal: explain each heuristic, categorize, and discuss applicability to our address set
 
-\textbf{Self-authorization} \newline
+\subsection{Self-authorization}
 The \texttt{approve} function required in all three token standards allows another address to spend tokens on behalf of the actual owners.
@@
 
-\textbf{Deposit address reuse} \newline
+\subsection{Deposit address reuse}
 This heuristic exploits the common practice of crypto exchanges creating so-called deposit addresses for each user, which forward funds to a main address.
@@
 
-\textbf{Airdrop multi participation} \newline
+\subsection{Airdrop multi participation}
 Airdrops are popular token distribution mechanisms, and recipients are mostly chosen based on past protocol activity.
@@
 
-\textbf{Graph-based network analysis/Transaction Graph Analysis}\newline
+\subsection{Graph-based network analysis}
 Token networks -> Victor, Casale Brunet
@@
 Applied 3 node embedding methods to this graph (Diff2Vec, Role2Vec and deep walk.
+\textbf{Node embeddings}
 
+Projects addresses to points in a low-dimensional vector space based on who it interacts with.
+In this vector space, adresses belonging to the same entity should be close together in Euclidian distance.
+
+Consider constructing an undirected graph from all Ethereum transactions where nodes are composed of distinct addresses, and an edge is placed between two nodes if there is a transaction between them.
+
+At this abstraction layer, we seek to learn a ``node embedding function``that projects a node to a d-dimensional vector representation.
+Importantly I want this embedding to capture semantic information about the node, such as which other addresses it frequently interact with.
+To do so, we leverage popular graph representation learning algorithms.
+(Grover and Leskovec, 2016; Rozemberczki and Sarkar, 2018).
+In particular, we focus on Diff2Vec, Role2Vec and
+
+Given an address, to find its cluster, we can search for the closest k vectors in Rd.
+In practice, we accomplish this efficiently using FAISS (Johnson et al., 2019).
+This will always return k addresses.
+
+Node embedding methods form a class of network representation learning methods that map graph nodes to vectors in a low-dimensional space.
+They are designed to represent vertices with similar neighborhood structure by vectors that are close in the vector space.
+Intuitively, addresses that interact with the same set of addresses in the Ethereum transaction graph should be close in the embedded space.
+Research in node embedding has been catalyzed by Word2Vec, an embedding method for natural language processing.
+... In this work, we use these techniques on the Ethereum transaction graph to link addresses owned by the same user.
+...
+The set of addresses used in interactions characterize a user.
+Users with multiple accounts might interact with the same addresses or services from most of the.
+Furthermore, they may unintentionally reveal their address clusters.
+Our deanonymization methods are conducted on a transaction graph with nodes as Ethereum addresses and edges as transactions.
+From the library of \cite
 Diff2Vec, Role2Vec, DeepWalk \\
+Transaction Graph Analysis
 
-\textbf{Time-of-day transaction activity} \\
+\subsection{Time-of-day transaction activity}
 Transaction timestamps reveal the daily activity patterns of the account owner -> example
@@
 
-\textbf{Gas price distribution} \\
+\subsection{Gas price distribution}
 Gas price definition, often set by the wallet software (slow, medium, fast), given the changes in traffic volume we normalice the gas price bxy the daily network average in our dataset.

### 2023-08-08 python/activity.py
Add python scripts for Venn and activity figures

@@ -1,0 +1,71 @@
+import seaborn as sns
+import pandas as pd
+import matplotlib.pyplot as plt
+
+
+# Get all transfers as a pandas dataframe except the '_id', 'userAddress' and 'isSet' column
+df_transfer = pd.read_csv('../data/raw_transfer_events.csv', usecols=lambda x: x not in ['_id', 'userAddress', 'isSet'])
+
+# Get all transactions as a pandas dataframe except the '_id' column
+df_transactions_eth = pd.read_csv('../data/raw_ethereum_transactions.csv', usecols=lambda x: x not in ['_id'])
+df_transactions_polygon = pd.read_csv('../data/raw_polygon_transactions.csv', usecols=lambda x: x not in ['_id'])
+df_tx = pd.concat([df_transactions_eth, df_transactions_polygon])
+
+# Drop duplicates
+print(df_transfer.shape[0])
+df_transfer = df_transfer.drop_duplicates()
+print(f'Total number of transfer events: {df_transfer.shape[0]}')
+# Count number of transfers per chain
+print(df_transfer.groupby('chainName').size().reset_index(name='count'))
+
+# Drop duplicates
+print(df_tx.shape[0])
+df_tx = df_tx.drop_duplicates()
+print(f'Total number of transactions: {df_tx.shape[0]}')
+# Count number of transactions per chain
+print(df_tx.groupby('chainName').size().reset_index(name='count'))
+
+# Convert timestamp to datetime
+df_transfer['timeStamp'] = pd.to_datetime(df_transfer['timeStamp'], unit='s')
+df_tx['timeStamp'] = pd.to_datetime(df_tx['timeStamp'], unit='s')
+
+# Get the number of transfers per day and chainName and create a new dataframe
+#df_transfer_grouped = df_transfer.groupby([pd.Grouper(key='timeStamp', freq='D'), 'chainName']).size().reset_index(name='count')
+df_transfer_grouped = df_transfer.groupby([pd.Grouper(key='timeStamp', freq='M'), 'chainName']).size().reset_index(name='count')
+df_transfer_grouped['type'] = 'transfer'
+
+# Get the number of transactions per month and chainName and create a new dataframe
+#df_tx_grouped = df_tx.groupby([pd.Grouper(key='timeStamp', freq='D'), 'chainName']).size().reset_index(name='count')
[…]

### 2023-08-08 python/venn-diagramm.py

@@ -1,0 +1,21 @@
+from matplotlib_venn import venn2
+import matplotlib.pyplot as plt
+
+# Data
+polygon_only = 83774
+ethereum_only = 7867
+both = 49950
+
+venn = venn2(subsets=(polygon_only, ethereum_only, both), set_labels=(None, None), set_colors=('#A5D7D2','#D20537'))
+
+
+ax = plt.gca()
+ax.text(-0.3, 0.3, 'Polygon PoS', fontsize=12, ha='center', va='center')
+ax.text(0.75, 0.3, 'Ethereum Mainnet', fontsize=12, ha='center', va='center')
+
+venn.get_label_by_id('10').set_position((-0.4, 0))
+venn.get_label_by_id('01').set_position((0.65, 0))
+venn.get_label_by_id('11').set_position((0.2, 0))
+
+plt.savefig('../figures/venn_diagram.png', dpi=500, bbox_inches='tight')
+plt.show()

### 2023-08-08 paper.tex
Add data-preparation info

@@
 By using our network-specific address subsets, we were able to significantly decrease the number of required API calls.
-We gathered all transactions and token transfers up until block height \texttt{17,670,000} on Ethereum (July 11, 2023) and block \texttt{44,990,000} on Polygon (July 12, 2023).
-The output was saved in separate CSV files.
-We then imported this data into a MongoDB database\footnote{\url{https://www.mongodb.com/}}.
-In total, we collected 30,689,978 token transfers and 16,092,531 normal transactions. Figure X visualizes the number of daily transactions and token transfers for each chain. Can see activity.
+We gathered all transactions and token transfers up until block number \texttt{17,670,000} on Ethereum (July 11, 2023) and block number \texttt{44,990,000} on Polygon (July 12, 2023).
+In total, we collected more than 30 million %30,689,978
+token transfers and more than 16 million %16,092,531
+ normal transactions. The output was stored in CSV files and later imported  into a MongoDB\footnote{\url{https://www.mongodb.com/}} database.
+
+The database contains separate collections for transactions and transfers.
+Both collections share fields including the transaction hash, timestamp in seconds from the UNIX epoch, the amount of gas used in the transaction, the gas price specified by the user and the nonce (for EOAs, the nonce corresponds to the number of transactions sent beginning from 0).
+
+The transaction data field includes a from and to address ('to' address either smart contract or EOA for simple transfers), a value field (native asset), the transaction's input (mostly referred to as calldata), the name of the function called (added by Etherscan, none if simple transfer of Ether or Matic).
+We added the chain Name to combine the data from both chains.
+
+Token transfer receipts include the transaction hash, UNIX timestamp, sender and recipient address, nonce, gas price, the amount of gas, chain information, the token contract address and name, tokenType, and token standard specific fields: value, tokenDecimal for ERC-20, tokenID for ERC-721, and value/tokenID for ERC-1155.
+
+\iffalse
+Transactions: hash, from, to, timestamp, nonce, value, gasprice, gasUsed, input, functionName, chainName
+Transfers: hash, from (sender), to (recipient), contractAddress (tokenContract address), value (amount, only for ERC20, ERC1155), nonce, tokenName, gas price, gas used, chainName, tokenType (token standard), token ID (only for ERC721/ERC1155), ((isSet, userAddress))
 
@@
 Transfer Events Polygon: 22,857,200
-
-Statistics about data, how many transactions on Polygon, how many on Ethereum, how many transfers on Polygon, how many on Ethereum -> Show in Figure
-
 Transactions = 16,092,531
@@
 
-%\begin{table}[h]
-%\centering
-%\begin{tabular}{lcc}
-%\hline \hline
-%  & Transactions & Transfers \\
-% \hline
-% Polygon & Cell 2 & Cell 3 \\
-% Ethereum & Cell 5 & Cell 6 \\
-% \hline
-% Total & 16,184,993 & 30,689,978 \\
-% \hline \hline
-%\end{tabular}
-%\caption{Size of raw data}
-%\label{tab:data_size}
-%\end{table}
+Most of the activity revolves around NFTs, especially on Polygon.
+Figure X visualizes the number of daily transactions and token transfers for each chain.
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=\textwidth]{../figures/transfers_tx_by_chain.png}
+	\caption{Monthly Transactions and Token Transfers by chain}
+	\label{fig:Data}
+\end{figure} 
+Transfer Events, adding Information (isInSet) \\
+Transactions \\
+Filtering, Intra-set transfers\\
+Data Structure, Fields \\
+We reduced this set to addresses that were active/recorded on either Ethereum or Polygon using Blockscan\footnote{\url{https://blockscan.com/}}. This reduced the address set from to X.
+Using Blockscan\footnote{\url{https://blockscan.com/}}, we were able to reduce the address set to addresses that were recorded on either Ethereum or Polygon.
+\fi
 
-Transaction hash, timestamp in seconds from the UNIX epoch, gas used in the transaction, specified gas price, nonce
+\subsection{Intra-set asset transfers}
+Our goal is to cluster addresses belonging to the same real-world entity that were recorded in Decentraland during this 9-month period. Therefore, we disregard addresses outside of this set.
 
-The transaction data fields contain the transaction hash, from and to address, the timestamp in seconds from the UNIX epoch, a nonce, value, input (often referred to as calldata), the amount of gas used in the transaction, the specified gas price, the name of the function called (added by Etherscan) and the name of the blockchain.
+Since all of our addresses are EOAs (some multisig smart contract wallets). -> Check this?
 
-Token transfer receipts include the transaction hash, UNIX timestamp, sender and recipient address, nonce, gas price, the amount of gas, chain information, the token contract address and name, tokenType, and token standard specific fields: value, tokenDecimal for ERC-20, tokenID for ERC-721, and value/tokenID for ERC-1155.
+implications
+advantage that we do not need to check if a specific address is a contract.
 
-%Transfer Events, adding Information (isInSet) \\
-%Transactions \\
-%Filtering, Intra-set transfers\\
-%Data Structure, Fields \\
-%We reduced this set to addresses that were active/recorded on either Ethereum or Polygon using Blockscan\footnote{\url{https://blockscan.com/}}. This reduced the address set from to X.
-%Using Blockscan\footnote{\url{https://blockscan.com/}}, we were able to reduce the address set to addresses that were recorded on either Ethereum or Polygon.
+Filter transactions and transfers events where both the \texttt{from} (sender) and the \texttt{to} (recipient) address are in the address set
+
+call/define it intra-set transfers: includes all token transfers and standard native asset transfers. Use this to generate network graph. or for our other clustering heuristics.
 
 \subsection{ENS Names}
+In order to evaluate some of our clustering methods, we need a ground truth. Similarly to \cite{Beres2020}, we use Ethereum Name Service identifiers as ground truth information.
 
-For detecting ground truth pairs in order to evaluate our node embedding methods, we gathered data from ENS contract...
-Additional data, ENS \\
+ENS is a distributed, open, and extensible naming system based on the Ethereum blockchain.
+In spirit, it is similar to the well-known Domain Name Service (DNS).
+However, in ENS the registry is implemented in Ethereum smart contracts.
+ENS maps human-readable names like alice.eth to machine-readable identifiers such as Ethereum addresses.
+Therefore, ENS provides a more user-friendly way of transferring assets on Ethereum, where users can use ENS names as recipient addresses instead of the error-prone hexadecimal Ethereum addresses.
+
+Implemented as NFTs %Currently, all the subdomains or non .eth domains are not NFT, unless the domain registrar itself supports NFT such as (dcl.eth, and .kred).
+
+Find all addresses that transferred/minted etc. an ENS Name.
+Check for each address in the list if the address points to an human-readable name.
+If two addresses point to the same ENS name we consider them belonging to the same entity.
+
+We use ENS names with exactly two unique addresses to measure the performance of different profiling techniques.
+
+assume ENS names that point to multiple addresses, see
+
+To get this information, we query .
+
+%For detecting ground truth pairs in order to evaluate our node embedding methods, we gathered data from ENS contract...
+% Check EDNS
 

### 2023-08-09 paper.tex
Minor corrections to intro

@@
 \textbf{Related work}\\
-Previous work in this field can be broadly distinguished between methods%heuristics
+Previous work in this field can be broadly distinguished between methods %heuristics
  developed for the unspent transaction output (UTXO) model (e.g, Bitcoin and ZCash) and the account-based model (e.g., Ethereum, Polygon).
@@
 \newline
-In contrast to the UTXO-model, native transactions in account-based blockchains can only move funds between a single sender and receiver, and the ``change``remains in the sender account.
+In contrast to the UTXO-model, native transactions in account-based blockchains can only move funds between a single sender and receiver, and the ``change`` remains in the sender account.
 Subsequent transactions necessarily use the same address again.
@@
 Due to Decentraland's blockchain-based architecture, each avatar contains information about a user's Web3 address.
+\newline
 We test the applicability of existing heuristics, and if feasible, their efficacy in detecting entities using multiple addresses is evaluated.
@@
 
-Implemented as NFTs %Currently, all the subdomains or non .eth domains are not NFT, unless the domain registrar itself supports NFT such as (dcl.eth, and .kred).
+%When ENS .eth registrar migrated in May 2019, the .eth registrar became an
 
-Find all addresses that transferred/minted etc. an ENS Name.
+%Currently, all the subdomains or non .eth domains are not NFT, unless the domain registrar itself supports NFT such as (dcl.eth, and .kred).
+If you want to turn all subdomains which you own, you have to create a registrar
+
+Find all addresses that transferred/minted an ENS Name.
+
 Check for each address in the list if the address points to an human-readable name.
+
 If two addresses point to the same ENS name we consider them belonging to the same entity.
@@
 
-To get this information, we query .
+\begin{enumerate}
+	\item From transfer event data, get addresses that interacted with ENS or DCL Registrar as a list
+	\item For each address, find the ENS name it points to using web3.py.ens module (Infura as provider) w3.ens('0xAB') - Ens List
+	\item Find addresses that point to the same human-readable name (group by ENS Name and find instances where exactly 2 addresses point to the same name)
+	\item Save in a CSV (ens\_pairs.csv)
+\end{enumerate}
 
@@
 % Check EDNS
+
+From the web3.py documentation \url{https://web3py.readthedocs.io/en/stable/ens_overview.html}
+%The Ethereum Name Service (ENS) is analogous to the Domain Name Service.
+It enables users and developers to use human-friendly names in place of error-prone hexadecimal addresses, content hashes, and more.
+%The ens module is included with web3.py. It provides an interface to look up domains and addresses, add resolver records, or get and set metadata.
 

### 2023-08-10 paper.tex
ENS pairs section

--- 2023-08-08 paper.tex
@@
 \usepackage{pst-all} % Not working with Sweave!!!
+\usepackage{tikz}
+\usetikzlibrary{positioning, intersections}
 
@@
 Due to Decentraland's blockchain-based architecture, each avatar contains information about a user's Web3 address.
+\newline
 We test the applicability of existing heuristics, and if feasible, their efficacy in detecting entities using multiple addresses is evaluated.
 The main objective is to estimate the number of real-world entities that these addresses represent. The clustering of addresses is limited to this set only, without considering any %(clusters for)
- addresses outside of it, e.g., that were not registered in Decentraland during the given time frame.
+ addresses outside of it, e.g., that were not registered in Decentraland during the given time frame. \newline
 Furthermore, we introduce our own heuristics for identifying address clusters and evaluate their suitability for implementation in other contexts.
@@
 \citep{roth2019tokenization} \newline
-Token standards specify basic interfaces that allow for interoperability between contracts.
+\textit{Token standards} specify basic interfaces that allow for interoperability between contracts.
 These standards do not prescribe an implementation but set minimum requirements without restricting the design beyond that \citep{mastering_ethereum}.
 The most common token standards are ERC-20\footnote{https://eips.ethereum.org/EIPS/eip-20} for fungible tokens, ERC-721\footnote{https://eips.ethereum.org/EIPS/eip-721} for non-fungible tokens (NFTs) and ERC-1155\footnote{https://eips.ethereum.org/EIPS/eip-1155} for semi-fungible tokens.\newline
-When a (blockchain) transaction completes, it produces a transaction receipt that contains log entries providing information about the actions that occurred during its execution \citep{mastering_ethereum}.
+When a transaction completes, it produces a transaction receipt  that contains log entries providing information about the actions that occurred during its execution.
+Solidity\footnote{Solidity is the dominant high-level programming language for smart contracts targeting the EVM.} high-level objects called \textit{Events} construct these logs, which can be queried from a full node and are stored separately from the state.
+\citep{mastering_ethereum} \newline
 The standarization of tokens allows us to listen for ``transfer events``, which are emitted whenever an token changes ownership.
@@
 
-%Solidity high-level objects called \textit{Events} construct these logs, which can be queried from a full node and are stored separately from the state.
-
-%Token Definition
-%Implemented in a standardized way
-%Three most popular token standards
-%Transfer emits Events/Logs/Transaction receipts, we can listen for Events
-
 \subsection{Decentraland}
@@
 \textit{First}, its open architecture allows compiling snapshots of user activity, including the users' locations  within the metaverse.
-This was done by \cite{metaverse-retailing2023}, who captured snapshots of users/avatar locations over a period of 10 months.
-The addresses used in this paper are provided form this work.
+This was done by \cite{metaverse-retailing2023}, who captured snapshots of avatar locations over a period of 10 months.
+The addresses used in this thesis are provided form that work.
 \textit{Second}, users who connect their Web3 account can own various digital assets, such as monetary units, land parcels, and avatar collectibles (e.g.
 wearables, emotes, and names).
-Smart contracts on Ethereum and Polygon track and manage the ownership of these assets \cite{goldbergschaer2023}.
-As a result, this allows us to analyze the entire transaction history and derive information about the avatars’/users' economic activity.
+Smart contracts on Ethereum and Polygon track and manage the ownership of these assets \citep{goldbergschaer2023}.
+This allows us to analyze the entire transaction history and derive information about the users' economic activity.
+%avatars'
 \newline
-The Decentraland ecosystem has two main tokens.
+Initially, Decentraland launched with two native tokens.
 \textit{LAND}, an NFT compliant with ERC-721, manages the ownership of land parcels in Decentraland.
@@
 The majority of purchases and trades are settled in MANA.
-Furthermore, Decentraland %the foundation/DAO/developers
-operates/provides/hosts a virtual/smart-contract-based marketplace where its users may buy or exchange LAND or other in-game collectibles.
+\newline
+Moreover, the Decentraland core team/developers provide a smart-contract-based marketplace where the users may buy or exchange LAND or other in-game collectibles. %the foundation/DAO/developers
 
@@
 %Goods: in-world assets, such as avatar wearables, merchandise, or tickets, as well as tokenized vouchers that can be redeemed for real-world goods or services.
+%The Decentraland ecosystem has two main tokens.
 
@@
 Anyone who has contributed to the pool may then generate a new address and withdraw their funds without revealing the link between the deposit and withdrawal addresses.
-This is achieved using zK-SNARKS.
+This is achieved using zkSNARKs (zero knowledge, succinct, non-interactive argument of knowledge).
 Each depositor inserts a hash value in a Merkle-tree.
@@
  For a more detailed description of how Tornado Cash works, see \cite{nadler2023tornado} or \cite{Beres2020}.
-For a mathematical discussion of ZKSNARKs, please refer to Petkus (2019), Thaler (2022) or Berentsen et al.
+\newline %For a mathematical discussion around zkSNARKs, please refer to Petkus (2019), Thaler (2022) or Berentsen et al.
 (2022).
-\newline
 In the context of this work, it is sufficient to know that third parties can still observe the addresses that have deposited to and withdrawn from the pool.
-The number of addresses that have deposited in a particular pool is defined as the \textit{anonymity set}.
-Typically, a larger anonymity set will provide a higher level of privacy, as a more deposit addresses can be associated with any given withdrawal address.
-\newline
-In theory, if the anonymity set is large enough, third parties will not be able to link a specific depositor address to a specific withdrawal address.
+The set of all deposits that a particular withdrawal could be originated from is defined as the \textit{anonymity set}.
+In theory, a larger anonymity set will provide a higher level of privacy and third parties will not be able to link a specific depositor address to a specific withdrawal address.
 However, this is not always the case.
-For example, some users withdraw from the pool with the same address as they deposited.
+For example, some users (might) withdraw from the pool with the same address as they deposited.
 According to \cite{nadler2023tornado}, careless use of the protocol, testing transactions or external incentive mechanisms might be reasons for this behaviour.
 \newline
-Furthermore, \cite{Beres2020} and \cite{wu2022tutela} have proposed approaches to de-anonymize Tornado cash transactions using various clustering heuristics.
-These methods are discussed in more detail in the next section.
+In addition, \cite{Beres2020} and \cite{wu2022tutela} propose approaches to de-anonymize Tornado cash transactions using various clustering heuristics.
+These methods are discussed in more detail in section 4.
 % making use of address re-use, transaction activity, transaction cost choice, or more complex transaction graph and network analyses.
-
-%The best known smart-contract based non-custodial mixer is Tornado Cash.
 
@@
 The set of remaining addresses consists of 137,544 addresses.
-Subsets are visualized as a Venn diagram in \ref{fig:Venn}.
+Subsets are visualized as a Venn diagram in Figure \ref{fig:Venn}.
 
@@
 \subsection{Transactions and Token Transfer Events}
-The address dataset was used to collect transaction and token transfer event data from Ethereum and Polygon.
+The address subsets were used to collect transaction and token transfer event data from Ethereum and Polygon.
 Ethereum or Polygon data can be accessed directly through a node or an application programming interface (API) provider like Infura or Etherscan.
@@
 By using our network-specific address subsets, we were able to significantly decrease the number of required API calls.
-We gathered all transactions and token transfers up until block height \texttt{17,670,000} on Ethereum (July 11, 2023) and block \texttt{44,990,000} on Polygon (July 12, 2023).
-The output was saved in separate CSV files.
-We then imported this data into a MongoDB database\footnote{\url{https://www.mongodb.com/}}.
-In total, we collected 30,689,978 token transfers and 16,092,531 normal transactions. Figure X visualizes the number of daily transactions and token transfers for each chain. Can see activity.
+We gathered all transactions and token transfers up until block \texttt{17,670,000} on Ethereum (July 11, 2023) and block \texttt{44,990,000} on Polygon (July 12, 2023).
+In total, we collected more than 30 million %30,689,978
+token transfers and more than 16 million %16,092,531
+ normal transactions.
+While the amount of transactions is similar comparing between the two networks, there are 3x more transfer events on polygon.
+The database contains distinct collections for transactions and transfers.
+See appendix for information on the different fields.
 
+The output was stored in separate CSV files and also imported into a MongoDB\footnote{\url{https://www.mongodb.com/}} database.
+
+\iffalse
 Transfer Events: 30,689,978
@@
 Transfer Events Polygon: 22,857,200
-
-Statistics about data, how many transactions on Polygon, how many on Ethereum, how many transfers on Polygon, how many on Ethereum -> Show in Figure
 
@@
 
-%\begin{table}[h]
-%\centering
-%\begin{tabular}{lcc}
-%\hline \hline
-%  & Transactions & Transfers \\
-% \hline
-% Polygon & Cell 2 & Cell 3 \\
-% Ethereum & Cell 5 & Cell 6 \\
-% \hline
-% Total & 16,184,993 & 30,689,978 \\
-% \hline \hline
-%\end{tabular}
-%\caption{Size of raw data}
-%\label{tab:data_size}
-%\end{table}
+Figure X visualizes the number of daily transactions and token transfers for each chain.
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=\textwidth]{../figures/transfers_tx_by_chain.png}
+	\caption{Monthly Transactions and Token Transfers by chain}
+	\label{fig:Data}
+\end{figure} 
+Transfer Events, adding Information (isInSet) \\
+Transactions \\
+Filtering, Intra-set transfers\\
+Data Structure, Fields \\
+\fi
 
-Transaction hash, timestamp in seconds from the UNIX epoch, gas used in the transaction, specified gas price, nonce
+\subsection{Intra-set asset transfers}
+When it comes to entity clustering, we essentially want to answer the question of how many real-world entities our remaining  137,544 addresses represent.
+Another way to put this would be: Are users interacting through multiple EOAs with Decentraland and if so, are we able to detect them?
+(logging in to Decentraland with multiple addresses) \newline
+To achieve this, we often only consider transactions or token transfers where both the 'from' and the 'to' address are within this narrowed pool of addresses.
+For normal transactions, this means that we only consider native asset transfers (Ether or matic).
+\newline
+As nearly all addresses are Externally Owned Accounts (EOAs), we do not need to differentiate between EOAs and smart contract accounts, which further simplifies the clustering process. \newline
+We use this dataset to generate the network graphs.
+Also for other clustering heuristics we often make this reduction, for example: In the self-approval approach, we only consider approval transactions where another address from the set is approved.
 
-The transaction data fields contain the transaction hash, from and to address, the timestamp in seconds from the UNIX epoch, a nonce, value, input (often referred to as calldata), the amount of gas used in the transaction, the specified gas price, the name of the function called (added by Etherscan) and the name of the blockchain.
+%filter our transactions and token transfers to entries where both the 'from' and the 'to' are within this narrowed pool of addresses.
+We define this as intra-set asset transfers.
+For the transactions, this means that we only consider native asset (Ether or matic) transfers.
+%between two EOAs
+%As nearly all addresses are Externally Owned Accounts (EOAs), we do not need to differentiate between EOAs and smart contract accounts, which further simplifies the process.
 
-Token transfer receipts include the transaction hash, UNIX timestamp, sender and recipient address, nonce, gas price, the amount of gas, chain information, the token contract address and name, tokenType, and token standard specific fields: value, tokenDecimal for ERC-20, tokenID for ERC-721, and value/tokenID for ERC-1155.
+%As already mentioned in the introduction, the goal of this paper is to cluster addresses within who (1) were active in Decentraland during the 9-month period (e.g., within the initial dataset) and (2) transacted or interacted with any token on Ethereum or Polygon.
+%Essentialy, we want to answer two main research questions when it comes to clustering:
+%1. How many unique entities does the address set represent (i.e. were active on Decentraland during the 9-month period)?
+%2. Are users interacting through multiple accounts/EOAs/addresses with Decentraland?
+%we focus on on-chain data (and not user location or avatar data), allowing us to exclude addresses that have not transacted or interacted with any token on Ethereum or Polygon. 
+%As mentioned in the introduction, the goal of this paper is to cluster addresses belongig to the same entity that were recorded/active in Decentraland during the 9-month period.
+Therefore, we disregard addresses outside of this set.
+Also, since we only look at on-chain data, we cannot cluster addresses without activity on Polygon or Ethereum.
+Doing these two reductions, there are  141, 591 'clusterable' addresses remaining.
+%Since all of our addresses are EOAs (some multisig smart contract wallets). -> Check this?
 
-%Transfer Events, adding Information (isInSet) \\
-%Transactions \\
-%Filtering, Intra-set transfers\\
-%Data Structure, Fields \\
-%We reduced this set to addresses that were active/recorded on either Ethereum or Polygon using Blockscan\footnote{\url{https://blockscan.com/}}. This reduced the address set from to X.
-%Using Blockscan\footnote{\url{https://blockscan.com/}}, we were able to reduce the address set to addresses that were recorded on either Ethereum or Polygon.
+\subsection{ENS ground-truth pairs}
+Similarly to \cite{Beres2020}, we use Ethereum Name Service (ENS) identifiers as ground truth information to evaluate some of the clustering methods.\newline
+\textit{ENS} is a naming system that relies on the Ethereum smart contracts.
+Its main purpose is to map human-readable names, such as \texttt{`alice.eth`}, to machine-readable identifiers, like Ethereum addresses.
+The architecture of ENS comprises two main components: the registry and resolvers.
+\newline
+The \textit{ENS registry} consists of a single smart contract\footnote{The registry contract is ERC-721 compliant, which means that .eth registrations can be transferred in the same way as other NFTs.} that maintains a list of all domains and subdomains, recording the ``owner`` and ``resolver`` for each.
+The registry allows the owner of a domain to make changes to that data.
+%Domain owners may set the resolver for the domain.
+\newline
+\textit{Resolvers} are responsible for %(the actual process of)
+ translating names into addresses.
+Any contract that adheres to the relevant standards may act as a resolver in ENS.
+The process of resolving a name involves two steps: \textit{First}, the registry must be queried to find out which resolver is responsible for the name, and \textit{second}, that resolver must be asked for the response to the query.
+\newline
+In addition to regular resolution from name to address, ENS also supports ``reverse resolution``, allowing for a mapping from address back to a name (or other metadata).
+Reverse resolution is accomplished via the special domain \texttt{`addr.reverse`}% and the resolver function \texttt{name()}.
+.
+This domain is owned by a special purpose registrar contract that allocates subdomains to the owner of the matching address - for instance, the address \texttt{`0x1234\dots`} may claim the name \texttt{`1234\dots.addr.reverse`}, and configure a resolver and records on it.
+The resolver in turn supports the \texttt{name()} function, which returns the name associated with that address.\newline
+ Reverse resolution %(without a library)
+ follows the same pattern as forward resolution: Get the resolver for \texttt{`1234....addr.reverse'} (where \texttt{`1234...`} is the address you want to reverse-resolve), and call the \texttt{name()} function on that resolver.
+However, ENS does not enforce the accuracy of reverse records.
+This means \texttt{`1234....addr.reverse`} may claim that the name associated to their address is \texttt{`alice.eth`}.
 
-\subsection{ENS Names}
+Figure \ref{fig:ENS} illustrates how we used record changes and reverse resolutions to generate ground truth pairs: Initially, the domain name \texttt{`foo.eth`} resolves to address \texttt{`0xABC...`}.
+The owner also set a reverse resolution for this address, indicated by the the edge from the address to the domain name.
+Next, the owner of \texttt{`foo.eth`} decides to change the resolved address to \texttt{`0xDEF...`}, again setting a reverse record.
+Nevertheless, \texttt{`ABC....addr.reverse`} still points to \texttt{`foo.eth`}.
+If we query the name corresponding to both \texttt{`0xABC...`} and \texttt{`0xDEF...`}, both will return the same name, even though a specific name can only resolve to one address at a time.
+We make the assumption that both addresses belong to the same entity if this specific case occurs.
+%We did not observe cases where someone set a reverse record to a completely unrelated address (e.g. alice.eth)
 
-For detecting ground truth pairs in order to evaluate our node embedding methods, we gathered data from ENS contract...
-Additional data, ENS \\
+\begin{figure*}[h!]
+	\begin{center}
+		\begin{tikzpicture}[
+    every node/.style={minimum width=2.5cm, minimum height=0.6cm, align=center},
+    every path/.style={->},
+    node distance=2cm and 6cm]
+
+		\node (A) {\texttt{foo.eth}};
+		\node[right=of A] (B) {\texttt{0xABC...}};
+		\node[below=of B] (C) {\texttt{0xDEF...}};
+
+		\draw[dotted] (A) -- (B) node[midway, above, name=pathAB] {\footnotesize{forward resolution}};
+		\draw ([yshift=-5pt]B.west) -- ([yshift=-5pt]A.east) node[midway, below] {\footnotesize{reverse resolution}};
+		\draw (A.south) -- (C.west) node[midway, sloped, above] {\footnotesize{forward resolution'}};
+		\draw ([yshift=-5pt]C.west) -- ([yshift=-5pt]A.south) node[midway, sloped, below] {\footnotesize{reverse resolution'}};
+
+		% Adding a cross over "forward resolution"
+        \draw[red, thick, -] (pathAB.south west) -- (pathAB.north east);
+        \draw[red, thick, -] (pathAB.south east) -- (pathAB.north west);
+
+		\end{tikzpicture}
+		\caption{Changing the record to another address does not change the old reverse resolution (Simplified Schematic Representation)}
+		\label{fig:ENS}
+	\end{center}
+\end{figure*}
+
+We applied the following methodology to find ground truth pairs: First, we collected all addresses that interacted ENS (NFTs) to reduce the amount of name look-ups.
+For each remaining address, we checked if it points to an ENS domain name\footnote{This was done via the ENS module within web3.py \url{https://web3py.readthedocs.io/en/stable/ens_overview.html}}.
+If it did, we stored the associated domain alongside the address.
+(ens\_list.csv).
+%(It provides an interface to look up domains and addresses).
+Using the newly generated list, we checked if two addresses point to the same ENS domain. If this check was met, we stored both addresses alongside the domain (ens\_pairs.csv)
+
+We found 11,440 reverse records and 40 address pairs.
+(addresses pointing to the same .eth name) We use these pairs as our ground truth to measure the performance of different profiling/clustering techniques.
+Small sample but should still possible to evaluate the methods.
+
+\iffalse
+-Check for each address in the list if the address points to an human-readable name.
+(reverse mapping must be set/configured) From the web3.py documentation \url{https://web3py.readthedocs.io/en/stable/ens_overview.html } %The ens module is included with web3.py.
+It provides an interface to look up domains and addresses, add resolver records, or get and set metadata.
+-If two addresses point to the same ENS name we consider them belonging to the same entity. 
+-Normally, one .eth domain cannot point/map to multiple Ethereum addresses. Forward resolution. This is likely due to the owner change and the record not updated.
+
+%However, if someone sets the forward resolution to a new address (owner) including a reverse resolution for his ENS name, the (reverse) resolution from 0x05d.addr.reverse still resolves to the the ENS domain name.
+%Only the forward resolution from the name to the address is changed.
+The reverse record resolution from the old address to the name is still there.
+For an visual explanation please see Figure \ref{fig:ENS}.
+%In addition to regular resolution from name to address, ENS also supports ``reverse resolution``, making it possible to map from address back to a name (or other metadata).
+%Anyone who owns a domain at any level may configure subdomains - for themselves or others - as desired.
+For instance, if Alice owns 'alice.eth', she can create 'pay.alice.eth' and configure it as she wishes.
+%Currently, all the subdomains or non .eth domains are not NFTs, unless the domain registrar itself supports NFT such as (dcl.eth, and .kred).
+%If the owner sets a reverse resolution set with his new address, we have two addresses pointing to the same ens name.
+
+%While 'regular' resolution involves mapping from a name to an address, reverse resolution maps from an address back to a name - or other metadata.
+ENS supports reverse resolution to allow applications to display ENS names in place of hexadecimal addresses.
+Before this can be done, the owner of the address has to configure reverse resolution for their address.
+%In spirit, it is similar to the well-known Domain Name Service (DNS). However, in ENS the registry is implemented in Ethereum smart contracts.
+%Therefore, ENS provides a more user-friendly way of transferring assets on Ethereum, where users can use ENS names as recipient addresses instead of the error-prone hexadecimal Ethereum addresses.
+%Resolving a name is a two-step process: First, ask the registry what resolver is responsible for the name, and second, ask that resolver for the answer to your query.\newline
+
+\fi
 
@@
 In Section 5 we will then apply  and, if possible, evaluate the heuristics deemed suited for us.
-
 %detailed explanation
@@
 
-%\section{Appendix}
+\section{Appendix}
+
+Database
+
+%% Table
+\begin{table}[h!]
+  \centering
+  \footnotesize
+  \begin{tabular}{l p{9cm} cc}
+    \hline\hline
+    Field & Description & Transfers & Transactions\\ \hline
+    \texttt{hash} & Transaction hash & \checkmark & \checkmark \\
+    \texttt{timeStamp} & Timestamp in seconds from the UNIX epoch & \checkmark & \checkmark \\
+    \texttt{gasUsed} & Amount of gas used by the transaction & \checkmark & \checkmark \\
+    \texttt{gasPrice} & Gas price specified for this transaction & \checkmark & \checkmark \\
+    \texttt{nonce} &  \textbullet{ }EOAs: \newline \textbullet{ }CAs: & \checkmark & \checkmark \\
+    \texttt{from} & \textbullet{ }Transactions: Address initiating the transaction\newline \textbullet{ }Transfers: Sender address & \checkmark & \checkmark \\
+    \texttt{to} & \textbullet{ }The recipient's hexadecimal address.
+For transactions (native asset/token transfer or contract execution) \newline \textbullet{ }Transfers: Recipient address & \checkmark & \checkmark\\
+    \texttt{value} &  \textbullet{ }Transactions: Amount of native asset sent \newline \textbullet{ }Transfers: Amount of token sent (\texttt{NaN} for NFTs)  & \checkmark & \checkmark\\
+    \texttt{tokenID} &  Token identifier (\texttt{NaN} for ERC-20 tokens) & \checkmark & \\
+    \texttt{input} & Calldata & Contract execution or deployment instructions & \checkmark \\
+    \texttt{functionName} & Name of the function called, added by Etherscan / Polygonscan (\texttt{NaN} if not available) & \checkmark & \\
+    \texttt{type} & Token standard. Created manually to combine token transfer events from different standards & \checkmark & \\
+    \texttt{chainName} & Name of the blockchain. Created manually to combine Ethereum and Polygon data & \checkmark & \checkmark\\
+    \hline\hline
+  \end{tabular}
+  \caption{Database Collection Fields}
+  \label{tbl:database_schema}
+\end{table}
+
+Distinction: Transaction is a message sent from an externally owned account
+((isSet, userAddress))
+%%
+
 \end{document}

### 2023-08-10 python/activity.py
Update python scripts
- Activity
- ENS pairs
- Venn diagram figure

@@ -17,6 +17,7 @@ df_transfer = df_transfer.drop_duplicates()
 print(f'Total number of transfer events: {df_transfer.shape[0]}')
 # Count number of transfers per chain
 print(df_transfer.groupby('chainName').size().reset_index(name='count'))
+print(df_transfer.groupby(['chainName','tokenType']).size().reset_index(name='count'))
 
 # Drop duplicates
 print(df_tx.shape[0])

### 2023-08-10 python/ens-pairs.py

@@ -1,6 +1,7 @@
 import pandas as pd
 from web3 import Web3
 from pymongo import MongoClient
+from tqdm import tqdm
 
 # Connect to db collections
 client = MongoClient('mongodb://localhost:27017/')
@@ -16,33 +17,29 @@ vitalik_address = '0xd8dA6BF26964aF9D7eEd9e03E53415D37aA96045'.lower()
 vitalik = w3.ens.name(vitalik_address)
 print(vitalik)
 
-# Get addresses that interacted with ENS as a list
+# Get all addresses that interacted with an ENS NFT as a list
 query_conditions = {
-    "tokenName": "Ethereum Name Service",
+    "tokenName": {"$in": ["Ethereum Name Service", "DCL Registrar"]},
     "tokenType": 721
 }
-
 ens_df = pd.DataFrame(list(transfers.find(query_conditions)))
 ens_users = ens_df['userAddress'].unique().tolist()
+print(f'Number of ENS users: {len(ens_users)}')
 
-
+# For each address, find the ENS name it points to (reverse record)
 data = []
-# For each address, find the ENS name it points to
-for i,address in enumerate(ens_users):
+for i,address in tqdm(enumerate(ens_users)):
     ens_name = w3.ens.name(address)
     data.append([address, ens_name])
     if i%100 == 0:
         print(f'Addresses checked: {i}/{len(ens_users)}')
 
-
 # Create ens_list.csv
 df = pd.DataFrame(data, columns=['Address', 'ENS Name'])
 df.to_csv('../data/ens_list.csv')
-df = pd.read_csv('../data/ens_list.csv')
-
 
 # Create ens_pairs.csv
-# group by ENS Name and find 2 addresses that point to the same name
+# group by ENS Name and find instances where exactly 2 addresses point to the same name
 grouped_df = df.groupby('ENS Name').filter(lambda x: len(x) == 2)
 data = []
 for ens_name, group in grouped_df.groupby('ENS Name'):

### 2023-08-10 python/venn-diagramm.py

@@ -1,12 +1,23 @@
+import pandas as pd
 from matplotlib_venn import venn2
 import matplotlib.pyplot as plt
 
-# Data
-polygon_only = 83774
-ethereum_only = 7867
-both = 49950
+df = pd.read_csv('../data/subsets.csv', index_col=[0])
 
-venn = venn2(subsets=(polygon_only, ethereum_only, both), set_labels=(None, None), set_colors=('#A5D7D2','#D20537'))
+# Addresses active only on Ethereum
+eth_only = df[(df['Ethereum'] == 1) & (df['Polygon'] == 0)]
+eth_only_count = len(eth_only)
+
+# Addresses active only on Polygon
+polygon_only = df[(df['Ethereum'] == 0) & (df['Polygon'] == 1)]
+polygon_only_count = len(polygon_only)
+
+# Addresses active on both Ethereum and Polygon
+both_active = df[(df['Ethereum'] == 1) & (df['Polygon'] == 1)]
+both_active_count = len(both_active)
+
+
+venn = venn2(subsets=(polygon_only_count, eth_only_count, both_active_count), set_labels=(None, None), set_colors=('#A5D7D2','#D20537'))
 
 
 ax = plt.gca()

### 2023-08-10 paper.tex
Update privacy enhancing protocol section

@@
 Previous work in this field can be broadly distinguished between methods %heuristics
- developed for the unspent transaction output (UTXO) model (e.g, Bitcoin and ZCash) and the account-based model (e.g., Ethereum, Polygon).
+ developed for the unspent transaction output (UTXO) model (e.g, Bitcoin and ZCash) and the account-based model (e.g., Ethereum and Polygon).
 While both models share the concept of addresses, the notion of accounts is not present in UTXO-based blockchains.
@@
 They quantitavely compare graph-representation learning algorithms (a subset of machine learning) and propose further user profiling techniques based on time-of-day activity and transaction fees.
-Using ENS address pairs as ground truth, the authors rigorously test their methods and apply their findings to significantly reduce the privacy guarantees of Tornado Cash, a non-custodial privacy-enhancing protocol on Ethereum.
+Using ENS address pairs as ground truth, the authors rigorously test their methods and apply their findings to significantly reduce the privacy guarantees of \textit{Tornado Cash}, a non-custodial privacy-enhancing protocol on Ethereum.
 \newline
@@
 Further, they also propose a set of new clustering heuristics targeting Tornado Cash,  showing that careless user behavior can still reveal identity.
-They build an application built on those heuristics to measure the anonymity of an Ethereum address.
-All of the methods mentioned will be discussed in greater detail in Section 3.
+Based on those heuristics, they build an application built to measure the anonymity of an Ethereum address.
+\newline All of the methods mentioned will be discussed in greater detail in Section 3.
 \newline
@@
 These patterns are common to interaction graphs in social networks.
-Further, \cite{Payette2017} propose a segmentation of the Ethereum address space into four distinct behaviour groups sharing similar attributes using k-means clustering.
+Further, \cite{Payette2017} propose a segmentation of the Ethereum address space into four distinct behaviour groups sharing similar attributes while using k-means clustering.
 \newline
-Rather than treating users as entities and analyzing on-chain data, \cite{yu2023} propose a novel approach for correlation analysis by exploiting network information.
+Rather than treating users as entities and analyzing on-chain data, \cite{yu2023} propose (a novel) approach for correlation analysis by exploiting network information.
 Although this approach has the potential to avoid the impact of privacy-enhancing technologies, it introduces a new set of limitations and problems.
@@
 The remainder of this paper is structured as follows: In Section 2, we provide a brief overview of the basic concepts necessary to understand the setup.
-The include Ethereum accounts and the EVM, tokens, Decentraland, and privacy-enhancing protocols.
+This includes Ethereum accounts and the EVM, tokens, Decentraland, and privacy-enhancing protocols.
 Section 3 describes our methodology for data collection and preparation.
-The fourth section provides a detailed explanation of various clustering heuristics.The fifth section applies the clustering heuristics described in section 4, after which we discuss the results of our analysis and summarize our findings in sections 6 and 7.
+The fourth section provides a detailed explanation of various clustering heuristics.
+The fifth section applies the clustering heuristics described in section 4, after which we discuss the results of our analysis and summarize our findings in sections 6 and 7.
 
@@
 This was done by \cite{metaverse-retailing2023}, who captured snapshots of avatar locations over a period of 10 months.
-The addresses used in this thesis are provided form that work.
+The addresses they collected are used for this thesis.
 \textit{Second}, users who connect their Web3 account can own various digital assets, such as monetary units, land parcels, and avatar collectibles (e.g.
@@
 The set of all deposits that a particular withdrawal could be originated from is defined as the \textit{anonymity set}.
-In theory, a larger anonymity set will provide a higher level of privacy and third parties will not be able to link a specific depositor address to a specific withdrawal address.
+In theory, a larger anonymity set will provide a higher level of privacy, since  any withdrawal address could be linked to a larger set of deposit addresses.
+However, in practice this does not always hold true.
+%this is not always the case
+Some users reveal the link between their withdrawal and deposit addresses, which also affects the privacy of other depositors.
+For example, by withdrawing from the pool with the same address they deposited or directly send funds between the two addresses.
+According to \cite{nadler2023tornado}, careless use of the protocol, testing transactions or external incentive mechanisms might be reasons for this behaviour.
+\newline
+In addition, \cite{Beres2020} and \cite{wu2022tutela} propose approaches to de-anonymize Tornado cash transactions using various clustering heuristics.
+These methods are discussed in more detail in section 4.
+
+\iffalse
+In theory, a larger anonymity set will provide a higher level of privacy as third parties will not be able to link a specific depositor address to a specific withdrawal address.
 However, this is not always the case.
@@
 These methods are discussed in more detail in section 4.
-% making use of address re-use, transaction activity, transaction cost choice, or more complex transaction graph and network analyses.
+%it is more difficult to link a withdrawal address to a specific depositor address)
+%making use of address re-use, transaction activity, transaction cost choice, or more complex transaction graph and network analyses.
+\fi
 
@@
 
-Figure \ref{fig:ENS} illustrates how we used record changes and reverse resolutions to generate ground truth pairs: Initially, the domain name \texttt{`foo.eth`} resolves to address \texttt{`0xABC...`}.
+Figure \ref{fig:ENS} illustrates the mechanism that allowed us to generate ground truth pairs: Initially, the domain name \texttt{`foo.eth`} resolves to address \texttt{`0xABC...`}.
 The owner also set a reverse resolution for this address, indicated by the the edge from the address to the domain name.
@@
 \subsection{Self-authorization}
-The \texttt{approve} function required in all three token standards allows another address to spend tokens on behalf of the actual owners.
+\iffalse
+	This heuristic was formulated in \cite{FV:17}. 
+	All three token standards have/require functionality around approvals.
+These functions allow another address to spend tokens on behalf of the actual owners.
+This is mainly used in connection with smart contracts, but can also be applied for regular EOAs.
+Users could approve another address they own.
+Reasons for this might be risk distribution over several addresses with partial accessibility ...
+		- approve(address,uint256)
+		- setApprovalForAll(address,bool) for both ERC-721 and ERC-1155
+		- safeBatchTransferFrom(address,address,uint256[],uint256[],bytes)
+\fi
+
+The \texttt{`approve`} function required in all three token standards allows another address to spend tokens on behalf of the actual owners.
 This functionality is mainly used in connection with smart contracts, but can also be applied for regular EOAs.
@@
 \citep{FV:17}
+
+Since we have all the addresses transactions, we can find transactions where someone approved another address from our set.
+
+The first step is to get all approval transactions.
+We achieve this using the 'input'/calldata field.
+The first X bytes are always the function selector.
+We filter for the known function selectors for all standards.
+Next, we get the approved address/spender, also from the calldata, it is always at the same spot.
+We filter for spenders within the address set and for spenders who are different from the 'from' address.
+How many transactions are remaining?
 
@@
 \citep{FV:17}
+We only have the addresses' transaction or token transfers, in order to get the exchange addresses, we would need to go one step further. -> We do not apply this with our dataset.
 
@@
 Projects addresses to points in a low-dimensional vector space based on who it interacts with.
-In this vector space, adresses belonging to the same entity should be close together in Euclidian distance.
+In this vector space, adresses belonging to the same entity should be close together in Euclidean distance.
 
@@
 We chose 6 bins (4 hour intervals) according to Beres.
+
+\subsection{Own heuristics}
 

### 2023-08-10 python/approvals.py
Update approvals.py to search for all function signatures

@@ -1,5 +1,6 @@
 from pymongo import MongoClient
 import pandas as pd
+import re
 
 # Connect to db collection
 client = MongoClient('mongodb://localhost:27017/')
@@ -8,7 +9,19 @@ transactions = db['transactions']
 users = pd.read_csv('../data/subsets.csv')['Address'].to_list()
 
 # Query all approval transactions
-approvals = pd.DataFrame(list(transactions.find({"functionName": "approve(address spender, uint256 rawAmount)"})))
+# approvals = pd.DataFrame(list(transactions.find({"functionName": "approve(address spender, uint256 rawAmount)"})))
+# print(f'Total approvals: {len(approvals)}')
+
+
+# List of function signatures you're interested in
+signatures = [
+    "0x095ea7b3",  # approve(address,uint256) for both ERC-20 and ERC-721
+    "0xa22cb465",  # setApprovalForAll(address,bool) for both ERC-721 and ERC-1155
+    "0x2eb2c2d6"   # safeBatchTransferFrom(address,address,uint256[],uint256[],bytes) for ERC-1155
+]
+
+# MongoDB query to get transactions where the 'input' starts with any of the function signatures
+approvals = pd.DataFrame(list(transactions.find({"input": {"$in": [re.compile(f"^{sig}") for sig in signatures]}})))
 print(f'Total approvals: {len(approvals)}')
 
 # Extract spender address from calldata, Add '0x' to the start of each address

### 2023-08-11 paper.tex
Corrections and updates until clustering heuristics

@@
 All these methods will not be the focus of this work and therefore not discussed.
+\newline
 As suggested by \cite{nakamotoBitcoin2008} in the Bitcoin whitepaper, most Bitcoin wallet implementations use a new key pair for each transaction to keep them from being linked to a common owner.
-\newline
 In contrast to the UTXO-model, native transactions in account-based blockchains can only move funds between a single sender and receiver, and the ``change`` remains in the sender account.
@@
 The account-based model essentially relies on address reuse on the protocol level \citep{Beres2020}.
-Therefore, privacy guarantees should be lower and most users likely use only a small number of addresses.
+Therefore, privacy guarantees should be lower as most participants are likely to use only a small number of addresses.
 \newline
@@
 Further, they also propose a set of new clustering heuristics targeting Tornado Cash,  showing that careless user behavior can still reveal identity.
-Based on those heuristics, they build an application built to measure the anonymity of an Ethereum address.
+Based on those heuristics, they built an application to measure the anonymity of an Ethereum address.
 \newline All of the methods mentioned will be discussed in greater detail in Section 3.
@@
 Although this approach has the potential to avoid the impact of privacy-enhancing technologies, it introduces a new set of limitations and problems.
-Thus, this approach may be of great interest for further research, particularly when privacy-enhancing techniques become more widely used.
+Thus, this approach may be of great interest for future research, particularly when privacy-enhancing techniques become more widely used.
 
@@
 In this work, we perform entity identification on an address set containing 473,927 addresses.
-To obtain these addresses, a separate project collected snapshots of avatar activity in Decentraland over an ten-month period from July 2022 to April 2023.
+To obtain these addresses, a separate project collected snapshots of avatar activity in Decentraland over an nine-month period from July 2022 to April 2023.
 Due to Decentraland's blockchain-based architecture, each avatar contains information about a user's Web3 address.
@@
 \subsection{Contract Accounts and EOAs}
-Account-based blockchains usually distinguish between \textit{externally owned accounts} (EOAs) and \textit{contract accounts} (smart contracts).
-EOAs are created and controlled by private keys and can be used to hold the native protocol asset, send and receive transactions, and interact with contract accounts.
-Contract accounts are controlled by the contract's code, their state can be modified through transactions sent to the contract and they cannot initiate transactions.
+Account-based blockchains usually distinguish between externally owned accounts (EOAs) and contract accounts (smart contracts).
+\textit{EOAs} are created and controlled by private keys and can be used to hold the native protocol asset, send and receive transactions, and interact with contract accounts.
+\textit{Contract accounts} are controlled by the contract's code, their state can be modified through transactions sent to the contract and they cannot initiate transactions.
 \citep{buterin2014ethereum} \newline Each account has a 20-byte address encoded in hexadecimal.
@@
 This allows other blockchain implementations to adopt this standardized framework for contract execution.\newline
-Polygon is a so-called sidechain and aims to address the scalability limitations of Ethereum.
+\textit{Polygon} is a so-called sidechain and aims to address the scalability limitations of Ethereum.
 The adoption of the EVM means that both blockchains share the same user address schemes.
@@
 When a transaction completes, it produces a transaction receipt  that contains log entries providing information about the actions that occurred during its execution.
-Solidity\footnote{Solidity is the dominant high-level programming language for smart contracts targeting the EVM.} high-level objects called \textit{Events} construct these logs, which can be queried from a full node and are stored separately from the state.
+Solidity\footnote{Solidity is the dominant high-level programming language for smart contracts targeting the EVM.} high-level objects called ``Events`` construct these logs, which can be queried from a full node and are stored separately from the state.
 \citep{mastering_ethereum} \newline
@@
 \textit{Decentraland} is the first large-scale blockchain-based virtual world.
-It has attracted the attention of well-known companies like Tommy Hilfiger, Samsung, PepsiCo, Diesel, Adidas, and Netflix, who are actively engaged in it  \citep{metaverse-retailing2023}.\newline
+Well-known companies like Tommy Hilfiger, Samsung, PepsiCo, Diesel, Adidas, and Netflix, who are actively engaging in Decentraland  \citep{metaverse-retailing2023}.\newline
 Decentraland is an ideal platform for empirical research for two main reasons.
@@
 \newline
-Moreover, the Decentraland core team/developers provide a smart-contract-based marketplace where the users may buy or exchange LAND or other in-game collectibles. %the foundation/DAO/developers
+Moreover, the Decentraland core developers provide a smart-contract-based marketplace where users may buy or exchange LAND or other in-game collectibles. %developers/core team
 
@@
 \subsection{Non-custodial crypto asset mixers}
-%intuition of how it works,  distinction between custodial and non-custodial, Tornado cash = SC based
 According to \cite{nadler2023tornado}, crypto-asset mixers are currently the most widely used approach to achieve privacy on public blockchains.
@@
 In the custodial setup, users send their assets to a centralized service provider's public deposit address.
-In return, the provider sends the assets back to a privately relayed recipient address.
+After some delay, the provider sends the assets back to a privately relayed recipient address.
 This approach is fully trust-based, as the service provider has complete control over the assets and access to the identifying data.
@@
 %Subsequently, users can withdraw their asset from the mixer whenever they consider that the size of the anonymity set is satisfactory.
- For a more detailed description of how Tornado Cash works, see \cite{nadler2023tornado} or \cite{Beres2020}.
-\newline %For a mathematical discussion around zkSNARKs, please refer to Petkus (2019), Thaler (2022) or Berentsen et al.
-(2022).
+ For a more detailed description of how Tornado Cash works, see \cite{nadler2023tornado} or \cite{Beres2020}. \newline
 In the context of this work, it is sufficient to know that third parties can still observe the addresses that have deposited to and withdrawn from the pool.
 The set of all deposits that a particular withdrawal could be originated from is defined as the \textit{anonymity set}.
-In theory, a larger anonymity set will provide a higher level of privacy, since  any withdrawal address could be linked to a larger set of deposit addresses.
+In theory, a larger anonymity set will provide a higher level of privacy, since  any withdrawal address could be linked to more deposit addresses.
 However, in practice this does not always hold true.
@@
 Overall, 59,651 addresses were recorded on Ethereum, 129,988 on Polygon, with 52,095 addresses appearing on both networks simultaneously.
-The set of remaining addresses consists of 137,544 addresses.
+The set of ``clusterable`` addresses therefore counts 137,544 addresses.
 Subsets are visualized as a Venn diagram in Figure \ref{fig:Venn}.
@@
 In total, we collected more than 30 million %30,689,978
-token transfers and more than 16 million %16,092,531
+token transfer events and more than 16 million %16,092,531
  normal transactions.
-While the amount of transactions is similar comparing between the two networks, there are 3x more transfer events on polygon.
-The database contains distinct collections for transactions and transfers.
-See appendix for information on the different fields.
-
-The output was stored in separate CSV files and also imported into a MongoDB\footnote{\url{https://www.mongodb.com/}} database.
+While the amount of transactions is similar between the two networks, there are three times more transfer events on Polygon.
+\newline The output was stored in separate CSV files and also imported into a MongoDB\footnote{\url{https://www.mongodb.com/}} database.The database contains distinct collections for transactions and transfers.
+For information on the different data fields, see Appendix.
 
@@
 \subsection{Intra-set asset transfers}
-When it comes to entity clustering, we essentially want to answer the question of how many real-world entities our remaining  137,544 addresses represent.
-Another way to put this would be: Are users interacting through multiple EOAs with Decentraland and if so, are we able to detect them?
-(logging in to Decentraland with multiple addresses) \newline
-To achieve this, we often only consider transactions or token transfers where both the 'from' and the 'to' address are within this narrowed pool of addresses.
-For normal transactions, this means that we only consider native asset transfers (Ether or matic).
+In this project, we want to use entity clustering to determine the number of entities that are represented by the remaining 137,544 addresses.
+Or, to phrase it differently, do users interact with Decentraland using multiple EOAs, and can we identify addresses that belong to the same user?
 \newline
-As nearly all addresses are Externally Owned Accounts (EOAs), we do not need to differentiate between EOAs and smart contract accounts, which further simplifies the clustering process. \newline
-We use this dataset to generate the network graphs.
-Also for other clustering heuristics we often make this reduction, for example: In the self-approval approach, we only consider approval transactions where another address from the set is approved.
+To achieve this, we often only need to consider transactions or token transfer events where both the ``\texttt{from}`` (sender) and the ``\texttt{to}`` (recipient) address are within the address set.
+Regarding normal transactions, this means that we only keep native asset transfers (Ether or Matic) as almost all addresses are EOAs.
+\newline
+The intra-set asset transfer dataset is mainly used to generate the network graphs (see section xx).
+When clustering addresses using graph-based approaches, this has the advantage that we do not need to differentiate between EOAs and smart contract account later on.
+Furthermore, it allows us to observe and visualize the asset flows between users.
+In total, we have 974,478 intra-set token transfers and 210,548 intra-set native asset transfers (101,621 Matic, 108,927 Ether).
 
-%filter our transactions and token transfers to entries where both the 'from' and the 'to' are within this narrowed pool of addresses.
+\iffalse
+%As nearly all addresses are Externally Owned Accounts (EOAs), we do not need to differentiate between EOAs and smart contract accounts, which further simplifies the clustering process. \newline
+%(logging in to Decentraland with multiple addresses) When it comes to entity clustering, we essentially want to answer the question of how many real-world entities our remaining  137,544 addresses represent.
+-Also for other clustering heuristics we often make this reduction, for example: In the self-approval approach, we only consider approval transactions where another address from the set is approved.
+-filter our transactions and token transfers to entries where both the 'from' and the 'to' are within this narrowed pool of addresses.
 We define this as intra-set asset transfers.
@@
 %between two EOAs
-%As nearly all addresses are Externally Owned Accounts (EOAs), we do not need to differentiate between EOAs and smart contract accounts, which further simplifies the process.
-
-%As already mentioned in the introduction, the goal of this paper is to cluster addresses within who (1) were active in Decentraland during the 9-month period (e.g., within the initial dataset) and (2) transacted or interacted with any token on Ethereum or Polygon.
-%Essentialy, we want to answer two main research questions when it comes to clustering:
-%1. How many unique entities does the address set represent (i.e. were active on Decentraland during the 9-month period)?
-%2. Are users interacting through multiple accounts/EOAs/addresses with Decentraland?
-%we focus on on-chain data (and not user location or avatar data), allowing us to exclude addresses that have not transacted or interacted with any token on Ethereum or Polygon. 
-%As mentioned in the introduction, the goal of this paper is to cluster addresses belongig to the same entity that were recorded/active in Decentraland during the 9-month period.
+-As already mentioned in the introduction, the goal of this paper is to cluster addresses within who (1) were active in Decentraland during the 9-month period (e.g., within the initial dataset) and (2) transacted or interacted with any token on Ethereum or Polygon.
+-Essentialy, we want to answer two main research questions when it comes to clustering:
+1. How many unique entities does the address set represent (i.e. were active on Decentraland during the 9-month period)?
+2. Are users interacting through multiple accounts/EOAs/addresses with Decentraland?
+-we focus on on-chain data (and not user location or avatar data), allowing us to exclude addresses that have not transacted or interacted with any token on Ethereum or Polygon. 
+-As mentioned in the introduction, the goal of this paper is to cluster addresses belongig to the same entity that were recorded/active in Decentraland during the 9-month period.
 Therefore, we disregard addresses outside of this set.
@@
 Doing these two reductions, there are  141, 591 'clusterable' addresses remaining.
-%Since all of our addresses are EOAs (some multisig smart contract wallets). -> Check this?
+-Since all of our addresses are EOAs (some multisig smart contract wallets). -> Check this?
+\fi
 
@@
 \textit{ENS} is a naming system that relies on the Ethereum smart contracts.
-Its main purpose is to map human-readable names, such as \texttt{`alice.eth`}, to machine-readable identifiers, like Ethereum addresses.
+Its main purpose is to map human-readable names, such as \texttt{`alice.eth`}, to machine-readable identifiers, mostly Ethereum addresses.
 The architecture of ENS comprises two main components: the registry and resolvers.
@@
 The registry allows the owner of a domain to make changes to that data.
-%Domain owners may set the resolver for the domain.
+\citep{ENSdocs} %Domain owners may set the resolver for the domain.
 \newline
@@
  translating names into addresses.
-Any contract that adheres to the relevant standards may act as a resolver in ENS.
+Any contract that adheres to the relevant standards may act as a resolver.
 The process of resolving a name involves two steps: \textit{First}, the registry must be queried to find out which resolver is responsible for the name, and \textit{second}, that resolver must be asked for the response to the query.
@@
 In addition to regular resolution from name to address, ENS also supports ``reverse resolution``, allowing for a mapping from address back to a name (or other metadata).
-Reverse resolution is accomplished via the special domain \texttt{`addr.reverse`}% and the resolver function \texttt{name()}.
+Reverse resolution is accomplished via %special
+ domain \texttt{`addr.reverse`}% and the resolver function \texttt{name()}.
 .
@@
 However, ENS does not enforce the accuracy of reverse records.
-This means \texttt{`1234....addr.reverse`} may claim that the name associated to their address is \texttt{`alice.eth`}.
+This means \texttt{`1234....addr.reverse`} may falsely claim that the name associated to their address is \texttt{`alice.eth`}.
 
-Figure \ref{fig:ENS} illustrates the mechanism that allowed us to generate ground truth pairs: Initially, the domain name \texttt{`foo.eth`} resolves to address \texttt{`0xABC...`}.
-The owner also set a reverse resolution for this address, indicated by the the edge from the address to the domain name.
-Next, the owner of \texttt{`foo.eth`} decides to change the resolved address to \texttt{`0xDEF...`}, again setting a reverse record.
-Nevertheless, \texttt{`ABC....addr.reverse`} still points to \texttt{`foo.eth`}.
-If we query the name corresponding to both \texttt{`0xABC...`} and \texttt{`0xDEF...`}, both will return the same name, even though a specific name can only resolve to one address at a time.
-We make the assumption that both addresses belong to the same entity if this specific case occurs.
+Figure \ref{fig:ENS} illustrates the mechanism that allowed us to generate ground truth pairs in a simplified way: Initially, the domain name \texttt{`foo.eth`} resolves to address \texttt{`0xABC...`}.
+The owner has also set a reverse resolution for this address, indicated by the the edge from the address to the domain name.
+Next, the owner (he) decides to change the resolved address to \texttt{`0xDEF...`}.
+Again, he is setting a reverse record.
+As a domain can only point to one address at the time, the previous mapping from address to old address is deleted.
+However, \texttt{`ABC....addr.reverse`} still points to \texttt{`foo.eth`} and when we query the name corresponding to \texttt{`0xABC...`} and \texttt{`0xDEF...`}, both will return \texttt{`foo.eth`}.
+If this special case occurs, we assume that both addresses belong to the same entity.
 %We did not observe cases where someone set a reverse record to a completely unrelated address (e.g. alice.eth)
@@
 We applied the following methodology to find ground truth pairs: First, we collected all addresses that interacted ENS (NFTs) to reduce the amount of name look-ups.
-For each remaining address, we checked if it points to an ENS domain name\footnote{This was done via the ENS module within web3.py \url{https://web3py.readthedocs.io/en/stable/ens_overview.html}}.
-If it did, we stored the associated domain alongside the address.
-(ens\_list.csv).
+For each of the remaining addresses, we checked if it points to an ENS domain name\footnote{This was done via the ENS module within web3.py \url{https://web3py.readthedocs.io/en/stable/ens_overview.html}}.
+If it did, we stored the associated ENS domain alongside the address in a CSV file.
 %(It provides an interface to look up domains and addresses).
-Using the newly generated list, we checked if two addresses point to the same ENS domain. If this check was met, we stored both addresses alongside the domain (ens\_pairs.csv)
-
-We found 11,440 reverse records and 40 address pairs.
-(addresses pointing to the same .eth name) We use these pairs as our ground truth to measure the performance of different profiling/clustering techniques.
-Small sample but should still possible to evaluate the methods.
+Using the newly generated list, we checked if two addresses point to the same ENS domain. If this check was met, we stored both addresses alongside the ENS domain. \newline
+We found 11,440 reverse records and 40 address pairs. %(addresses pointing to the same .eth name)
+We use these pairs as our ground truth to measure the performance of different clustering heuristics.
+Even though this is a small sample compared to the total number of 'clusterable' addresses, we should still be able to evaluate (compare) the methods and infer their efficacy.
+%profiling techniques
 

### 2023-08-11 paper.tex
Update Clustering Heuristics section
- Update introduction to section
- Update deposit address reuse

@@
 We use these pairs as our ground truth to measure the performance of different clustering heuristics.
-Even though this is a small sample compared to the total number of 'clusterable' addresses, we should still be able to evaluate (compare) the methods and infer their efficacy.
+Even though this is a small sample compared to the total number of clusterable addresses, we should still be able to evaluate (compare) the methods and infer their efficacy.
 %profiling techniques
@@
 \section{Clustering Heuristics}
-In this section, we provide a overview of clustering heuristics in the context of account-based blockchains and on-chain data.
-We will give a detailed explanation of the intuition/rationale behind the heuristic, the workings and discuss the applicability for our case.
-In Section 5 we will then apply  and, if possible, evaluate the heuristics deemed suited for us.
-%detailed explanation
+In this section, we present an overview of clustering heuristics in the context of account-based blockchains and on-chain data.
+We will give a detailed explanation of the mechanics and rationale behind the heuristic and assess its applicability to our case.
+In Section 5, we will implement and evaluate the heuristics we determine to be suitable for our objectives.
+
 % Goal: explain each heuristic, categorize, and discuss applicability to our address set
+%In Section 5 we will then apply  and, if possible, evaluate the heuristics deemed suited for us.
+%intuition
 
 \subsection{Self-authorization}
+
 \iffalse
@@
 \subsection{Deposit address reuse}
+The concept of deposit address reuse was first introduced and systematically utilized by \cite{FV:17}. It was subsequently adoped by \cite{wu2022tutela}. \newline 
+This heuristic relies on the prevalent practice of crypto exchanges generating unique deposit addresses for each user.
+These addresses then forward the funds to an exchange's main address.
+It is highly likely that multiple addresses sending funds to the same deposit address are controlled by the same entity.
+They key challenge of this approach lies in identifying these deposit addresses, which could either be EOAs or smart contracts.
+\newline
+Deposit addresses share the characteristic that they forward the received funds to a major exchange account.
+Two parameters are essential for deposit address detection: the discrepancy between the amount received and forwarded (since the exchange must pay gas fees), and the time lag between receiving and forwarding funds.
+However, our dataset only includes the direct transactions or token transfers associated with the addresses.
+The transactions between deposit and main exchange address are absent.
+Consequently, this clustering heuristic is not applicable to our data.
+
+\iffalse
+\cite{FV:17} was the first to formulate and systematically exploit this heuristic, which was also applied later on by \cite{wu2022tutela}.
 This heuristic exploits the common practice of crypto exchanges creating so-called deposit addresses for each user, which forward funds to a main address.
 Multiple addresses that send funds to the same deposit address are highly likely controlled by the same entity.
-\citep{FV:17}
-We only have the addresses' transaction or token transfers, in order to get the exchange addresses, we would need to go one step further. -> We do not apply this with our dataset.
+The main challenge of this approach is detecting deposit addresses, which can be either EOAs but also smart contracts.
+- Exchanges typically create so-called deposit addresses, which will forward received funds to a main address.
+As these deposit addresses are created per customer, multiple addresses that send funds to the same deposit address are highly likely to be controlled by the same entity.
+The key challeng lies in identifying these deposit addresses.
+Their characteristic property is that they forward received amounts to a major exchange account.
+The forwarded amount is often slightly less than what was received, as the exchange has to pay for the transaction costs.
+In most cases, deposit addresses are EOAs, but they can also be smart contracts.
+Identifying deposit addresses relies on two parameters: the maximum amount difference between what was received and forwarded and the maximum time difference between receiving and forwarding.
+In this project, we only collected the addresses' direct transactions or token transfers.
+This would allow us to see deposit addresses, however, with this data we cannot find the second step: the deposit address forwarding the asset to the exchanges main address.
+Therefore, we do not apply this clustering heuristic here.
+Since we only collected the addresses' direct transactions or token transfers, the second step between deposit and exchange address is not available/present in our dataset. 
+\fi
 

### 2023-08-11 paper.tex
Update self-authorization

@@
 \subsection{Self-authorization}
+This heuristic was formulated in \cite{FV:17}. 
+	All three token standards have/require functionality to allow another address to spend/transfer tokens on behalf of the actual owner.
 
-\iffalse
-	This heuristic was formulated in \cite{FV:17}. 
-	All three token standards have/require functionality around approvals.
-These functions allow another address to spend tokens on behalf of the actual owners.
-This is mainly used in connection with smart contracts, but can also be applied for regular EOAs.
-Users could approve another address they own.
-Reasons for this might be risk distribution over several addresses with partial accessibility ...
-		- approve(address,uint256)
-		- setApprovalForAll(address,bool) for both ERC-721 and ERC-1155
-		- safeBatchTransferFrom(address,address,uint256[],uint256[],bytes)
-\fi
+	For the ERC-20 standard: \texttt{approve(address spender, uint256 amount)}
+	For the ERC-721 standard: \texttt{approve(address to, uint256 tokenId)} and \texttt{setApprovalForAll(address operator, bool approved)}\\
+	For the ERC-1155 standard: \texttt{setApprovalForAll(address operator, bool approved)}
 
-The \texttt{`approve`} function required in all three token standards allows another address to spend tokens on behalf of the actual owners.
 This functionality is mainly used in connection with smart contracts, but can also be applied for regular EOAs.
-Users could approve another address they own, a reason for this might be risk distribution over several addresses with partial accessibility.
+Users could approve another address they own, a reason for this might be risk distribution over several addresses with partial accessibility or testing.
 \citep{FV:17}
@@
 Since we have all the addresses transactions, we can find transactions where someone approved another address from our set.
+
+\iffalse
+	- approve(address,uint256)
+	- setApprovalForAll(address,bool) for both ERC-721 and ERC-1155
 
@@
 How many transactions are remaining?
+Finally, we extract all unique pairs of owners and spenders, disregarding the type of token or the amount.
+\fi
 

### 2023-08-11 paper.tex
Update clustering heuristics section

@@
 While the amount of transactions is similar between the two networks, there are three times more transfer events on Polygon.
-\newline The output was stored in separate CSV files and also imported into a MongoDB\footnote{\url{https://www.mongodb.com/}} database.The database contains distinct collections for transactions and transfers.
-For information on the different data fields, see Appendix.
+\newline The output was stored in separate CSV files and also imported into a MongoDB\footnote{\url{https://www.mongodb.com/}} database.
+The database contains distinct collections for transactions and transfers.
+For additional information on the different data fields, see Appendix.
 
@@
 \subsection{Self-authorization} 
-This heuristic was formulated in \cite{FV:17}. 
-	All three token standards have/require functionality to allow another address to spend/transfer tokens on behalf of the actual owner.
+	All three token standards require functions to allow another address to transfer tokens on behalf of the actual owner.
+For the ERC-20 standard, this is achieved through the \texttt{`approve`} function, accepting the spender's address and the token amount as parameters\footnote{\texttt{approve(address spender, uint256 amount)}}.
+The ERC-721 has two functions dedicated to approvals: One for authorizing the transfer of a specific NFT\footnote{\texttt{approve(address to, uint256 tokenId)}} and one to permit transferring all of the owner's NFTs within the collection\footnote{\texttt{setApprovalForAll(address operator, bool approved)}}.
+The latter function also appears in the ERC-1155 standard.
+The approval functionality of these tokens is primarily used in connection with smart contracts (DEX or NFT Marketplace), but can also be applied for regular EOAs.
+\newline
+The ``self authorization`` heuristic, proposed by \cite{FV:17}, suggests that users might authorize another address they own, possibly for risk distribution across several addresses or for testing purposes.
+\citep{FV:17} \newline
+Given our dataset includes all address transactions, we can easily employ this heuristic. %Since all the addresses' transactions are available in our dataset, we are able to apply this heuristic.
 
+\iffalse
 	For the ERC-20 standard: \texttt{approve(address spender, uint256 amount)}
@@
 
-This functionality is mainly used in connection with smart contracts, but can also be applied for regular EOAs.
-Users could approve another address they own, a reason for this might be risk distribution over several addresses with partial accessibility or testing.
-\citep{FV:17}
-
-Since we have all the addresses transactions, we can find transactions where someone approved another address from our set.
-
-\iffalse
 	- approve(address,uint256)
@@
 \subsection{Deposit address reuse}
-The concept of deposit address reuse was first introduced and systematically utilized by \cite{FV:17}. It was subsequently adoped by \cite{wu2022tutela}. \newline 
+The concept of deposit address reuse was first introduced and systematically utilized by \cite{FV:17} and subsequently adoped by \cite{wu2022tutela}.
 This heuristic relies on the prevalent practice of crypto exchanges generating unique deposit addresses for each user.
@@
 Airdrops are popular token distribution mechanisms, and recipients are mostly chosen based on past protocol activity.
-A famous example is Uniswap's UNI airdrop, where each address that interacted with the protocol received a fixed amount of UNI tokens\footnote{\url{https://blog.uniswap.org/uni}}.
-These distribution mechanisms are often not Sybil-resistant, leading to people creating multiple addresses in anticipation of an airdrop.
+Probably the most well known example is Uniswap's UNI airdrop, where each address that interacted with the protocol until a specified cutoff date received a fixed amount of 400 UNI tokens\footnote{\url{https://blog.uniswap.org/uni}}.
+Often, these distribution mechanisms are not Sybil-resistant, leading to people creating multiple addresses in anticipation of an airdrop.
 However, managing the tokens on all of these addresses is impractical, which is why they are often aggregated into one address.
 \citep{FV:17}
+
+\iffalse
+Airdrops are a popular mechanism to distribute tokens.
+On the Ethereum blockchain, they are performed through smart contracts.
+The owners of the smart contract choose recipients either based on past activity, or ask users to sign up through online forms.
+Some of these registration processes require users to perform certain actions on social media, such as posting articles or following users.
+The amount of tokens given to each user is either fixed, or based on existing account balances.
+If the amount is fixed, there is an incentive to cheat the system.
+We identify Airdrops where a fixed number of tokens is distributed to many recipients. Then we search for addresses that have been forwarded the same amount from the initial recipients. 
+This heuristic depends on two inputs.
+First, a set of aidrops with equal mounts, characterized by a signature of a distributing address, a token network and an amount.
+Second, the minimum nuber of token aggregations into a single address.
+The second parameter is trivial to choose, as multi-participation in its smallest form consist of two aidrop recipient addresses forwarding their tokens to a third adddress.
+In this case, a single entity would be in control of at least 3 addresses.
+The main challenge lies in identying airdrops. To do so, we first examine all same-source, fixed amount token distributions.
+
+\fi
 

### 2023-08-12 paper.tex
Update introduction and data collection

@@
 Public permissionless blockchains such as Bitcoin \citep{nakamotoBitcoin2008} and Ethereum \citep{buterin2014ethereum} allow users %individuals
- to participate with multiple pseudonymous addresses.
-The creation of these addresses is virtually cost free.
+ to participate with multiple pseudonymous addresses, the creation of which is virtually cost free.
 Contrary to popular belief, these blockchains are entirely transparent.
-All transactions are stored as part of the blockchain's history and publicly observable.
+All transactions are publicly observable and stored as part of the blockchain's history.
 This has opened up a nascent scientific field dealing with entity identification within blockchain networks.
@@
 Nonetheless, these protocols are not yet widely adopted and careless user behaviour can undermine the privacy guarantees they offer. \newline
-%As such/In conclusion
-The topic of privacy, or lack thereof, will remain significant for future blockchain development and research.
+With these considerations in mind, the topic of privacy, or lack thereof, will remain significant for future blockchain development and research.
 
-%The most prominent/widely used non-custodial mixer is Tornado cash (Schär, Tutela).
 %If someone obtains information that allows them to link a blockchain address to an entity, they may effectively observe that entity’s entire transaction history and associated activity.
@@
 \textbf{Related work}\\
-Previous work in this field can be broadly distinguished between methods %heuristics
- developed for the unspent transaction output (UTXO) model (e.g, Bitcoin and ZCash) and the account-based model (e.g., Ethereum and Polygon).
+Previous work in this field can be broadly distinguished between methods developed for the unspent transaction output (UTXO) model (e.g, Bitcoin and ZCash) and the account-based model (e.g., Ethereum and Polygon).
 While both models share the concept of addresses, the notion of accounts is not present in UTXO-based blockchains.
@@
 
-A number of address clustering heuristics in the UTXO setup have been proposed for Bitcoin and derivatives \citep{Androulaki2013, Meiklejohn2013, Haslhofer2016, jourdan2018, kappos2022}.
-All these methods will not be the focus of this work and therefore not discussed.
+Several address clustering heuristics in the UTXO setup have been proposed for Bitcoin and its derivatives \citep{Androulaki2013, Meiklejohn2013, Haslhofer2016, jourdan2018, kappos2022}.
+However, these methods are outside the scope of this work and will not discussed.
 \newline
 As suggested by \cite{nakamotoBitcoin2008} in the Bitcoin whitepaper, most Bitcoin wallet implementations use a new key pair for each transaction to keep them from being linked to a common owner.
-In contrast to the UTXO-model, native transactions in account-based blockchains can only move funds between a single sender and receiver, and the ``change`` remains in the sender account.
+Unlike the UTXO-model, native transactions in account-based blockchains can only move funds between a single sender and receiver, and the ``change`` remains in the sender account.
 Subsequent transactions necessarily use the same address again.
 The account-based model essentially relies on address reuse on the protocol level \citep{Beres2020}.
-Therefore, privacy guarantees should be lower as most participants are likely to use only a small number of addresses.
+Consequently, privacy guarantees should be lower as participants typically use a limited set of addresses.
 \newline
@@
 \newline
-\cite{Beres2020} propose more universally applicable methods, as they argue that Victor’s heuristics, while powerful, assume participation in certain on-chain events.
-Their technique interprets transactions or token transfers as network graphs, with addresses as nodes and asset transfers as edges.
-They quantitavely compare graph-representation learning algorithms (a subset of machine learning) and propose further user profiling techniques based on time-of-day activity and transaction fees.
+\cite{Beres2020} propose more universally applicable methods, arguing that Victor’s heuristics, while powerful, assume participation in certain on-chain events.
+Their approach interprets transactions or token transfers as network graphs, with addresses as nodes and asset transfers as edges.
+They quantitavely compare graph-representation learning algorithms (a subset of machine learning) and propose further user profiling techniques based on time-of-day activity and transaction fee patterns.
 Using ENS address pairs as ground truth, the authors rigorously test their methods and apply their findings to significantly reduce the privacy guarantees of \textit{Tornado Cash}, a non-custodial privacy-enhancing protocol on Ethereum.
@@
 Further, they also propose a set of new clustering heuristics targeting Tornado Cash,  showing that careless user behavior can still reveal identity.
-Based on those heuristics, they built an application to measure the anonymity of an Ethereum address.
-\newline All of the methods mentioned will be discussed in greater detail in Section 3.
+Based on those heuristics, they developed an application to measure the anonymity of an Ethereum address.
+\newline All of the aforementioned methods will be discussed in greater depth in Section 3.
 \newline
@@
 Similarly, \cite{casalebrunet2021} apply network graph analysis to various non-fungible token (NFT) ecosystems.
-Both find that many of the networks follow either a star or a hub-and-spoke pattern.
-These patterns are common to interaction graphs in social networks.
-Further, \cite{Payette2017} propose a segmentation of the Ethereum address space into four distinct behaviour groups sharing similar attributes while using k-means clustering.
+Both find that many of the networks follow either a star or a hub-and-spoke pattern, common to interaction graphs in social networks.
+Moreover, \cite{Payette2017} propose a segmentation of the Ethereum address space into four distinct behaviour groups sharing similar attributes while using k-means clustering.
 \newline
@@
 \textit{Decentraland} is the first large-scale blockchain-based virtual world.
-Well-known companies like Tommy Hilfiger, Samsung, PepsiCo, Diesel, Adidas, and Netflix, who are actively engaging in Decentraland  \citep{metaverse-retailing2023}.\newline
+Well-known companies like Tommy Hilfiger, Samsung, PepsiCo, Diesel, Adidas, and Netflix, are actively engaging in Decentraland  \citep{metaverse-retailing2023}.\newline
 Decentraland is an ideal platform for empirical research for two main reasons.
 \textit{First}, its open architecture allows compiling snapshots of user activity, including the users' locations  within the metaverse.
-This was done by \cite{metaverse-retailing2023}, who captured snapshots of avatar locations over a period of 10 months.
+This was done by \cite{metaverse-retailing2023}, who captured snapshots of avatar locations over a period of nine months.
 The addresses they collected are used for this thesis.
@@
 Some users reveal the link between their withdrawal and deposit addresses, which also affects the privacy of other depositors.
-For example, by withdrawing from the pool with the same address they deposited or directly send funds between the two addresses.
+For example, by withdrawing from the pool with the same address they deposited or directly sending funds between the two addresses.
 According to \cite{nadler2023tornado}, careless use of the protocol, testing transactions or external incentive mechanisms might be reasons for this behaviour.
@@
 The set of ``clusterable`` addresses therefore counts 137,544 addresses.
-Subsets are visualized as a Venn diagram in Figure \ref{fig:Venn}.
+The subsets are visualized as a Venn diagram in Figure \ref{fig:Venn}.
 
@@
  normal transactions.
-While the amount of transactions is similar between the two networks, there are three times more transfer events on Polygon.
+While the amount of transactions is similar between the two networks, Polygon has roughly three times more transfer events.
 \newline The output was stored in separate CSV files and also imported into a MongoDB\footnote{\url{https://www.mongodb.com/}} database.
 The database contains distinct collections for transactions and transfers.
-For additional information on the different data fields, see Appendix.
+For additional information on the data fields of each collection, see Appendix.
 
@@
 \subsection{Intra-set asset transfers}
-In this project, we want to use entity clustering to determine the number of entities that are represented by the remaining 137,544 addresses.
+In this thesis, we want to employ entity clustering heuristics to determine the number of entities represented by the remaining 137,544 addresses.
 Or, to phrase it differently, do users interact with Decentraland using multiple EOAs, and can we identify addresses that belong to the same user?
@@
 To achieve this, we often only need to consider transactions or token transfer events where both the ``\texttt{from}`` (sender) and the ``\texttt{to}`` (recipient) address are within the address set.
+We call this reduced dataset ``intra-set asset transfers``.
 Regarding normal transactions, this means that we only keep native asset transfers (Ether or Matic) as almost all addresses are EOAs.
@@
 The intra-set asset transfer dataset is mainly used to generate the network graphs (see section xx).
-When clustering addresses using graph-based approaches, this has the advantage that we do not need to differentiate between EOAs and smart contract account later on.
+When clustering addresses using graph-based approaches, this has the advantage that we do not need to differentiate between EOA and smart contract account later on.
 Furthermore, it allows us to observe and visualize the asset flows between users.
@@
 \iffalse
-%As nearly all addresses are Externally Owned Accounts (EOAs), we do not need to differentiate between EOAs and smart contract accounts, which further simplifies the clustering process. \newline
+%further simplifies the clustering process. \newline
 %(logging in to Decentraland with multiple addresses) When it comes to entity clustering, we essentially want to answer the question of how many real-world entities our remaining  137,544 addresses represent.
@@
 The owner has also set a reverse resolution for this address, indicated by the the edge from the address to the domain name.
-Next, the owner (he) decides to change the resolved address to \texttt{`0xDEF...`}.
-Again, he is setting a reverse record.
-As a domain can only point to one address at the time, the previous mapping from address to old address is deleted.
+Next, the owner decides to change the resolved address to \texttt{`0xDEF...`}, again setting a reverse record.
+As a domain can only point to one address at the time, the previous mapping from \texttt{`foo.eth`} to the old address is deleted.
 However, \texttt{`ABC....addr.reverse`} still points to \texttt{`foo.eth`} and when we query the name corresponding to \texttt{`0xABC...`} and \texttt{`0xDEF...`}, both will return \texttt{`foo.eth`}.
@@
 
-We applied the following methodology to find ground truth pairs: First, we collected all addresses that interacted ENS (NFTs) to reduce the amount of name look-ups.
-For each of the remaining addresses, we checked if it points to an ENS domain name\footnote{This was done via the ENS module within web3.py \url{https://web3py.readthedocs.io/en/stable/ens_overview.html}}.
-If it did, we stored the associated ENS domain alongside the address in a CSV file.
-%(It provides an interface to look up domains and addresses).
-Using the newly generated list, we checked if two addresses point to the same ENS domain. If this check was met, we stored both addresses alongside the ENS domain. \newline
-We found 11,440 reverse records and 40 address pairs. %(addresses pointing to the same .eth name)
-We use these pairs as our ground truth to measure the performance of different clustering heuristics.
-Even though this is a small sample compared to the total number of clusterable addresses, we should still be able to evaluate (compare) the methods and infer their efficacy.
-%profiling techniques
+We applied the following methodology to find ground truth pairs: First, we gathered all addresses that interacted with ENS (NFTs) to reduce the amount of name look-ups.
+Second, we iterated over each remaining address and checked if it reverse-resolved to an ENS domain\footnote{This was done via the ENS module within web3.py \url{https://web3py.readthedocs.io/en/stable/ens_overview.html}, which provides an interface to look up domains and addresses.}.
+If so, we logged the ENS domain and address in a CSV file.
+Third, using our new list, we identified if two addresses referenced the same ENS domain.
+If matched, we recorded both addresses alongside the ENS domain.
+\newline
+From this, we identified 11,440 reverse records and 40 address pairs, %(addresses pointing to the same .eth name)
+which we utilized as our ground truth to evaluate various clustering heuristics.
+Although this sample is relatively small, it allows us to assess and draw conclusions about the effectiveness of the methods.%profiling techniques/methods
 

### 2023-08-13 python/cluster-node-embedding.py
Add script for clustering node embeddings

@@ -1,0 +1,97 @@
+from utils import *
+
+all_transfers_df = pd.read_csv('../data/all_intra_transfers.csv', index_col=[0])
+
+# Create network graph
+G = nx.from_pandas_edgelist(all_transfers_df, 'from', 'to', create_using=nx.MultiDiGraph())
+G = clean_graph(G)
+
+# Get the largest connected component
+largest_cc = max(nx.connected_components(G), key=len)
+G_cc = G.subgraph(largest_cc)
+
+# Recode the graph's nodes, node_map maps from address to index
+G_cc, node_map = recode_graph(G_cc)
+
+# Create reverse map (from indices to addresses)
+idx_map = dict(zip(node_map.values(),node_map.keys()))
+ordered_addresses = [idx_map[idx] for idx in range(len(node_map))]
+
+print(f'Nodes: {len(G_cc.nodes())}\nEdges: {len(G_cc.edges())}')
+
+#Get the embeddings
+
+#Diff2Vec
+emb_d2v_df = pd.read_csv('../data/embeddings/diff2vec.csv', index_col='address')
+embeddings_d2v = emb_d2v_df.values
+faiss_index_d2v = DistCalculation(embeddings_d2v, node_map)
+#Role2Vec
+emb_r2v_df = pd.read_csv('../data/embeddings/role2vec.csv', index_col='address')
+embeddings_r2v = emb_r2v_df.values
+faiss_index_r2v = DistCalculation(embeddings_r2v, node_map)
+#Deepwalk
+emb_dw_df = pd.read_csv('../data/embeddings/deepWalk.csv', index_col='address')
+embeddings_dw = emb_dw_df.values
+faiss_index_deepWalk = DistCalculation(embeddings_dw, node_map)
+
+#Get clusters
+threshold = 0.7
+
+class UnionFind:
+    def __init__(self, n):
+        self.parent = [i for i in range(n)]
+        self.rank = [0] * n
+
+    def find(self, x):
+        if self.parent[x] != x:
+            self.parent[x] = self.find(self.parent[x])
+        return self.parent[x]
+
+    def union(self, x, y):
+        rootX = self.find(x)
+        rootY = self.find(y)
+        if rootX != rootY:
+            if self.rank[rootX] > self.rank[rootY]:
+                self.parent[rootY] = rootX
+            else:
+                self.parent[rootX] = rootY
[…]

### 2023-08-13 python/compute-normalizedGas-and-timeOfDay.py
Rename scripts

@@ -46,7 +46,6 @@ hist_df = compute_histogram(transaction_df_filtered, 6, 'ToD')
 combined_stats_hist_ToD = pd.concat([stats_df, hist_df], axis=1)
 combined_stats_hist_ToD.to_csv('../data/timeOfDay.csv')
 
-
 ################
 ### GasPrice ###
 ################

### 2023-08-13 python/utils.py
update get_dist_idx function

@@ -120,7 +120,7 @@ class DistCalculation:
         self.index.add(self.X)
         self.node_map = node_map
 
-    def get_dist_idx(self, idx):
+    def get_dist_idx(self, idx, k=None):
         """
         computes the distance and the indices of the nearest neighbors for the vector at index idx.
         Args:
@@ -128,6 +128,8 @@ class DistCalculation:
         Returns:
             tuple: Two numpy arrays. The first one contains the distances to the nearest neighbors and the second one contains the indices of these neighbors.
         """
+        if k is None:
+            k = self.X.shape[0]
         D, I = self.index.search(self.X[idx:idx + 1], self.X.shape[0])
         return D[0, 1:], I[0, 1:]
 

### 2023-08-13 python/data-retrieval/concatenate-transfer-event-data.py
Restructure python folder

@@ -1,18 +1,18 @@
 import pandas as pd
 
 # Get Ethereum and Polygon subsets
-users = pd.read_csv('../data/subsets.csv')
+users = pd.read_csv('../../data/subsets.csv')
 polygon_addresses = users.loc[users['Polygon'] == 1, 'Address'].tolist()
 ethereum_addresses = users.loc[users['Ethereum'] == 1, 'Address'].tolist()
 
 """ERC-721"""
 # Ethereum
-ethereum_721 = pd.read_csv('../data/ethereum_erc721.csv')
+ethereum_721 = pd.read_csv('../../data/ethereum_erc721.csv')
 ethereum_721['isSetFrom'] = ethereum_721['from'].isin(ethereum_addresses)
 ethereum_721['isSetTo'] = ethereum_721['to'].isin(ethereum_addresses)
 ethereum_721 = ethereum_721.drop_duplicates()
 # Polygon
-polygon_721 = pd.read_csv('../data/polygon_erc721.csv')
+polygon_721 = pd.read_csv('../../data/polygon_erc721.csv')
 polygon_721['isSetFrom'] = polygon_721['from'].isin(polygon_addresses)
 polygon_721['isSetTo'] = polygon_721['to'].isin(polygon_addresses)
 polygon_721 = polygon_721.drop_duplicates()
@@ -24,12 +24,12 @@ if len(erc721) == len(polygon_721) + len(ethereum_721):
 
 """ERC-20"""
 # Ethereum
-ethereum_20 = pd.read_csv('../data/ethereum_erc20.csv')
+ethereum_20 = pd.read_csv('../../data/ethereum_erc20.csv')
 ethereum_20['isSetFrom'] = ethereum_20['from'].isin(ethereum_addresses)
 ethereum_20['isSetTo'] = ethereum_20['to'].isin(ethereum_addresses)
 ethereum_20 = ethereum_20.drop_duplicates()
 # Polygon
-polygon_20 = pd.read_csv('../data/polygon_erc20.csv')
+polygon_20 = pd.read_csv('../../data/polygon_erc20.csv')
 polygon_20['isSetFrom'] = polygon_20['from'].isin(polygon_addresses)
 polygon_20['isSetTo'] = polygon_20['to'].isin(polygon_addresses)
 polygon_20 = polygon_20.drop_duplicates()
@@ -47,12 +47,12 @@ if len(erc20) == len(ethereum_20) + len(polygon_20):
 
 """ERC-1155"""
 # Ethereum
[…]

### 2023-08-13 python/data-retrieval/create-intra-set-csvs.py

@@ -8,7 +8,7 @@ transfers = db['transfers']
 transactions = db['transactions']
 
 # Get list of active addresses on both networks
-users = pd.read_csv('../data/subsets.csv')
+users = pd.read_csv('../../data/subsets.csv')
 user_addresses = list(set(users.loc[users['Polygon'] == 1, 'Address']).union(users.loc[users['Ethereum'] == 1, 'Address']))
 
 ## Intra-set token transfers
@@ -21,7 +21,7 @@ transfer_df = pd.DataFrame(list(transfers.find(query_conditions)))
 
 # Drop duplicates
 transfer_df = transfer_df.drop(['_id', 'isSet', 'userAddress'], axis=1).drop_duplicates().reset_index(drop=True)
-transfer_df.to_csv('../data/token_transfers.csv')
+transfer_df.to_csv('../../data/intra_token_transfers.csv')
 
 
 ## Intra-set native asset transfers
@@ -35,4 +35,4 @@ transaction_df = pd.DataFrame(list(transactions.find(query_conditions)))
 
 # Drop duplicates
 transaction_df = transaction_df.drop(['_id'], axis=1).drop_duplicates().reset_index(drop=True)
-transaction_df.to_csv('../data/native_transfers.csv')
+transaction_df.to_csv('../../data/intra_native_transfers.csv')

### 2023-08-14 paper.tex
Update network-representation learning

@@
 \subsection{Intra-set asset transfers}
+\label{sec:intra-set}
 In this thesis, we want to employ entity clustering heuristics to determine the number of entities represented by the remaining 137,544 addresses.
@@
 
-\subsection{Graph-based network analysis}
-Token networks -> Victor, Casale Brunet
+\subsection{Network-representation learning - Node embeddings}
 
-%The set of addresses used in interactions characterize a users.
-Users with multiple accounts might interact with the same addresses from most of them.
-Furthermore, as users move funds between their personal addresses, they may unintetionally reveal their address clusters.
-Clustering experiments conducted on a transaction/transfer graph with nodes as addresses and edges as transactions/transfers.
-Rozemberczki provides a library of node embedding methods to discover address pairs that might belong to the same user.
-Preprocessing steps: transfers as undirected edges, remove loops and multi-edges, exlcude nodes outside the largest connected component.
-Resulting graph.
+According to \cite{Beres2020}, \textit{node embedding} methods form a class of network representation learning\footnote{Sometimes also referred to as ``graph representation learning``} methods that map graph nodes to vectors in a low-dimensional vector space.
+These methods aim to represent vertices with similar neighborhood structure by vectors that are close in the vector space.
+\newline
+\cite{Beres2020} first introduced this approach on a Ethereum transaction graph for the purpose of entity identification to pair Ethereum addresses associated with deposits and withdrawals from Tornado cash.
+Building on this, \cite{wu2022tutela} refined and expanded one particular node embedding method to deanonymize Ethereum users at scale.
+\newline
+The foundation for these node-embedding methods is an undirected graph where nodes are composed of distinct addresses, and an edge is placed between two nodes if there is a transaction between them.
+\newline
+To construct the network graph, we use the intra-set asset transfers as described in section \ref{sec:intra-set}.
+This differs from the approach taken by \cite{Beres2020} and \cite{wu2022tutela}.
+\cite{Beres2020} collected all transactions and token transfer events of their address set, but did not refine this data to only include intra-set asset transfers.
+\cite{wu2022tutela} do not operate on a specific address set, but use all Ethereum transactions to build the network graph, ignoring token transfer events.
+\newline %vielleicht erklären wieso wir es anders gemacht haben
+Addresses that interact with the same set of addresses in the asset transfer graph should be close in Euclidean distance.
+The reasons for this are twofold.
+For one, users with multiple accounts may interact with the same addresses or services from most of them.
+For another, as users move funds between their personal addresses, they may unintentionally reveal their address clusters.
+\newline
+\cite{karateclub} provide a variety of node embedding methods as a Python library\footnote{\url{https://github.com/benedekrozemberczki/karateclub}}.
+They further subdivide into neighborhood (proximity) preserving and structural node embeddings methods.
+We focus on the three methods that performed best in \cite{Beres2020} experiments, namely ``Diff2Vec`` \citep{rozemberczki2020difftovec}, ``Role2Vec`` \citep{ahmed2018roletovec}, and ``Deepwalk`` \citep{perozzi2014}.
+Diff2Vec and DeepWalk are both neighborhood preserving, while Role2Vec is a structural node embedding method.
+Explaining each method in detail would be out of scope for this thesis.
+However, we will briefly introduce the intuition behind each method and their main characteristics.
+
+All these methods use random walks/ a random process ...
+
+\textbf{Diff2Vec} % Neighborhood preserving 
+The intuition of Diff2Vec is to summarize a node by its neighborhood through a diffusion-like random process.
+Specifically, there are four steps to Diff2Vec: 1) Generating a diffusion graph, 2) sampling a node sequence, 3) extracting features, 4) learning a neural network embedding
+
+\textbf{DeepWalk}
+
+\textbf{Role2Vec} % Structural node embedding, Structural Node Level Embedding
+Random walks will likely visit nearby vertices first, which makes them
+suitable for finding communities, rather than roles (structural
+similarity). To overcome the above problems, we propose the Role2Vec
+framework which serves as a basis for generalizing many existing methods that use traditional random walks. Strucural feature matrix.
+
+Using the library described by \cite{karateclub} requires certain preprocessing steps for the network graph.
+Firstly, transactions must be treated as undirected edges.
+Secondly, self-transactions (loops) and multi-edges should be removed.
+Moreover, nodes outside the largest connected component are excluded.
+The resulting network graph has 51,566 nodes and 249,302 edges.
+
+It is worth noting that unlike \cite{wu2022tutela}'s approach, we decided not to include edge weights.
+This choice facilitated the easy application of Rozemberczki's library and eliminated the need to create a custom method.
+%used the class provided by Beres to do this
+
+Based on the network graph, we generate 128 dimensional representations (feature vectors) for the addresses using the three methods.
+Given an address/node embedding, to find its cluster/neighbors, we can search for the closest k vectors.
+In practice, we accomplish this efficiently using FAISS (Johnson et al., 2019).
+This will always return k addresses.
+ordered list
+
+Evaluation - run experiments ten times for each method and report the average rank of the target address.
+
+%Research in node embedding has been accelerated by Word2Vec, which is an embedding method for natural language processing. This approach has been extended to learn graph/network embeddings.
+
+%Rozemberczki provides a library of node embedding methods to discover address pairs that might belong to the same user.
 Applied 3 node embedding methods to this graph (Diff2Vec, Role2Vec and deep walk.
-\textbf{Node embeddings}
 
-Projects addresses to points in a low-dimensional vector space based on who it interacts with.
-In this vector space, adresses belonging to the same entity should be close together in Euclidean distance.
-
-Consider constructing an undirected graph from all Ethereum transactions where nodes are composed of distinct addresses, and an edge is placed between two nodes if there is a transaction between them.
-
-At this abstraction layer, we seek to learn a ``node embedding function``that projects a node to a d-dimensional vector representation.
+%At this abstraction layer, we seek to learn a ``node embedding function``that projects a node to a d-dimensional vector representation.
 Importantly I want this embedding to capture semantic information about the node, such as which other addresses it frequently interact with.
@@
 
-Given an address, to find its cluster, we can search for the closest k vectors in Rd.
-In practice, we accomplish this efficiently using FAISS (Johnson et al., 2019).
-This will always return k addresses.
+%Token networks -> Victor, Casale Brunet
 
-Node embedding methods form a class of network representation learning methods that map graph nodes to vectors in a low-dimensional space.
-They are designed to represent vertices with similar neighborhood structure by vectors that are close in the vector space.
-Intuitively, addresses that interact with the same set of addresses in the Ethereum transaction graph should be close in the embedded space.
-Research in node embedding has been catalyzed by Word2Vec, an embedding method for natural language processing.
-... In this work, we use these techniques on the Ethereum transaction graph to link addresses owned by the same user.
-...
-The set of addresses used in interactions characterize a user.
-Users with multiple accounts might interact with the same addresses or services from most of the.
-Furthermore, they may unintentionally reveal their address clusters.
-Our deanonymization methods are conducted on a transaction graph with nodes as Ethereum addresses and edges as transactions.
-From the library of \cite
-Diff2Vec, Role2Vec, DeepWalk \\
-Transaction Graph Analysis
-
-\subsection{Time-of-day transaction activity}
+\subsection{Time-of-day transaction activity and gas price selection}
 Transaction timestamps reveal the daily activity patterns of the account owner -> example
@@
 
-\subsection{Gas price distribution}
 Gas price definition, often set by the wallet software (slow, medium, fast), given the changes in traffic volume we normalice the gas price bxy the daily network average in our dataset.

### 2023-08-14 paper.tex
Update paper

@@
 \vfill
-\textbf{Keywords:} Keyword 1, Keyword 2, Keyword 3, Keyword 4.\\
+\textbf{Keywords:} Blockchain, Accounts, Clustering Heuristics, Entity Identification, Node Embedding Algorithms.\\
 \noindent\textbf{JEL:} X00, X00, X00
@@
 \subsection{ENS ground-truth pairs}
+\label{sec:ens}
 Similarly to \cite{Beres2020}, we use Ethereum Name Service (ENS) identifiers as ground truth information to evaluate some of the clustering methods.\newline
@@
 Probably the most well known example is Uniswap's UNI airdrop, where each address that interacted with the protocol until a specified cutoff date received a fixed amount of 400 UNI tokens\footnote{\url{https://blog.uniswap.org/uni}}.
-Often, these distribution mechanisms are not Sybil-resistant, leading to people creating multiple addresses in anticipation of an airdrop.
+Especially in the early days of DeFi, these distribution mechanisms were not Sybil-resistant, leading to people creating multiple addresses in anticipation of an airdrop.
 However, managing the tokens on all of these addresses is impractical, which is why they are often aggregated into one address.
 \citep{FV:17}
+
+Victor searches for aidrop events by ... This approach would be applicable to our dataset, however, we were not able to detect significant airdrop events.
+
+For completeness, we searched for the addresses that forwarded the UNI airdrop to another address. We found X addresses and would cluster those.
 
@@
 
-\subsection{Network-representation learning - Node embeddings}
+\subsection{Node embeddings}
 
@@
 \newline
-\cite{Beres2020} first introduced this approach on a Ethereum transaction graph for the purpose of entity identification to pair Ethereum addresses associated with deposits and withdrawals from Tornado cash.
+\cite{Beres2020} first introduced this approach on a Ethereum transaction graph for the purpose of entity identification to pair Ethereum addresses associated with Tornado cash deposits and withdrawals.
 Building on this, \cite{wu2022tutela} refined and expanded one particular node embedding method to deanonymize Ethereum users at scale.
@@
 \newline
-To construct the network graph, we use the intra-set asset transfers as described in section \ref{sec:intra-set}.
-This differs from the approach taken by \cite{Beres2020} and \cite{wu2022tutela}.
-\cite{Beres2020} collected all transactions and token transfer events of their address set, but did not refine this data to only include intra-set asset transfers.
-\cite{wu2022tutela} do not operate on a specific address set, but use all Ethereum transactions to build the network graph, ignoring token transfer events.
+To construct the network graph, we use the intra-set asset transfers described in section \ref{sec:intra-set}.
+This approach differs from the methodologies adopted by \cite{Beres2020} and \cite{wu2022tutela}.
+On one hand, \cite{Beres2020} collected all transactions and token transfer events of their address set, but did not refine this data to only include intra-set asset transfers.
+On the other hand, \cite{wu2022tutela} do not operate on a specific address set, but use all Ethereum transactions to build the network graph, ignoring token transfer events.
 \newline %vielleicht erklären wieso wir es anders gemacht haben
-Addresses that interact with the same set of addresses in the asset transfer graph should be close in Euclidean distance.
-The reasons for this are twofold.
-For one, users with multiple accounts may interact with the same addresses or services from most of them.
-For another, as users move funds between their personal addresses, they may unintentionally reveal their address clusters.
+Using the network graph, node embedding methods seek to learn a function that projects a node to a $d$-dimensional vector representation (also called feature vector).
+This is a way of simplifying the graph information by associating each node with a point in the Euclidean space.
+Various node embedding methods have been developed and applied to different domains.
+\citep{rozemberczki2020difftovec} \newline
+The intuition behind node-embedding approaches is that addresses which interact with the same set of addresses within the network graph should be close in Euclidean distance.
+\cite{Beres2020} cites two main reasons for this.
+Firstly, users with multiple accounts often interact with the same addresses or services from most of them.
+Secondly, when users move funds between their personal addresses, they may unintentionally reveal their address clusters.
 \newline
 \cite{karateclub} provide a variety of node embedding methods as a Python library\footnote{\url{https://github.com/benedekrozemberczki/karateclub}}.
-They further subdivide into neighborhood (proximity) preserving and structural node embeddings methods.
-We focus on the three methods that performed best in \cite{Beres2020} experiments, namely ``Diff2Vec`` \citep{rozemberczki2020difftovec}, ``Role2Vec`` \citep{ahmed2018roletovec}, and ``Deepwalk`` \citep{perozzi2014}.
+They categorize the methods into neighborhood (proximity) preserving and structural.
+\newline
+We focus on the three methods that performed best in \cite{Beres2020} experiments: ``Diff2Vec`` \citep{rozemberczki2020difftovec}, ``Role2Vec`` \citep{ahmed2018roletovec}, and ``Deepwalk`` \citep{perozzi2014}.
 Diff2Vec and DeepWalk are both neighborhood preserving, while Role2Vec is a structural node embedding method.
-Explaining each method in detail would be out of scope for this thesis.
-However, we will briefly introduce the intuition behind each method and their main characteristics.
+Although all of these methods utilize random walks to capture graph information, they differ in their approaches to leveraging these random walks for constructing Euclidean feature vectors.
+A detailed explanation of each method is beyond the scope of this thesis.
+For a concise overview of Diff2Vec, please refer to \cite{wu2022tutela}.
+The interested reader can consult the originial publications.
+\newline
+Using the library described by \cite{karateclub} requires certain preprocessing steps for the network graph.
+Transactions must be treated as undirected edges and loops (self-transactions) and multi-edges should be removed.
+Moreover, nodes outside the largest connected component are excluded.
+The resulting network graph includes 51,566 nodes and 249,302 edges.
+\newline
+It is worth noting that unlike \cite{wu2022tutela}, we decided not to include edge weights.
+For instance, if Alice sent Bob Ether 3 times and Bob sent Alice Ether 2 times, the edge weight would correspond to 5.
+This choice facilitated the application of \cite{rozemberczki2020difftovec}'s library and eliminated the need to create a custom method.
+\newline
+Based on our network graph, we generate 128-dimensional feature vectors for each address and method. \newline
+Given an node embedding, we can search for the closest $k$ vectors to any given vector.
+As in \cite{wu2022tutela}, we accomplish this using FAISS (Facebook AI Similarity Search) by \cite{johnson2019faiss}, which always returns a list of $k$ nodes, ranked by their Euclidean distance to the given node\footnote{In our case, we set k as the total number of nodes in the network}.
+\newline
+To evaluate and the three node embedding algorithms, we use ENS address pairs described in \ref{sec:ens} as ground truth.
+We run each node embedding method ten times and report the average rank of the target address.
+For comparison, we  compute the mean, median and standard deviation of the average rank for each method.
 
-All these methods use random walks/ a random process ...
-
+\iffalse
 \textbf{Diff2Vec} % Neighborhood preserving 
@@
 Specifically, there are four steps to Diff2Vec: 1) Generating a diffusion graph, 2) sampling a node sequence, 3) extracting features, 4) learning a neural network embedding
-
 \textbf{DeepWalk}
-
 \textbf{Role2Vec} % Structural node embedding, Structural Node Level Embedding
@@
 
-Using the library described by \cite{karateclub} requires certain preprocessing steps for the network graph.
-Firstly, transactions must be treated as undirected edges.
-Secondly, self-transactions (loops) and multi-edges should be removed.
-Moreover, nodes outside the largest connected component are excluded.
-The resulting network graph has 51,566 nodes and 249,302 edges.
+Research in node embedding has been accelerated by Word2Vec, which is an embedding method for natural language processing. This approach has been extended to learn graph/network embeddings.
 
-It is worth noting that unlike \cite{wu2022tutela}'s approach, we decided not to include edge weights.
-This choice facilitated the easy application of Rozemberczki's library and eliminated the need to create a custom method.
-%used the class provided by Beres to do this
-
-Based on the network graph, we generate 128 dimensional representations (feature vectors) for the addresses using the three methods.
-Given an address/node embedding, to find its cluster/neighbors, we can search for the closest k vectors.
-In practice, we accomplish this efficiently using FAISS (Johnson et al., 2019).
-This will always return k addresses.
-ordered list
-
-Evaluation - run experiments ten times for each method and report the average rank of the target address.
-
-%Research in node embedding has been accelerated by Word2Vec, which is an embedding method for natural language processing. This approach has been extended to learn graph/network embeddings.
-
-%Rozemberczki provides a library of node embedding methods to discover address pairs that might belong to the same user.
-Applied 3 node embedding methods to this graph (Diff2Vec, Role2Vec and deep walk.
-
-%At this abstraction layer, we seek to learn a ``node embedding function``that projects a node to a d-dimensional vector representation.
-Importantly I want this embedding to capture semantic information about the node, such as which other addresses it frequently interact with.
-To do so, we leverage popular graph representation learning algorithms.
-(Grover and Leskovec, 2016; Rozemberczki and Sarkar, 2018).
-In particular, we focus on Diff2Vec, Role2Vec and
-
-%Token networks -> Victor, Casale Brunet
+Token networks -> Victor, Casale Brunet
+\fi
 
 \subsection{Time-of-day transaction activity and gas price selection}
+
+In addition to node embedding methods on Ethereum transaction graphs, \cite{Beres2020} propose  clustering heuristics based on time-of-day transaction activity and gas price distribution. \newline
+Time-of-day transaction activity uses all transaction timestamps initiated by a given address.
+These UNIX timestamps are converted to hours of the day.
+Beres argues that this may reveal daily activity patterns of the account owner.
+He represents an address by a vector including the mean, median and standard deviation, as well as a activity histogram divided into 4-6 hour bins.
+
+Similarly, he argues that users may also reveal patterns.
+
 Transaction timestamps reveal the daily activity patterns of the account owner -> example
-Given the set of timestamps, an account is represented by the vector including the mean, median and standard deviation, as well as the time-of-day activity histogram dividid into $b_{hour}$ bins.
-We chose 50 bins (from beres)
+Given the set of timestamps, an account is represented by the vector including the mean, median and standard deviation, as well as the time-of-day activity histogram divided into $b_{hour}$ bins.
+Beres chose 50 bins.
 
+Before Ethereum 1559, user would set the gas price manually.
 Gas price definition, often set by the wallet software (slow, medium, fast), given the changes in traffic volume we normalice the gas price bxy the daily network average in our dataset.
@@
 
-\subsection{Own heuristics}
+We will not use/apply both methods since their performance is significantly worse than node embeddings.
+However, we tested a two-step approach.
+First we used node embedding to find the k nearest neighbors.
+Using this, we ordered the addresses by their euclidean distance based on time-of-day and gas price feature vectors.
+We checked if applying this two step approach significantly improved the average rank.
+-> do not show results now, just say that what we want to do.
+
+\subsection{Tornado cash heuristics}
+Address match: Same address making a deposit and withdrawal from the same tornado pool
+Unique gas price: Prior to EIP-1559, Ethereum users could specify the gas price when making a deposit or withdrawal to a Tornado Cash pool Those who do so tend to specify gas prices that are identidal for deposit and withdrawal transactions.
+
+Linked addresses: Addresses that interacted, two sets, one corresponding to the unique Tornado Cash deposit addresses and one to the unique Tornado Cash withdraw addresses.
+Find transactions betwee transactions between addresses of each set.
+
+Multiple denomination: studies an address' history of transactions. Deposit portfolio == withdraw portfolio. Example:
+
+Torn minting -> not explain
+
+\subsection{LAND transfers}
+In addition to the existing clustering heuristics, we propose our own one.
+We argue, given the high value of land parcels, that if someone sends his LAND NFT to another address without any compensation, there is a large probability that this user transfers LAND between his wallets.
 
@@
 \section{Data Analysis}
+Self-authorization
+Airdrop
+Node embeddings
 
@@
 
-Database
-
 %% Table
@@
   \centering
-  \footnotesize
-  \begin{tabular}{l p{9cm} cc}
-    \hline\hline
-    Field & Description & Transfers & Transactions\\ \hline
-    \texttt{hash} & Transaction hash & \checkmark & \checkmark \\
-    \texttt{timeStamp} & Timestamp in seconds from the UNIX epoch & \checkmark & \checkmark \\
-    \texttt{gasUsed} & Amount of gas used by the transaction & \checkmark & \checkmark \\
-    \texttt{gasPrice} & Gas price specified for this transaction & \checkmark & \checkmark \\
-    \texttt{nonce} &  \textbullet{ }EOAs: \newline \textbullet{ }CAs: & \checkmark & \checkmark \\
-    \texttt{from} & \textbullet{ }Transactions: Address initiating the transaction\newline \textbullet{ }Transfers: Sender address & \checkmark & \checkmark \\
-    \texttt{to} & \textbullet{ }The recipient's hexadecimal address.
-For transactions (native asset/token transfer or contract execution) \newline \textbullet{ }Transfers: Recipient address & \checkmark & \checkmark\\
-    \texttt{value} &  \textbullet{ }Transactions: Amount of native asset sent \newline \textbullet{ }Transfers: Amount of token sent (\texttt{NaN} for NFTs)  & \checkmark & \checkmark\\
-    \texttt{tokenID} &  Token identifier (\texttt{NaN} for ERC-20 tokens) & \checkmark & \\
-    \texttt{input} & Calldata & Contract execution or deployment instructions & \checkmark \\
-    \texttt{functionName} & Name of the function called, added by Etherscan / Polygonscan (\texttt{NaN} if not available) & \checkmark & \\
-    \texttt{type} & Token standard. Created manually to combine token transfer events from different standards & \checkmark & \\
-    \texttt{chainName} & Name of the blockchain. Created manually to combine Ethereum and Polygon data & \checkmark & \checkmark\\
-    \hline\hline
+  \tiny
+  \begin{tabular}{ll p{4cm} l}
+    \hline
+    \textbf{Collection} & \textbf{Fields} & \textbf{Description} & \textbf{Example} \\ \hline
+    Transactions & \texttt{\_id} & Unique identifier & 64b3c65ed2daf924bfdce72b
+ \\
+    (16,184,993 rows) & \texttt{hash} & Transaction hash & 0x8d9490e9f0992e68490cfcb126e76290eca3bf668a... \\
+     & \texttt{timeStamp} & Timestamp in seconds from the UNIX epoch &  1657777314\\
+     & \texttt{gasUsed} & Amount of gas used by the transaction &  144176  \\
+     & \texttt{gasPrice} & Gas price specified for this transaction in Wei &  12449848873 \\
+     & \texttt{nonce} &   &   \\
+     & \texttt{from} & Address initiating the transaction &   \\
+     & \texttt{to} & Target (either native asset transfer or function call) &  \\
+     & \texttt{value} & The amount of Ether/Matic in Wei & 500 \\
+     & \texttt{input} & Calldata & 0x095ea7b30000000000000000000000001111111254fb6c44bac0bed2854e76f90643097dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff \\
+     & \texttt{functionName} & added by Etherscan & approve(address spender, uint256 rawAmount) \\
+     & \texttt{chainName} & Chain indicator & Ethereum or Polygon \\
+    \hline
+    Transfers & \texttt{\_id} & see above & see above\\
+    (36.4M rows) & \texttt{hash} & see above & see above \\
+     & \texttt{timeStamp} & see above & see above\\
+     & \texttt{gasUsed} & see above &  see above\\
+     & \texttt{gasPrice} & see above & see above \\
+     & \texttt{nonce} &  see above & see above \\
+     & \texttt{from} &  Sender address & see above \\
+     & \texttt{to} &  Recipient address & see above \\
+     & \texttt{value} & Amount of tokens transferred in Wei, only for fungible or semi-fungible tokens & 10000000000000000 or NaN (ERC-721) \\
+     & \texttt{tokenID} &  Identifier of the NFT or semi-fungible token &  or NaN (ERC20) \\
+     & \texttt{contractAddress} & The token contract address &  0xc02aaa39b223fe8d0a0e5c4f27ead9083c756cc2 \\
+     & \texttt{tokenName} & The specified token name &  Wrapped Ether\\
+     & \texttt{tokenType} & Token standard indicator &  20 or 721 or 1155\\
+     & \texttt{chainName} & see above &  see above \\
+     & \texttt{isSet} & Indicator if from or to address are from address set &  from or to \\
+     & \texttt{userAddress} & Address of interested user & 0x000000085d9a759bb5c3d459d638739c0f48deb0\\
+    \hline
   \end{tabular}
-  \caption{Database Collection Fields}
+  \caption{Database/Dataset Description}
   \label{tbl:database_schema}
@@
 
-Distinction: Transaction is a message sent from an externally owned account
-((isSet, userAddress))
-%%
+%Distinction: Transaction is a message sent from an externally owned account
 

### 2023-08-14 paper.tex
Update airdrop multi participation & time-of-day

@@
 The ``self authorization`` heuristic, proposed by \cite{FV:17}, suggests that users might authorize another address they own, possibly for risk distribution across several addresses or for testing purposes.
-\citep{FV:17} \newline
+\newline
 Given our dataset includes all address transactions, we can easily employ this heuristic. %Since all the addresses' transactions are available in our dataset, we are able to apply this heuristic.
@@
 Probably the most well known example is Uniswap's UNI airdrop, where each address that interacted with the protocol until a specified cutoff date received a fixed amount of 400 UNI tokens\footnote{\url{https://blog.uniswap.org/uni}}.
-Especially in the early days of DeFi, these distribution mechanisms were not Sybil-resistant, leading to people creating multiple addresses in anticipation of an airdrop.
-However, managing the tokens on all of these addresses is impractical, which is why they are often aggregated into one address.
-\citep{FV:17}
-
-Victor searches for aidrop events by ... This approach would be applicable to our dataset, however, we were not able to detect significant airdrop events.
-
-For completeness, we searched for the addresses that forwarded the UNI airdrop to another address. We found X addresses and would cluster those.
+Especially in the early days of airdrops, these distribution mechanisms were not Sybil-resistant, leading to people creating multiple addresses in anticipation of an airdrop.
+However, \cite{FV:17} argues that managing the tokens on all of these addresses is impractical, which is why they are often aggregated into one address.
+He finds around 500 same-source, fixed amount token distribution events with at least 1,000 recipients while also taking into account the block difference between the individual aidrop token transfers.
+He defines multi-participation when two airdrop recipients forward their tokens to a single address.
+Since we do not have a whole view of the airdrop distribution events, we are not able to find them using our data.
+One possible approach would be to manually select known airdrops.
+However, this process takes very long and is not guaranteed to cluster a lot of addresses, since most new airdrop events were made with some kind of sybil-resistance.
+Nevertheless, to test this approach we searched for addresses that forwarded the UNI airdrop to another address.
+We found X addresses that did that, but no two addresses forwarding the amount to a third address.
 
@@
 The main challenge lies in identying airdrops. To do so, we first examine all same-source, fixed amount token distributions.
-
 \fi
@@
 For a concise overview of Diff2Vec, please refer to \cite{wu2022tutela}.
-The interested reader can consult the originial publications.
+The interested reader may consult the originial publications.
 \newline
+With our intra-set asset transfer data (\ref{sec:intra-set}) and ENS address pairs (\ref{sec:ens}), we were able to apply and evaluate the node embedding methods described above.
 Using the library described by \cite{karateclub} requires certain preprocessing steps for the network graph.
@@
 It is worth noting that unlike \cite{wu2022tutela}, we decided not to include edge weights.
-For instance, if Alice sent Bob Ether 3 times and Bob sent Alice Ether 2 times, the edge weight would correspond to 5.
+For instance, if Alice sent Bob Ether three times and Bob sent Alice Ether two times, the edge weight would correspond to five.
 This choice facilitated the application of \cite{rozemberczki2020difftovec}'s library and eliminated the need to create a custom method.
@@
 Given an node embedding, we can search for the closest $k$ vectors to any given vector.
-As in \cite{wu2022tutela}, we accomplish this using FAISS (Facebook AI Similarity Search) by \cite{johnson2019faiss}, which always returns a list of $k$ nodes, ranked by their Euclidean distance to the given node\footnote{In our case, we set k as the total number of nodes in the network}.
+As in \cite{wu2022tutela}, we accomplish this using FAISS (Facebook AI Similarity Search) by \cite{johnson2019faiss}, which always returns a list of $k$ nodes, ranked by their Euclidean distance to the given node\footnote{We set $k = 51,566$, the total number of nodes in the network graph}.
 \newline
-To evaluate and the three node embedding algorithms, we use ENS address pairs described in \ref{sec:ens} as ground truth.
+To evaluate the three node embedding algorithms, we use our ENS address pairs as ground truth.
 We run each node embedding method ten times and report the average rank of the target address.
@@
 
-In addition to node embedding methods on Ethereum transaction graphs, \cite{Beres2020} propose  clustering heuristics based on time-of-day transaction activity and gas price distribution. \newline
-Time-of-day transaction activity uses all transaction timestamps initiated by a given address.
-These UNIX timestamps are converted to hours of the day.
-Beres argues that this may reveal daily activity patterns of the account owner.
-He represents an address by a vector including the mean, median and standard deviation, as well as a activity histogram divided into 4-6 hour bins.
-
-Similarly, he argues that users may also reveal patterns.
-
-Transaction timestamps reveal the daily activity patterns of the account owner -> example
-Given the set of timestamps, an account is represented by the vector including the mean, median and standard deviation, as well as the time-of-day activity histogram divided into $b_{hour}$ bins.
-Beres chose 50 bins.
-
-Before Ethereum 1559, user would set the gas price manually.
-Gas price definition, often set by the wallet software (slow, medium, fast), given the changes in traffic volume we normalice the gas price bxy the daily network average in our dataset.
-Make example.
-Given the normalized gas prices of the transactions sent, an account is represented by the mean, median and standard deviation, as well as the normalized gas price histogram divided into $b_{gas}$ bins.
-We chose 6 bins (4 hour intervals) according to Beres.
-
-We will not use/apply both methods since their performance is significantly worse than node embeddings.
-However, we tested a two-step approach.
-First we used node embedding to find the k nearest neighbors.
-Using this, we ordered the addresses by their euclidean distance based on time-of-day and gas price feature vectors.
-We checked if applying this two step approach significantly improved the average rank.
--> do not show results now, just say that what we want to do.
+Apart from the node embedding methods applied to Ethereum transaction graphs, \cite{Beres2020} suggested employing clustering heuristics based on time-of-day transaction activity and gas price distribution.
+\newline
+Time-of-day transaction activity considers all transaction timestamps initiated by a particular address.
+These UNIX timestamps are transformed into hour-of-the-day based values.
+\cite{Beres2020} argues that this may expose daily activity patterns of the account owner.
+Address are represented by a vector including the mean, median and standard deviation, as well as a activity histogram divided into 4-6 hour bins.
+\newline
+Additionaly, they argue that users may reveal patterns when choosing their gas price.
+Prior to EIP-1559, users could set the gas price manually.
+In practice, most wallet user interfaces offered three levels of gas prices: slow, average, and fast.
+Selecting the the fast option would ensure almost immediate inclusion in the blockhain.
+They normalize the gas price by the daily network average to account for the changes in Ethereum traffic volume.
+The combination of gas price levels that a user select forms their personal gas price profile.
+An account is represented by a vector including the mean, median, and standard deviation of the normalized gas prices of the transactions sent.
+Additionally, the normalized gas price histogram divided into 50 bins is used, which they determined to be optimal for clustering performance.
+\newline
+We will not employ both methods due to their significantly poorer performance compared to node embeddings.
+Nevertheless, we tested a two-step approach: In the first step, we implemented node embedding methods to find the k nearest neighbors.
+In the second step, we ordered the addresses by their Euclidean distance derived from the time-of-day and/or gas price feature vectors.
+We analyzed the impact of this two-step approach on the average rank of a target address.
 
@@
 Node embeddings
+
+\begin{table}[h!]
+\scriptsize
+  \centering
+  \begin{tabular}{lllll}
+    \hline
+	\textbf{ENS domain name} &  & \textbf{Average Rank} &\\
+	  & Diff2Vec & Role2Vec & DeepWalk \\
+	\hline
+	blabla.eth & 2 & 3 & 4 \\
+	blabla.eth & 2 & 3 & 4 \\
+	blabla.eth & 2 & 3 & 4 \\
+	blabla.eth & 2 & 3 & 4 \\
+    \hline
+  \end{tabular}
+  \caption{Database/Dataset Description}
+  \label{tbl:database_schema}
+\end{table}
 

### 2023-08-14 paper.tex
Update clustering heuristics section

@@
 Given an node embedding, we can search for the closest $k$ vectors to any given vector.
-As in \cite{wu2022tutela}, we accomplish this using FAISS (Facebook AI Similarity Search) by \cite{johnson2019faiss}, which always returns a list of $k$ nodes, ranked by their Euclidean distance to the given node\footnote{We set $k = 51,566$, the total number of nodes in the network graph}.
+As in \cite{wu2022tutela}, we accomplish this using FAISS (Facebook AI Similarity Search), developed by \cite{johnson2019faiss}, which always returns a list of $k$ nodes, ranked by their Euclidean distance to the given node\footnote{We set $k = 51566$, the total number of nodes in the network graph}.
 \newline
@@
 
-Apart from the node embedding methods applied to Ethereum transaction graphs, \cite{Beres2020} suggested employing clustering heuristics based on time-of-day transaction activity and gas price distribution.
+Apart from the node embedding methods applied to Ethereum transaction graphs, \cite{Beres2020} suggest employing clustering heuristics based on time-of-day transaction activity and gas price distribution.
 \newline
-Time-of-day transaction activity considers all transaction timestamps initiated by a particular address.
+\textit{Time-of-day transaction activity} considers all transaction timestamps initiated by a particular address.
 These UNIX timestamps are transformed into hour-of-the-day based values.
-\cite{Beres2020} argues that this may expose daily activity patterns of the account owner.
-Address are represented by a vector including the mean, median and standard deviation, as well as a activity histogram divided into 4-6 hour bins.
+\cite{Beres2020} argue that account owners may expose daily activity patterns and represent addresses by a vector including the mean, median and standard deviation, as well as an activity histogram divided into 4-6 hour bins.
 \newline
-Additionaly, they argue that users may reveal patterns when choosing their gas price.
+Additionaly, the \textit{gas price distribution} heuristic leverages the possibility of users revealing patterns when choosing their gas price.
 Prior to EIP-1559, users could set the gas price manually.
 In practice, most wallet user interfaces offered three levels of gas prices: slow, average, and fast.
-Selecting the the fast option would ensure almost immediate inclusion in the blockhain.
+Selecting the the fast option would ensure almost immediate inclusion in the blockchain.
 They normalize the gas price by the daily network average to account for the changes in Ethereum traffic volume.
@@
 We will not employ both methods due to their significantly poorer performance compared to node embeddings.
-Nevertheless, we tested a two-step approach: In the first step, we implemented node embedding methods to find the k nearest neighbors.
-In the second step, we ordered the addresses by their Euclidean distance derived from the time-of-day and/or gas price feature vectors.
+Nevertheless, we test a two-step approach: In the first step, we implemented Diff2Vec to find the 10 nearest neighbors.
+In the second step, we ordered the remaining addresses by their Euclidean distance derived from the time-of-day and/or gas price feature vectors.
 We analyzed the impact of this two-step approach on the average rank of a target address.
@@
 \subsection{LAND transfers}
-In addition to the existing clustering heuristics, we propose our own one.
+In addition to the existing clustering heuristics, we propose our heuristic utilizing transfers of high-value NFTs such as LAND.
 We argue, given the high value of land parcels, that if someone sends his LAND NFT to another address without any compensation, there is a large probability that this user transfers LAND between his wallets.
@@
   \centering
-  \begin{tabular}{lllll}
+  \begin{tabular}{llll}
     \hline
-	\textbf{ENS domain name} &  & \textbf{Average Rank} &\\
-	  & Diff2Vec & Role2Vec & DeepWalk \\
+	\textbf{ENS domain name} & \textbf{Diff2Vec} & \textbf{Role2Vec} & \textbf{DeepWalk} \\
 	\hline
-	blabla.eth & 2 & 3 & 4 \\
-	blabla.eth & 2 & 3 & 4 \\
-	blabla.eth & 2 & 3 & 4 \\
-	blabla.eth & 2 & 3 & 4 \\
+	anisofim.eth & 2.5 & 6.2 & 2.7 \\
+	arisalzberg.eth & 577.3 & 33.3 & 58.8 \\
+	atearnz.eth & 2.8 & 2.5 & 3.3 \\
+	awedjob.eth & 106.8 & 71.1 & 20.1 \\
+	captvicky.eth & NaN & NaN & NaN \\
+	disruptor.eth & 11.1 & 3.0 & 1.4 \\
+	dragonkiller.eth & 30.7 & 1.0 & 1.0 \\
+	eibriel.eth & 44.3 & 91.2 & 545.4 \\
+	epdrabbit.eth & 16.3 & 10.4 & 4.1 \\
+	erikarand.eth & 1.0 & 1.0 & 1.0 \\
+	hyperspek.eth & 129.1 & 10.0 & 605.4 \\
+	jamesmillerblog.eth & NaN & NaN & NaN \\
+	jasonhsu.eth & 1.0 & 1.0 & 1.8 \\
+	joeyz.eth & 1.9 & 1.0 & 1.0 \\
+	keastie.eth & 10.4 & 1.0 & 18.2 \\
+	linkg.eth & 4.0 & 1.0 & 10.3 \\
+	lulox.eth & 4.2 & 1.5 & 27.2 \\
+	maruudn.eth & 5.7 & 5.6 & 108.5 \\
+	maryana.eth & 52.3 & 373.8 & 9.0 \\
+	meanboss.eth & 9.0 & 9.0 & 51.8 \\
+	metatiger.dcl.eth & 474.2 & 86.7 & 2.4 \\
+	mgdivingnz.eth & 1.7 & 5.0 & 1.0 \\
+	mrcryp.eth & 2.7 & 1.0 & 2.3 \\
+	nicebhaiya.eth & 1.3 & 3.4 & 2.4 \\
+	niceguy.eth & 1.0 & 1.0 & 2.2 \\
+	ornellaweb3.eth & 3.7 & 2.0 & 284.0 \\
+	pinkboots.eth & 16.9 & 14.4 & 2.2 \\
+	remx.eth & 3.6 & 2.6 & 1.7 \\
+	rileybeans.eth & 1.5 & 2.0 & 1.6 \\
+	robertjames.eth & 2.7 & 1.0 & 1.1 \\
+	rsantos.eth & 2.0 & 13.6 & 101.2 \\
+	sannin.eth & 64.8 & 1.1 & 1.6 \\
+	smileface.eth & 3.0 & 19.3 & 1.7 \\
+	theartcollection.eth & 11.0 & 5.6 & 3.4 \\
+	turkii13.eth & 52.1 & 68.9 & 47.3 \\
+	tweetious.eth & 10.3 & 4.0 & 227.0 \\
+    \hline
+    Mean & 46.038 & 28.073 & 62.084 \\
+    Median & 4.2 & 3.4 & 3.3 \\
+    Standard deviation & 120.504 & 68.814 &  139.932\\
+    Within 5 nearest neighbors & 17 (0.5) & 19 (0.56) & 20 (0.59) \\
+    Within 10 nearest neighbors & 19 (0.56) & 24 (0.71) & 21 (0.62)\\
     \hline
   \end{tabular}
-  \caption{Database/Dataset Description}
-  \label{tbl:database_schema}
+  \caption{Average Rank of ENS Domain Names for Different Embedding Methods, Addresses outside of largest connected component have a NaN value}
+  \label{tbl:ENS_Domain_Ranks}
 \end{table}

### 2023-08-15 paper.tex
Add figures and update Analysis/Clustering heuristics

@@
 Prof. Dr. Fabian Schär \\ 
-Credit Suisse Asset Management (Schweiz) Professor for \\ 
-Distributed Ledger Technologies and Fintech \\
+Professor for Distributed Ledger Technologies and Fintech \\
 Center for Innovative Finance, University of Basel
@@
  addresses outside of it, e.g., that were not registered in Decentraland during the given time frame. \newline
-Furthermore, we introduce our own heuristics for identifying address clusters and evaluate their suitability for implementation in other contexts.
+Furthermore, we introduce our own heuristic for identifying address clusters and evaluate its suitability for implementation in other contexts.
 %Anwenden/discuss and evaluate existing heuristics to my specific address set.
@@
 	\includegraphics[width=0.6\textwidth]{../figures/venn_diagram.png}
-	\caption{Venn Diagram of address subsets}
+	\caption{Address Subsets Visualized in a Venn Diagram}
 	\label{fig:Venn}
@@
 \newline
-To achieve this, we often only need to consider transactions or token transfer events where both the ``\texttt{from}`` (sender) and the ``\texttt{to}`` (recipient) address are within the address set.
+To achieve this, we often only %need to
+consider transactions or token transfer events where both the ``\texttt{from}`` (sender) and the ``\texttt{to}`` (recipient) address are within the address set.
 We call this reduced dataset ``intra-set asset transfers``.
@@
 \newline
-The intra-set asset transfer dataset is mainly used to generate the network graphs (see section xx).
+The intra-set asset transfer dataset is mainly used to generate the network graphs (see Section \ref{sec:node}). %used for the node embedding methods
 When clustering addresses using graph-based approaches, this has the advantage that we do not need to differentiate between EOA and smart contract account later on.
@@
 \subsection{Node embeddings}
+\label{sec:node}
 
@@
 \textit{Time-of-day transaction activity} considers all transaction timestamps initiated by a particular address.
-These UNIX timestamps are transformed into hour-of-the-day based values.
-\cite{Beres2020} argue that account owners may expose daily activity patterns and represent addresses by a vector including the mean, median and standard deviation, as well as an activity histogram divided into 4-6 hour bins.
-\newline
+These UNIX timestamps are transformed into hour-of-the-day-based values.
+The authors argue that account owners may expose daily activity patterns and represent addresses by a vector including the mean, median and standard deviation, as well as an activity histogram divided into 4-6 hour bins \citep{Beres2020}.
+Figure \ref{fig:ToD} illustrates the time-of-day activity histogram and kde for a selected ENS address pair, divided into two hour intervals.\newline
 Additionaly, the \textit{gas price distribution} heuristic leverages the possibility of users revealing patterns when choosing their gas price.
-Prior to EIP-1559, users could set the gas price manually.
+Prior to EIP-1559\footnote{\url{https://eips.ethereum.org/EIPS/eip-1559}}, users could set the gas price manually.
 In practice, most wallet user interfaces offered three levels of gas prices: slow, average, and fast.
 Selecting the the fast option would ensure almost immediate inclusion in the blockchain.
-They normalize the gas price by the daily network average to account for the changes in Ethereum traffic volume.
+To account for the changes in Ethereum traffic volume, the gas price is normalized by the daily network average.
 The combination of gas price levels that a user select forms their personal gas price profile.
-An account is represented by a vector including the mean, median, and standard deviation of the normalized gas prices of the transactions sent.
-Additionally, the normalized gas price histogram divided into 50 bins is used, which they determined to be optimal for clustering performance.
-\newline
+An account is represented by a vector including the mean, median, and standard deviation and a normalized gas price histogram divided into 50 bins, which they determined to be optimal for clustering performance.
+\citep{Beres2020} \newline
 We will not employ both methods due to their significantly poorer performance compared to node embeddings.
@@
 
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=0.8\textwidth]{../figures/time-of-day-activity.png}
+	\caption{Time-of-day activity histogram and kde}
+	\label{fig:ToD}
+\end{figure}
+
 \subsection{Tornado cash heuristics}
-Address match: Same address making a deposit and withdrawal from the same tornado pool
-Unique gas price: Prior to EIP-1559, Ethereum users could specify the gas price when making a deposit or withdrawal to a Tornado Cash pool Those who do so tend to specify gas prices that are identidal for deposit and withdrawal transactions.
 
-Linked addresses: Addresses that interacted, two sets, one corresponding to the unique Tornado Cash deposit addresses and one to the unique Tornado Cash withdraw addresses.
-Find transactions betwee transactions between addresses of each set.
+\cite{wu2022tutela} proposed five heuristics targeted at Tornado cash, highlighting that careless user behavior can still reveal identity, despite using a mixer.
+The heuristics they identified are as follows: \newline
+``Address match`` refers to instances where individuals use the same address for both depositing and withdrawing from the Tornado pool.
+``Unique gas price`` involves users selecting a distinct (specific) gas price for both their deposit and withdrawal transactions (prior to EIP-1559).
+``Linked ETH addresses`` examines whether a deposit address has interacted with a withdrawal address outside of Tornado Cash.
+``Multiple denomination`` assesses an address' transaction history; two addresses with matching deposit and withdrawal portfolios are considered a pair.
+``Torn minting`` identifies a specific user behavior when withdrawing so-called Anonymity points, an incentive scheme reward for increasing the anonymity set when depositing assets into Tornado cash.
 
-Multiple denomination: studies an address' history of transactions. Deposit portfolio == withdraw portfolio. Example:
-
-Torn minting -> not explain
+We found only 2 Tornado cash withdrawal transactions within our dataset.
 
 \subsection{LAND transfers}
-In addition to the existing clustering heuristics, we propose our heuristic utilizing transfers of high-value NFTs such as LAND.
-We argue, given the high value of land parcels, that if someone sends his LAND NFT to another address without any compensation, there is a large probability that this user transfers LAND between his wallets.
+In addition to the existing clustering heuristics, we propose our own heuristic based on transfers of high-value NFTs such as LAND.
+We argue that, given the high value of Decentraland land parcels, there is a high probability that addresses are controlled by the same entity when LAND is transferred without any compensation.
+A user might perform such transfers to rearrange their LAND holdings, e.g., by upgrading to a more secure wallet implementation.
+\newline
+The primary challenge of this approach is to identify LAND transfers without any compensation.
+To accomplish this, we identify token or native asset transfers that took place within the same transaction as a LAND transfer.
+Upon manually examining various implementations of LAND trades on the most popular NFT marketplace contracts, we identified a pattern where the user address appears both in the from and to fields if a trade occurred.
+An example is shown on Figure \ref{fig:LAND_example}.
+In the case of pure LAND transfers, the sending and receiving addresses are the same for all transfers within a transaction.
+However, this approach does not consider other LAND trading schemes, including off-chain compensation or non-atomic (within multiple transactions) trade settlement.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=\textwidth]{../figures/land-opensea.png}
+	\caption{LAND trade on Opensea, Source: \url{https://etherscan.io/tx/0x2c2a70114e9080596bf5da6ad9c9b9f6d7e4c85a9d3b06e992f7248f9457a2ec}}
+	\label{fig:LAND_example}
+\end{figure}
 
@@
 \section{Data Analysis}
-Self-authorization
-Airdrop
-Node embeddings
+This section analyzes clustering heuristics applicable to our address set using the collected data.
+These include self-authorization, node embedding, and our proposed approach involving LAND transfers.
+
+\subsection{Self-authorization}
+
+For this clustering heuristic, we analyze the transaction data of the addresses, focusing on the transaction's ``calldata``.
+The first four bytes of the calldata represent the selector of the function signature, which specifies the smart contract function to be invoked.
+\newline
+\textit{First}, we query all transactions that begin with a function signature related to the approval functions corresponding to ERC-20, ERC-721 and ERC-1155 token standards.
+This step helps us identify all approval transactions.
+\newline
+\textit{Second}, we extract the approved address (spender address), which is always located at the same position within the calldata due to token standardization.
+We then record the spender address in a new field within our dataframe.
+\newline
+\textit{Third}, we implement two filters on the approval transactions.
+The first filter checks if the spender address is part of our address set, and the second ensures that the spender address is different from the address initiating the transaction, thus eliminating self-approvals, which may occur due to a user interface bug or testing transactions.
+\newline
+\textit{Fourth}, we group the remaining approvals by the initiating address and proceed to form the clusters.
+
+We identified 16 clusters across 126 self-authorizing transactions, comprising 115 distinct addresses.
+After manual inspection, we excluded a cluster containing 80 addresses that had all approvals issued by the same address for the same token contract.
+The token contract represents a collection of wearable NFTs on Polygon called ``Renaissance King by René Mäkelä`` and may use an uncommon or even faulty token distribution/minting scheme.
+\newline Ultimately, we discovered 35 addresses associated with 15 distinct entities.
+
+\subsection{Node embeddings}
+
+1. Show that we tested different datasets to build network graph, best performing was intra-set asset transfers\\
+2. Evaluated the performance by average rank for the three methods, show results, describe how this method may be flawed/ why maybe not ideal\\
+3. Show how we clustered addresses using a treshold of euclidean distance, describe and visualize clustering results (histograms) \\
+4. Describe two step approach test, may need further research and would be ideal to incorporate into node embedding feature vectors \\
 
@@
 
+\subsection{LAND transfers}
+
 %%%%%%%%%%%%%%%%%%
@@
 \section{Discussion}
+Discuss which approach worked best for clustering a predefined address set
+A reference implementation for clustering a predefined address set using node embeddings on Github
 

### 2023-08-15 python/daily-activity-pattern.py

@@ -1,0 +1,13 @@
+from utils import *
+
+all_transfers_df = pd.read_csv('../data/all_intra_transfers.csv', index_col=[0])
+ens_pairs = pd.read_csv('../data/ens_pairs.csv', index_col=[0])
+
+# Specify the addresses to be compared
+addresses = ['0xa5dbd5f2f45cec05ace6c08f0b75bec711ea9517','0xf1289a44a9e7f75809de380ffa261f6095387c72']
+
+show_patterns(all_transfers_df, addresses, hour_bins=12, show_kde=True, figsize=(15, 10))
+plt.suptitle("erikarand.eth", fontsize=20, weight='bold')
+plt.tight_layout()
+plt.savefig('../figures/time-of-day-activity.png', bbox_inches='tight', dpi=500)
+plt.show()

### 2023-08-15 python/utils.py

@@ -64,32 +64,40 @@ def address_txs(address_str):
     return txs.sort_values("timeStamp")
 
 
-def show_patterns(events_df, addresses, hour_bins=24, figsize=(15, 3), show_kde=False):
+def show_patterns(events_df, addresses, hour_bins=24, figsize=(15, 15), show_kde=True):
     """Show side channels distribution of the given addresses"""
     addresses = [addr.lower() for addr in addresses]
     events_df['timeStamp'] = pd.to_datetime(events_df['timeStamp'], unit='s')
     events_df['hour'] = events_df['timeStamp'].dt.hour * 3600 + events_df['timeStamp'].dt.minute * 60 + events_df[
         'timeStamp'].dt.second
     sns.set_theme(context='paper')
-    if show_kde:
-        fig, ax = plt.subplots(1, figsize=(7.5, 3))
-        for address in addresses:
-            user_txs = events_df[events_df["from"] == address]
-            print(address, len(user_txs))
-        try:
-            for address in addresses:
-                user_txs = events_df[events_df["from"] == address]
-                sns.kdeplot(user_txs['hour'], ax=ax)
-            format_x_axis(ax, hour_bins)
-        except Exception as e:
-            print(e)
 
-    fig, ax = plt.subplots(1, figsize=(7.5, 3))
-    bin_edges = np.linspace(events_df['hour'].min(), events_df['hour'].max(), hour_bins + 1)  # set common bin edges
+    # Create a 2x1 grid of subplots
+    fig, (ax_hist, ax_kde) = plt.subplots(2, 1, figsize=figsize, gridspec_kw={'height_ratios': [2, 1]})
+
+    # Plot histogram on ax_hist
+    bin_edges = np.linspace(events_df['hour'].min(), events_df['hour'].max(), hour_bins + 1)
     for address in addresses:
         user_txs = events_df[events_df["from"] == address]
-        sns.histplot(user_txs["hour"], bins=bin_edges, kde=False, ax=ax, alpha=0.5)  # use common bin edges
-        format_x_axis(ax, hour_bins)
+        sns.histplot(user_txs["hour"], bins=bin_edges, kde=False, ax=ax_hist, alpha=0.5)
+        format_x_axis(ax_hist, hour_bins) # assuming you have this function to format the x-axis
+
+    ax_hist.set_xlabel('Hour', fontsize=14)
+    ax_hist.set_ylabel('Frequency', fontsize=14)
+
[…]

### 2023-08-15 python/self-authorization.py
Rename file

@@ -1,6 +1,7 @@
 from pymongo import MongoClient
 import pandas as pd
 import re
+import networkx as nx
 
 # Connect to db collection
 client = MongoClient('mongodb://localhost:27017/')
@@ -8,12 +9,7 @@ db = client['address-clustering']
 transactions = db['transactions']
 users = pd.read_csv('../data/subsets.csv')['Address'].to_list()
 
-# Query all approval transactions
-# approvals = pd.DataFrame(list(transactions.find({"functionName": "approve(address spender, uint256 rawAmount)"})))
-# print(f'Total approvals: {len(approvals)}')
-
-
-# List of function signatures you're interested in
+# List of function signatures of approval functions
 signatures = [
     "0x095ea7b3",  # approve(address,uint256) for both ERC-20 and ERC-721
     "0xa22cb465",  # setApprovalForAll(address,bool) for both ERC-721 and ERC-1155
@@ -43,4 +39,22 @@ filtered_self_approvals = filtered_self_approvals[['hash','from', 'to', 'spender
 grouped_df = filtered_self_approvals.groupby(['from']).size().reset_index(name='Number of Approvals given')
 print(grouped_df)
 print(filtered_self_approvals)
+
+
+# Build clusters
+
+G = nx.DiGraph()
+# Add edges from 'from' address to 'spender'
+for idx, row in filtered_self_approvals.iterrows():
+    G.add_edge(row['from'], row['spender'])
+clusters = list(nx.connected_components(G.to_undirected()))
+cluster_df = pd.DataFrame(columns=['Cluster_ID', 'Address'])
+
+# Assign a cluster ID to each address
+for cluster_id, cluster in enumerate(clusters):
+    for address in cluster:
+        cluster_df = cluster_df.append({'Cluster_ID': cluster_id, 'Address': address}, ignore_index=True)
+
+print(cluster_df)
+
 

### 2023-08-15 python/data-retrieval-preparation/tornado_transactions.py
Move script to data-retrieval folder

@@ -40,7 +40,7 @@ tornado_pools = pd.DataFrame(tornado, columns=['contract_address', 'pool'])
 tornado_pools['contract_address'] = tornado_pools['contract_address'].str.lower()
 tornado_pools.set_index('contract_address', inplace=True)
 tornado_pool_addresses = tornado_pools.index.tolist()
-#tornado_pools.to_csv('../data/tornado-pools.csv')
+#tornado_pools.to_csv('../../data/tornado-pools.csv')
 
 # Transactions
 tornado_transactions = pd.DataFrame(list(transactions.find({"$or": [{"from": {"$in": tornado_pool_addresses}}, {"to": {"$in": tornado_pool_addresses}}]})))
@@ -64,5 +64,5 @@ df['pool'] = df['contractAddress'].map(tornado_dict)
 
 # Save the DataFrame to a CSV file
 df.reset_index(drop=True, inplace=True)
-df.to_csv('../data/tornado.csv')
+df.to_csv('../../data/tornado_trx_transfers.csv')
 print(df)

### 2023-08-15 paper.tex
Small update to Node embedding section

@@
 After manual inspection, we excluded a cluster containing 80 addresses that had all approvals issued by the same address for the same token contract.
-The token contract represents a collection of wearable NFTs on Polygon called ``Renaissance King by René Mäkelä`` and may use an uncommon or even faulty token distribution/minting scheme.
+The token contract represents a collection of wearable NFTs on Polygon called ``Renaissance King by René Mäkelä`` and may use an uncommon or potentially even faulty token minting scheme.
 \newline Ultimately, we discovered 35 addresses associated with 15 distinct entities.
@@
 \subsection{Node embeddings}
+As described in previous sections, we tested different datasets to create the network graph using our ENS address pairs as ground truth.
+Der Approach ist zwar stark an Beres angelehnt, jedoch wendet er es an um pairs of deposit und withdrawal addressen zu clustern.
 
-1. Show that we tested different datasets to build network graph, best performing was intra-set asset transfers\\
-2. Evaluated the performance by average rank for the three methods, show results, describe how this method may be flawed/ why maybe not ideal\\
-3. Show how we clustered addresses using a treshold of euclidean distance, describe and visualize clustering results (histograms) \\
-4. Describe two step approach test, may need further research and would be ideal to incorporate into node embedding feature vectors \\
+We found the intra-set asset transfers to perform best in terms of the average rank of a target address. 
+Create network graph
+Run ten separate experiments and calculate the average rank for each target address. The results of this are shown in Table X. Explain table, NaN values, within 5 nearest neighbors etc.
+
+%1. Show that we tested different datasets to build network graph, best performing was intra-set asset transfers\\
+%2. Evaluated the performance by average rank for the three methods, show results, describe how this method may be flawed/ why maybe not ideal\\
 
@@
 \end{table}
+
+3. Show how we clustered addresses using a treshold of euclidean distance, describe and visualize clustering results (histograms) \\
+4. Describe two step approach test, may need further research and would be ideal to incorporate into node embedding feature vectors \\
 

### 2023-08-15 paper.tex
Add tornado cash heuristics results

@@
 
-We found only 2 Tornado cash withdrawal transactions within our dataset.
+We identified 84 transactions tied to Tornado cash pools, including 72 deposits, 10 withdrawals, and two transactions where the same address sent 0.1 Ether to the corresponding pool without invoking the deposit function.
+Despite applying all clustering heuristics except "Torn minting," we found no clusters.
 

### 2023-08-16 paper.tex
Small paper updates until section 5

@@
 %Anpassen, erweitern
+%We are the apply this approach to a predefind set of addresses at scale to cluster addresses within this set
 
@@
 \citep{roth2019tokenization} \newline
-\textit{Token standards} specify basic interfaces that allow for interoperability between contracts.
+\textit{Token standards} specify basic interfaces that allow for interoperability between smart contracts.
 These standards do not prescribe an implementation but set minimum requirements without restricting the design beyond that \citep{mastering_ethereum}.
-The most common token standards are ERC-20\footnote{https://eips.ethereum.org/EIPS/eip-20} for fungible tokens, ERC-721\footnote{https://eips.ethereum.org/EIPS/eip-721} for non-fungible tokens (NFTs) and ERC-1155\footnote{https://eips.ethereum.org/EIPS/eip-1155} for semi-fungible tokens.\newline
+The most common token standards are ERC-20\footnote{\url{https://eips.ethereum.org/EIPS/eip-20}} for fungible tokens, ERC-721\footnote{\url{https://eips.ethereum.org/EIPS/eip-721}} for non-fungible tokens (NFTs) and ERC-1155\footnote{\url{https://eips.ethereum.org/EIPS/eip-1155}} for semi-fungible tokens.\newline
 When a transaction completes, it produces a transaction receipt  that contains log entries providing information about the actions that occurred during its execution.
@@
 The database contains distinct collections for transactions and transfers.
-For additional information on the data fields of each collection, see Appendix.
+For additional information on the data fields of each collection, see Appendix \ref{sec:database}.
 
@@
 \label{sec:intra-set}
-In this thesis, we want to employ entity clustering heuristics to determine the number of entities represented by the remaining 137,544 addresses.
+%In this thesis
+We want to employ entity clustering heuristics to determine the number of entities represented by the remaining 137,544 addresses.
 Or, to phrase it differently, do users interact with Decentraland using multiple EOAs, and can we identify addresses that belong to the same user?
 \newline
-To achieve this, we often only %need to
-consider transactions or token transfer events where both the ``\texttt{from}`` (sender) and the ``\texttt{to}`` (recipient) address are within the address set.
+To achieve this, we often only consider transactions or token transfer events where both the ``\texttt{from}`` (sender) and the ``\texttt{to}`` (recipient) address are within the address set.
 We call this reduced dataset ``intra-set asset transfers``.
@@
 In addition to regular resolution from name to address, ENS also supports ``reverse resolution``, allowing for a mapping from address back to a name (or other metadata).
-Reverse resolution is accomplished via %special
+Reverse resolution is accomplished via the %special
  domain \texttt{`addr.reverse`}% and the resolver function \texttt{name()}.
@@
 
-We applied the following methodology to find ground truth pairs: First, we gathered all addresses that interacted with ENS (NFTs) to reduce the amount of name look-ups.
-Second, we iterated over each remaining address and checked if it reverse-resolved to an ENS domain\footnote{This was done via the ENS module within web3.py \url{https://web3py.readthedocs.io/en/stable/ens_overview.html}, which provides an interface to look up domains and addresses.}.
+We applied the following methodology to find ground truth pairs: \textit{First}, we gathered all addresses that interacted with ENS (NFTs) to reduce the amount of name look-ups.
+\textit{Second}, we iterated over each remaining address and checked if it reverse-resolved to an ENS domain\footnote{This was done via the ENS module within web3.py \url{https://web3py.readthedocs.io/en/stable/ens_overview.html}, which provides an interface to look up domains and addresses.}.
 If so, we logged the ENS domain and address in a CSV file.
-Third, using our new list, we identified if two addresses referenced the same ENS domain.
+\textit{Third}, using our new list, we identified if two addresses referenced the same ENS domain.
 If matched, we recorded both addresses alongside the ENS domain.
 \newline
-From this, we identified 11,440 reverse records and 40 address pairs, %(addresses pointing to the same .eth name)
-which we utilized as our ground truth to evaluate various clustering heuristics.
+From this, we identified 11,440 reverse records and 40 pairs of addresses pointing to the same ENS name, which we utilized as our ground truth to evaluate various clustering heuristics.
 Although this sample is relatively small, it allows us to assess and draw conclusions about the effectiveness of the methods.%profiling techniques/methods
@@
 In this section, we present an overview of clustering heuristics in the context of account-based blockchains and on-chain data.
-We will give a detailed explanation of the mechanics and rationale behind the heuristic and assess its applicability to our case.
+We will provide a detailed explanation of the mechanics and rationale behind the heuristic and assess its applicability to our case.
 In Section 5, we will implement and evaluate the heuristics we determine to be suitable for our objectives.
@@
 \newline
-Given our dataset includes all address transactions, we can easily employ this heuristic. %Since all the addresses' transactions are available in our dataset, we are able to apply this heuristic.
+Since our dataset includes all address transactions, we can easily employ this heuristic. %Since all the addresses' transactions are available in our dataset, we are able to apply this heuristic.
 
@@
 They key challenge of this approach lies in identifying these deposit addresses, which could either be EOAs or smart contracts.
-\newline
+\citep{FV:17}\newline
 Deposit addresses share the characteristic that they forward the received funds to a major exchange account.
@@
 The transactions between deposit and main exchange address are absent.
-Consequently, this clustering heuristic is not applicable to our data.
+Consequently, this clustering heuristic is not applicable.
+%with our data
 
@@
 Nevertheless, to test this approach we searched for addresses that forwarded the UNI airdrop to another address.
-We found X addresses that did that, but no two addresses forwarding the amount to a third address.
+We found eight such transfers, but none involved two addresses sending to a third address.
 
@@
 On the other hand, \cite{wu2022tutela} do not operate on a specific address set, but use all Ethereum transactions to build the network graph, ignoring token transfer events.
-\newline %vielleicht erklären wieso wir es anders gemacht haben
+After comparing these two methodologies with ours, we determined that intra-set asset transfers were the most effective for clustering a pre-defined set of addresses using node-embedding methods.\newline
 Using the network graph, node embedding methods seek to learn a function that projects a node to a $d$-dimensional vector representation (also called feature vector).
@@
 \iffalse
+%write here that we tested different datasets to create the network graph but intra-set asset transfers performed best for our task.
 \textbf{Diff2Vec} % Neighborhood preserving 
@@
 The authors argue that account owners may expose daily activity patterns and represent addresses by a vector including the mean, median and standard deviation, as well as an activity histogram divided into 4-6 hour bins \citep{Beres2020}.
-Figure \ref{fig:ToD} illustrates the time-of-day activity histogram and kde for a selected ENS address pair, divided into two hour intervals.\newline
+Figure \ref{fig:ToD} illustrates the time-of-day activity histogram and kernel density estimation (KDE) for a selected ENS address pair, divided into two hour intervals.\newline
 Additionaly, the \textit{gas price distribution} heuristic leverages the possibility of users revealing patterns when choosing their gas price.
@@
 We will not employ both methods due to their significantly poorer performance compared to node embeddings.
-Nevertheless, we test a two-step approach: In the first step, we implemented Diff2Vec to find the 10 nearest neighbors.
-In the second step, we ordered the remaining addresses by their Euclidean distance derived from the time-of-day and/or gas price feature vectors.
-We analyzed the impact of this two-step approach on the average rank of a target address.
+Nevertheless, we test a two-step approach: In the first step, we implement Diff2Vec to find the 10 nearest neighbors.
+In the second step, we order the remaining addresses by their Euclidean distance derived from the time-of-day and/or gas price feature vectors.
+We analyze the impact of this two-step approach on the average rank of a target address.
 
@@
 	\includegraphics[width=0.8\textwidth]{../figures/time-of-day-activity.png}
-	\caption{Time-of-day activity histogram and kde}
+	\caption{Time-of-day activity histogram and KDE for a specific ENS address pair}
 	\label{fig:ToD}
@@
 In addition to the existing clustering heuristics, we propose our own heuristic based on transfers of high-value NFTs such as LAND.
-We argue that, given the high value of Decentraland land parcels, there is a high probability that addresses are controlled by the same entity when LAND is transferred without any compensation.
+We argue that, given the high value of Decentraland land parcels, there is a strong likelihood that addresses are controlled by the same entity when LAND is transferred without any compensation.
 A user might perform such transfers to rearrange their LAND holdings, e.g., by upgrading to a more secure wallet implementation.
 \newline
-The primary challenge of this approach is to identify LAND transfers without any compensation.
+The primary challenge of this approach is to detect LAND transfers without any compensation.
 To accomplish this, we identify token or native asset transfers that took place within the same transaction as a LAND transfer.
-Upon manually examining various implementations of LAND trades on the most popular NFT marketplace contracts, we identified a pattern where the user address appears both in the from and to fields if a trade occurred.
-An example is shown on Figure \ref{fig:LAND_example}.
+Upon manually examining various implementations of LAND trades on the most popular NFT marketplace contracts, we noticed a recurring pattern: the user address appears in both the ``from`` and ``to`` fields if a trade takes place.
+Figure \ref{fig:LAND_example} illustrates an example of this pattern.
 In the case of pure LAND transfers, the sending and receiving addresses are the same for all transfers within a transaction.
@@
 
+\subsection{Database}
+\label{sec:database}
+
 %% Table

### 2023-08-16 paper.tex
Upate node embedding analysis

@@
 On the other hand, \cite{wu2022tutela} do not operate on a specific address set, but use all Ethereum transactions to build the network graph, ignoring token transfer events.
-After comparing these two methodologies with ours, we determined that intra-set asset transfers were the most effective for clustering a pre-defined set of addresses using node-embedding methods.\newline
+After comparing these two methodologies with ours, we determined that intra-set asset transfers were the most effective for clustering a pre-defined set of addresses.
+%using node-embedding methods.
+\newline
 Using the network graph, node embedding methods seek to learn a function that projects a node to a $d$-dimensional vector representation (also called feature vector).
@@
 The token contract represents a collection of wearable NFTs on Polygon called ``Renaissance King by René Mäkelä`` and may use an uncommon or potentially even faulty token minting scheme.
-\newline Ultimately, we discovered 35 addresses associated with 15 distinct entities.
+Ultimately, we discovered 35 addresses associated with 15 distinct entities.
 
 \subsection{Node embeddings}
-As described in previous sections, we tested different datasets to create the network graph using our ENS address pairs as ground truth.
+
+Our analysis of node embeddings begins with the network graph discussed in Section 4.4.
+The graph, which represents the largest connected component of intra-set asset transfers, contains no multi-edges or self-loops.
+This allows us to employ \cite{karateclub} Python library.
+\newline
+Next, we conduct ten independent experiments for each method, using the same input parameters as \cite{Beres2020}.
+Each experiment yields a node embedding in the form of a matrix with 51,566 rows corresponding to the number of embedded nodes, and 128 columns, representing feature vector dimensions.
+We use this matrix to generate a list of the k nearest neighbors of each node ranked by the Euclidean distance.
+This is accomplished by using the FAISS similarity search library.
+\newline
+The ranked list allows to search pairs of ENS addresses and report their relative rank.
+Table \ref{tbl:ENS_Domain_Ranks} shows the results for each address pair averaged over the ten experiments.
+Additionally, we calculated the method's mean, median, standard deviation and the rate of the target address being within the 5 or 10 nearest neighbors.
+
+Two addresses are not part of the largest connected component (network graph) and therefore show NaN values, for completeness they are still shown in the table.
+We can say that for these addresses/pairs, the methods are all surprisingly good in finding the target address -> node embedding methoden schreiben den beiden addressen/nodes sehr ähnliche feature vectoren zu.
+
+On average, the target address is found within the X nearest neighbors. Random guess would yield an average of 25k. Maximum is 51,566.
+
+In 50\% of cases, the target address has a rank of 4.2 or less.
+
+We find the target address within the 5 nearest neighbors in xxx.
+and within the 10 nearest neighbors in xxx
+
+Role2Vec seems to work best
+
+Still small sample, we cannot definitely say that role2vec is clearly better than the other methods. Luckily all methods are good.
+
+Average rank may not always be the best method, since a user can control more than two addresses.
+Make example: If someone has 20 addresses and all are found within the twenty nearest neighbors, but our address pairs only has found the twentieth address as a ground truth pair.
+
+%Evaluated the performance by average rank for the three methods, show results, describe how this method may be flawed/ why maybe not ideal
+%As described in previous sections, we tested different datasets to create the network graph using our ENS address pairs as ground truth.
 Der Approach ist zwar stark an Beres angelehnt, jedoch wendet er es an um pairs of deposit und withdrawal addressen zu clustern.
-
 We found the intra-set asset transfers to perform best in terms of the average rank of a target address.
-Create network graph
-Run ten separate experiments and calculate the average rank for each target address. The results of this are shown in Table X. Explain table, NaN values, within 5 nearest neighbors etc.
-
-%1. Show that we tested different datasets to build network graph, best performing was intra-set asset transfers\\
-%2. Evaluated the performance by average rank for the three methods, show results, describe how this method may be flawed/ why maybe not ideal\\
 

### 2023-08-16 paper.tex
Update analysis section

--- 2023-08-16 paper.tex
@@
 
-For this clustering heuristic, we analyze the transaction data of the addresses, focusing on the transaction's ``calldata``.
+To find self-authorization, we analyze the transaction data of the addresses, focusing on the transaction's ``calldata``.
 The first four bytes of the calldata represent the selector of the function signature, which specifies the smart contract function to be invoked.
@@
 This step helps us identify all approval transactions.
-\newline
 \textit{Second}, we extract the approved address (spender address), which is always located at the same position within the calldata due to token standardization.
 We then record the spender address in a new field within our dataframe.
-\newline
 \textit{Third}, we implement two filters on the approval transactions.
-The first filter checks if the spender address is part of our address set, and the second ensures that the spender address is different from the address initiating the transaction, thus eliminating self-approvals, which may occur due to a user interface bug or testing transactions.
-\newline
+The first filter checks if the spender address is part of our address set, and the second ensures that the spender address is different from the address initiating the transaction, which may occur due to a user interface bug or testing transactions.
 \textit{Fourth}, we group the remaining approvals by the initiating address and proceed to form the clusters.
@@
 The token contract represents a collection of wearable NFTs on Polygon called ``Renaissance King by René Mäkelä`` and may use an uncommon or potentially even faulty token minting scheme.
-\newline Ultimately, we discovered 35 addresses associated with 15 distinct entities.
+Ultimately, we discovered 35 addresses associated with 15 distinct entities.
 
 \subsection{Node embeddings}
-As described in previous sections, we tested different datasets to create the network graph using our ENS address pairs as ground truth.
+
+Our analysis of node embedding methods starts with a network graph built from intra-set asset transfers.
+We treat addresses as nodes and add undirected edges between them if they interacted with each other.
+\newline
+To use the Python library developed by \cite{karateclub}, we remove multi-edges and loops (transfers with same sender and recipient address) and only consider nodes within the largest connected component.
+The resulting network graph includes 51,566 nodes and 249,302 edges.
+As previously stated, we utilize the Diff2Vec, Role2Vec and DeepWalk methods from the library.
+\newline
+Subsequently, we run ten independent experiments for each method.
+Our choice of input parameters is identical to \cite{Beres2020}.
+Each experiment returns a node embedding in the form of a matrix with 51,566 rows corresponding to the number of nodes in the graph, and 128 columns, representing the feature vector dimensions.
+\newline
+For any node within the embedding, we can easily order all other nodes (addresses) by the Euclidean distance. %We can easily order nodes by the Euclidean distance to a given node. 
+We achieve this through the Faiss library, suitable for efficient similarity search and clustering of dense vectors.  \newline
+This enables us to search for our ENS ground truth pairs and report their relative rank.
+The results for each address pair, averaged over ten experiments are presented in Table \ref{tbl:ENS_Domain_Ranks}.
+Additionally, we calculated the mean, median, standard deviation and the rate of the target address appearing within the five or ten nearest neighbors for each method.
+\newline
+All three methods demonstrated remarkable efficacy in locating the target address, which indicates their ability to find multiple addresses controlled by a single entity.
+%Ability to assign highly similar feature vectors to both addresses within a ground truth pair.
+Role2Vec seems to be the most effective method, with the target address, on average, being found within the 28 nearest neighbors.
+In contrast, Diff2Vec and DeepWalk produced slightly higher averages of 46 and 62, respectively.
+Furthermore, Role2Vec found the target address within the five nearest neighbors in 19 of 34 cases and within the ten nearest neighbors in 71\% of cases.
+Despite the findings of \cite{Beres2020}, it appears that Diff2Vec is slightly less effective than Role2Vec or DeepWalk, although it is still generally successful. \newline
+It is noteworthy that two address pairs are not included in the network graph and therefore display no values.
+However, they have been included to demonstrate that the intra-set asset transfer approach may not always be applicable to cluster all addresses of a predefined set.
+\newline
+We also need to consider, that average rank may not be the most appropriate evaluation metric, particularly when a user controls significantly than two addresses.
+For example, if a single entity controls 20 addresses.
+Only one pair of addresses is detected as ground truth.
+Even if the algorithm finds all 20 addresses within the nearest neighbors but identifies our ground truth pair as the last one, we will score it lower than another algorithm that finds only one of the twenty addresses but within, for example, the ten nearest neighbors.
+
+%We can say that for these address pairs, the methods are all surprisingly good in finding the target address -> node embedding methoden schreiben den beiden addressen/nodes sehr ähnliche feature vectoren zu.
+%Role2Vec seems to work best out of the three, it has the lowest mean (28) and standard deviation and almost the same median as deepwalk.
+%In contrast to Beres, where diff2vec worked best, in our case it is slightly less good then the other methods but still good overall.
+%Average rank may not always be the best method, since a user can control more than two addresses.
+Make example: If someone has 20 addresses and all are found within the twenty nearest neighbors, but our address pairs only has found the twentieth address as a ground truth pair.
+%Since we have Random guess would yield an average of 25k. Maximum is 51,566.
+
+%As described in previous sections, we tested different datasets to create the network graph using our ENS address pairs as ground truth.
 Der Approach ist zwar stark an Beres angelehnt, jedoch wendet er es an um pairs of deposit und withdrawal addressen zu clustern.
-
 We found the intra-set asset transfers to perform best in terms of the average rank of a target address.
-Create network graph
-Run ten separate experiments and calculate the average rank for each target address. The results of this are shown in Table X. Explain table, NaN values, within 5 nearest neighbors etc.
-
-%1. Show that we tested different datasets to build network graph, best performing was intra-set asset transfers\\
-%2. Evaluated the performance by average rank for the three methods, show results, describe how this method may be flawed/ why maybe not ideal\\
 
@@
 
-3. Show how we clustered addresses using a treshold of euclidean distance, describe and visualize clustering results (histograms) \\
-4. Describe two step approach test, may need further research and would be ideal to incorporate into node embedding feature vectors \\
+After evaluating the different node embedding methods, we want to cluster addresses to assess the number of entities represented by the 51,566 nodes in the network/addresses.
+%to make a statement about the real number of users
+One approach might involve assigning the $k$ nearest neighbours of a node to a cluster and subsequently merging clusters until each node is assigned to exactly one cluster.
+However, selecting an appropriate $k$ is challenging, and it is hard to make the case that each address should belong to a cluster of $k$/ that each entity uses at least $k$ addresses.
+Instead, we choose to build clusters based on a Euclidean distance treshold value.
+All neighbors of a node that fall below this treshold are considered a cluster.
+Subsequently, we merge overlapping clusters; for instance, if node A is clustered with nodes B and C, and node C is clustered with X, we form a cluster comprising A, B, C, and X.
+We explored various treshold values and visualized the resulting cluster sizes in a histogram. %to better understand the distribution
+
+%4. Describe two step approach test, may need further research and would be ideal to incorporate into node embedding feature vectors \\
 
 \subsection{LAND transfers}
+
+Intra-token-transfer events -> select all LAND transfers -> report the transaction hash\\
+find all transfer events and transactions for the list of transaction hashes, drop duplicates, combine transactions and token transfers\\
+Detect purchases, report in new column\\
+Filter for simple transfers, build clusters\\
+Visualization
 
@@
 \section{Discussion}
-Discuss which approach worked best for clustering a predefined address set
-A reference implementation for clustering a predefined address set using node embeddings on Github
+
+%The results chapter or section simply and objectively reports what you found, without speculating on why you found these results.
+The discussion interprets the meaning of the results, puts them in context, and explains why they matter.
+
+%discussion is an in-depth exploration of the results, going into detail about the meaning of your findings and citing relevant sources to put them in context.
+
+%Discussion section: (a) Try to explain "What do your results mean?", and (b) how they relate to the literature,
+
+Discuss which approach worked best for clustering a predefined address set and why.
+
+%A reference implementation for clustering a predefined address set using node embeddings on Github
+
+Limitations
 
@@
 \section{Conclusion}
+
+%The conclusion is more shorter and more general: it concisely answers your main research question and makes recommendations based on your overall findings.
+%Conclusions section: Re-state the main points in a new concise way that you want your readers to remember.
 

### 2023-08-17 python/cluster-node-embedding.py
Add script for clustering of node embedding

@@ -1,6 +1,8 @@
+import matplotlib.pyplot as plt
+
 from utils import *
 
-all_transfers_df = pd.read_csv('../data/all_intra_transfers.csv', index_col=[0])
+all_transfers_df = pd.read_csv('../data/all_intra_transfers.csv', index_col=[0], low_memory=False)
 
 # Create network graph
 G = nx.from_pandas_edgelist(all_transfers_df, 'from', 'to', create_using=nx.MultiDiGraph())
@@ -35,7 +37,8 @@ embeddings_dw = emb_dw_df.values
 faiss_index_deepWalk = DistCalculation(embeddings_dw, node_map)
 
 #Get clusters
-threshold = 0.7
+threshold = 0.5
+nn = 10
 
 class UnionFind:
     def __init__(self, n):
@@ -58,17 +61,17 @@ class UnionFind:
                 if self.rank[rootX] == self.rank[rootY]:
                     self.rank[rootY] += 1
 
-uf = UnionFind(embeddings_d2v.shape[0])
+uf = UnionFind(embeddings_r2v.shape[0])
 
-for i in tqdm(range(embeddings_d2v.shape[0]), desc="Creating initial clusters"):
-    D, I = faiss_index_r2v.get_dist_idx(i, 5)
+for i in tqdm(range(embeddings_r2v.shape[0]), desc="Creating initial clusters"):
+    D, I = faiss_index_r2v.get_dist_idx(i)
     neighbours = set(I[0][D[0] < threshold])
     for neighbor in neighbours:
         uf.union(i, neighbor)
 
 # Extract clusters from union-find
 clusters_dict = {}
-for i in range(embeddings_d2v.shape[0]):
+for i in range(embeddings_r2v.shape[0]):
     root = uf.find(i)
     if root not in clusters_dict:
         clusters_dict[root] = set()
@@ -81,17 +84,27 @@ cluster_df = pd.DataFrame({'ClusterID': range(len(clusters)), 'Nodes': clusters}
 
 # Visualize clusters
 cluster_sizes = [len(cluster) for cluster in clusters] # Get cluster sizes
+sorted_cluster_sizes = sorted(cluster_sizes, reverse=True)
 
 # Plot histogram
 plt.figure(figsize=(10, 6))
 plt.hist(cluster_sizes, bins=max(cluster_sizes)-min(cluster_sizes), align='left', edgecolor='black', color='blue', alpha=0.7)
[…]

### 2023-08-17 python/cluster_node_embedding_iter.py

@@ -1,0 +1,97 @@
+import numpy as np
+
+from utils import *
+
+all_transfers_df = pd.read_csv('../data/all_intra_transfers.csv', index_col=[0], low_memory=False)
+
+# Create network graph
+G = nx.from_pandas_edgelist(all_transfers_df, 'from', 'to', create_using=nx.MultiDiGraph())
+G = clean_graph(G)
+
+# Get the largest connected component
+largest_cc = max(nx.connected_components(G), key=len)
+G_cc = G.subgraph(largest_cc)
+
+# Recode the graph's nodes, node_map maps from address to index
+G_cc, node_map = recode_graph(G_cc)
+
+# Create reverse map (from indices to addresses)
+idx_map = dict(zip(node_map.values(),node_map.keys()))
+ordered_addresses = [idx_map[idx] for idx in range(len(node_map))]
+
+print(f'Nodes: {len(G_cc.nodes())}\nEdges: {len(G_cc.edges())}')
+
+# Get Role2Vec embeddings
+emb_r2v_df = pd.read_csv('../data/embeddings/role2vec.csv', index_col='address')
+embeddings_r2v = emb_r2v_df.values
+faiss_index_r2v = DistCalculation(embeddings_r2v, node_map)
+
+
+class UnionFind:
+    def __init__(self, n):
+        self.parent = [i for i in range(n)]
+        self.rank = [0] * n
+
+    def find(self, x):
+        if self.parent[x] != x:
+            self.parent[x] = self.find(self.parent[x])
+        return self.parent[x]
+
+    def union(self, x, y):
+        rootX = self.find(x)
+        rootY = self.find(y)
+        if rootX != rootY:
+            if self.rank[rootX] > self.rank[rootY]:
+                self.parent[rootY] = rootX
+            else:
+                self.parent[rootX] = rootY
+                if self.rank[rootX] == self.rank[rootY]:
+                    self.rank[rootY] += 1
+
+
+# Set up the plot
+plt.figure(figsize=(10, 6))
+
+# Iterate over different thresholds
+thresholds = [0.6, 0.7, 0.8]
+colors = sns.color_palette("deep", 3)
+
+for i, threshold in enumerate(thresholds):
+    uf = UnionFind(embeddings_r2v.shape[0])
+    for j in tqdm(range(embeddings_r2v.shape[0]), desc=f"Creating clusters with threshold {threshold}"):
[…]

### 2023-08-17 python/data-retrieval-preparation/find-ens-pairs.py
Move find-ens-pairs to data-retrieval folder

@@ -36,7 +36,7 @@ for i,address in tqdm(enumerate(ens_users)):
 
 # Create ens_list.csv
 df = pd.DataFrame(data, columns=['Address', 'ENS Name'])
-df.to_csv('../data/ens_list.csv')
+df.to_csv('../../data/ens_list.csv')
 
 # Create ens_pairs.csv
 # group by ENS Name and find instances where exactly 2 addresses point to the same name
@@ -47,4 +47,4 @@ for ens_name, group in grouped_df.groupby('ENS Name'):
     data.append([ens_name, addresses[0], addresses[1]])
 
 ens_addresses_df = pd.DataFrame(data, columns=['ens_name', 'addr1', 'addr2']).set_index('ens_name')
-ens_addresses_df.to_csv('../data/ens_pairs.csv')
+ens_addresses_df.to_csv('../../data/ens_pairs.csv')

### 2023-08-17 paper.tex
Update analysis section

@@
 \usetikzlibrary{positioning, intersections}
+\usepackage{subcaption}
 
@@
 	\includegraphics[width=\textwidth]{../figures/land-opensea.png}
-	\caption{LAND trade on Opensea, Source: \url{https://etherscan.io/tx/0x2c2a70114e9080596bf5da6ad9c9b9f6d7e4c85a9d3b06e992f7248f9457a2ec}}
+	\caption{LAND trade on Opensea, Source: \href{https://etherscan.io/tx/0x2c2a70114e9080596bf5da6ad9c9b9f6d7e4c85a9d3b06e992f7248f9457a2ec}{Etherscan}}
 	\label{fig:LAND_example}
 \end{figure}
+
+\vspace{2em}
 
@@
 These include self-authorization, node embedding, and our proposed approach involving LAND transfers.
+%we describe our approach/method and the results.
 
@@
 
-To find self-authorization, we analyze the transaction data of the addresses, focusing on the transaction's ``calldata``.
+To find self-authorizations, we analyze the transaction data of the addresses, focusing on the transaction's ``calldata``.
 The first four bytes of the calldata represent the selector of the function signature, which specifies the smart contract function to be invoked.
@@
 \newline
-For any node within the embedding, we can easily order all other nodes (addresses) by the Euclidean distance. %We can easily order nodes by the Euclidean distance to a given node. 
-We achieve this through the Faiss library, suitable for efficient similarity search and clustering of dense vectors.  \newline
+For any node within the embedding, we can easily order all other nodes by the Euclidean distance. %We can easily order nodes by the Euclidean distance to a given node. 
+We achieve this through the Faiss library, which is suitable for efficient similarity search and clustering of dense vectors. \newline
 This enables us to search for our ENS ground truth pairs and report their relative rank.
@@
 In contrast, Diff2Vec and DeepWalk produced slightly higher averages of 46 and 62, respectively.
-Furthermore, Role2Vec found the target address within the five nearest neighbors in 19 of 34 cases and within the ten nearest neighbors in 71\% of cases.
-Despite the findings of \cite{Beres2020}, it appears that Diff2Vec is slightly less effective than Role2Vec or DeepWalk, although it is still generally successful. \newline
+Furthermore, Role2Vec found the target address within the ten nearest neighbors in 24 out of 34 cases (71\%).
+Diff2Vec is slightly less effective than Role2Vec or DeepWalk, although still generally successful.
+\newline
 It is noteworthy that two address pairs are not included in the network graph and therefore display no values.
@@
 
-%We can say that for these address pairs, the methods are all surprisingly good in finding the target address -> node embedding methoden schreiben den beiden addressen/nodes sehr ähnliche feature vectoren zu.
 %Role2Vec seems to work best out of the three, it has the lowest mean (28) and standard deviation and almost the same median as deepwalk.
@@
 Make example: If someone has 20 addresses and all are found within the twenty nearest neighbors, but our address pairs only has found the twentieth address as a ground truth pair.
-%Since we have Random guess would yield an average of 25k. Maximum is 51,566.
-
 %As described in previous sections, we tested different datasets to create the network graph using our ENS address pairs as ground truth.
@@
   \centering
-  \begin{tabular}{llll}
+  \begin{tabular}{lrrr}
     \hline
@@
 	awedjob.eth & 106.8 & 71.1 & 20.1 \\
-	captvicky.eth & NaN & NaN & NaN \\
+	captvicky.eth & - & - & - \\
 	disruptor.eth & 11.1 & 3.0 & 1.4 \\
@@
 	hyperspek.eth & 129.1 & 10.0 & 605.4 \\
-	jamesmillerblog.eth & NaN & NaN & NaN \\
+	jamesmillerblog.eth & - & - & - \\
 	jasonhsu.eth & 1.0 & 1.0 & 1.8 \\
@@
 
-After evaluating the different node embedding methods, we want to cluster addresses to assess the number of entities represented by the 51,566 nodes in the network/addresses.
+After evaluating the different node embedding methods, we want to cluster addresses to assess the number of entities represented by the 51,566 nodes in the network.
 %to make a statement about the real number of users
+We use the node embedding generated by Role2Vec.
 One approach might involve assigning the $k$ nearest neighbours of a node to a cluster and subsequently merging clusters until each node is assigned to exactly one cluster.
-However, selecting an appropriate $k$ is challenging, and it is hard to make the case that each address should belong to a cluster of $k$/ that each entity uses at least $k$ addresses.
-Instead, we choose to build clusters based on a Euclidean distance treshold value.
-All neighbors of a node that fall below this treshold are considered a cluster.
+However, selecting an appropriate $k$ is challenging, and it is hard to make the case that each address belongs to a cluster of at least $k$ for entity identification.
+\newline
+Instead, we choose to build clusters based on the Euclidean distance.
+All neighbors of a node below a certain treshold are considered a cluster (entity).
 Subsequently, we merge overlapping clusters; for instance, if node A is clustered with nodes B and C, and node C is clustered with X, we form a cluster comprising A, B, C, and X.
-We explored various treshold values and visualized the resulting cluster sizes in a histogram. %to better understand the distribution
+\newline
+We explore the senstitivity of clusters to various treshold values.
+The impact of changing the threshold value is shown in Figure \ref{fig:threshold_sensitivity} and Table \ref{tbl:cluster_table}.
+We chose these tresholds after manual inspection of ground truth pair distances.
+For better visibility, we only display clusters smaller than 20.
+At thresholds of 0.6, 0.7, and 0.8, we find 23,608, 18,592, and 14,793 clusters, respectively.
+Regardless of the threshold, the largest cluster always consists of more than 500 addresses.
+Unsurprisingly, higher tresholds result in fewer single-address clusters.
+The effect of the threshold is most pronounced for single address clusters, while affecting other cluster sizes much less.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{../figures/cluster_histogram.png}
+	\caption{Cluster Size Histogram for different distance thresholds}
+	\label{fig:threshold_sensitivity}
+\end{figure}
+
+\begin{table}[h!]
+\scriptsize
+  \centering
+  \begin{tabular}{lrrr}
+    \hline
+	\textbf{Threshold} & \textbf{0.6} & \textbf{0.7} & \textbf{0.8} \\
+	\hline
+Total clusters & 23,608 & 18,592 & 14,793 \\
+Size of largest cluster & 516 & 532 & 544\\
+Clusters of size >50 & 3 & 9 & 14\\
+    \hline
+  \end{tabular}
+  \caption{A table}
+  \label{tbl:cluster_table}
+\end{table}
 
 %4. Describe two step approach test, may need further research and would be ideal to incorporate into node embedding feature vectors \\
+%Performing an inner merge for the largest clusters of each threshold results in a cluster consisting of 516 addresses, this means the clusters overlap perfectly.
 
@@
 
+For the LAND transfer heuristic, we started by selecting all LAND transfer events from our intra-set token transfer dataframe.
+We store the transaction hash as a list and later collect all transactions and token transfers for transactions within the hash list.
+Afterwards we delete duplicates.
+We detect purchases by ....
+If a transaction consisted of a purchase, we mark it in a new column.
+Later on, we filter for all simple transfers and build clusters.
+
+For visualization we ....
+
+\iffalse
 Intra-token-transfer events -> select all LAND transfers -> report the transaction hash\\
@@
 Filter for simple transfers, build clusters\\
-Visualization
+\fi
 
@@
 The discussion interprets the meaning of the results, puts them in context, and explains why they matter.
-
-%discussion is an in-depth exploration of the results, going into detail about the meaning of your findings and citing relevant sources to put them in context.
-
+%Discussion is an in-depth exploration of the results, going into detail about the meaning of your findings and citing relevant sources to put them in context.
 %Discussion section: (a) Try to explain "What do your results mean?", and (b) how they relate to the literature,
+%DISCUSSION provides the explanation and interpretation of results or findings by comparing with the findings in prior studies.
 
@@
 
+Despite the findings of \cite{Beres2020}, it appears that Diff2Vec is slightly less effective than Role2Vec or DeepWalk, although it is still generally successful.
+
+Limitations
 %A reference implementation for clustering a predefined address set using node embeddings on Github
-
-Limitations
 
@@
 %Conclusions section: Re-state the main points in a new concise way that you want your readers to remember.
+%CONCLUSION is to write the output of the work/ investigations in summarized form
 

### 2023-08-17 python/activity-by-chain.py
Minor code updates

@@ -2,7 +2,6 @@ import seaborn as sns
 import pandas as pd
 import matplotlib.pyplot as plt
 
-
 # Get all transfers as a pandas dataframe except the '_id', 'userAddress' and 'isSet' column
 df_transfer = pd.read_csv('../data/raw_transfer_events.csv', usecols=lambda x: x not in ['_id', 'userAddress', 'isSet'])
 

### 2023-08-17 paper.tex
Update analysis

@@
 We call this reduced dataset ``intra-set asset transfers``.
-Regarding normal transactions, this means that we only keep native asset transfers (Ether or Matic) as almost all addresses are EOAs.
+Regarding normal transactions, this means that we only keep native asset transfers/payments (Ether or Matic) as almost all addresses are EOAs.
 \newline
@@
 Furthermore, it allows us to observe and visualize the asset flows between users.
-In total, we have 974,478 intra-set token transfers and 210,548 intra-set native asset transfers (101,621 Matic, 108,927 Ether).
+In total, we have 974,478 intra-set token transfers and 210,548 intra-set native asset transfers/payments (101,621 Matic, 108,927 Ether).
 
@@
 The primary challenge of this approach is to detect LAND transfers without any compensation.
-To accomplish this, we identify token or native asset transfers that took place within the same transaction as a LAND transfer.
+To accomplish this, we identify token or native asset transfers/payments that took place within the same transaction as a LAND transfer.
 Upon manually examining various implementations of LAND trades on the most popular NFT marketplace contracts, we noticed a recurring pattern: the user address appears in both the ``from`` and ``to`` fields if a trade takes place.
@@
 
-To find self-authorizations, we analyze the transaction data of the addresses, focusing on the transaction's ``calldata``.
-The first four bytes of the calldata represent the selector of the function signature, which specifies the smart contract function to be invoked.
-\newline
-\textit{First}, we query all transactions that begin with a function signature related to the approval functions corresponding to ERC-20, ERC-721 and ERC-1155 token standards.
-This step helps us identify all approval transactions.
-\textit{Second}, we extract the approved address (spender address), which is always located at the same position within the calldata due to token standardization.
+We analyze the addresses' transaction data to find self-authorizations, focusing on the transaction's ``calldata``.
+The first four bytes of the calldata represent the function selector, which unambiguously specifies the smart contract function the transaction originator wants to invoke.
+\newline
+\textit{First}, we identify all transactions that begin with a function signature related to the approval functions corresponding to ERC-20, ERC-721, and ERC-1155 token standards.
+\textit{Second}, we extract the approved (spender) address, which is always located at the same position within the calldata due to token standardization.
 We then record the spender address in a new field within our dataframe.
@@
 The first filter checks if the spender address is part of our address set, and the second ensures that the spender address is different from the address initiating the transaction, which may occur due to a user interface bug or testing transactions.
-\textit{Fourth}, we group the remaining approvals by the initiating address and proceed to form the clusters.
+\textit{Fourth}, we group the remaining approvals by the initiating address and form the clusters.
 
 We identified 16 clusters across 126 self-authorizing transactions, comprising 115 distinct addresses.
-After manual inspection, we excluded a cluster containing 80 addresses that had all approvals issued by the same address for the same token contract.
+After manual inspection, we excluded a cluster containing 80 addresses with all approvals issued by the same address for the same token contract.
 The token contract represents a collection of wearable NFTs on Polygon called ``Renaissance King by René Mäkelä`` and may use an uncommon or potentially even faulty token minting scheme.
@@
 Our analysis of node embedding methods starts with a network graph built from intra-set asset transfers.
-We treat addresses as nodes and add undirected edges between them if they interacted with each other.
-\newline
-To use the Python library developed by \cite{karateclub}, we remove multi-edges and loops (transfers with same sender and recipient address) and only consider nodes within the largest connected component.
+We treat addresses as nodes and add undirected edges between them if they interact with each other.
+\newline
+To use the Python library developed by \cite{karateclub}, we remove multi-edges and loops (transfers with the same sender and recipient address) and only consider nodes within the largest connected component.
 The resulting network graph includes 51,566 nodes and 249,302 edges.
-As previously stated, we utilize the Diff2Vec, Role2Vec and DeepWalk methods from the library.
+As previously stated, we utilize the Diff2Vec, Role2Vec, and DeepWalk methods from the library.
 \newline
@@
 \newline
-For any node within the embedding, we can easily order all other nodes by the Euclidean distance. %We can easily order nodes by the Euclidean distance to a given node. 
-We achieve this through the Faiss library, which is suitable for efficient similarity search and clustering of dense vectors. \newline
+For any node within the embedding, we can easily order all other nodes by the Euclidean distance.
+We achieve this through the Faiss library, which is suitable for efficient similarity search and clustering of dense vectors.
+\newline
 This enables us to search for our ENS ground truth pairs and report their relative rank.
-The results for each address pair, averaged over ten experiments are presented in Table \ref{tbl:ENS_Domain_Ranks}.
-Additionally, we calculated the mean, median, standard deviation and the rate of the target address appearing within the five or ten nearest neighbors for each method.
-\newline
+The results for each address pair, averaged over ten experiments, are presented in Table \ref{tbl:ENS_Domain_Ranks}.
+Additionally, we calculated the mean, median, standard deviation, and the rate of the target address appearing within the five or ten nearest neighbors for each method.
+
 All three methods demonstrated remarkable efficacy in locating the target address, which indicates their ability to find multiple addresses controlled by a single entity.
-%Ability to assign highly similar feature vectors to both addresses within a ground truth pair.
-Role2Vec seems to be the most effective method, with the target address, on average, being found within the 28 nearest neighbors.
+Role2Vec is the most effective method, with the target address, on average, found within the 28 nearest neighbors.
 In contrast, Diff2Vec and DeepWalk produced slightly higher averages of 46 and 62, respectively.
 Furthermore, Role2Vec found the target address within the ten nearest neighbors in 24 out of 34 cases (71\%).
-Diff2Vec is slightly less effective than Role2Vec or DeepWalk, although still generally successful.
-\newline
-It is noteworthy that two address pairs are not included in the network graph and therefore display no values.
-However, they have been included to demonstrate that the intra-set asset transfer approach may not always be applicable to cluster all addresses of a predefined set.
-\newline
-We also need to consider, that average rank may not be the most appropriate evaluation metric, particularly when a user controls significantly than two addresses.
-For example, if a single entity controls 20 addresses.
-Only one pair of addresses is detected as ground truth.
-Even if the algorithm finds all 20 addresses within the nearest neighbors but identifies our ground truth pair as the last one, we will score it lower than another algorithm that finds only one of the twenty addresses but within, for example, the ten nearest neighbors.
-
-%Role2Vec seems to work best out of the three, it has the lowest mean (28) and standard deviation and almost the same median as deepwalk.
-%In contrast to Beres, where diff2vec worked best, in our case it is slightly less good then the other methods but still good overall.
-%Average rank may not always be the best method, since a user can control more than two addresses.
-Make example: If someone has 20 addresses and all are found within the twenty nearest neighbors, but our address pairs only has found the twentieth address as a ground truth pair.
+Diff2Vec is barely less effective than Role2Vec or DeepWalk, although still generally successful.
+\newline
+Notably, two address pairs are not present within the network graph and therefore display no values.
+However, they have been included to demonstrate that the intra-set asset transfer approach may only sometimes be applicable to cluster all addresses of a predefined set.
+\newline
+We also need to consider that average rank may not be the most appropriate evaluation metric, particularly when a user controls more than two addresses.
+Suppose a single entity controlling 20 addresses, but only one pair of addresses is detected as ground truth.
+Even if the algorithm finds all 20 addresses within the nearest neighbors but identifies the ground truth pair as the last one, we will score it lower than another algorithm that finds only one of the twenty addresses but within the ten nearest neighbors.
+
 %As described in previous sections, we tested different datasets to create the network graph using our ENS address pairs as ground truth.
@@
 
-After evaluating the different node embedding methods, we want to cluster addresses to assess the number of entities represented by the 51,566 nodes in the network.
-%to make a statement about the real number of users
+After evaluating the different node embedding methods, we want to cluster the addresses to assess the number of entities represented by the 51,566 nodes in the network.
 We use the node embedding generated by Role2Vec.
-One approach might involve assigning the $k$ nearest neighbours of a node to a cluster and subsequently merging clusters until each node is assigned to exactly one cluster.
-However, selecting an appropriate $k$ is challenging, and it is hard to make the case that each address belongs to a cluster of at least $k$ for entity identification.
+\newline
+One approach might involve grouping a node's $k$ nearest neighbours to a cluster and subsequently merging clusters until each node is assigned to exactly one cluster.
+However, selecting an appropriate $k$ is challenging, and it is hard to make the case that each address belongs to a cluster of at least $k$ nodes.
 \newline
 Instead, we choose to build clusters based on the Euclidean distance.
-All neighbors of a node below a certain treshold are considered a cluster (entity).
-Subsequently, we merge overlapping clusters; for instance, if node A is clustered with nodes B and C, and node C is clustered with X, we form a cluster comprising A, B, C, and X.
-\newline
-We explore the senstitivity of clusters to various treshold values.
-The impact of changing the threshold value is shown in Figure \ref{fig:threshold_sensitivity} and Table \ref{tbl:cluster_table}.
-We chose these tresholds after manual inspection of ground truth pair distances.
-For better visibility, we only display clusters smaller than 20.
+All neighbors of a node below a certain threshold are considered a cluster.
+Afterward, we merge overlapping clusters; for instance, if node A is clustered with nodes B and C, and node C is clustered with nodes A and X, we form a cluster comprising A, B, C, and X.
+\newline
+We explore the sensitivity of clusters to various Euclidean distance threshold values.
+Figure \ref{fig:threshold_sensitivity} shows the histogram of cluster sizes and Table \ref{tbl:cluster_table} displays the number of resulting clusters depending on various threshold values.
+We chose said values after looking at the distance between ground truth pairs.
+For better visibility, we only display clusters below 20 addresses in Figure \ref{fig:threshold_sensitivity}.
 At thresholds of 0.6, 0.7, and 0.8, we find 23,608, 18,592, and 14,793 clusters, respectively.
-Regardless of the threshold, the largest cluster always consists of more than 500 addresses.
-Unsurprisingly, higher tresholds result in fewer single-address clusters.
+Regardless of the threshold, the largest cluster has more than 500 addresses.
+Unsurprisingly, higher thresholds result in fewer single-address clusters and more large sized clusters.
 The effect of the threshold is most pronounced for single address clusters, while affecting other cluster sizes much less.
@@
 \begin{table}[h!]
-\scriptsize
+\small
   \centering
-  \begin{tabular}{lrrr}
+  \begin{tabular}{lrrrrrrr}
     \hline
-	\textbf{Threshold} & \textbf{0.6} & \textbf{0.7} & \textbf{0.8} \\
+	\textbf{Threshold} & \textbf{0.5} & \textbf{0.55} &\textbf{0.6} & \textbf{0.65} & \textbf{0.7} & \textbf{0.75} & \textbf{0.8} \\
 	\hline
-Total clusters & 23,608 & 18,592 & 14,793 \\
-Size of largest cluster & 516 & 532 & 544\\
-Clusters of size >50 & 3 & 9 & 14\\
+Total clusters 			& 29,502 & 26,762 & 23,608 & 21,229 & 18,592 & 16,361 & 14,793 \\
+Size of largest cluster & 499 & 	512 & 516 & 	524 & 532 & 535 & 544\\
+Clusters of size 50+ 	& 2 & 2 & 3 & 7 & 9  & 13 & 14\\
     \hline
   \end{tabular}
-  \caption{A table}
+  \caption{Clustering results for different threshold values}
   \label{tbl:cluster_table}
@@
 
-For the LAND transfer heuristic, we started by selecting all LAND transfer events from our intra-set token transfer dataframe.
-We store the transaction hash as a list and later collect all transactions and token transfers for transactions within the hash list.
-Afterwards we delete duplicates.
-We detect purchases by ....
-If a transaction consisted of a purchase, we mark it in a new column.
-Later on, we filter for all simple transfers and build clusters.
+To implement the LAND transfer heuristic, we select all hashes of transactions where LAND was transferred between two Decentraland addresses.
+Then, we gather all token and native asset transfers associated with the previously selected transaction hashes, and remove any duplicates.
+We group the data by transaction hash and examine the sender (from) and recipient (to) fields for each transaction.
+If the same user address appears as both the sender and recipient, we mark the transaction as a purchase.
+Finally, we filter out purchases from our intra-set LAND transfers and create address clusters based on the remaining LAND transfers.
+
+413 addresses, 161 clusters, most clusters of 2 or 3 addresses, one cluster of 71 addresses.
+From the remaining 413 addresses, we can form 161 clusters. Most clusters consists of 2 or 3 addresses. There is one cluster of 71 addresses which is likely
 
@@
      & \texttt{gasUsed} & Amount of gas used by the transaction &  144176  \\
-     & \texttt{gasPrice} & Gas price specified for this transaction in Wei &  12449848873 \\
+     & \texttt{gasPrice} & The price of gas the originator is willing to pay &  12449848873 \\
      & \texttt{nonce} &   &   \\
      & \texttt{from} & Address initiating the transaction &   \\
-     & \texttt{to} & Target (either native asset transfer or function call) &  \\
-     & \texttt{value} & The amount of Ether/Matic in Wei & 500 \\
+     & \texttt{to} & The destination address (either native asset transfer or function call) &  \\
+     & \texttt{value} & The amount of Ether/Matic to send to the destination & 500 \\
      & \texttt{input} & Calldata & 0x095ea7b30000000000000000000000001111111254fb6c44bac0bed2854e76f90643097dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff \\

### 2023-08-17 python/cluster-node-embedding.py
Update cluster node embedding scripts

@@ -1,5 +1,3 @@
-import matplotlib.pyplot as plt
-
 from utils import *
 
 all_transfers_df = pd.read_csv('../data/all_intra_transfers.csv', index_col=[0], low_memory=False)
@@ -37,7 +35,7 @@ embeddings_dw = emb_dw_df.values
 faiss_index_deepWalk = DistCalculation(embeddings_dw, node_map)
 
 #Get clusters
-threshold = 0.5
+threshold = 0.75
 nn = 10
 
 class UnionFind:
@@ -86,25 +84,13 @@ cluster_df = pd.DataFrame({'ClusterID': range(len(clusters)), 'Nodes': clusters}
 cluster_sizes = [len(cluster) for cluster in clusters] # Get cluster sizes
 sorted_cluster_sizes = sorted(cluster_sizes, reverse=True)
 
-# Plot histogram
-plt.figure(figsize=(10, 6))
-plt.hist(cluster_sizes, bins=max(cluster_sizes)-min(cluster_sizes), align='left', edgecolor='black', color='blue', alpha=0.7)
-plt.title(f'Histogram of Cluster Sizes with {threshold} threshold')
-plt.xlabel('Cluster Size')
-plt.ylabel('Number of Clusters')
-plt.xlim([0.5, 30])
-plt.ylim([0, 15000])
-
-#plt.xticks([max(cluster_sizes)])
-plt.grid(axis='y', linestyle='--', alpha=0.7)
-plt.tight_layout()
-plt.savefig(f'../figures/cluster_histogram_{threshold}.png')
-plt.show()
 print(cluster_df)
 
 # Find the indices of clusters with sizes greater than 50
 indices_large_clusters = [i for i, size in enumerate(cluster_sizes) if size > 50]
 
-# Print the clusters with sizes greater than 100
+# Print the clusters with sizes greater than 50
 for index in indices_large_clusters:
     print(f'Cluster {index}: {clusters[index]}')
+
+print(sorted_cluster_sizes[0])

### 2023-08-17 python/cluster_node_embedding_iter.py

@@ -79,9 +79,8 @@ for i, threshold in enumerate(thresholds):
                  label=f'{threshold}', edgecolor='black', linewidth=0.5)
 
     # Largest cluster
-    largest_cluster = clusters[cluster_sizes.index(max(cluster_sizes))]
-    print(f'Largest cluster nodes: {largest_cluster}')
-
+    #largest_cluster = clusters[cluster_sizes.index(max(cluster_sizes))]
+    #print(f'Largest cluster nodes: {largest_cluster}')
 
 # Customize plot
 #plt.title('Histogram of Cluster Sizes', fontsize=20)

### 2023-08-17 paper.tex
Update paper

@@
 
-413 addresses, 161 clusters, most clusters of 2 or 3 addresses, one cluster of 71 addresses.
-From the remaining 413 addresses, we can form 161 clusters. Most clusters consists of 2 or 3 addresses. There is one cluster of 71 addresses which is likely
+From the remaining 413 addresses, we can form 161 clusters.
+The clusters are visualized in Figure \ref{fig:LAND_clusters}.
+Most clusters consist of 2 or 3 addresses, one cluster of 71 addresses.
+Marked in green.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.6\textwidth]{../figures/land_clusters.png}
+	\caption{LAND clusters}
+	\label{fig:LAND_clusters}
+\end{figure}
+
+This cluster is also observable when we visualize the LAND token network.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.6\textwidth]{../figures/land_network.png}
+	\caption{LAND token network, edges blue indicate a purchase}
+	\label{fig:LAND_network}
+\end{figure}
 

### 2023-08-18 paper.tex
Update LAND heuristics analysis

--- 2023-08-17 paper.tex
@@
 
-\subsection{ENS ground-truth pairs}
+\subsection{ENS address pairs}
 \label{sec:ens}
@@
 
-To implement the LAND transfer heuristic, we select all hashes of transactions where LAND was transferred between two Decentraland addresses.
-Then, we gather all token and native asset transfers associated with the previously selected transaction hashes, and remove any duplicates.
-We group the data by transaction hash and examine the sender (from) and recipient (to) fields for each transaction.
-If the same user address appears as both the sender and recipient, we mark the transaction as a purchase.
-Finally, we filter out purchases from our intra-set LAND transfers and create address clusters based on the remaining LAND transfers.
-
-413 addresses, 161 clusters, most clusters of 2 or 3 addresses, one cluster of 71 addresses.
-From the remaining 413 addresses, we can form 161 clusters. Most clusters consists of 2 or 3 addresses. There is one cluster of 71 addresses which is likely
-
-For visualization we ....
-
-\iffalse
-Intra-token-transfer events -> select all LAND transfers -> report the transaction hash\\
-find all transfer events and transactions for the list of transaction hashes, drop duplicates, combine transactions and token transfers\\
-Detect purchases, report in new column\\
-Filter for simple transfers, build clusters\\
-\fi
+To implement the LAND transfer heuristic, we select all transaction hashes of LAND transfers between two Decentraland addresses.
+Next, we gather all token and native asset transfers associated with the selected transaction hashes.
+We group the data by transaction hash and examine each transaction's sender (from) and recipient (to) address.
+If the same user address appears as the sender and recipient, we mark the transaction as a purchase.
+Finally, we filter out purchases and create address clusters based on the remaining LAND transfers.
+
+A total of 740 LAND transfers were recorded, involving 413 unique addresses.
+Of these transfers, none involved any form of compensation within the same transaction.
+Upon analysis, we were able to group these addresses into 161 distinct clusters.
+The distribution of these clusters is shown in Figure \ref{fig:LAND_clusters}.
+Notably, the majority of clusters consist of two or three addresses.
+However, one cluster stands out, containing a significantly higher count of 71 addresses.
+This prominent cluster has been marked in green for ease of identification.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.5\textwidth]{../figures/land_clusters.png}
+	\caption{LAND clusters}
+	\label{fig:LAND_clusters}
+\end{figure}
+
+LAND transfers between Decentraland addresses can also be visualized as a token network graph.
+Figure \ref{fig:LAND_network} presents the resulting graph.
+In this graph, red edges signify simple transfers, whereas blue edges represent LAND transfers made as part of a trade/purchase.
+Notably, the big cluster previously mentioned is visible on the top-right of the largest connected component.
+\newline
+A few key observations can be made from this network graph.
+First, most LAND transfers involve some form of compensation, in line with expectations.
+Second, certain nodes play a central role in LAND trading, indicated by their high connectivity within the network.
+Lastly, a recurring behavior pattern is observed wherein an individual address purchases LAND and subsequently transfers it to a third address.
+%This could reflect a common strategy among participants in the LAND market.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{../figures/land_network.png}
+	\caption{LAND token network}
+	\label{fig:LAND_network}
+\end{figure}
 
@@
 
+Vergleichen mit \cite{wu2022tutela} und \cite{Beres2020}
+
+The large cluster may incorrectly be marked/maybe off-chain compensation? -> auction address
+
 Limitations
 %A reference implementation for clustering a predefined address set using node embeddings on Github
+
+Assentiar consuetae ha opinionum mentemque ob ii.
+Ne conflantur de intelligat et me cohibendam.
+Imaginandi ob to at agnoscerem et mutationum.
+In methodum ob ii at quicquid lectorum.
+Procuravi ha dependent ob evidenter tangantur concipere.
+Immortalem objectivus deo eae rei attingebam ita advertebam quamprimum.
+Typis patet prius qua nia mem ens.
+Suppono sim ita pendere nam agnosci quopiam vestiri spondeo dum.
+Tes illum mundo vetus signa fit talem res his.
 
@@
 %CONCLUSION is to write the output of the work/ investigations in summarized form
+
+Assentiar consuetae ha opinionum mentemque ob ii.
+Ne conflantur de intelligat et me cohibendam.
+Imaginandi ob to at agnoscerem et mutationum.
+In methodum ob ii at quicquid lectorum.
+Procuravi ha dependent ob evidenter tangantur concipere.
+Immortalem objectivus deo eae rei attingebam ita advertebam quamprimum.
+Typis patet prius qua nia mem ens.
+Suppono sim ita pendere nam agnosci quopiam vestiri spondeo dum.
+Tes illum mundo vetus signa fit talem res his.
+Assentiar consuetae ha opinionum mentemque ob ii.
+Ne conflantur de intelligat et me cohibendam.
+Imaginandi ob to at agnoscerem et mutationum.
+In methodum ob ii at quicquid lectorum.
+Procuravi ha dependent ob evidenter tangantur concipere.
+Immortalem objectivus deo eae rei attingebam ita advertebam quamprimum.
+Typis patet prius qua nia mem ens.
+Suppono sim ita pendere nam agnosci quopiam vestiri spondeo dum.
+Tes illum mundo vetus signa fit talem res his.
+Assentiar consuetae ha opinionum mentemque ob ii.
+Ne conflantur de intelligat et me cohibendam.
+Imaginandi ob to at agnoscerem et mutationum.
+In methodum ob ii at quicquid lectorum.
+Procuravi ha dependent ob evidenter tangantur concipere.
+Immortalem objectivus deo eae rei attingebam ita advertebam quamprimum.
+Typis patet prius qua nia mem ens.
+Suppono sim ita pendere nam agnosci quopiam vestiri spondeo dum.
+Tes illum mundo vetus signa fit talem res his.
 

### 2023-08-18 python/cluster-node-embedding.py
Reorganize/clean code and folders

@@ -5,21 +5,13 @@ all_transfers_df = pd.read_csv('../data/all_intra_transfers.csv', index_col=[0],
 # Create network graph
 G = nx.from_pandas_edgelist(all_transfers_df, 'from', 'to', create_using=nx.MultiDiGraph())
 G = clean_graph(G)
-
-# Get the largest connected component
 largest_cc = max(nx.connected_components(G), key=len)
 G_cc = G.subgraph(largest_cc)
-
-# Recode the graph's nodes, node_map maps from address to index
-G_cc, node_map = recode_graph(G_cc)
-
-# Create reverse map (from indices to addresses)
-idx_map = dict(zip(node_map.values(),node_map.keys()))
+G_cc, node_map = recode_graph(G_cc) # Recode the graph's nodes, node_map maps from address to index
+idx_map = dict(zip(node_map.values(),node_map.keys())) # Create reverse map (from indices to addresses)
 ordered_addresses = [idx_map[idx] for idx in range(len(node_map))]
 
 print(f'Nodes: {len(G_cc.nodes())}\nEdges: {len(G_cc.edges())}')
-
-#Get the embeddings
 
 #Diff2Vec
 emb_d2v_df = pd.read_csv('../data/embeddings/diff2vec.csv', index_col='address')
@@ -34,9 +26,9 @@ emb_dw_df = pd.read_csv('../data/embeddings/deepWalk.csv', index_col='address')
 embeddings_dw = emb_dw_df.values
 faiss_index_deepWalk = DistCalculation(embeddings_dw, node_map)
 
-#Get clusters
-threshold = 0.75
-nn = 10
+# Parameters
+threshold = 0.5 # Threshold for clustering
+nn = 10 # Number of nearest neighbours to consider
 
 class UnionFind:
     def __init__(self, n):
@@ -64,8 +56,8 @@ uf = UnionFind(embeddings_r2v.shape[0])
 for i in tqdm(range(embeddings_r2v.shape[0]), desc="Creating initial clusters"):
     D, I = faiss_index_r2v.get_dist_idx(i)
     neighbours = set(I[0][D[0] < threshold])
-    for neighbor in neighbours:
-        uf.union(i, neighbor)
+    for neighbour in neighbours:
+        uf.union(i, neighbour)
 
 # Extract clusters from union-find
 clusters_dict = {}
@@ -86,11 +78,10 @@ sorted_cluster_sizes = sorted(cluster_sizes, reverse=True)
 
 print(cluster_df)
 
[…]

### 2023-08-18 python/daily-activity-pattern.py

@@ -1,13 +1,0 @@
-from utils import *
-
-all_transfers_df = pd.read_csv('../data/all_intra_transfers.csv', index_col=[0])
-ens_pairs = pd.read_csv('../data/ens_pairs.csv', index_col=[0])
-
-# Specify the addresses to be compared
-addresses = ['0xa5dbd5f2f45cec05ace6c08f0b75bec711ea9517','0xf1289a44a9e7f75809de380ffa261f6095387c72']
-
-show_patterns(all_transfers_df, addresses, hour_bins=12, show_kde=True, figsize=(15, 10))
-plt.suptitle("erikarand.eth", fontsize=20, weight='bold')
-plt.tight_layout()
-plt.savefig('../figures/time-of-day-activity.png', bbox_inches='tight', dpi=500)
-plt.show()

### 2023-08-18 python/data-retrieval-preparation/compute-normalizedGas-and-timeOfDay.py

@@ -2,7 +2,6 @@ import pandas as pd
 import numpy as np
 from datetime import datetime
 
-
 def add_ToD(df):
     df['timeStamp'] = pd.to_datetime(df['timeStamp'], unit='s')
     df['ToD'] = df['timeStamp'].dt.hour * 3600 + df['timeStamp'].dt.minute * 60 + df['timeStamp'].dt.second
@@ -21,12 +20,10 @@ def compute_histogram(data, bins, col_name='ToD'):
     hist_data = data.groupby(['from', 'bin']).size().unstack(fill_value=0)
     return hist_data
 
-
 # Load data
-ethereum_trx = pd.read_csv('../data/raw_ethereum_transactions.csv', index_col=[0])
-polygon_trx = pd.read_csv('../data/raw_polygon_transactions.csv', index_col=[0])
+ethereum_trx = pd.read_csv('../../data/raw_ethereum_transactions.csv', index_col=[0])
+polygon_trx = pd.read_csv('../../data/raw_polygon_transactions.csv', index_col=[0])
 transaction_df = pd.concat([ethereum_trx, polygon_trx])
-
 
 #################
 ### TimeOfDay ###
@@ -44,7 +41,7 @@ hist_df = compute_histogram(transaction_df_filtered, 6, 'ToD')
 
 # Save to csv
 combined_stats_hist_ToD = pd.concat([stats_df, hist_df], axis=1)
-combined_stats_hist_ToD.to_csv('../data/timeOfDay.csv')
+combined_stats_hist_ToD.to_csv('../../data/timeOfDay.csv')
 
 ################
 ### GasPrice ###
@@ -76,4 +73,4 @@ hist_df = compute_histogram(transaction_df_normalizedGas, 50, 'normalized_gasPri
 
 # Save to csv
 combined_stats_hist_nG = pd.concat([stats_df, hist_df], axis=1)
-combined_stats_hist_nG.to_csv('../data/normalizedGas.csv')
+combined_stats_hist_nG.to_csv('../../data/normalizedGas.csv')

### 2023-08-18 python/data-visualization/daily-activity-pattern.py

@@ -1,0 +1,61 @@
+import pandas as pd
+import seaborn as sns
+import matplotlib.pyplot as plt
+import numpy as np
+
+
+def format_x_axis(ax, hour_bins):
+    """Formats the x-axis of the time histogram."""
+    ax.set_xlim([0, 86400])
+    x_ticks = np.linspace(0, 86400, hour_bins + 1)
+    ax.set_xticks(x_ticks)
+    x_labels = [f'{int(tick / 3600)}' for tick in x_ticks]
+    ax.set_xticklabels(x_labels)
+
+
+def show_patterns(events_df, addresses, ens_name, hour_bins=24, figsize=(15, 15), show_kde=True):
+    """Show side channels distribution of the given addresses"""
+    addresses = [addr.lower() for addr in addresses]
+    events_df['timeStamp'] = pd.to_datetime(events_df['timeStamp'], unit='s')
+    events_df['hour'] = events_df['timeStamp'].dt.hour * 3600 + events_df['timeStamp'].dt.minute * 60 + events_df[
+        'timeStamp'].dt.second
+    sns.set_theme(context='paper')
+
+    # Create a 2x1 grid of subplots
+    fig, (ax_hist, ax_kde) = plt.subplots(2, 1, figsize=figsize, gridspec_kw={'height_ratios': [2, 1]})
+
+    # Plot histogram on ax_hist
+    bin_edges = np.linspace(events_df['hour'].min(), events_df['hour'].max(), hour_bins + 1)
+    for address in addresses:
+        user_txs = events_df[events_df["from"] == address]
+        sns.histplot(user_txs["hour"], bins=bin_edges, kde=False, ax=ax_hist, alpha=0.5)
+        format_x_axis(ax_hist, hour_bins) # assuming you have this function to format the x-axis
+
+    ax_hist.set_xlabel('Hour', fontsize=14)
+    ax_hist.set_ylabel('Frequency', fontsize=14)
+
+    # Plot KDE on ax_kde
+    if show_kde:
+        for address in addresses:
+            user_txs = events_df[events_df["from"] == address]
+            sns.kdeplot(user_txs['hour'], ax=ax_kde)
+            format_x_axis(ax_kde, hour_bins) # assuming you have this function to format the x-axis
+
+    ax_kde.set_xlabel('Hour', fontsize=14)
+    ax_kde.set_ylabel('Density', fontsize=14)
+
[…]

### 2023-08-18 python/data-visualization/venn-diagram.py

@@ -2,7 +2,7 @@ import pandas as pd
 from matplotlib_venn import venn2
 import matplotlib.pyplot as plt
 
-df = pd.read_csv('../data/subsets.csv', index_col=[0])
+df = pd.read_csv('../../data/subsets.csv', index_col=[0])
 
 # Addresses active only on Ethereum
 eth_only = df[(df['Ethereum'] == 1) & (df['Polygon'] == 0)]
@@ -16,9 +16,7 @@ polygon_only_count = len(polygon_only)
 both_active = df[(df['Ethereum'] == 1) & (df['Polygon'] == 1)]
 both_active_count = len(both_active)
 
-
 venn = venn2(subsets=(polygon_only_count, eth_only_count, both_active_count), set_labels=(None, None), set_colors=('#A5D7D2','#D20537'))
-
 
 ax = plt.gca()
 ax.text(-0.3, 0.3, 'Polygon PoS', fontsize=12, ha='center', va='center')
@@ -28,5 +26,5 @@ venn.get_label_by_id('10').set_position((-0.4, 0))
 venn.get_label_by_id('01').set_position((0.65, 0))
 venn.get_label_by_id('11').set_position((0.2, 0))
 
-plt.savefig('../figures/venn_diagram.png', dpi=500, bbox_inches='tight')
+plt.savefig('../../figures/venn_diagram.png', dpi=500, bbox_inches='tight')
 plt.show()

### 2023-08-18 python/histogram_node_embedding_cluster.py

@@ -1,5 +1,3 @@
-import numpy as np
-
 from utils import *
 
 all_transfers_df = pd.read_csv('../data/all_intra_transfers.csv', index_col=[0], low_memory=False)
@@ -25,7 +23,6 @@ print(f'Nodes: {len(G_cc.nodes())}\nEdges: {len(G_cc.edges())}')
 emb_r2v_df = pd.read_csv('../data/embeddings/role2vec.csv', index_col='address')
 embeddings_r2v = emb_r2v_df.values
 faiss_index_r2v = DistCalculation(embeddings_r2v, node_map)
-
 
 class UnionFind:
     def __init__(self, n):
@@ -71,16 +68,10 @@ for i, threshold in enumerate(thresholds):
             clusters_dict[root] = set()
         clusters_dict[root].add(k)
     clusters = list(clusters_dict.values())
-
-    cluster_sizes = [len(cluster) for cluster in clusters]  # Get cluster sizes
-
-    # Plot histogram using Seaborn
+    cluster_sizes = [len(cluster) for cluster in clusters]
     sns.histplot(cluster_sizes, bins=max(cluster_sizes) - min(cluster_sizes), color=colors[i], alpha=0.5,
                  label=f'{threshold}', edgecolor='black', linewidth=0.5)
 
-    # Largest cluster
-    #largest_cluster = clusters[cluster_sizes.index(max(cluster_sizes))]
-    #print(f'Largest cluster nodes: {largest_cluster}')
 
 # Customize plot
 #plt.title('Histogram of Cluster Sizes', fontsize=20)

### 2023-08-18 python/self-authorization.py

@@ -40,9 +40,7 @@ grouped_df = filtered_self_approvals.groupby(['from']).size().reset_index(name='
 print(grouped_df)
 print(filtered_self_approvals)
 
-
 # Build clusters
-
 G = nx.DiGraph()
 # Add edges from 'from' address to 'spender'
 for idx, row in filtered_self_approvals.iterrows():

### 2023-08-18 paper.tex
Update analysis

@@
 	\includegraphics[width=0.8\textwidth]{../figures/time-of-day-activity.png}
-	\caption{Time-of-day activity histogram and KDE for a specific ENS address pair}
+	\caption{Time-of-day activity histogram and KDE for a selected ENS address pair}
 	\label{fig:ToD}
@@
 For any node within the embedding, we can easily order all other nodes by the Euclidean distance.
-We achieve this through the Faiss library, which is suitable for efficient similarity search and clustering of dense vectors.
-\newline
+We achieve this through the Faiss library, which is suitable for efficient similarity search and clustering of dense vectors \citep{johnson2019faiss}.\newline
 This enables us to search for our ENS ground truth pairs and report their relative rank.
@@
 
-To implement the LAND transfer heuristic, we select all transaction hashes of LAND transfers between two Decentraland addresses.
+To implement this clustering heuristic, we select all transaction hashes of LAND transfers between two Decentraland addresses.
 Next, we gather all token and native asset transfers associated with the selected transaction hashes.
-We group the data by transaction hash and examine each transaction's sender (from) and recipient (to) address.
+We group the data by transaction hash and examine each transfer's sender (from) and recipient (to) address.
 If the same user address appears as the sender and recipient, we mark the transaction as a purchase.
@@
 
+LAND transfers between Decentraland addresses can also be visualized as a token network graph.
+Figure \ref{fig:LAND_network} presents the resulting graph.
+In this graph, red edges signify simple transfers, whereas blue edges represent LAND transfers made as part of a trade/purchase.
+Notably, the 71-address cluster previously mentioned is visible on the top-right of the largest connected component.
+\newline
+A few key observations can be made from this network graph.
+First, most LAND transfers involve some form of compensation, in line with expectations.
+Second, certain nodes play a central role in LAND trading, indicated by their high connectivity within the network.
+Lastly, a recurring behavior pattern is observed wherein an individual address purchases LAND and subsequently transfers it to a third address.
+%This could reflect a common strategy among participants in the LAND market.
+
 \begin{figure}[h]
@@
 
-LAND transfers between Decentraland addresses can also be visualized as a token network graph.
-Figure \ref{fig:LAND_network} presents the resulting graph.
-In this graph, red edges signify simple transfers, whereas blue edges represent LAND transfers made as part of a trade/purchase.
-Notably, the big cluster previously mentioned is visible on the top-right of the largest connected component.
-\newline
-A few key observations can be made from this network graph.
-First, most LAND transfers involve some form of compensation, in line with expectations.
-Second, certain nodes play a central role in LAND trading, indicated by their high connectivity within the network.
-Lastly, a recurring behavior pattern is observed wherein an individual address purchases LAND and subsequently transfers it to a third address.
-%This could reflect a common strategy among participants in the LAND market.
-
 \begin{figure}[h]
 	\centering
-	\includegraphics[width=\textwidth]{../figures/land_network.png}
+	\includegraphics[width=0.5\textwidth]{../figures/land_network.png}
 	\caption{LAND token network}
@@
 
+\newpage
+
 %%%%%%%%%%%%%%%%%%
@@
 %The results chapter or section simply and objectively reports what you found, without speculating on why you found these results.
-The discussion interprets the meaning of the results, puts them in context, and explains why they matter.
-%Discussion is an in-depth exploration of the results, going into detail about the meaning of your findings and citing relevant sources to put them in context.
-%Discussion section: (a) Try to explain "What do your results mean?", and (b) how they relate to the literature,
-%DISCUSSION provides the explanation and interpretation of results or findings by comparing with the findings in prior studies.
-
-Discuss which approach worked best for clustering a predefined address set and why.
-
-Despite the findings of \cite{Beres2020}, it appears that Diff2Vec is slightly less effective than Role2Vec or DeepWalk, although it is still generally successful.
-
-Vergleichen mit \cite{wu2022tutela} und \cite{Beres2020}
-
-The large cluster may incorrectly be marked/maybe off-chain compensation? -> auction address
-
-Limitations
-%A reference implementation for clustering a predefined address set using node embeddings on Github
-
-Assentiar consuetae ha opinionum mentemque ob ii.
-Ne conflantur de intelligat et me cohibendam.
-Imaginandi ob to at agnoscerem et mutationum.
-In methodum ob ii at quicquid lectorum.
-Procuravi ha dependent ob evidenter tangantur concipere.
-Immortalem objectivus deo eae rei attingebam ita advertebam quamprimum.
-Typis patet prius qua nia mem ens.
-Suppono sim ita pendere nam agnosci quopiam vestiri spondeo dum.
-Tes illum mundo vetus signa fit talem res his.
+
+%The discussion
+%... interprets the meaning of the results, puts them in context, and explains why they matter.
+%... is an in-depth exploration of the results, going into detail about the meaning of your findings and citing relevant sources to put them in context.
+%... Try to explain "What do your results mean?", and how they relate to the literature,
+%... provides the explanation and interpretation of results or findings by comparing with the findings in prior studies.
+
+Throughout our analysis, we successfully applied three clustering heuristics to our address set, utilizing the available on-chain data.
+These heuristics were self-authorization, node embedding, and LAND transfers.
+In the following discussion, we will examine each of these approaches step-by-step.
+
+%%%%%%%%%%%%%%%%%%%%
+Self-authorization is a straightforward technique, but results in very few identified address clusters.
+This is because it requires a highly specific on-chain behavior, which is rarely observed in practice.
+In particular, approvals are seldom used to authorize another externally owned account one might own.
+We also encountered a significant number of false-positives due to non-standard implementations.
+After excluding these instances, we identified a total of 15 entities consisting of 35 addresses.
+This outcome aligns with findings by \cite{FV:17}, who also observed that the heuristic captures only a small proportion of addresses.
+In his analysis of transaction data up to Ethereum block number 8,500,000 he identified 4,599 entities from 7,107 addresses.
+%%%%%%%%%%%%%%%%%%%%
+
+Address clustering through node embedding methods proved to be the most effective approach in our analysis.
+Unlike methods that require participation in specific on-chain events, node embedding examines the entire interaction network between addresses, making it broadly applicable.
+\newline
+Our implementation of node embedding methods differs from previous approaches by \cite{Beres2020} and \cite{wu2022tutela}.
+We construct the network graph based on asset transfers between addresses of our predefined set and analyze on-chain data from two distinct blockchain networks: Polygon and Ethereum.
+
+The main reasons for this are the different clustering objectives of previous implementations.
+\cite{wu2022tutela} aimed to cluster addresses without a predefined set, therefore using transaction data for network graph construction.
+Conversely, \cite{Beres2020} try to match deposit and withdrawal addresses for Tornado Cash, relying on all token transfers and transactions to cluster addresses based on similar on-chain behavior.
+Since it is not likely that withdrawal and deposit addresses from Tornado cash interacted with each other, the approach chosen by \cite{Beres2020} is better suited for that specific case.\newline
+We validated our approach using ENS address pairs as ground truth and found better results in terms of average rank, when building the network graph out of intra-set asset transfers compared to using all token transfer events or transactions.
+\newline
+Subsequently, we applied three node embedding algorithms that showed strong performance in the experiments of Beres et al.
+and compared their effectiveness.
+Our results indicate that Role2Vec is the best-performing method, locating the ground truth pair within the five nearest neighbors in 70\% of cases.
+This contrasts with Beres's findings, which identified Diff2Vec as the best method.
+\newline
+However, determining why one approach outperforms another is challenging.
+Both Diff2Vec and DeepWalk preserve neighborhood characteristics, while Role2Vec is a structural node embedding method.
+% expand on structural node embedding and give possible explanation
+Nevertheless, given the small sample size and the overall strong performance of all methods, the differences in results might be specific to the data at hand.
+
+Wir haben eine eigene Methode entwickelt zum Clustern von Network embeddings.
+Wir bauen Clusters abhängig von Euclidischer distanz zwischen feature vectors von nodes. 
+Dazu benutzen wir die embeddings von role2vec.
+Clusters aber sehr abhängig von threshold oder der methode wie man sie bildet, möglichkeit wäre weitere information (time-of-day) mit einfliessen zu lassen (evtl.
+sogar in den vector einbauen) -> wir haben es getestet aber kein (signifikantes) improvement für unsere address pairs gefunden.
+Könnte aber auch sein dass wir es falsch angewendet haben.
+
+%und Beres hat ein kleineres Set an addressen (er will nur deposit und withdraw addressen von tornado cash clustern) und benutzt all token transfers und transaktionen, nicht nur diese zwischen den addressen, was bei ihm auch nicht viele wären da er es mit tornado anschaut und es nicht sinnvoll wäre zwischen den addressen zu interagieren.
+%Im Gegensatz zu früheren implementierungen haben wir intra-set asset transfers benutzt um den graph zu bilden.
+das ist so weil bei unser spezifischen aufgabe ein vordefiniertes grosses addressen set zu clustern dies besser gelingt als bspw.
+alle transaktionen im ethereum netzwerk anzuschauen wie tutela oder wie beres der einfach alle token transfers der withdrawal und deposit addressen von tornado cash anschaut, wo sie eher weniger interaktionen haben als bei uns.
+%Node embeddings mussten wir an unsere Gegebenheiten anpassen. Evaluierung mittels unsern ENS address paaren, hat gezeigt dass diese methode sehr gut funktioniert um ähnliche addressen zu finden.
+%Despite the findings of \cite{Beres2020}, it appears that Diff2Vec is slightly less effective than Role2Vec or DeepWalk, although it is still generally successful. 
+%Schwierig zu sagen wieso der eine Appraoch besser ist als der andere, der unterschied zwischen r2v und den anderen zwei ist das r2v ein role-based algorithmus ist und dies für unser spezielles datenset und unsere ENS address pairs besser zu funktionieren scheint.
+Aber nicht sehr aussagekräftig da kleines sample und alle approaches recht gut.
+%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%
+-Eine weitere Methode basierend auf spezifischen on-chain Event vorgeschlagen.
+-The large cluster may incorrectly be marked/maybe off-chain compensation? -> auction address
+-lässt sich gut visualisieren und evtl. auch nachvollziehen
+-eigener approach hat ein spezifisches on-chain event zur voraussetzung, basiert auf annahme dass LAND nicht einfach so weitergegeben wird, ist auch auf andere nfts oder grosse token transfers anwendbar.
+hat auch funktioniert aber wieder relativ wenige clusters gefunden, hat es falsch positive dabei?
+zb.
+offchain zahlungen und on-chain token transferiert
+%%%%%%%%%%%%%%%%%%%%%
+
+-Discuss which approach worked best for clustering a predefined address set and why. 
+Diskutiere alle resultate gemeinsam, vom anfangs set über on-chain und intra-set zu den clusters.
+
+other Limitations -> ENS pairs? Incorporate time-of-day/normalized gas into feature vectors, two step approach
 

### 2023-08-18 paper.tex
Update discussion

@@
 Unlike methods that require participation in specific on-chain events, node embedding examines the entire interaction network between addresses, making it broadly applicable.
-\newline
 Our implementation of node embedding methods differs from previous approaches by \cite{Beres2020} and \cite{wu2022tutela}.
 We construct the network graph based on asset transfers between addresses of our predefined set and analyze on-chain data from two distinct blockchain networks: Polygon and Ethereum.
-
+\newline
 The main reasons for this are the different clustering objectives of previous implementations.
@@
 \newline
-Subsequently, we applied three node embedding algorithms that showed strong performance in the experiments of Beres et al.
-and compared their effectiveness.
+Subsequently, we applied three node embedding algorithms that showed strong performance in the experiments of \cite{Beres2020} and compared their effectiveness.
 Our results indicate that Role2Vec is the best-performing method, locating the ground truth pair within the five nearest neighbors in 70\% of cases.
-This contrasts with Beres's findings, which identified Diff2Vec as the best method.
-\newline
-However, determining why one approach outperforms another is challenging.
-Both Diff2Vec and DeepWalk preserve neighborhood characteristics, while Role2Vec is a structural node embedding method.
+This contrasts with previous findings, which identified Diff2Vec as the most effective method.
+\newline
+Determining why one approach outperforms another is challenging.
+Both Diff2Vec and DeepWalk preserve neighborhood characteristics, while Role2Vec is a structural node embedding method, meaning that ...
+A possible explanation is that Role2Vec ...
 % expand on structural node embedding and give possible explanation
-Nevertheless, given the small sample size and the overall strong performance of all methods, the differences in results might be specific to the data at hand.
-
-Wir haben eine eigene Methode entwickelt zum Clustern von Network embeddings.
-Wir bauen Clusters abhängig von Euclidischer distanz zwischen feature vectors von nodes. 
-Dazu benutzen wir die embeddings von role2vec.
-Clusters aber sehr abhängig von threshold oder der methode wie man sie bildet, möglichkeit wäre weitere information (time-of-day) mit einfliessen zu lassen (evtl.
+Nevertheless, given the small sample size and the overall strong performance of all methods, the differences in results might be specific to the data at hand. \newline
+We devised a novel method for creating clusters from our node embeddings, enabling us to estimate the number of entities represented by the 51,566 network graph nodes/addresses.
+This method involved calculating the Euclidean distance between pairs of feature vectors, specifically using the node embedding matrix generated by Role2Vec.
+Nodes were clustered if their distance fell below a predetermined threshold, and any overlapping clusters were subsequently merged.
+\newline
+Though our method may not be the ideal approach for clustering, it is likely more effective than simply clustering a fixed number of $k$ addresses.
+We observed that the number of clusters and their size is highly sensitive to the chosen distance threshold, making it challenging to assess the accuracy of these clusters.
+We have provided a sensitivity analysis to illustrate this issue.
+The distances between the feature vectors tend to be quite narrow (dense vectors), and even the distances between ground truth pairs exhibit significant variation.
+\newline
+We explored potential enhancements to our method, such as incorporating additional information (e.g., Time of Day, normalized Gas) into the feature vectors.
+Unfortunately, these modifications did not yield improvements.
+Similarly, a two-step approach to clustering also proved unsuccessful.
+These areas remain open for future research.
+
+%Clusters aber sehr abhängig von threshold oder der methode wie man sie bildet, möglichkeit wäre weitere information (time-of-day) mit einfliessen zu lassen (evtl.
 sogar in den vector einbauen) -> wir haben es getestet aber kein (signifikantes) improvement für unsere address pairs gefunden.
 Könnte aber auch sein dass wir es falsch angewendet haben.
-
 %und Beres hat ein kleineres Set an addressen (er will nur deposit und withdraw addressen von tornado cash clustern) und benutzt all token transfers und transaktionen, nicht nur diese zwischen den addressen, was bei ihm auch nicht viele wären da er es mit tornado anschaut und es nicht sinnvoll wäre zwischen den addressen zu interagieren.

### 2023-08-18 paper.tex
Update discussion

@@
 Unlike methods that require participation in specific on-chain events, node embedding examines the entire interaction network between addresses, making it broadly applicable.
+\newline
 Our implementation of node embedding methods differs from previous approaches by \cite{Beres2020} and \cite{wu2022tutela}.
-We construct the network graph based on asset transfers between addresses of our predefined set and analyze on-chain data from two distinct blockchain networks: Polygon and Ethereum.
-\newline
-The main reasons for this are the different clustering objectives of previous implementations.
-\cite{wu2022tutela} aimed to cluster addresses without a predefined set, therefore using transaction data for network graph construction.
+We construct the network graph based on asset transfers between addresses of our predefined set and simultaneously analyze data from Polygon and Ethereum.
+The main reason is previous implementations' different settings and research questions.
+\cite{wu2022tutela} aim to cluster addresses without a predefined set, therefore using transaction data for network graph construction.
 Conversely, \cite{Beres2020} try to match deposit and withdrawal addresses for Tornado Cash, relying on all token transfers and transactions to cluster addresses based on similar on-chain behavior.
-Since it is not likely that withdrawal and deposit addresses from Tornado cash interacted with each other, the approach chosen by \cite{Beres2020} is better suited for that specific case.\newline
+Since it is not very common that Tornado cash withdrawal and deposit addresses interact with each other, the approach chosen by \cite{Beres2020} is better suited for their objectives.
+\newline
 We validated our approach using ENS address pairs as ground truth and found better results in terms of average rank, when building the network graph out of intra-set asset transfers compared to using all token transfer events or transactions.
@@
 Our results indicate that Role2Vec is the best-performing method, locating the ground truth pair within the five nearest neighbors in 70\% of cases.
-This contrasts with previous findings, which identified Diff2Vec as the most effective method.
+This contrasts with previous findings, which identified Diff2Vec as the most effective method out of the three.
 \newline
@@
 % expand on structural node embedding and give possible explanation
-Nevertheless, given the small sample size and the overall strong performance of all methods, the differences in results might be specific to the data at hand. \newline
-We devised a novel method for creating clusters from our node embeddings, enabling us to estimate the number of entities represented by the 51,566 network graph nodes/addresses.
-This method involved calculating the Euclidean distance between pairs of feature vectors, specifically using the node embedding matrix generated by Role2Vec.
-Nodes were clustered if their distance fell below a predetermined threshold, and any overlapping clusters were subsequently merged.
+Nevertheless, given the small sample size, possible flaws in the evaluation via average rank and the overall strong performance of all methods, the differences in results might be specific to the data at hand.
+\newline
+Next, we created clusters from our node embeddings, enabling us to estimate the number of entities represented by the 51,566 network graph nodes representing addresses.
+Our method involves calculating the Euclidean distance between pairs of feature vectors, specifically using the node embedding matrix generated by Role2Vec.
+Nodes are clustered if their distance falls below a predetermined threshold, and any overlapping clusters are subsequently merged.
 \newline
@@
 We have provided a sensitivity analysis to illustrate this issue.
-The distances between the feature vectors tend to be quite narrow (dense vectors), and even the distances between ground truth pairs exhibit significant variation.
-\newline
-We explored potential enhancements to our method, such as incorporating additional information (e.g., Time of Day, normalized Gas) into the feature vectors.
+The distances between the feature vectors tend to be quite narrow (dense vectors), and even the distances between various ground truth pairs exhibit significant variation.
+\newline
+We explored potential enhancements to our method, such as incorporating additional information, e.g., time-of-day-activity and/or gas price selection into the feature vectors.
 Unfortunately, these modifications did not yield improvements.

### 2023-08-18 paper.tex
Update discussion

@@
 
-Throughout our analysis, we successfully applied three clustering heuristics to our address set, utilizing the available on-chain data.
-These heuristics were self-authorization, node embedding, and LAND transfers.
-In the following discussion, we will examine each of these approaches step-by-step.
+Throughout our analysis, we successfully applied three heuristics to cluster our address set, while utilizing on-chain data.
+In the following discussion, we will examine each of the approaches step-by-step.
+%The heuristics we applied were self-authorization, node embedding, and LAND transfers.
 
 %%%%%%%%%%%%%%%%%%%%
-Self-authorization is a straightforward technique, but results in very few identified address clusters.
+Implementing the self-authorization heuristic is straightforward, but results in very few identified address clusters.
 This is because it requires a highly specific on-chain behavior, which is rarely observed in practice.
@@
 This outcome aligns with findings by \cite{FV:17}, who also observed that the heuristic captures only a small proportion of addresses.
-In his analysis of transaction data up to Ethereum block number 8,500,000 he identified 4,599 entities from 7,107 addresses.
+In his analysis of Ethereum transaction data up to block number 8,500,000 he identified 4,599 entities from 7,107 addresses.
 %%%%%%%%%%%%%%%%%%%%
@@
 \newline
-Our implementation of node embedding methods differs from previous approaches by \cite{Beres2020} and \cite{wu2022tutela}.
-We construct the network graph based on asset transfers between addresses of our predefined set and simultaneously analyze data from Polygon and Ethereum.
-The main reason is previous implementations' different settings and research questions.
-\cite{wu2022tutela} aim to cluster addresses without a predefined set, therefore using transaction data for network graph construction.
-Conversely, \cite{Beres2020} try to match deposit and withdrawal addresses for Tornado Cash, relying on all token transfers and transactions to cluster addresses based on similar on-chain behavior.
+Our implementation of node embedding methods differs from previous approaches by \cite{Beres2020} and \cite{wu2022tutela}, the main reason being different settings and research questions.
+We construct the network graph based on the asset transfers within our address set and simultaneously analyze Polygon and Ethereum data.
+\newline
+Conversely, \cite{wu2022tutela} aim to cluster addresses without a predefined set, therefore using transaction data for network graph construction.
+\cite{Beres2020} try to match deposit and withdrawal addresses for Tornado Cash, relying on all token transfers and transactions to cluster addresses based on similar on-chain behavior.
 Since it is not very common that Tornado cash withdrawal and deposit addresses interact with each other, the approach chosen by \cite{Beres2020} is better suited for their objectives.
-\newline
-We validated our approach using ENS address pairs as ground truth and found better results in terms of average rank, when building the network graph out of intra-set asset transfers compared to using all token transfer events or transactions.
-\newline
-Subsequently, we applied three node embedding algorithms that showed strong performance in the experiments of \cite{Beres2020} and compared their effectiveness.
+
+Moreover, we validated our approach and found better results in terms of average rank of ENS pairs, when building the network graph out of intra-set asset transfers compared to using all token transfer events and/or transactions.
+\newline
+%Moreover, when evaluating different network graphs as the starting point to create node embeddings we found better results in terms of average rank with the intra-set asset transfer dataset, instead of using all transfer events and/or transactions.
+We applied three node embedding algorithms that showed strong performance in the experiments by \cite{Beres2020} and assessed their effectiveness.
 Our results indicate that Role2Vec is the best-performing method, locating the ground truth pair within the five nearest neighbors in 70\% of cases.
-This contrasts with previous findings, which identified Diff2Vec as the most effective method out of the three.
-\newline
-Determining why one approach outperforms another is challenging.
-Both Diff2Vec and DeepWalk preserve neighborhood characteristics, while Role2Vec is a structural node embedding method, meaning that ...
-A possible explanation is that Role2Vec ...
-% expand on structural node embedding and give possible explanation
-Nevertheless, given the small sample size, possible flaws in the evaluation via average rank and the overall strong performance of all methods, the differences in results might be specific to the data at hand.
-\newline
-Next, we created clusters from our node embeddings, enabling us to estimate the number of entities represented by the 51,566 network graph nodes representing addresses.
+This diverges from previous findings that favored Diff2Vec as the most effective of the three methods.
+\newline
+Determining why one approach outperforms another is complex.
+Diff2Vec and DeepWalk, both neighborhood-preserving algorithms, mainly capture node proximity.
+However, as noted by ..., this does not necessarily imply similarity, especially when addresses may frequently interact without being controlled by the same entity.
+In contrast, Role2Vec, a structural node embedding method, identifies nodes with similar network roles.
+In our scenario, network position or role may better represent similarity and structural relatedness among nodes in our evaluation sample.
+Despite these insights, the differences in results could be specific to the data at hand, given the small sample size, potential evaluation metric flaws, and the overall robust performance of all methods.
+\newline
+Next, we created clusters from our node embeddings, enabling us to estimate the number of entities represented by the 51,566 addresses.
 Our method involves calculating the Euclidean distance between pairs of feature vectors, specifically using the node embedding matrix generated by Role2Vec.

### 2023-08-19 paper.tex
Update discussion

@@
 %The results chapter or section simply and objectively reports what you found, without speculating on why you found these results. 
-
 %The discussion
@@
 
-Throughout our analysis, we successfully applied three heuristics to cluster our address set, while utilizing on-chain data.
+Throughout our analysis, we successfully applied three heuristics to cluster our address set while making use of on-chain data.
 In the following discussion, we will examine each of the approaches step-by-step.
-%The heuristics we applied were self-authorization, node embedding, and LAND transfers.
-
-%%%%%%%%%%%%%%%%%%%%
-Implementing the self-authorization heuristic is straightforward, but results in very few identified address clusters.
+
+%\textbf{Self-authorization}\\
+Implementing the \textit{self-authorization} heuristic is straightforward, but results in very few identified address clusters.
 This is because it requires a highly specific on-chain behavior, which is rarely observed in practice.
@@
 In his analysis of Ethereum transaction data up to block number 8,500,000 he identified 4,599 entities from 7,107 addresses.
-%%%%%%%%%%%%%%%%%%%%
-
-Address clustering through node embedding methods proved to be the most effective approach in our analysis.
-Unlike methods that require participation in specific on-chain events, node embedding examines the entire interaction network between addresses, making it broadly applicable.
+
+%\textbf{Graph representation learning}\\
+Address clustering through \textit{graph representation learning} proved to be the most effective approach in our analysis.
+Unlike methods that require participation in specific on-chain events, node embedding algorithms examine the entire interaction network between addresses, making it broadly applicable.
 \newline
@@
 \newline
-Conversely, \cite{wu2022tutela} aim to cluster addresses without a predefined set, therefore using transaction data for network graph construction.
+Conversely, \cite{wu2022tutela} aim to cluster addresses without a predefined set, therefore using Ethereum transaction data for network graph construction.
 \cite{Beres2020} try to match deposit and withdrawal addresses for Tornado Cash, relying on all token transfers and transactions to cluster addresses based on similar on-chain behavior.
 Since it is not very common that Tornado cash withdrawal and deposit addresses interact with each other, the approach chosen by \cite{Beres2020} is better suited for their objectives.
-
+\newline
 Moreover, we validated our approach and found better results in terms of average rank of ENS pairs, when building the network graph out of intra-set asset transfers compared to using all token transfer events and/or transactions.
-\newline
-%Moreover, when evaluating different network graphs as the starting point to create node embeddings we found better results in terms of average rank with the intra-set asset transfer dataset, instead of using all transfer events and/or transactions.
-We applied three node embedding algorithms that showed strong performance in the experiments by \cite{Beres2020} and assessed their effectiveness.
+A possible extension would include incorporating edge weights, similar to \cite{wu2022tutela}, however, we refrained from doing this because we would have needed to implement a custom node embedding algorithm.\newline
+We applied three node embedding algorithms that delivered robust results in the experiments by \cite{Beres2020} and assessed their effectiveness in detecting ground truth pairs.
 Our results indicate that Role2Vec is the best-performing method, locating the ground truth pair within the five nearest neighbors in 70\% of cases.
-This diverges from previous findings that favored Diff2Vec as the most effective of the three methods.
-\newline
-Determining why one approach outperforms another is complex.
-Diff2Vec and DeepWalk, both neighborhood-preserving algorithms, mainly capture node proximity.
-However, as noted by ..., this does not necessarily imply similarity, especially when addresses may frequently interact without being controlled by the same entity.
-In contrast, Role2Vec, a structural node embedding method, identifies nodes with similar network roles.
-In our scenario, network position or role may better represent similarity and structural relatedness among nodes in our evaluation sample.
+This diverges from the findings of \cite{Beres2020}, who determined Diff2Vec to be the superior method among the three evaluated.
+\newline
+Determining why one approach outperforms another is challenging.
+DeepWalk and Diff2Vec, both neighborhood-preserving algorithms, mainly capture node proximity.
+As noted by \cite{ahmed2018roletovec}, this does not necessarily imply similarity, especially when addresses frequently interact with each other without being controlled by the same entity.
+In contrast, Role2Vec, a structural node embedding method, identifies nodes with similar roles within the network.
+In our evaluation sample, network position or role may better represent similarity and structural relatedness among nodes.
 Despite these insights, the differences in results could be specific to the data at hand, given the small sample size, potential evaluation metric flaws, and the overall robust performance of all methods.
 \newline
-Next, we created clusters from our node embeddings, enabling us to estimate the number of entities represented by the 51,566 addresses.
+Creating clusters out of the node embeddings, enables us to estimate the number of entities represented by the 51,566 addresses.
 Our method involves calculating the Euclidean distance between pairs of feature vectors, specifically using the node embedding matrix generated by Role2Vec.
@@
 \newline
-Though our method may not be the ideal approach for clustering, it is likely more effective than simply clustering a fixed number of $k$ addresses.
+While our clustering method may not be ideal, it is probably more effective than, for example, clustering a fixed number of $k$ neighbors.
 We observed that the number of clusters and their size is highly sensitive to the chosen distance threshold, making it challenging to assess the accuracy of these clusters.
 We have provided a sensitivity analysis to illustrate this issue.
-The distances between the feature vectors tend to be quite narrow (dense vectors), and even the distances between various ground truth pairs exhibit significant variation.
-\newline
+The distances between the feature vectors tend to be quite narrow, with significant variation even among various ground truth pairs' distances.
+Regardless of the distance threshold, we were able to locate a cluster of 500+ addresses.
+Manual inspection revealed that these address show very similar on-chain patterns: They are only active on Polygon, most of the transfers are NFT mints and all NFTs are somehow related to Decentraland.
+Further, they transfer specific NFTs to the same address.
+Unsere Vermutung ist dass es ein Bot ist der mit vielen verschiedenen Adressen auf Decentraland aktiv ist, an verschiedene Orte/Events geht um dort NFT airdrops zu erhalten.
+Wenn sie etwas wert sind aggregiert er die NFTs auf eine addresse und verkauft sie über den marketplace.
+Man könnte diese Vermutung mit den bewegungsdaten validieren/überprüfen.
+Spannend dass der node embedding algo trotz limiterten informationen dieses pattern entdeckt hat.
+Etwas das in zukunft ein problem werden könnte -> evtl.
+sehr viel Bot aktivität auf DCL und evtl.
+mehr Research reinfliessen könnte.
+
 We explored potential enhancements to our method, such as incorporating additional information, e.g., time-of-day-activity and/or gas price selection into the feature vectors.
 Unfortunately, these modifications did not yield improvements.
-Similarly, a two-step approach to clustering also proved unsuccessful.
-These areas remain open for future research.
-
-%Clusters aber sehr abhängig von threshold oder der methode wie man sie bildet, möglichkeit wäre weitere information (time-of-day) mit einfliessen zu lassen (evtl.
-sogar in den vector einbauen) -> wir haben es getestet aber kein (signifikantes) improvement für unsere address pairs gefunden.
-Könnte aber auch sein dass wir es falsch angewendet haben.
-%und Beres hat ein kleineres Set an addressen (er will nur deposit und withdraw addressen von tornado cash clustern) und benutzt all token transfers und transaktionen, nicht nur diese zwischen den addressen, was bei ihm auch nicht viele wären da er es mit tornado anschaut und es nicht sinnvoll wäre zwischen den addressen zu interagieren.
-%Im Gegensatz zu früheren implementierungen haben wir intra-set asset transfers benutzt um den graph zu bilden.
-das ist so weil bei unser spezifischen aufgabe ein vordefiniertes grosses addressen set zu clustern dies besser gelingt als bspw.
-alle transaktionen im ethereum netzwerk anzuschauen wie tutela oder wie beres der einfach alle token transfers der withdrawal und deposit addressen von tornado cash anschaut, wo sie eher weniger interaktionen haben als bei uns.
-%Node embeddings mussten wir an unsere Gegebenheiten anpassen. Evaluierung mittels unsern ENS address paaren, hat gezeigt dass diese methode sehr gut funktioniert um ähnliche addressen zu finden.
-%Despite the findings of \cite{Beres2020}, it appears that Diff2Vec is slightly less effective than Role2Vec or DeepWalk, although it is still generally successful. 
-%Schwierig zu sagen wieso der eine Appraoch besser ist als der andere, der unterschied zwischen r2v und den anderen zwei ist das r2v ein role-based algorithmus ist und dies für unser spezielles datenset und unsere ENS address pairs besser zu funktionieren scheint.
-Aber nicht sehr aussagekräftig da kleines sample und alle approaches recht gut.
-%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%
--Eine weitere Methode basierend auf spezifischen on-chain Event vorgeschlagen.
--The large cluster may incorrectly be marked/maybe off-chain compensation? -> auction address
--lässt sich gut visualisieren und evtl. auch nachvollziehen
--eigener approach hat ein spezifisches on-chain event zur voraussetzung, basiert auf annahme dass LAND nicht einfach so weitergegeben wird, ist auch auf andere nfts oder grosse token transfers anwendbar.
+%vielleicht auch falsch gemacht
+Similarly, a two-step approach to clustering also proved unsuccessful. These areas remain open for future research.
+
+%Moreover, when evaluating different network graphs as the starting point to create node embeddings we found better results in terms of average rank with the intra-set asset transfer dataset, instead of using all transfer events and/or transactions.
+
+%\textbf{LAND transfers}\\
+The \textit{LAND transfer} heuristic again looks at very specific on-chain behavior.
+740 transfers, 413 addressen und 161 or 160 entities with 342 addresses.
+-The large cluster may incorrectly be marked/maybe off-chain compensation?
+-> auction address
+
+ We use the fact that these addresses are related to Decentraland and therefore choose LAND.
+But this could also be applied to other NFTs or large ERC20 token/Ether/stablecoin transfers.
+Main reasoning: revealing clusters by sending high-value amount to other address why?
+reorganize wallet(s), upgrade security, increased value of NFTs/assets over time -> change from metamask (starting option) to hardware wallet.
+
+ Pro: lässt sich gut visualisieren und evtl. auch nachvollziehen
+ Kontra: Likely a lot of false-positives with this appraoch, could be something missing in the on-chain data.
+
+%eigener approach hat ein spezifisches on-chain event zur voraussetzung, basiert auf annahme dass LAND nicht einfach so weitergegeben wird, ist auch auf andere nfts oder grosse token transfers anwendbar.
 hat auch funktioniert aber wieder relativ wenige clusters gefunden, hat es falsch positive dabei?
@@
 
--Discuss which approach worked best for clustering a predefined address set and why. 
 Diskutiere alle resultate gemeinsam, vom anfangs set über on-chain und intra-set zu den clusters.
+470k -> 135k on chain -> 51k intra-set transfer -> etc.
 

### 2023-08-19 python/network-visualizer.py

@@ -32,9 +32,9 @@ class NetworkVisualizer:
         fig, ax = plt.subplots(figsize=(20, 20))
 
         # Nodes
-        color_map = ['orange' if node in self.addresses else 'skyblue' if node == '0x0000000000000000000000000000000000000000' else 'darkgrey' for node in G]
+        color_map = ['orange' if node in self.addresses else 'black' for node in G]
         node_size = [v * 10 for v in dict(G.degree(weight='weight')).values()]
-        nx.draw_networkx_nodes(G, pos, node_color=color_map, node_size=node_size, ax=ax)
+        nx.draw_networkx_nodes(G, pos, node_color=color_map, node_size=node_size, alpha=0.5, ax=ax)
 
         # Edges
         edge_colors = ['red' if u in self.addresses else 'lightgreen' for u, v in G.edges()]

### 2023-08-19 python/network-visualizer.py
Update discussion - Add network visualization of aggregating address

@@ -27,37 +27,39 @@ class NetworkVisualizer:
 
         # Graph
         G = nx.from_pandas_edgelist(data, 'from', 'to', edge_attr='weight', create_using=nx.MultiDiGraph())
-        pos = nx.spring_layout(G, scale=100, k=5)
+        pos = nx.spring_layout(G, scale=1, k=2)
 
         fig, ax = plt.subplots(figsize=(20, 20))
 
         # Nodes
         color_map = ['orange' if node in self.addresses else 'black' for node in G]
         node_size = [v * 10 for v in dict(G.degree(weight='weight')).values()]
-        nx.draw_networkx_nodes(G, pos, node_color=color_map, node_size=node_size, alpha=0.5, ax=ax)
+        node_alpha = [1 if node in self.addresses else 0.3 for node in G]
+        nx.draw_networkx_nodes(G, pos, node_color=color_map, node_size=node_size, alpha=node_alpha, ax=ax)
 
         # Edges
         edge_colors = ['red' if u in self.addresses else 'lightgreen' for u, v in G.edges()]
-        edge_widths = [0.05 * data.get('weight', 1) for u, v, data in G.edges(data=True)]
+        edge_widths = [0.07 * data.get('weight', 1) for u, v, data in G.edges(data=True)]
         nx.draw_networkx_edges(G, pos, edge_color=edge_colors, width=edge_widths, alpha=1, ax=ax, arrowstyle="-")
 
         # Labels
         degree_weight = dict(G.degree(weight='weight'))
         sorted_nodes = sorted(degree_weight.items(), key=lambda x: x[1], reverse=True)
-        top_nodes = [n for n, d in sorted_nodes[:5]]
+        top_nodes = [n for n, d in sorted_nodes[:1]]
         labels = {node: node[:7] for node in top_nodes}
-        nx.draw_networkx_labels(G, pos, labels=labels, font_color='black', font_weight='bold', ax=ax)
+        nx.draw_networkx_labels(G, pos, labels=labels, font_color='black', font_size=20, font_weight='bold', ax=ax)
 
         plt.axis('off')
+        plt.tight_layout()
         plt.savefig(filename, dpi=500, transparent=False)
         plt.show()
-        print(labels)
 
 
 if __name__ == "__main__":
[…]

### 2023-08-20 paper.tex
Update discussion - Add network visualization of aggregating address
Update discussion

@@
 Our implementation of node embedding methods differs from previous approaches by \cite{Beres2020} and \cite{wu2022tutela}, the main reason being different settings and research questions.
-We construct the network graph based on the asset transfers within our address set and simultaneously analyze Polygon and Ethereum data.
+We construct the network graph based on asset transfers within our address set and simultaneously analyze Polygon and Ethereum data.
 \newline
@@
 \newline
-Moreover, we validated our approach and found better results in terms of average rank of ENS pairs, when building the network graph out of intra-set asset transfers compared to using all token transfer events and/or transactions.
+Moreover, we validated our approach and found better results in terms of average rank of ground truth address pairs, when building the network graph out of intra-set asset transfers compared to using all token transfer events and/or transactions.
 A possible extension would include incorporating edge weights, similar to \cite{wu2022tutela}, however, we refrained from doing this because we would have needed to implement a custom node embedding algorithm.\newline
@@
 \newline
-While our clustering method may not be ideal, it is probably more effective than, for example, clustering a fixed number of $k$ neighbors.
+While our clustering method may not be ideal, it is probably more effective than clustering a fixed number of $k$ neighbors for each node.
 We observed that the number of clusters and their size is highly sensitive to the chosen distance threshold, making it challenging to assess the accuracy of these clusters.
@@
 The distances between the feature vectors tend to be quite narrow, with significant variation even among various ground truth pairs' distances.
-Regardless of the distance threshold, we were able to locate a cluster of 500+ addresses.
-Manual inspection revealed that these address show very similar on-chain patterns: They are only active on Polygon, most of the transfers are NFT mints and all NFTs are somehow related to Decentraland.
-Further, they transfer specific NFTs to the same address.
-Unsere Vermutung ist dass es ein Bot ist der mit vielen verschiedenen Adressen auf Decentraland aktiv ist, an verschiedene Orte/Events geht um dort NFT airdrops zu erhalten.
-Wenn sie etwas wert sind aggregiert er die NFTs auf eine addresse und verkauft sie über den marketplace.
-Man könnte diese Vermutung mit den bewegungsdaten validieren/überprüfen.
-Spannend dass der node embedding algo trotz limiterten informationen dieses pattern entdeckt hat.
-Etwas das in zukunft ein problem werden könnte -> evtl.
-sehr viel Bot aktivität auf DCL und evtl.
-mehr Research reinfliessen könnte.
-
-We explored potential enhancements to our method, such as incorporating additional information, e.g., time-of-day-activity and/or gas price selection into the feature vectors.
+Regardless of the threshold value, we were able to locate a cluster of more than 500 addresses.
+Manual inspection revealed that these address show very similar on-chain patterns: They are all exclusively active on Polygon and most of the transfers are mints of Decentraland related NFTs.
+Further, they transfer some NFTs to address \texttt{0xE2e2F2240a84A61B7dFF50a86ee10d5FaF7faCa8}.
+The transfers to and from this address are shown in Figure \ref{fig:cluster}.
+Incoming transfers are indicated by green edges, while outgoing transfers are shown by red edges.
+We hypothesize that the network in question may be operated by a user/bot that creates multiple distinct addresses and actively engages with Decentraland.
+It seems likely that this bot may target specific locations or events where NFTs are (automatically) air-dropped to avatars in presence.
+If these NFTs hold value, the bot may then aggregate them to the main address and sell them on the Decentraland marketplace.
+This hypothesis could be verified with the Decentraland movement data.
+Notably, despite the limited on-chain data available, the node embedding algorithm was able to detect this activity pattern.
+Bot activity may become a problem for open and permissionless metaverse platforms like Decentraland and an interesting topic for future research. \newline
+Finally, we explored potential enhancements to the graph representation learning method, such as incorporating time-of-day-activity and/or gas price selection data into the feature vectors.
 Unfortunately, these modifications did not yield improvements.
@@
 
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.7\textwidth]{../figures/network_visualization_0xe2e.png}
+	\caption{Token Transfer Graph for \texttt{0xE2e2F$\dots$faCa8}}
+	\label{fig:cluster}
+\end{figure}
+
+%\textbf{LAND transfers}\\
+The \textit{LAND transfer} heuristic is targeted at users revealing address clusters by sending high-value assets to other addresses.
+In this specific case, we use the information that all addresses are related to Decentraland and therefore analyze LAND transfers.
+However, the approach could be applied (more generally) to other NFT collections or large asset transfers in general.
+\newline
+The main intuition/assumption behind this approach is that users may want to reorganize their accounts from time to time, mostly to increase security guarantees or spread the risk around multiple accounts.
+As a concrete example, some users may have started with a simple browser-based wallet but as the value of their assets and their knowledge grew, they changed to a more secure hardware wallet.
+We detect 161 entities with 413 addresses applying this approach.
+One entity with 70 address is very likely a false-positive, including an address that participated in the intial LAND auction and subsequently distributed LAND.
+This may have happened through some off-chain compensation.
+The advantage of this method is that it is relatively easy to visualise and understand.
+The disadvantage is that it demands a specific on-chain behaviour and is only scalable with significant effort.
+Additionally, many events that occur off-chain are not detectable in the data, resulting in an increased occurrence of false positives.
+
 %Moreover, when evaluating different network graphs as the starting point to create node embeddings we found better results in terms of average rank with the intra-set asset transfer dataset, instead of using all transfer events and/or transactions.
-
-%\textbf{LAND transfers}\\
-The \textit{LAND transfer} heuristic again looks at very specific on-chain behavior.
-740 transfers, 413 addressen und 161 or 160 entities with 342 addresses.
--The large cluster may incorrectly be marked/maybe off-chain compensation?
--> auction address
-
- We use the fact that these addresses are related to Decentraland and therefore choose LAND.
-But this could also be applied to other NFTs or large ERC20 token/Ether/stablecoin transfers.
-Main reasoning: revealing clusters by sending high-value amount to other address why?
-reorganize wallet(s), upgrade security, increased value of NFTs/assets over time -> change from metamask (starting option) to hardware wallet.
-
- Pro: lässt sich gut visualisieren und evtl. auch nachvollziehen
- Kontra: Likely a lot of false-positives with this appraoch, could be something missing in the on-chain data.
-
-%eigener approach hat ein spezifisches on-chain event zur voraussetzung, basiert auf annahme dass LAND nicht einfach so weitergegeben wird, ist auch auf andere nfts oder grosse token transfers anwendbar.
-hat auch funktioniert aber wieder relativ wenige clusters gefunden, hat es falsch positive dabei?
-zb.
-offchain zahlungen und on-chain token transferiert
+%740 transfers, 413 addressen und 161 or 160 entities with 342 addresses. -The large cluster may incorrectly be marked/maybe off-chain compensation? -> auction address
 %%%%%%%%%%%%%%%%%%%%%
 
-Diskutiere alle resultate gemeinsam, vom anfangs set über on-chain und intra-set zu den clusters.
+In this thesis, we set out to cluster 470k addresses observed in Decentraland.
+Focusing on on-chain data on Ethereum and Polygon, we reduced the address set to 135k.
+Depending on various assumptions, we were able to cluster entities interacting through more than one address.
+Merging the clusters resulting after applying each of the three clustering heuristics and assuming a treshold value of 0.5 for node embedding, we could cluster X addresses to Y entities.
+Assuming that all other addresses are single clusters, we argue that the total number of active users during that time frame was ...
+
+other Limitations -> ENS pairs? Incorporate time-of-day/normalized gas into feature vectors, two step approach
+Limitations: various assumptions, possibly false-positives, some clusters may well be undetected.
+
+%Diskutiere alle resultate gemeinsam, vom anfangs set über on-chain und intra-set zu den clusters.
 470k -> 135k on chain -> 51k intra-set transfer -> etc.
-
-other Limitations -> ENS pairs? Incorporate time-of-day/normalized gas into feature vectors, two step approach
 
@@
  \\
-    (16,184,993 rows) & \texttt{hash} & Transaction hash & 0x8d9490e9f0992e68490cfcb126e76290eca3bf668a... \\
+    (16.1M rows) & \texttt{hash} & Transaction hash & 0x8d9490e9f0992e68490cfcb126e76290eca3bf668a... \\
      & \texttt{timeStamp} & Timestamp in seconds from the UNIX epoch &  1657777314\\

### 2023-08-20 paper.tex
Update discussion

@@
 A detailed explanation of each method is beyond the scope of this thesis.
+The interested reader may consult the originial publications.
 For a concise overview of Diff2Vec, please refer to \cite{wu2022tutela}.
-The interested reader may consult the originial publications.
 \newline
@@
 To account for the changes in Ethereum traffic volume, the gas price is normalized by the daily network average.
-The combination of gas price levels that a user select forms their personal gas price profile.
+The combination of gas price levels a user select forms their personal gas price profile.
 An account is represented by a vector including the mean, median, and standard deviation and a normalized gas price histogram divided into 50 bins, which they determined to be optimal for clustering performance.
@@
 
-\cite{wu2022tutela} proposed five heuristics targeted at Tornado cash, highlighting that careless user behavior can still reveal identity, despite using a mixer.
+\cite{wu2022tutela} propose five heuristics targeted at Tornado cash, highlighting that careless user behavior can still reveal identity, despite using a mixer.
 The heuristics they identified are as follows: \newline
 ``Address match`` refers to instances where individuals use the same address for both depositing and withdrawing from the Tornado pool.
-``Unique gas price`` involves users selecting a distinct (specific) gas price for both their deposit and withdrawal transactions (prior to EIP-1559).
+``Unique gas price`` involves users selecting a distinct gas price for both their deposit and withdrawal transactions (prior to EIP-1559).
 ``Linked ETH addresses`` examines whether a deposit address has interacted with a withdrawal address outside of Tornado Cash.
@@
 
-We identified 84 transactions tied to Tornado cash pools, including 72 deposits, 10 withdrawals, and two transactions where the same address sent 0.1 Ether to the corresponding pool without invoking the deposit function.
-Despite applying all clustering heuristics except "Torn minting," we found no clusters.
+We identified 84 transactions tied to Tornado cash pools, including 72 deposits, 10 withdrawals, and two transactions where an address sent 0.1 Ether to the corresponding pool without invoking the deposit function.
+Despite applying all clustering heuristics except "Torn minting", we found no clusters.
 
@@
 We argue that, given the high value of Decentraland land parcels, there is a strong likelihood that addresses are controlled by the same entity when LAND is transferred without any compensation.
-A user might perform such transfers to rearrange their LAND holdings, e.g., by upgrading to a more secure wallet implementation.
+A user might perform such transfers to rearrange their LAND holdings, e.g., by upgrading to a more secure wallet.
 \newline
@@
 Our analysis of node embedding methods starts with a network graph built from intra-set asset transfers.
-We treat addresses as nodes and add undirected edges between them if they interact with each other.
+We treat addresses as nodes and add undirected edges between them if they interacted with each other.
 \newline
@@
 For any node within the embedding, we can easily order all other nodes by the Euclidean distance.
-We achieve this through the Faiss library, which is suitable for efficient similarity search and clustering of dense vectors \citep{johnson2019faiss}.\newline
+We achieve this through the FAISS Python library, which is suitable for efficient similarity search and clustering of dense vectors \citep{johnson2019faiss}.\newline
 This enables us to search for our ENS ground truth pairs and report their relative rank.
@@
 One approach might involve grouping a node's $k$ nearest neighbours to a cluster and subsequently merging clusters until each node is assigned to exactly one cluster.
-However, selecting an appropriate $k$ is challenging, and it is hard to make the case that each address belongs to a cluster of at least $k$ nodes.
+However, selecting an appropriate $k$ is challenging, and it is hard to make the case that each address belongs to a cluster of at least $k$.
 \newline
@@
 Next, we gather all token and native asset transfers associated with the selected transaction hashes.
-We group the data by transaction hash and examine each transfer's sender (from) and recipient (to) address.
+We group the data by transaction hash and examine each transfer's sender (\texttt{from}) and recipient (\texttt{to}) address.
 If the same user address appears as the sender and recipient, we mark the transaction as a purchase.
@@
 This prominent cluster has been marked in green for ease of identification.
-
+\newline
 LAND transfers between Decentraland addresses can also be visualized as a token network graph.
@@
 A few key observations can be made from this network graph.
-First, most LAND transfers involve some form of compensation, in line with expectations.
-Second, certain nodes play a central role in LAND trading, indicated by their high connectivity within the network.
+In line with our expectations, most LAND transfers involve some form of compensation.
+Moreover, certain nodes play a central role in LAND trading, indicated by their high connectivity within the network.
 Lastly, a recurring behavior pattern is observed wherein an individual address purchases LAND and subsequently transfers it to a third address.
@@
 	\includegraphics[width=0.5\textwidth]{../figures/land_clusters.png}
-	\caption{LAND clusters}
+	\caption{Resulting LAND clusters, with largest cluster marked in green}
 	\label{fig:LAND_clusters}
@@
 Address clustering through \textit{graph representation learning} proved to be the most effective approach in our analysis.
-Unlike methods that require participation in specific on-chain events, node embedding algorithms examine the entire interaction network between addresses, making it broadly applicable.
+Unlike methods that require participation in specific on-chain events, node embedding algorithms examine the entire asset transfer network between addresses, making it broadly applicable.
 \newline
@@
 \newline
-Moreover, we validated our approach and found better results in terms of average rank of ground truth address pairs, when building the network graph out of intra-set asset transfers compared to using all token transfer events and/or transactions.
+Moreover, we validated our approach and found better results in terms of average rank of ground truth address pairs, when building the network graph from intra-set asset transfers compared to using all token transfer events and/or transactions.
 A possible extension would include incorporating edge weights, similar to \cite{wu2022tutela}, however, we refrained from doing this because we would have needed to implement a custom node embedding algorithm.\newline
@@
 Manual inspection revealed that these address show very similar on-chain patterns: They are all exclusively active on Polygon and most of the transfers are mints of Decentraland related NFTs.
-Further, they transfer some NFTs to address \texttt{0xE2e2F2240a84A61B7dFF50a86ee10d5FaF7faCa8}.
+Further, they transfer some NFTs to address \texttt{``0xE2e2F2240a84A61B7dFF50a86ee10d5FaF7faCa8``}.
 The transfers to and from this address are shown in Figure \ref{fig:cluster}.
 Incoming transfers are indicated by green edges, while outgoing transfers are shown by red edges.
-We hypothesize that the network in question may be operated by a user/bot that creates multiple distinct addresses and actively engages with Decentraland.
+We hypothesize that the network in question may be operated by a user or even bot that creates multiple distinct addresses and actively engages with Decentraland.
 It seems likely that this bot may target specific locations or events where NFTs are (automatically) air-dropped to avatars in presence.
-If these NFTs hold value, the bot may then aggregate them to the main address and sell them on the Decentraland marketplace.
+If the NFTs hold value, the bot may then aggregate them to the main address and sell them on the Decentraland marketplace.
 This hypothesis could be verified with the Decentraland movement data.
+\newline
 Notably, despite the limited on-chain data available, the node embedding algorithm was able to detect this activity pattern.
-Bot activity may become a problem for open and permissionless metaverse platforms like Decentraland and an interesting topic for future research. \newline
-Finally, we explored potential enhancements to the graph representation learning method, such as incorporating time-of-day-activity and/or gas price selection data into the feature vectors.
-Unfortunately, these modifications did not yield improvements.
-%vielleicht auch falsch gemacht
-Similarly, a two-step approach to clustering also proved unsuccessful. These areas remain open for future research.
+Bot activity may become a concern for open and permissionless metaverse platforms like Decentraland and an interesting topic for future research.
+\newline
+Finally, we explored potential enhancements to the graph representation learning method, such as incorporating time-of-day-activity and/or gas price selection information into the feature vectors generated by Role2Vec.
+Unfortunately, these modifications did not lead to any significant improvements.
+This outcome may be attributed to challenges in implementation, particularly in scaling the values without disturbing the integrity of the dense feature vectors.
+Similarly, a two-step approach for clustering, re-ranking the nearest neighbors of a node according to similarity in time-of-day activity and/or normalized gas price vectors, proved unsuccessful.
+These ideas remain open for further development of clustering heuristics in the future.
 
@@
 \newline
-The main intuition/assumption behind this approach is that users may want to reorganize their accounts from time to time, mostly to increase security guarantees or spread the risk around multiple accounts.
-As a concrete example, some users may have started with a simple browser-based wallet but as the value of their assets and their knowledge grew, they changed to a more secure hardware wallet.
+The main assumption behind this approach is that users may want to reorganize their accounts from time to time, mostly to increase security guarantees or spread the risk around multiple accounts.
+As a concrete example, some users may have started with a simple browser-based wallet but as the value of their assets increased and their knowledge grew, they changed to a more secure hardware wallet.
 We detect 161 entities with 413 addresses applying this approach.
-One entity with 70 address is very likely a false-positive, including an address that participated in the intial LAND auction and subsequently distributed LAND.
-This may have happened through some off-chain compensation.
+One cluster with 70 address is very likely a not a single entity.
+It includes an address that participated in the intial LAND auction and subsequently distributed LAND.
+This may have happened through off-chain compensation.
 The advantage of this method is that it is relatively easy to visualise and understand.
@@
 
-In this thesis, we set out to cluster 470k addresses observed in Decentraland.
-Focusing on on-chain data on Ethereum and Polygon, we reduced the address set to 135k.
+In this thesis, we set out to cluster 473,927 addresses observed in Decentraland.
+Focusing on on-chain data on Ethereum and Polygon, we reduced the set to 137,544 addresses.
 Depending on various assumptions, we were able to cluster entities interacting through more than one address.
-Merging the clusters resulting after applying each of the three clustering heuristics and assuming a treshold value of 0.5 for node embedding, we could cluster X addresses to Y entities.
-Assuming that all other addresses are single clusters, we argue that the total number of active users during that time frame was ...
+Merging the clusters after applying each of the three clustering heuristics and assuming a treshold value of 0.5 for node embedding, we could cluster X addresses to Y entities.
+Further assuming that all other addresses are single clusters, we argue that the total number of active users during that time frame was Z.
 
@@
 %Diskutiere alle resultate gemeinsam, vom anfangs set über on-chain und intra-set zu den clusters.
-470k -> 135k on chain -> 51k intra-set transfer -> etc.
 

### 2023-08-21 paper.tex
Add combined results

@@
 
-\newpage
+\subsection{Combining clustering results}
+
+Combining the results of self-authorization, learned node embedding and LAND transfers, we can cluster 37.5\% (51,581 out of 137,544) of addresses representing 29,680 entities. \newline
+We assume that the unclustered addresses each represent individual entities, a (strict) distance threshold of 0.5 for clustering addresses generated by Role2Vec and remove the 71-address cluster found in self-authorization.
+We estimate a total of 115,643 active users during the studied time frame.
+Among them, 8,483 entities (X \%) interacted with Decentraland through more than one address.
+The largest entity consists of 499 addresses.
+The distribution of cluster sizes can be seen in Figure \ref{fig:barplot_clusters}.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\textwidth]{../figures/cluster-size-distribution.png}
+	\caption{Number of clusters by Cluster Size}
+	\label{fig:barplot_clusters}
+\end{figure}
 
@@
 
-In this thesis, we set out to cluster 473,927 addresses observed in Decentraland.
-Focusing on on-chain data on Ethereum and Polygon, we reduced the set to 137,544 addresses.
-Depending on various assumptions, we were able to cluster entities interacting through more than one address.
-Merging the clusters after applying each of the three clustering heuristics and assuming a treshold value of 0.5 for node embedding, we could cluster X addresses to Y entities.
-Further assuming that all other addresses are single clusters, we argue that the total number of active users during that time frame was Z.
-
-other Limitations -> ENS pairs? Incorporate time-of-day/normalized gas into feature vectors, two step approach
-Limitations: various assumptions, possibly false-positives, some clusters may well be undetected.
-
+The goal of this research/thesis was to identify the number of entities represented by the 473,927 addresses observed in Decentraland between.
+By focusing on Ethereum and Polygon on-chain data, we narrowed down the address set to 137,544.
+Combining the three clustering heuristics applied, we successfully clustered 37.5\% (51,581) of these addresses into 29,680 entities.
+\newline
+Assuming the remaining addresses each represent individual entities, we estimate a total of 115,643 active users during the studied time frame.
+Among them, 8,483 entities used more than one address, with the largest entity having 499 addresses.
+The distribution of cluster sizes can be seen in Figure \ref{fig:barplot_clusters}.
+
+Assumptions: Assumptions: Role2Vec with a distance threshold of 0.5 (strict)
+Removed large self-authorization cluster
+
+Most clusters through graph representation learning
+Very dependent on threshold
+X \% use more than one address
+Large address clusters could be some bot behavior
+
+%Limitations: various assumptions, possibly false-positives, some clusters may well be undetected. 
+%other Limitations -> ENS pairs? Incorporate time-of-day/normalized gas into feature vectors, two step approach
 %Diskutiere alle resultate gemeinsam, vom anfangs set über on-chain und intra-set zu den clusters.
@@
 
-%The conclusion is more shorter and more general: it concisely answers your main research question and makes recommendations based on your overall findings.
-%Conclusions section: Re-state the main points in a new concise way that you want your readers to remember.
-%CONCLUSION is to write the output of the work/ investigations in summarized form
-
-Assentiar consuetae ha opinionum mentemque ob ii.
-Ne conflantur de intelligat et me cohibendam.
-Imaginandi ob to at agnoscerem et mutationum.
-In methodum ob ii at quicquid lectorum.
-Procuravi ha dependent ob evidenter tangantur concipere.
-Immortalem objectivus deo eae rei attingebam ita advertebam quamprimum.
-Typis patet prius qua nia mem ens.
-Suppono sim ita pendere nam agnosci quopiam vestiri spondeo dum.
-Tes illum mundo vetus signa fit talem res his.
-Assentiar consuetae ha opinionum mentemque ob ii.
-Ne conflantur de intelligat et me cohibendam.
-Imaginandi ob to at agnoscerem et mutationum.
-In methodum ob ii at quicquid lectorum.
-Procuravi ha dependent ob evidenter tangantur concipere.
-Immortalem objectivus deo eae rei attingebam ita advertebam quamprimum.
-Typis patet prius qua nia mem ens.
-Suppono sim ita pendere nam agnosci quopiam vestiri spondeo dum.
-Tes illum mundo vetus signa fit talem res his.
-Assentiar consuetae ha opinionum mentemque ob ii.
-Ne conflantur de intelligat et me cohibendam.
-Imaginandi ob to at agnoscerem et mutationum.
-In methodum ob ii at quicquid lectorum.
-Procuravi ha dependent ob evidenter tangantur concipere.
-Immortalem objectivus deo eae rei attingebam ita advertebam quamprimum.
-Typis patet prius qua nia mem ens.
-Suppono sim ita pendere nam agnosci quopiam vestiri spondeo dum.
-Tes illum mundo vetus signa fit talem res his.
+%...Re-state the main points in a new concise way that you want your readers to remember.
+%...write the output of the work/ investigations in summarized form
+%...intended to help the reader understand why your research should matter to them after they have finished reading the paper.
+%...not merely a summary of your points or a re-statement of your research problem but a synthesis of key points.
+For most essays, one well-developed paragraph is sufficient for a conclusion, although in some cases, a two-or-three paragraph conclusion may be required.
+
+Clustering heuristics -> specific on-chain events, user patterns, graph representation learning
+Best -> graph representation learning
+Combination as extension
 
@@
 
-\subsection{Database}
+\subsection{Database Schema}
 \label{sec:database}

### 2023-08-21 python/cluster-node-embedding.py
Store results and add script to combine them

@@ -54,7 +54,7 @@ class UnionFind:
 uf = UnionFind(embeddings_r2v.shape[0])
 
 for i in tqdm(range(embeddings_r2v.shape[0]), desc="Creating initial clusters"):
-    D, I = faiss_index_r2v.get_dist_idx(i)
+    D, I = faiss_index_r2v.get_dist_idx(i) # number of neighbors not specified, so it will return all
     neighbours = set(I[0][D[0] < threshold])
     for neighbour in neighbours:
         uf.union(i, neighbour)
@@ -71,17 +71,25 @@ clusters = list(clusters_dict.values())
 
 # Convert clusters to DataFrame
 cluster_df = pd.DataFrame({'ClusterID': range(len(clusters)), 'Nodes': clusters})
-
-# Visualize clusters
-cluster_sizes = [len(cluster) for cluster in clusters] # Get cluster sizes
-sorted_cluster_sizes = sorted(cluster_sizes, reverse=True)
-
 print(cluster_df)
 
+# Restructure DataFrame to have one row per node and convert node indices to addresses
+cluster_list = []
+for cluster_id, nodes in cluster_df.iterrows():
+    for node in nodes['Nodes']:
+        address = idx_map[node]
+        cluster_list.append([cluster_id, address])
+
+new_cluster_df = pd.DataFrame(cluster_list, columns=['ClusterID', 'Address'])
+print(new_cluster_df)
+new_cluster_df.to_csv('../data/clusters_R2V_0_5.csv', index=False)
+
+
 # Show clusters with sizes greater than 50
+cluster_sizes = [len(cluster) for cluster in clusters] # Get cluster sizes
+sorted_cluster_sizes = sorted(cluster_sizes, reverse=True)
 indices_large_clusters = [i for i, size in enumerate(cluster_sizes) if size > 50]
 for index in indices_large_clusters:
     print(f'Cluster {index}: {clusters[index]}')
 
-# Print the size of the largest cluster
-print(sorted_cluster_sizes[0])
+print(sorted_cluster_sizes[0]) # Size of the largest cluster

### 2023-08-21 python/combine-clusters.py

@@ -1,0 +1,71 @@
+import pandas as pd
+import matplotlib.pyplot as plt
+import seaborn as sns
+
+# Create the three dataframes
+df1 = pd.read_csv('../data/clusters/clusters_R2V_0_5.csv')
+df2 = pd.read_csv('../data/clusters/clusters_selfAuthorization.csv')
+df3 = pd.read_csv('../data/clusters/clusters_LAND.csv', usecols=['ClusterID', 'Address'])
+
+# Update ClusterID in df2 and df3
+df2['ClusterID'] += df1['ClusterID'].max() + 1
+df3['ClusterID'] += df2['ClusterID'].max() + 1
+
+# Concatenate the three dataframes
+concat_df = pd.concat([df1, df2, df3], ignore_index=True)
+
+# Identify overlapping clusters
+merged_df = concat_df.merge(concat_df, on='Address')
+overlap_clusters = merged_df[merged_df['ClusterID_x'] != merged_df['ClusterID_y']]
+
+# Update cluster IDs in concat_df based on overlapping clusters
+for _, row in overlap_clusters.iterrows():
+    concat_df.loc[concat_df['ClusterID'] == row['ClusterID_y'], 'ClusterID'] = row['ClusterID_x']
+
+# Remove duplicate rows
+concat_df.drop_duplicates(inplace=True)
+
+concat_df.sort_values(by=['ClusterID'], inplace=True)
+concat_df.reset_index(drop=True, inplace=True)
+
+
+# Group by ClusterID and count the number of addresses in each cluster
+cluster_sizes = concat_df.groupby('ClusterID').size()
+clusters_with_multiple_addresses = cluster_sizes[cluster_sizes > 1]
+num_clusters_with_multiple_addresses = len(clusters_with_multiple_addresses)
+print(f"Number of clusters with more than one address: {num_clusters_with_multiple_addresses}")
+
+# Plot the distribution of cluster sizes
+# Define the bins and labels
+bins = [0, 1, 2, 3, 4, 5, 10, 20, 50, float('inf')]
+labels = ['1', '2', '3', '4', '5', '6-10', '11-20', '21-50', '50+']
+
+# Use pd.cut to categorize the cluster sizes into the defined bins
+bin_counts = pd.cut(cluster_sizes, bins=bins, labels=labels, right=True).value_counts()
+
+# Sort the bin counts by the order of the bins
+bin_counts = bin_counts.reindex(labels)
+
[…]

### 2023-08-21 python/self-authorization.py

@@ -46,13 +46,16 @@ G = nx.DiGraph()
 for idx, row in filtered_self_approvals.iterrows():
     G.add_edge(row['from'], row['spender'])
 clusters = list(nx.connected_components(G.to_undirected()))
-cluster_df = pd.DataFrame(columns=['Cluster_ID', 'Address'])
+cluster_df = pd.DataFrame(columns=['ClusterID', 'Address'])
 
 # Assign a cluster ID to each address
 for cluster_id, cluster in enumerate(clusters):
     for address in cluster:
-        cluster_df = cluster_df.append({'Cluster_ID': cluster_id, 'Address': address}, ignore_index=True)
+        cluster_df = cluster_df.append({'ClusterID': cluster_id, 'Address': address}, ignore_index=True)
 
 print(cluster_df)
 
+# Remove largest cluster
+cluster_df_clean = cluster_df[cluster_df['ClusterID']!=6]
+cluster_df_clean.to_csv('../data/clusters/clusters_selfAuthorization.csv', index=False)
 

### 2023-08-21 paper.tex
Add section to analysis, add potential conclusion contentsl

@@
 	\centering
-	\includegraphics[width=0.5\textwidth]{../figures/land_network.png}
+	\includegraphics[width=0.65\textwidth]{../figures/land_network.png}
 	\caption{LAND token network}
@@
 
-Combining the results of self-authorization, learned node embedding and LAND transfers, we can cluster 37.5\% (51,581 out of 137,544) of addresses representing 29,680 entities. \newline
-We assume that the unclustered addresses each represent individual entities, a (strict) distance threshold of 0.5 for clustering addresses generated by Role2Vec and remove the 71-address cluster found in self-authorization.
-We estimate a total of 115,643 active users during the studied time frame.
-Among them, 8,483 entities (X \%) interacted with Decentraland through more than one address.
-The largest entity consists of 499 addresses.
-The distribution of cluster sizes can be seen in Figure \ref{fig:barplot_clusters}.
+To conclude our clustering analysis, we combine the results of self-authorization, learned node embedding and LAND transfer heuristics.
+By doing so, we can cluster 51,581 out of 137,544 (37.5\%) addresses that represent 29,680 entities.
+For the remaining addresses, we consider each as an individual entity. 
+We applied a strict distance threshold of 0.5 for clustering embeddings generated by Role2Vec and excluded the 80-address cluster identified in self-authorization.
+Under these assumptions, we estimate 115,643 active users during the time frame studied.
+Out of these, 8,483 entities (7.3\%) interacted with Decentraland through multiple addresses.
+The largest entity comprises 499 addresses.
+We plot the distribution of cluster sizes in Figure \ref{fig:barplot_clusters}.
 
@@
 Combination as extension
+
+1. Public blockchain -> all data available -> allows us to analyse it and find information
+2. Clustering heuristics for account-based blockchains using on-chain data and on specific predefined address set
+3. Most successful graph representation learning because does not require participation in specific on-chain event / usage pattern
+4. From the various methods Role2Vec best
+5. Summarize Final results
+6. For researchers -> extend this approach -> apply it to other address sets -> package
+7.
 

### 2023-08-21 paper.tex
Update discussion

@@
 
-%\textbf{Self-authorization}\\
 Implementing the \textit{self-authorization} heuristic is straightforward, but results in very few identified address clusters.
@@
 We also encountered a significant number of false-positives due to non-standard implementations.
+We are very confident that this cluster is not controlled by the same entity, and therefore remove it.
 After excluding these instances, we identified a total of 15 entities consisting of 35 addresses.
@@
 
-%\textbf{Graph representation learning}\\
 Address clustering through \textit{graph representation learning} proved to be the most effective approach in our analysis.
@@
 
-\begin{figure}[h]
+\begin{figure}[h!]
 	\centering
@@
 Additionally, many events that occur off-chain are not detectable in the data, resulting in an increased occurrence of false positives.
-
-%Moreover, when evaluating different network graphs as the starting point to create node embeddings we found better results in terms of average rank with the intra-set asset transfer dataset, instead of using all transfer events and/or transactions.
 %740 transfers, 413 addressen und 161 or 160 entities with 342 addresses. -The large cluster may incorrectly be marked/maybe off-chain compensation? -> auction address
-%%%%%%%%%%%%%%%%%%%%%
-
-The goal of this research/thesis was to identify the number of entities represented by the 473,927 addresses observed in Decentraland between.
-By focusing on Ethereum and Polygon on-chain data, we narrowed down the address set to 137,544.
-Combining the three clustering heuristics applied, we successfully clustered 37.5\% (51,581) of these addresses into 29,680 entities.
-\newline
-Assuming the remaining addresses each represent individual entities, we estimate a total of 115,643 active users during the studied time frame.
-Among them, 8,483 entities used more than one address, with the largest entity having 499 addresses.
-The distribution of cluster sizes can be seen in Figure \ref{fig:barplot_clusters}.
-
-Assumptions: Assumptions: Role2Vec with a distance threshold of 0.5 (strict)
-Removed large self-authorization cluster
-
-Most clusters through graph representation learning
-Very dependent on threshold
-X \% use more than one address
-Large address clusters could be some bot behavior
-
-%Limitations: various assumptions, possibly false-positives, some clusters may well be undetected. 
-%other Limitations -> ENS pairs? Incorporate time-of-day/normalized gas into feature vectors, two step approach
-%Diskutiere alle resultate gemeinsam, vom anfangs set über on-chain und intra-set zu den clusters.
+
+Ultimately, we combined the results for each clustering heuristic mentioned above.
+Consequently, we managed to cluster 51,518 addresses, corresponding to 29,680 distinct entities.
+When adding the unclustered addresses, we identified 115,643 active users during the nine months, with 8,483 entities interacting through multiple addresses.
+\newline
+These results, however, are heavily influenced by the assumptions we made.
+We were conservative by setting a low distance threshold and treating all other addresses as individual entities.
+Raising the threshold would result in larger clusters and fewer entities.
+\newline
+The majority of addresses were clustered through graph representation learning methods.
+Unlike other clustering heuristics, this approach does not rely on specific on-chain behavior patterns or participation in particular events.
+Our implementation generally captures all addresses that have transferred within the address set at least once.
+Nevertheless, some clusters may still go undetected, while others may overestimate the number of addresses within a cluster.
+It is important to note that these methods are still only heuristics and testing the success on a large scale is not possible.
+\newline
+Role2Vec performed very best for our small test sample, but is not necessarily always be superior to Diff2Vec or DeepWalk.
+Incorporating time-of-day and normalized gas into feature vectors, or refining clusters using a two-step approach, requires further research but could enhance clustering results.
 
@@
 
+The goal of this research/thesis was to identify the number of entities represented by the 473,927 addresses observed in Decentraland between July 16, 2022 and April 23, 2023.
+By focusing on Ethereum and Polygon on-chain data, we narrowed the address set down to 137,544.
+
 Clustering heuristics -> specific on-chain events, user patterns, graph representation learning
@@
 Combination as extension
+Approach, especially our node embedding implementation can be used and extended to cluster other predefined address set
 
@@
 2. Clustering heuristics for account-based blockchains using on-chain data and on specific predefined address set
-3. Most successful graph representation learning because does not require participation in specific on-chain event / usage pattern
+3. Most successful graph representation learning because does not require participation in specific on-chain event / usage pattern, sehr vielversprechend
 4. From the various methods Role2Vec best
 5. Summarize Final results
-6. For researchers -> extend this approach -> apply it to other address sets -> package
-7.
+6. For researchers -> extend this approach -> apply it to other address sets -> add activity patterns ->
+7. Sth about bots
+8. Still a lot of natural activity on Decentraland and open infrastructure allows us to analyze it in detail as in this paper
 

### 2023-08-22 paper.tex
Edit introduction, preliminiaries, data collection

@@
 Public permissionless blockchains such as Bitcoin \citep{nakamotoBitcoin2008} and Ethereum \citep{buterin2014ethereum} allow users %individuals
- to participate with multiple pseudonymous addresses, the creation of which is virtually cost free.
+ to participate with multiple pseudonymous addresses, the creation of which is virtually cost-free.
 Contrary to popular belief, these blockchains are entirely transparent.
 All transactions are publicly observable and stored as part of the blockchain's history.
-This has opened up a nascent scientific field dealing with entity identification within blockchain networks.
+This circumstance has opened up a nascent scientific field dealing with entity identification within blockchain networks.
 Researchers try to cluster addresses controlled by the same user by analyzing on-chain data and detecting usage patterns.
@@
 %The majority of these methods are heuristic which often makes them difficult to evaluate due to the absence of any ground truth.
-\newline On one hand, identifying the addresses that belong to the same real-world entity is beneficial.
-According to \cite{FV:17} it allows better evaluation of network properties with respect to usage, distribution of wealth and detecting fraudulent activities.
+\newline On one hand, identifying addresses that belong to the same real-world entity is beneficial as it allows for better evaluation of network properties concerning usage, distribution of wealth, and detecting fraudulent activities \citep{FV:17}.
 For instance, if a user distributes their voting power across various addresses, they might manipulate an on-chain voting process that seems fair at the outset.
 \newline
-Conversely, the lack of privacy is also detrimental to most financial use cases (DeFi).
-As a response, multiple privacy-enhancing tools and protocols have been proposed to obfuscate transaction tracing.
-Nonetheless, these protocols are not yet widely adopted and careless user behaviour can undermine the privacy guarantees they offer. \newline
+Conversely, the lack of privacy is also detrimental to most financial use cases. As a response, multiple privacy-enhancing tools and protocols have been proposed to obfuscate transaction tracing. 
+Nonetheless, these protocols have yet to be widely adopted, and careless user behavior can undermine the privacy guarantees they offer. \newline
 With these considerations in mind, the topic of privacy, or lack thereof, will remain significant for future blockchain development and research.
@@
 \textbf{Related work}\\
-Previous work in this field can be broadly distinguished between methods developed for the unspent transaction output (UTXO) model (e.g, Bitcoin and ZCash) and the account-based model (e.g., Ethereum and Polygon).
-While both models share the concept of addresses, the notion of accounts is not present in UTXO-based blockchains.
+Previous work in this field can be broadly distinguished between methods developed for the unspent transaction output (UTXO) model (e.g., Bitcoin and ZCash) and the account-based model (e.g., Ethereum and Polygon).
+While both models share the concept of addresses, the notion of accounts is absent in UTXO-based blockchains.
 The way in which transactions are processed is fundamentally different, and therefore, clustering heuristics are not applicable to both paradigms.
@@
 As suggested by \cite{nakamotoBitcoin2008} in the Bitcoin whitepaper, most Bitcoin wallet implementations use a new key pair for each transaction to keep them from being linked to a common owner.
-Unlike the UTXO-model, native transactions in account-based blockchains can only move funds between a single sender and receiver, and the ``change`` remains in the sender account.
+Unlike the UTXO model, native transactions in account-based blockchains can only move funds between a single sender and receiver, and the ``change`` remains in the sender account.
 Subsequent transactions necessarily use the same address again.
-The account-based model essentially relies on address reuse on the protocol level \citep{Beres2020}.
+The account-based model essentially relies on address reuse at the protocol level \citep{Beres2020}.
 Consequently, privacy guarantees should be lower as participants typically use a limited set of addresses.
@@
 Their approach interprets transactions or token transfers as network graphs, with addresses as nodes and asset transfers as edges.
-They quantitavely compare graph-representation learning algorithms (a subset of machine learning) and propose further user profiling techniques based on time-of-day activity and transaction fee patterns.
+They quantitatively compare graph-representation learning algorithms (a subset of machine learning) and propose further user profiling techniques based on time-of-day activity and transaction fee patterns.
 Using ENS address pairs as ground truth, the authors rigorously test their methods and apply their findings to significantly reduce the privacy guarantees of \textit{Tornado Cash}, a non-custodial privacy-enhancing protocol on Ethereum.
 \newline
-\cite{wu2022tutela} extend on one of \cite{Beres2020} graph representation learning %node-embedding
- algorithms and apply it at scale.
+\cite{wu2022tutela} extend on one of \cite{Beres2020} graph representation learning algorithms and apply it at scale.
 Further, they also propose a set of new clustering heuristics targeting Tornado Cash,  showing that careless user behavior can still reveal identity.
 Based on those heuristics, they developed an application to measure the anonymity of an Ethereum address.
-\newline All of the aforementioned methods will be discussed in greater depth in Section 3.
+All of the aforementioned methods will be discussed in greater depth in Section 3.
 \newline
@@
 Similarly, \cite{casalebrunet2021} apply network graph analysis to various non-fungible token (NFT) ecosystems.
-Both find that many of the networks follow either a star or a hub-and-spoke pattern, common to interaction graphs in social networks.
-Moreover, \cite{Payette2017} propose a segmentation of the Ethereum address space into four distinct behaviour groups sharing similar attributes while using k-means clustering.
-\newline
-Rather than treating users as entities and analyzing on-chain data, \cite{yu2023} propose (a novel) approach for correlation analysis by exploiting network information.
-Although this approach has the potential to avoid the impact of privacy-enhancing technologies, it introduces a new set of limitations and problems.
-Thus, this approach may be of great interest for future research, particularly when privacy-enhancing techniques become more widely used.
+Both find that many networks follow a star or a hub-and-spoke pattern, similar to social network interaction graphs.
+Moreover, \cite{Payette2017} propose a segmentation of the Ethereum address space into four distinct behavior groups sharing similar attributes while applying k-means clustering.
+\newline
+Rather than treating users as entities and analyzing on-chain data, \cite{yu2023} propose a novel approach for correlation analysis by exploiting network information.
+Although this approach can potentially avoid the impact of privacy-enhancing technologies, it introduces new limitations and problems.
+Thus, this method may be of great interest for future research, particularly when privacy-enhancing techniques become more widely used.
 
@@
 In this work, we perform entity identification on an address set containing 473,927 addresses.
-To obtain these addresses, a separate project collected snapshots of avatar activity in Decentraland over an nine-month period from July 2022 to April 2023.
+To obtain these addresses, a separate project collected snapshots of avatar activity in Decentraland over nine months from July 2022 to April 2023.
 Due to Decentraland's blockchain-based architecture, each avatar contains information about a user's Web3 address.
@@
 We test the applicability of existing heuristics, and if feasible, their efficacy in detecting entities using multiple addresses is evaluated.
-The main objective is to estimate the number of real-world entities that these addresses represent. The clustering of addresses is limited to this set only, without considering any %(clusters for)
- addresses outside of it, e.g., that were not registered in Decentraland during the given time frame. \newline
-Furthermore, we introduce our own heuristic for identifying address clusters and evaluate its suitability for implementation in other contexts.
-%Anwenden/discuss and evaluate existing heuristics to my specific address set.
-%Anpassen, erweitern
-%We are the apply this approach to a predefind set of addresses at scale to cluster addresses within this set
-
-The remainder of this paper is structured as follows: In Section 2, we provide a brief overview of the basic concepts necessary to understand the setup.
-This includes Ethereum accounts and the EVM, tokens, Decentraland, and privacy-enhancing protocols.
+The main objective is to estimate the number of real-world entities these addresses represent.
+The clustering of addresses is limited to this set only, without considering any addresses outside of it, e.g., that were not registered in Decentraland during the given time frame.
+Furthermore, we introduce our heuristic for identifying address clusters and evaluate its suitability for implementation in other contexts.
+As of our knowledge, we are the first to cluster addresses within a predefined set on a large scale.
+%Anwenden/discuss/anpassen/erweitern and evaluate existing heuristics to my specific address set.
+
+The remainder of this paper is structured as follows: In Section 2, we provide a brief overview of the basic concepts necessary to understand the setup, including Ethereum accounts, tokens, Decentraland, and privacy-enhancing protocols.
 Section 3 describes our methodology for data collection and preparation.
@@
 \section{Preliminaries}
-% Introduce section
+
 \subsection{Contract Accounts and EOAs}
@@
 \subsection{Ethereum, Polygon and the EVM}
-Ethereum and Polygon are both smart contract based account-model blockchains. They share the same execution logic - the Ethereum Virtual machine (EVM).
+Ethereum and Polygon are both smart contract-based account-model blockchains. They share the same execution logic - the Ethereum Virtual Machine (EVM).
 The EVM provides a standardized framework for contract execution, ensuring that smart contracts produce deterministic results across all nodes in the network \citep{GW:14}.
-The EVM is independent of the underlying blockchain protocol.
-This allows other blockchain implementations to adopt this standardized framework for contract execution.\newline
+The EVM is independent of the underlying blockchain protocol, allowing other blockchain implementations to adopt this standardized framework for contract execution.\newline
 \textit{Polygon} is a so-called sidechain and aims to address the scalability limitations of Ethereum.
 The adoption of the EVM means that both blockchains share the same user address schemes.
-It further enables developers to deploy and execute Ethereum-based smart contracts on the Polygon network with minimal changes.
+It also enables developers to deploy and execute Ethereum-based smart contracts on the Polygon network with minimal changes.
 \citep{matic_whitepaper}
-%A high-level programming language is typically used to write smart contracts, and a compiler to convert them into bytecode \citep{mastering_ethereum}.
-Solidity is currently the dominant smart contract language.
-%Polygon PoS is a so-called sidechain, closely associated with Ethereum mainnet and used for scaling.
-%Ethereum Mainnet is the chain on which much of the Decentraland infrastructure has been deployed.
-%In addition, \cite{eip1014} introduces a new contract creation mechanism allowing for more predictable contract addresses.%EIP-1014
-%This allows developers to calculate the address of a contract before it is deployed.
+%A high-level programming language is typically used to write smart contracts, and a compiler to convert them into bytecode \citep{mastering_ethereum}
 
@@
 
-%Token standards specify basic interfaces that allow for interoperability between contracts.
-These standards do not prescribe an implementation but set minimum requirements without restricting the design beyond that.
-ERC-20 (fungible), ERC-721 (non-fungible) or ERC-1155 (semi-fungible) are the most widely used token standards.
-\newline
-
 \subsection{Decentraland}
-\textit{Decentraland} is the first large-scale blockchain-based virtual world.
-Well-known companies like Tommy Hilfiger, Samsung, PepsiCo, Diesel, Adidas, and Netflix, are actively engaging in Decentraland  \citep{metaverse-retailing2023}.\newline
-Decentraland is an ideal platform for empirical research for two main reasons.
-\textit{First}, its open architecture allows compiling snapshots of user activity, including the users' locations  within the metaverse.
-This was done by \cite{metaverse-retailing2023}, who captured snapshots of avatar locations over a period of nine months.
-The addresses they collected are used for this thesis.
-\textit{Second}, users who connect their Web3 account can own various digital assets, such as monetary units, land parcels, and avatar collectibles (e.g.
-wearables, emotes, and names).
+\textit{Decentraland} is the first large-scale blockchain-based virtual world, with well-known companies like Tommy Hilfiger, Samsung, PepsiCo, Diesel, Adidas, and Netflix actively engaging in it \citep{metaverse-retailing2023}.\newline
+Two main reasons make Decentraland an ideal platform for empirical research.
+\textit{First}, its open architecture allows compiling snapshots of user activity, including the users' location within the metaverse and Web3 address.
+Using this capability, \cite{metaverse-retailing2023} captured snapshots of avatar locations over a nine-month period and provided the Web3 addresses collected for this thesis.\newline
+\textit{Second}, users who connect their Web3 account can own various digital assets, such as monetary units, land parcels, and avatar collectibles (e.g., wearables, emotes, and names).
 Smart contracts on Ethereum and Polygon track and manage the ownership of these assets \citep{goldbergschaer2023}.
-This allows us to analyze the entire transaction history and derive information about the users' economic activity.
-%avatars'
+This allows us to analyze the entire transaction history and derive information about the avatars' economic activity.
 \newline
@@
 \newline
-Moreover, the Decentraland core developers provide a smart-contract-based marketplace where users may buy or exchange LAND or other in-game collectibles. %developers/core team
+Moreover, the Decentraland core developers provide a smart-contract-based marketplace where users can buy or trade LAND or other in-game collectibles.
 
@@
 %Goods: in-world assets, such as avatar wearables, merchandise, or tickets, as well as tokenized vouchers that can be redeemed for real-world goods or services.
-%The Decentraland ecosystem has two main tokens.
 
@@
 In the custodial setup, users send their assets to a centralized service provider's public deposit address.
-After some delay, the provider sends the assets back to a privately relayed recipient address.
+After some delay, the provider returns the assets to a privately relayed recipient address.
 This approach is fully trust-based, as the service provider has complete control over the assets and access to the identifying data.
-\newline
+\citep{nadler2023tornado} \newline
 In contrast, non-custodial crypto asset mixers (e.g., Tornado Cash) replace the trusted mixing party with a publicly verifiable smart contract.
 They rely on cryptographic schemes that allow anyone to prove and independently verify the validity of a withdrawal without disclosing the link to a specific deposit.
-This has the advantage that users do not have to share the identifying information with anyone and there is no liquidity risk as the funds are locked.
+This approach has the advantage that users do not have to share the identifying information with anyone, and there is no liquidity risk as the funds are locked.
 \citep{nadler2023tornado} \newline
-In a nutshell, the mixer works in the following way: Various entities deposit the same amount of a specific crpyto asset to a mixer address acting as a pool.
+In a nutshell, the mixer works in the following way: Various entities deposit the same amount of a specific crypto asset to a mixer address acting as a pool.
 Anyone who has contributed to the pool may then generate a new address and withdraw their funds without revealing the link between the deposit and withdrawal addresses.
-This is achieved using zkSNARKs (zero knowledge, succinct, non-interactive argument of knowledge).
-Each depositor inserts a hash value in a Merkle-tree.
-At the time of withdrawal, each legitimate withdrawer can prove unlinkably with a zero-knowledge proof that they know the pre-image of a previously inserted hash leaf in the Merkle-tree.
-%Subsequently, users can withdraw their asset from the mixer whenever they consider that the size of the anonymity set is satisfactory.
+This is achieved using zkSNARKs (zero-knowledge, succinct, non-interactive argument of knowledge).
+Each depositor inserts a hash value in a Merkle tree.
+At the time of withdrawal, each legitimate withdrawer can prove unlinkably with a zero-knowledge proof that they know the pre-image of a previously inserted hash leaf in the Merkle tree.
+%Subsequently, users can withdraw their assets from the mixer whenever they consider that the size of the anonymity set is satisfactory.
  For a more detailed description of how Tornado Cash works, see \cite{nadler2023tornado} or \cite{Beres2020}. \newline
@@
 The set of all deposits that a particular withdrawal could be originated from is defined as the \textit{anonymity set}.
-In theory, a larger anonymity set will provide a higher level of privacy, since  any withdrawal address could be linked to more deposit addresses.
-However, in practice this does not always hold true.
-%this is not always the case
-Some users reveal the link between their withdrawal and deposit addresses, which also affects the privacy of other depositors.
-For example, by withdrawing from the pool with the same address they deposited or directly sending funds between the two addresses.
-According to \cite{nadler2023tornado}, careless use of the protocol, testing transactions or external incentive mechanisms might be reasons for this behaviour.
+In theory, a larger anonymity set will provide a higher level of privacy since any withdrawal address could be linked to more deposit addresses. However, in practice, this does not always hold.
+Some users reveal the link between their withdrawal and deposit addresses, which also affects the privacy of other depositors, for example, by withdrawing from the pool with the same address they deposited or directly sending funds between the two addresses.
+According to \cite{nadler2023tornado}, careless use of the protocol, testing transactions, or external incentive mechanisms might be reasons for this behaviour.
 \newline
@@
 
-\iffalse
-In theory, a larger anonymity set will provide a higher level of privacy as third parties will not be able to link a specific depositor address to a specific withdrawal address.
+%In theory, a larger anonymity set will provide a higher level of privacy as third parties will not be able to link a specific depositor address to a specific withdrawal address.
 However, this is not always the case.
@@
 \newline
-In addition, \cite{Beres2020} and \cite{wu2022tutela} propose approaches to de-anonymize Tornado cash transactions using various clustering heuristics.
+%In addition, \cite{Beres2020} and \cite{wu2022tutela} propose approaches to de-anonymize Tornado cash transactions using various clustering heuristics.
 These methods are discussed in more detail in section 4.
@@
 %making use of address re-use, transaction activity, transaction cost choice, or more complex transaction graph and network analyses.
-\fi
 
@@
 \section{Data Collection and Preparation} 
-% Introduction Satz - Ausgangslage 
-The starting point for our work was a dataset comprising 473,927 distinct (Web3) addresses. %The original dataset comprised 473,927 distinct (Web3) addresses.
+The starting point for our work was a data set comprising 473,927 distinct Web3 addresses. %The original data set comprised 473,927 distinct (Web3) addresses.
  As we focus on clustering methods using on-chain data, we exclude addresses that have not been recorded on either Ethereum or Polygon.
@@
 By using our network-specific address subsets, we were able to significantly decrease the number of required API calls.
-We gathered all transactions and token transfers up until block \texttt{17,670,000} on Ethereum (July 11, 2023) and block \texttt{44,990,000} on Polygon (July 12, 2023).
+We gathered all transactions and token transfers up until block number \texttt{17,670,000} on Ethereum (July 11, 2023) and \texttt{44,990,000} on Polygon (July 12, 2023).
 In total, we collected more than 30 million %30,689,978
@@
 \label{sec:intra-set}
-%In this thesis
 We want to employ entity clustering heuristics to determine the number of entities represented by the remaining 137,544 addresses.
@@
 To achieve this, we often only consider transactions or token transfer events where both the ``\texttt{from}`` (sender) and the ``\texttt{to}`` (recipient) address are within the address set.
-We call this reduced dataset ``intra-set asset transfers``.
-Regarding normal transactions, this means that we only keep native asset transfers/payments (Ether or Matic) as almost all addresses are EOAs.
-\newline
-The intra-set asset transfer dataset is mainly used to generate the network graphs (see Section \ref{sec:node}). %used for the node embedding methods
+We call this reduced data set ``intra-set asset transfers``.
+Regarding normal transactions, this means that we only keep native asset transfers (payments), as almost all addresses are EOAs.
+\newline
+The intra-set asset transfer data set is mainly used to generate the network graphs (see Section \ref{sec:node}).
 When clustering addresses using graph-based approaches, this has the advantage that we do not need to differentiate between EOA and smart contract account later on.
@@
 
-\iffalse
-%further simplifies the clustering process. \newline
 %(logging in to Decentraland with multiple addresses) When it comes to entity clustering, we essentially want to answer the question of how many real-world entities our remaining  137,544 addresses represent.
--Also for other clustering heuristics we often make this reduction, for example: In the self-approval approach, we only consider approval transactions where another address from the set is approved.
--filter our transactions and token transfers to entries where both the 'from' and the 'to' are within this narrowed pool of addresses.
+%filter our transactions and token transfers to entries where both the 'from' and the 'to' are within this narrowed pool of addresses.
 We define this as intra-set asset transfers.
@@
 %between two EOAs
--As already mentioned in the introduction, the goal of this paper is to cluster addresses within who (1) were active in Decentraland during the 9-month period (e.g., within the initial dataset) and (2) transacted or interacted with any token on Ethereum or Polygon.
--Essentialy, we want to answer two main research questions when it comes to clustering:
-1. How many unique entities does the address set represent (i.e. were active on Decentraland during the 9-month period)?
-2. Are users interacting through multiple accounts/EOAs/addresses with Decentraland?
--we focus on on-chain data (and not user location or avatar data), allowing us to exclude addresses that have not transacted or interacted with any token on Ethereum or Polygon. 
--As mentioned in the introduction, the goal of this paper is to cluster addresses belongig to the same entity that were recorded/active in Decentraland during the 9-month period.
+%we focus on on-chain data (and not user location or avatar data), allowing us to exclude addresses that have not transacted or interacted with any token on Ethereum or Polygon. 
+%As mentioned in the introduction, the goal of this paper is to cluster addresses belongig to the same entity that were recorded/active in Decentraland during the 9-month period.
 Therefore, we disregard addresses outside of this set.
@@
 Doing these two reductions, there are  141, 591 'clusterable' addresses remaining.
--Since all of our addresses are EOAs (some multisig smart contract wallets). -> Check this?
-\fi
+%Since all of our addresses are EOAs (some multisig smart contract wallets).
 
@@
 
-We applied the following methodology to find ground truth pairs: \textit{First}, we gathered all addresses that interacted with ENS (NFTs) to reduce the amount of name look-ups.
-\textit{Second}, we iterated over each remaining address and checked if it reverse-resolved to an ENS domain\footnote{This was done via the ENS module within web3.py \url{https://web3py.readthedocs.io/en/stable/ens_overview.html}, which provides an interface to look up domains and addresses.}.
+We applied the following methodology to find ground truth pairs: \textit{First}, we gathered all addresses that interacted with ENS to reduce the amount of name look-ups.
+\textit{Second}, we iterated over each address and checked if it reverse-resolved to an ENS domain\footnote{This was done via the ENS module within web3.py \url{https://web3py.readthedocs.io/en/stable/ens_overview.html}, which provides an interface to look up domains and addresses.}.
 If so, we logged the ENS domain and address in a CSV file.
@@
 From this, we identified 11,440 reverse records and 40 pairs of addresses pointing to the same ENS name, which we utilized as our ground truth to evaluate various clustering heuristics.
-Although this sample is relatively small, it allows us to assess and draw conclusions about the effectiveness of the methods.%profiling techniques/methods
-
-\iffalse
--Check for each address in the list if the address points to an human-readable name.
+Although this sample is relatively small, it allows us to assess and draw conclusions about the effectiveness of the methods.
+
+%Check for each address in the list if the address points to an human-readable name.
 (reverse mapping must be set/configured) From the web3.py documentation \url{https://web3py.readthedocs.io/en/stable/ens_overview.html } %The ens module is included with web3.py.
 It provides an interface to look up domains and addresses, add resolver records, or get and set metadata.
--If two addresses point to the same ENS name we consider them belonging to the same entity. 
--Normally, one .eth domain cannot point/map to multiple Ethereum addresses. Forward resolution. This is likely due to the owner change and the record not updated.
-
-%However, if someone sets the forward resolution to a new address (owner) including a reverse resolution for his ENS name, the (reverse) resolution from 0x05d.addr.reverse still resolves to the the ENS domain name.
+%If two addresses point to the same ENS name we consider them belonging to the same entity. 
+%Normally, one .eth domain cannot point/map to multiple Ethereum addresses. Forward resolution. This is likely due to the owner change and the record not updated.
 %Only the forward resolution from the name to the address is changed.
@@
 For an visual explanation please see Figure \ref{fig:ENS}.
-%In addition to regular resolution from name to address, ENS also supports ``reverse resolution``, making it possible to map from address back to a name (or other metadata).
 %Anyone who owns a domain at any level may configure subdomains - for themselves or others - as desired.
@@
 %If the owner sets a reverse resolution set with his new address, we have two addresses pointing to the same ens name. 
-
 %While 'regular' resolution involves mapping from a name to an address, reverse resolution maps from an address back to a name - or other metadata.
@@
 
-\fi
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 In Section 5, we will implement and evaluate the heuristics we determine to be suitable for our objectives.
-
-% Goal: explain each heuristic, categorize, and discuss applicability to our address set
+%Goal: explain each heuristic, categorize, and discuss applicability to our address set
 %In Section 5 we will then apply  and, if possible, evaluate the heuristics deemed suited for us.
-%intuition
 
@@
 The latter function also appears in the ERC-1155 standard.
-The approval functionality of these tokens is primarily used in connection with smart contracts (DEX or NFT Marketplace), but can also be applied for regular EOAs.
+The approval functionality of these tokens is primarily used in connection with smart contracts (Decentralized Exchanges or NFT Marketplaces), but can also be applied for regular EOAs.
 \newline
@@
 \newline
-Since our dataset includes all address transactions, we can easily employ this heuristic. %Since all the addresses' transactions are available in our dataset, we are able to apply this heuristic.
+Since all the addresses' transactions are available in our data set, we can easily employ this heuristic. %Since our data set includes all address transactions, we can easily employ this heuristic. %
 
@@
 It is highly likely that multiple addresses sending funds to the same deposit address are controlled by the same entity.
-They key challenge of this approach lies in identifying these deposit addresses, which could either be EOAs or smart contracts.
+The key challenge of this approach lies in identifying these deposit addresses, which could either be EOAs or smart contracts.
 \citep{FV:17}\newline
@@
 Two parameters are essential for deposit address detection: the discrepancy between the amount received and forwarded (since the exchange must pay gas fees), and the time lag between receiving and forwarding funds.
-However, our dataset only includes the direct transactions or token transfers associated with the addresses.
+However, our data set only includes the direct transactions or token transfers associated with the addresses.
 The transactions between deposit and main exchange address are absent.
-Consequently, this clustering heuristic is not applicable.
-%with our data
+Consequently, this clustering heuristic is not applicable %with our data
+ and would require significantly more effort for gathering the required data.
 
@@
 Therefore, we do not apply this clustering heuristic here.
-Since we only collected the addresses' direct transactions or token transfers, the second step between deposit and exchange address is not available/present in our dataset. 
+Since we only collected the addresses' direct transactions or token transfers, the second step between deposit and exchange address is not available/present in our data set. 
 \fi
@@
 Nevertheless, to test this approach we searched for addresses that forwarded the UNI airdrop to another address.
-We found eight such transfers, but none involved two addresses sending to a third address.
+We found eight such transfers, but none involved two addresses sending funds to a third address.
 
@@
 \iffalse
-%write here that we tested different datasets to create the network graph but intra-set asset transfers performed best for our task.
+%write here that we tested different data sets to create the network graph but intra-set asset transfers performed best for our task.
 \textbf{Diff2Vec} % Neighborhood preserving 
@@
 
-%As described in previous sections, we tested different datasets to create the network graph using our ENS address pairs as ground truth.
+%As described in previous sections, we tested different data sets to create the network graph using our ENS address pairs as ground truth.
 Der Approach ist zwar stark an Beres angelehnt, jedoch wendet er es an um pairs of deposit und withdrawal addressen zu clustern.
@@
   \end{tabular}
-  \caption{Database/Dataset Description}
+  \caption{Database/data set Description}
   \label{tbl:database_schema}

### 2023-08-22 paper.tex
Minor corrections all over the paper

@@
  For a more detailed description of how Tornado Cash works, see \cite{nadler2023tornado} or \cite{Beres2020}. \newline
-In the context of this work, it is sufficient to know that third parties can still observe the addresses that have deposited to and withdrawn from the pool.
+In the context of this thesis, it is sufficient to know that third parties can still observe the addresses that have deposited to and withdrawn from the pool.
 The set of all deposits that a particular withdrawal could be originated from is defined as the \textit{anonymity set}.
@@
 Some users reveal the link between their withdrawal and deposit addresses, which also affects the privacy of other depositors, for example, by withdrawing from the pool with the same address they deposited or directly sending funds between the two addresses.
-According to \cite{nadler2023tornado}, careless use of the protocol, testing transactions, or external incentive mechanisms might be reasons for this behaviour.
+According to \cite{nadler2023tornado}, careless use of the protocol, testing transactions, or external incentive mechanisms might be reasons for this behavior.
 \newline
@@
 We gathered all transactions and token transfers up until block number \texttt{17,670,000} on Ethereum (July 11, 2023) and \texttt{44,990,000} on Polygon (July 12, 2023).
-In total, we collected more than 30 million %30,689,978
+In total, we collected over 30 million %30,689,978
 token transfer events and more than 16 million %16,092,531
@@
 This domain is owned by a special purpose registrar contract that allocates subdomains to the owner of the matching address - for instance, the address \texttt{`0x1234\dots`} may claim the name \texttt{`1234\dots.addr.reverse`}, and configure a resolver and records on it.
-The resolver in turn supports the \texttt{name()} function, which returns the name associated with that address.\newline
+The resolver in turn supports the \texttt{name()} function, which returns the ENS domain associated with that address.\newline
  Reverse resolution %(without a library)
@@
 The latter function also appears in the ERC-1155 standard.
-The approval functionality of these tokens is primarily used in connection with smart contracts (Decentralized Exchanges or NFT Marketplaces), but can also be applied for regular EOAs.
+The approval functionality of these tokens is primarily used in connection with smart contracts (e.g., Decentralized Exchanges or NFT Marketplaces), but can also be applied for regular EOAs.
 \newline
@@
 Consequently, this clustering heuristic is not applicable %with our data
- and would require significantly more effort for gathering the required data.
+ and it would require significantly more effort for gathering the required data.
 
@@
 He defines multi-participation when two airdrop recipients forward their tokens to a single address.
-Since we do not have a whole view of the airdrop distribution events, we are not able to find them using our data.
-One possible approach would be to manually select known airdrops.
+Since we do not have a whole view of the airdrop distribution events, we are not able to find them within our data.
+One possible approach would include manual selection of known airdrops.
 However, this process takes very long and is not guaranteed to cluster a lot of addresses, since most new airdrop events were made with some kind of sybil-resistance.
@@
 
-\iffalse
-Airdrops are a popular mechanism to distribute tokens.
-On the Ethereum blockchain, they are performed through smart contracts.
-The owners of the smart contract choose recipients either based on past activity, or ask users to sign up through online forms.
-Some of these registration processes require users to perform certain actions on social media, such as posting articles or following users.
-The amount of tokens given to each user is either fixed, or based on existing account balances.
-If the amount is fixed, there is an incentive to cheat the system.
-We identify Airdrops where a fixed number of tokens is distributed to many recipients. Then we search for addresses that have been forwarded the same amount from the initial recipients. 
-This heuristic depends on two inputs.
-First, a set of aidrops with equal mounts, characterized by a signature of a distributing address, a token network and an amount.
-Second, the minimum nuber of token aggregations into a single address.
-The second parameter is trivial to choose, as multi-participation in its smallest form consist of two aidrop recipient addresses forwarding their tokens to a third adddress.
-In this case, a single entity would be in control of at least 3 addresses.
-The main challenge lies in identying airdrops. To do so, we first examine all same-source, fixed amount token distributions.
-\fi
-
-\subsection{Node embeddings}
+\subsection{Graph representation learning}
 \label{sec:node}
-
-According to \cite{Beres2020}, \textit{node embedding} methods form a class of network representation learning\footnote{Sometimes also referred to as ``graph representation learning``} methods that map graph nodes to vectors in a low-dimensional vector space.
+According to \cite{Beres2020}, \textit{node embedding} methods form a class of graph representation learning\footnote{Sometimes also referred to as ``network representation learning``} methods that map graph nodes to vectors in a low-dimensional vector space.
 These methods aim to represent vertices with similar neighborhood structure by vectors that are close in the vector space.
@@
 \cite{Beres2020} first introduced this approach on a Ethereum transaction graph for the purpose of entity identification to pair Ethereum addresses associated with Tornado cash deposits and withdrawals.
-Building on this, \cite{wu2022tutela} refined and expanded one particular node embedding method to deanonymize Ethereum users at scale.
+Building on this, \cite{wu2022tutela} refined and expanded one particular node embedding algorithm to deanonymize Ethereum users at scale.
 \newline
@@
 
-Apart from the node embedding methods applied to Ethereum transaction graphs, \cite{Beres2020} suggest employing clustering heuristics based on time-of-day transaction activity and gas price distribution.
+Apart from the node embedding methods applied to Ethereum transaction graphs, \cite{Beres2020} suggest employing clustering heuristics based on time-of-day transaction activity and gas price selection patterns.
 \newline
@@
 These UNIX timestamps are transformed into hour-of-the-day-based values.
-The authors argue that account owners may expose daily activity patterns and represent addresses by a vector including the mean, median and standard deviation, as well as an activity histogram divided into 4-6 hour bins \citep{Beres2020}.
+The authors argue that account owners may expose daily activity patterns and represent addresses by a vector including the mean, median and standard deviation, as well as an activity histogram divided into four to six hour bins \citep{Beres2020}.
 Figure \ref{fig:ToD} illustrates the time-of-day activity histogram and kernel density estimation (KDE) for a selected ENS address pair, divided into two hour intervals.\newline
@@
 Selecting the the fast option would ensure almost immediate inclusion in the blockchain.
-To account for the changes in Ethereum traffic volume, the gas price is normalized by the daily network average.
-The combination of gas price levels a user select forms their personal gas price profile.
+To account for changes in Ethereum traffic volume, the gas price is normalized by the daily network average.
+The combination of gas price levels users select forms their personal gas price profile.
 An account is represented by a vector including the mean, median, and standard deviation and a normalized gas price histogram divided into 50 bins, which they determined to be optimal for clustering performance.
 \citep{Beres2020} \newline
-We will not employ both methods due to their significantly poorer performance compared to node embeddings.
+We will not employ both methods due to their significantly poorer stand-alone performance compared to node embeddings.
 Nevertheless, we test a two-step approach: In the first step, we implement Diff2Vec to find the 10 nearest neighbors.
@@
 In addition to the existing clustering heuristics, we propose our own heuristic based on transfers of high-value NFTs such as LAND.
-We argue that, given the high value of Decentraland land parcels, there is a strong likelihood that addresses are controlled by the same entity when LAND is transferred without any compensation.
-A user might perform such transfers to rearrange their LAND holdings, e.g., by upgrading to a more secure wallet.
+We argue that, given the high value of Decentraland's land parcels, there is a strong likelihood that addresses are controlled by the same entity when LAND is transferred without any compensation.
+Users might perform such transfers to rearrange their LAND holdings, e.g., by upgrading to a more secure wallet.
 \newline
 The primary challenge of this approach is to detect LAND transfers without any compensation.
-To accomplish this, we identify token or native asset transfers/payments that took place within the same transaction as a LAND transfer.
+To accomplish this, we identify token or native asset transfers that took place within the same transaction as a LAND transfer.
 Upon manually examining various implementations of LAND trades on the most popular NFT marketplace contracts, we noticed a recurring pattern: the user address appears in both the ``from`` and ``to`` fields if a trade takes place.
@@
 Figure \ref{fig:threshold_sensitivity} shows the histogram of cluster sizes and Table \ref{tbl:cluster_table} displays the number of resulting clusters depending on various threshold values.
-We chose said values after looking at the distance between ground truth pairs.
+We chose said values after observing the distance between ground truth pairs.
 For better visibility, we only display clusters below 20 addresses in Figure \ref{fig:threshold_sensitivity}.
@@
 
-To implement this clustering heuristic, we select all transaction hashes of LAND transfers between two Decentraland addresses.
+To implement the LAND transfer clustering heuristic, we select all transaction hashes of LAND transfers between two Decentraland addresses.
 Next, we gather all token and native asset transfers associated with the selected transaction hashes.
@@
 \newline
-LAND transfers between Decentraland addresses can also be visualized as a token network graph.
-Figure \ref{fig:LAND_network} presents the resulting graph.
-In this graph, red edges signify simple transfers, whereas blue edges represent LAND transfers made as part of a trade/purchase.
+LAND transfers between Decentraland addresses can also be visualized as a token network graph, as shown in Figure \ref{fig:LAND_network}.
+In this graph, red edges signify simple transfers, whereas blue edges represent LAND transfers made as part of a trade.
 Notably, the 71-address cluster previously mentioned is visible on the top-right of the largest connected component.
@@
 We also encountered a significant number of false-positives due to non-standard implementations.
-We are very confident that this cluster is not controlled by the same entity, and therefore remove it.
+We are very confident that the large cluster is not controlled by the same entity, and therefore remove it.
 After excluding these instances, we identified a total of 15 entities consisting of 35 addresses.
@@
 \newline
-The main assumption behind this approach is that users may want to reorganize their accounts from time to time, mostly to increase security guarantees or spread the risk around multiple accounts.
-As a concrete example, some users may have started with a simple browser-based wallet but as the value of their assets increased and their knowledge grew, they changed to a more secure hardware wallet.
+The main assumption behind this approach is that users may want to reorganize their accounts from time to time, mostly to increase security guarantees or spread the risk across multiple accounts.
+As a concrete example, some users may have started with a simple browser-based wallet but as the value of their assets increased and their knowledge grew, they switched to a more secure hardware wallet.
 We detect 161 entities with 413 addresses applying this approach.
@@
 Nevertheless, some clusters may still go undetected, while others may overestimate the number of addresses within a cluster.
-It is important to note that these methods are still only heuristics and testing the success on a large scale is not possible.
-\newline
-Role2Vec performed very best for our small test sample, but is not necessarily always be superior to Diff2Vec or DeepWalk.
+It is important to note that these methods are still only heuristic and testing their efficacy on a large scale is not possible.
+\newline
+Role2Vec performed best for our small test sample, but is not necessarily always be superior to Diff2Vec or DeepWalk.
 Incorporating time-of-day and normalized gas into feature vectors, or refining clusters using a two-step approach, requires further research but could enhance clustering results.
@@
 
-The goal of this research/thesis was to identify the number of entities represented by the 473,927 addresses observed in Decentraland between July 16, 2022 and April 23, 2023.
+The goal of this thesis was to identify the number of entities represented by the 473,927 addresses observed in Decentraland between July 16, 2022 and April 23, 2023.
+
+All blockchain transaction and token transfer data is publicly available. This allows us to apply various heuristics to cluster addresses belonging to the same entity by exploiting activity patterns.
+
 By focusing on Ethereum and Polygon on-chain data, we narrowed the address set down to 137,544.
+
+We found .... to be applicable to cluster a predefined address set. The approaches had to be modified and extended.
 
@@
 7. Sth about bots
-8. Still a lot of natural activity on Decentraland and open infrastructure allows us to analyze it in detail as in this paper
+
+8. Still a lot of natural activity on Decentraland and open infrastructure allows us to analyze it in detail as in this paper, exciting to analyze other things, endless possibilities.
+Address clustering will  make further advancements.
+From a user perspective it is important that privacy enhancing protocols are also further developed and users educated how to preserve privacy when transacting on blockchains.
+/ in the context of blockchains
 

### 2023-08-22 paper.tex
Update conclusion topics

@@
 
-The goal of this thesis was to identify the number of entities represented by the 473,927 addresses observed in Decentraland between July 16, 2022 and April 23, 2023.
-
-All blockchain transaction and token transfer data is publicly available. This allows us to apply various heuristics to cluster addresses belonging to the same entity by exploiting activity patterns.
-
-By focusing on Ethereum and Polygon on-chain data, we narrowed the address set down to 137,544.
-
-We found .... to be applicable to cluster a predefined address set. The approaches had to be modified and extended.
-
-Clustering heuristics -> specific on-chain events, user patterns, graph representation learning
-Best -> graph representation learning
-Combination as extension
-Approach, especially our node embedding implementation can be used and extended to cluster other predefined address set
-
-1. Public blockchain -> all data available -> allows us to analyse it and find information
-2. Clustering heuristics for account-based blockchains using on-chain data and on specific predefined address set
-3. Most successful graph representation learning because does not require participation in specific on-chain event / usage pattern, sehr vielversprechend
-4. From the various methods Role2Vec best
-5. Summarize Final results
-6. For researchers -> extend this approach -> apply it to other address sets -> add activity patterns ->
-7. Sth about bots
-
-8. Still a lot of natural activity on Decentraland and open infrastructure allows us to analyze it in detail as in this paper, exciting to analyze other things, endless possibilities.
+The goal of this thesis was to identify the number of entities represented by the 473,927 addresses observed in Decentraland between July 16, 2022 and April 23, 2023. \newline
+By exploiting activity patterns within the publicly available on-chain data, we are apble to apply various heuristics for clustering addresses controlled by the same entity.
+Focusing on Ethereum and Polygon on-chain data, we narrowed the address set down to 137,544.
+After introducing various concepts needed to understand this complex topic, we efficiently collected the required on-chain data.
+This feat was achieved by using information if an address was active on Ethereum and Polygon and subsequently gathering all transactions and token transfers related to the addresses via Etherscan.
+
+ENS pairs ...
+
+We looked at the existing clustering heuristics and discussed their applicablilty to our research question/setting.
+We found thee clustering heuristics, namely self-authorization, graph representation learning and non-compensated LAND transfers to be applicable to cluster a predefined address set.
+Self-authorization and graph representation learning through Ethereum transaction data were approaches proposed by \cite{FV:17} and \cite{Beres2020} respectively, while the LAND transfer heuristic was proposed by ourselves.
+We modified and extended the learned graph representation approach to best work with our research goal.
+As of our best knowledge, we are the first to work with intra-set asset transfers to construct the network graph for graph-representation learning.\newline
+The most successful clustering heuristic was graph representation learning, the reason being its general applicability, as it does not require participation in specific on-chain event / usage pattern.
+Topic for future research ...
+\newline
+The node embedding approach could be possibly further extended by incorporating time-of-day activity or gas price selection patterns for better clustering performance of predefined address sets.
+\newline
+Specifically looking at node embedding algorithms, we found the Role2Vec algorithm to be the most effective, finding the ground truth pair within the five nearest neighbors in 71 percent.
+
+Results/ Evaluation ...
+
+Clustering based on distance threshold, clusters dependent on this threshold...
+
+Visualizations ...
+
+Sth about bots ...
+
+Still a lot of natural activity on Decentraland and open infrastructure allows us to analyze it in detail as in this paper, exciting to analyze other things, endless possibilities.
 Address clustering will  make further advancements.
@@
 / in the context of blockchains
+
+%1. Public blockchain -> all data available -> allows us to analyse it and find information
+%2. Clustering heuristics for account-based blockchains using on-chain data and on specific predefined address set
+%3. sehr vielversprechend
+%4. From the various methods Role2Vec best
+%5. Summarize Final results
+%6. For researchers -> extend this approach -> apply it to other address sets -> add activity patterns ->
+%7. Sth about bots
+
+%Clustering heuristics -> specific on-chain events, user patterns, graph representation learning
+%All blockchain transaction and token transfer data is publicly available. This allows us to apply various heuristics to cluster addresses belonging to the same entity by exploiting activity patterns.
 

### 2023-08-22 python/data-retrieval-preparation/compute-normalizedGas-and-timeOfDay.py
Clean code

@@ -3,6 +3,7 @@ import numpy as np
 from datetime import datetime
 
 def add_ToD(df):
+    """ Add time of day column to DataFrame """
     df['timeStamp'] = pd.to_datetime(df['timeStamp'], unit='s')
     df['ToD'] = df['timeStamp'].dt.hour * 3600 + df['timeStamp'].dt.minute * 60 + df['timeStamp'].dt.second
     return df

### 2023-08-22 python/data-retrieval-preparation/concatenate-transfer-event-data.py

@@ -16,8 +16,9 @@ polygon_721 = pd.read_csv('../../data/polygon_erc721.csv')
 polygon_721['isSetFrom'] = polygon_721['from'].isin(polygon_addresses)
 polygon_721['isSetTo'] = polygon_721['to'].isin(polygon_addresses)
 polygon_721 = polygon_721.drop_duplicates()
-
+# Concatenate ERC-721 dataframes
 erc721 = pd.concat([ethereum_721, polygon_721], ignore_index=True)
+
 if len(erc721) == len(polygon_721) + len(ethereum_721):
     print('ERC-721: Length check passed')
 
@@ -33,9 +34,8 @@ polygon_20 = pd.read_csv('../../data/polygon_erc20.csv')
 polygon_20['isSetFrom'] = polygon_20['from'].isin(polygon_addresses)
 polygon_20['isSetTo'] = polygon_20['to'].isin(polygon_addresses)
 polygon_20 = polygon_20.drop_duplicates()
-
+# Concatenate ERC-20 dataframes
 erc20 = pd.concat([ethereum_20, polygon_20], ignore_index=True)
-
 # Convert values
 erc20['value'] = erc20['value'].apply(int)
 erc20['value'] = erc20['value'] / (10 ** erc20['tokenDecimal'])
@@ -56,7 +56,7 @@ polygon_1155 = pd.read_csv('../../data/polygon_erc1155.csv')
 polygon_1155['isSetFrom'] = polygon_1155['from'].isin(polygon_addresses)
 polygon_1155['isSetTo'] = polygon_1155['to'].isin(polygon_addresses)
 polygon_1155 = polygon_1155.drop_duplicates()
-
+# Concatenate ERC-1155 dataframes
 erc1155 = pd.concat([ethereum_1155, polygon_1155], ignore_index=True)
 erc1155 = erc1155.rename(columns={'tokenValue': 'value'})
 
@@ -64,43 +64,36 @@ if len(erc1155) == len(ethereum_1155) + len(polygon_1155):
     print('ERC-1155: Length check passed')
 
 
-## Concatenate the three DataFrames and check length
+"""Concatenate the ERC20, ERC721, ERC1155 DataFrames and check length"""
 events = pd.concat([erc20, erc721, erc1155], ignore_index=True)
 print(f'Length of all events: {len(events)}')
 if len(events) == len(erc20) + len(erc721) + len(erc1155):
     print('Events: Length check passed')
 
 
-## Add isSet column
-
+""" Add isSet column"""
[…]

### 2023-08-22 python/data-retrieval-preparation/create-intra-set-csvs.py

@@ -11,20 +11,18 @@ transactions = db['transactions']
 users = pd.read_csv('../../data/subsets.csv')
 user_addresses = list(set(users.loc[users['Polygon'] == 1, 'Address']).union(users.loc[users['Ethereum'] == 1, 'Address']))
 
-## Intra-set token transfers
+# Intra-set token transfers
 query_conditions = {
     "from": {"$in": user_addresses},
     "to": {"$in": user_addresses}
 }
-
 transfer_df = pd.DataFrame(list(transfers.find(query_conditions)))
 
 # Drop duplicates
 transfer_df = transfer_df.drop(['_id', 'isSet', 'userAddress'], axis=1).drop_duplicates().reset_index(drop=True)
 transfer_df.to_csv('../../data/intra_token_transfers.csv')
 
-
-## Intra-set native asset transfers
+# Intra-set native asset transfers
 query_conditions = {
     "input": "0x",
     "from": {"$in": user_addresses},

### 2023-08-22 paper.tex
Clean paper

@@
 \end{figure}
-
-\vspace{2em}
 
@@
   \end{tabular}
-  \caption{Average Rank of ENS Domain Names for Different Embedding Methods, Addresses outside of largest connected component have a NaN value}
+  \caption{Average Rank of ENS Domain Names for Different Embedding Methods}
   \label{tbl:ENS_Domain_Ranks}
@@
 \begin{table}[h!]
-\small
+\scriptsize
   \centering
@@
 	\centering
-	\includegraphics[width=0.65\textwidth]{../figures/land_network.png}
+	\includegraphics[width=\textwidth]{../figures/land_network.png}
 	\caption{LAND token network}
@@
 	\centering
-	\includegraphics[width=0.7\textwidth]{../figures/network_visualization_0xe2e.png}
+	\includegraphics[width=0.65\textwidth]{../figures/network_visualization_0xe2e.png}
 	\caption{Token Transfer Graph for \texttt{0xE2e2F$\dots$faCa8}}
@@
 
-%\textbf{LAND transfers}\\
 The \textit{LAND transfer} heuristic is targeted at users revealing address clusters by sending high-value assets to other addresses.
@@
 Additionally, many events that occur off-chain are not detectable in the data, resulting in an increased occurrence of false positives.
-%740 transfers, 413 addressen und 161 or 160 entities with 342 addresses. -The large cluster may incorrectly be marked/maybe off-chain compensation? -> auction address
 
@@
   \caption{Database/data set Description}
-  \label{tbl:database_schema}
 \end{table}

### 2023-08-22 paper.tex
Remove old comments and other small adjustments

@@
 \vfill
-\textbf{Keywords:} Blockchain, Accounts, Clustering Heuristics, Entity Identification, Node Embedding Algorithms.\\
-\noindent\textbf{JEL:} X00, X00, X00
+\textbf{Keywords:} Blockchain, Accounts, Clustering Heuristics, Entity Identification, Graph Representation Learning.\\
+%\noindent\textbf{JEL:} X00, X00, X00
 %\end{titlepage}
@@
 With these considerations in mind, the topic of privacy, or lack thereof, will remain significant for future blockchain development and research.
-
 %If someone obtains information that allows them to link a blockchain address to an entity, they may effectively observe that entity’s entire transaction history and associated activity.
@@
 Moreover, the Decentraland core developers provide a smart-contract-based marketplace where users can buy or trade LAND or other in-game collectibles.
-
-%Owners of multiple adjacent land parcels can combine them into an ESTATE, which acts as a wrapper token for the land parcels.
 %The term metaverse refers to Neal Stephenson’s 1992 novel Snow Crash and describes an immersive virtual world that is populated by humans-as-avatars.
-%Goods: in-world assets, such as avatar wearables, merchandise, or tickets, as well as tokenized vouchers that can be redeemed for real-world goods or services.
 
@@
 These methods are discussed in more detail in section 4.
-
 %In theory, a larger anonymity set will provide a higher level of privacy as third parties will not be able to link a specific depositor address to a specific withdrawal address.
@@
 \iffalse
-Transfer Events: 30,689,978
-Transfer Events Ethereum: 7,832,778
-Transfer Events Polygon: 22,857,200
-
-Transactions = 16,092,531
-Transactions Ethereum = 8,448,584
-Transactions Polygon = 7,643,947
-
+%Transfer Events: 30,689,978
+%Transfer Events Ethereum: 7,832,778
+%Transfer Events Polygon: 22,857,200
+%Transactions = 16,092,531
+%Transactions Ethereum = 8,448,584
+%Transactions Polygon = 7,643,947
 Figure X visualizes the number of daily transactions and token transfers for each chain.
@@
 \end{figure} 
-Transfer Events, adding Information (isInSet) \\
-Transactions \\
-Filtering, Intra-set transfers\\
-Data Structure, Fields \\
 \fi
@@
 In Section 5, we will implement and evaluate the heuristics we determine to be suitable for our objectives.
-%Goal: explain each heuristic, categorize, and discuss applicability to our address set
-%In Section 5 we will then apply  and, if possible, evaluate the heuristics deemed suited for us.
 
@@
 \newline
-Since all the addresses' transactions are available in our data set, we can easily employ this heuristic. %Since our data set includes all address transactions, we can easily employ this heuristic. %
+Since all the addresses' transactions are available in our data set, we can easily employ this heuristic.
 
@@
 For the ERC-1155 standard: \texttt{setApprovalForAll(address operator, bool approved)}
-
-	- approve(address,uint256)
-	- setApprovalForAll(address,bool) for both ERC-721 and ERC-1155
-
-The first step is to get all approval transactions.
-We achieve this using the 'input'/calldata field.
-The first X bytes are always the function selector.
-We filter for the known function selectors for all standards.
-Next, we get the approved address/spender, also from the calldata, it is always at the same spot.
-We filter for spenders within the address set and for spenders who are different from the 'from' address.
-How many transactions are remaining?
-Finally, we extract all unique pairs of owners and spenders, disregarding the type of token or the amount.
 \fi
@@
 
-\iffalse
-\cite{FV:17} was the first to formulate and systematically exploit this heuristic, which was also applied later on by \cite{wu2022tutela}.
-This heuristic exploits the common practice of crypto exchanges creating so-called deposit addresses for each user, which forward funds to a main address.
-Multiple addresses that send funds to the same deposit address are highly likely controlled by the same entity.
-The main challenge of this approach is detecting deposit addresses, which can be either EOAs but also smart contracts.
-- Exchanges typically create so-called deposit addresses, which will forward received funds to a main address.
-As these deposit addresses are created per customer, multiple addresses that send funds to the same deposit address are highly likely to be controlled by the same entity.
-The key challeng lies in identifying these deposit addresses.
-Their characteristic property is that they forward received amounts to a major exchange account.
-The forwarded amount is often slightly less than what was received, as the exchange has to pay for the transaction costs.
-In most cases, deposit addresses are EOAs, but they can also be smart contracts.
-Identifying deposit addresses relies on two parameters: the maximum amount difference between what was received and forwarded and the maximum time difference between receiving and forwarding.
-In this project, we only collected the addresses' direct transactions or token transfers.
-This would allow us to see deposit addresses, however, with this data we cannot find the second step: the deposit address forwarding the asset to the exchanges main address.
-Therefore, we do not apply this clustering heuristic here.
-Since we only collected the addresses' direct transactions or token transfers, the second step between deposit and exchange address is not available/present in our data set. 
-\fi
-
 \subsection{Airdrop multi participation}
@@
 %write here that we tested different data sets to create the network graph but intra-set asset transfers performed best for our task.
-\textbf{Diff2Vec} % Neighborhood preserving 
 The intuition of Diff2Vec is to summarize a node by its neighborhood through a diffusion-like random process.
 Specifically, there are four steps to Diff2Vec: 1) Generating a diffusion graph, 2) sampling a node sequence, 3) extracting features, 4) learning a neural network embedding
-\textbf{DeepWalk}
-\textbf{Role2Vec} % Structural node embedding, Structural Node Level Embedding
-Random walks will likely visit nearby vertices first, which makes them
-suitable for finding communities, rather than roles (structural
-similarity). To overcome the above problems, we propose the Role2Vec
-framework which serves as a basis for generalizing many existing methods that use traditional random walks. Strucural feature matrix.
-
-Research in node embedding has been accelerated by Word2Vec, which is an embedding method for natural language processing. This approach has been extended to learn graph/network embeddings.
-
-Token networks -> Victor, Casale Brunet
 \fi
@@
 \subsection{Time-of-day transaction activity and gas price selection}
-
 Apart from the node embedding methods applied to Ethereum transaction graphs, \cite{Beres2020} suggest employing clustering heuristics based on time-of-day transaction activity and gas price selection patterns.
@@
 \subsection{Tornado cash heuristics}
-
 \cite{wu2022tutela} propose five heuristics targeted at Tornado cash, highlighting that careless user behavior can still reveal identity, despite using a mixer.
@@
 \subsection{Self-authorization}
-
 We analyze the addresses' transaction data to find self-authorizations, focusing on the transaction's ``calldata``.
@@
 \subsection{Node embeddings}
-
 Our analysis of node embedding methods starts with a network graph built from intra-set asset transfers.
@@
 Even if the algorithm finds all 20 addresses within the nearest neighbors but identifies the ground truth pair as the last one, we will score it lower than another algorithm that finds only one of the twenty addresses but within the ten nearest neighbors.
-
-%As described in previous sections, we tested different data sets to create the network graph using our ENS address pairs as ground truth.
-Der Approach ist zwar stark an Beres angelehnt, jedoch wendet er es an um pairs of deposit und withdrawal addressen zu clustern.
-We found the intra-set asset transfers to perform best in terms of the average rank of a target address.
 
@@
 
-%4. Describe two step approach test, may need further research and would be ideal to incorporate into node embedding feature vectors \\
-%Performing an inner merge for the largest clusters of each threshold results in a cluster consisting of 516 addresses, this means the clusters overlap perfectly.
-
 \subsection{LAND transfers}
-
 To implement the LAND transfer clustering heuristic, we select all transaction hashes of LAND transfers between two Decentraland addresses.
@@
 \subsection{Combining clustering results}
-
 To conclude our clustering analysis, we combine the results of self-authorization, learned node embedding and LAND transfer heuristics.
@@
 
-Sth about bots ...
+Somethin about bots ...
 

### 2023-08-23 paper.tex
Update conclusion

@@
 
-The goal of this thesis was to identify the number of entities represented by the 473,927 addresses observed in Decentraland between July 16, 2022 and April 23, 2023. \newline
-By exploiting activity patterns within the publicly available on-chain data, we are apble to apply various heuristics for clustering addresses controlled by the same entity.
-Focusing on Ethereum and Polygon on-chain data, we narrowed the address set down to 137,544.
-After introducing various concepts needed to understand this complex topic, we efficiently collected the required on-chain data.
-This feat was achieved by using information if an address was active on Ethereum and Polygon and subsequently gathering all transactions and token transfers related to the addresses via Etherscan.
-
-ENS pairs ...
-
-We looked at the existing clustering heuristics and discussed their applicablilty to our research question/setting.
-We found thee clustering heuristics, namely self-authorization, graph representation learning and non-compensated LAND transfers to be applicable to cluster a predefined address set.
-Self-authorization and graph representation learning through Ethereum transaction data were approaches proposed by \cite{FV:17} and \cite{Beres2020} respectively, while the LAND transfer heuristic was proposed by ourselves.
-We modified and extended the learned graph representation approach to best work with our research goal.
-As of our best knowledge, we are the first to work with intra-set asset transfers to construct the network graph for graph-representation learning.\newline
-The most successful clustering heuristic was graph representation learning, the reason being its general applicability, as it does not require participation in specific on-chain event / usage pattern.
-Topic for future research ...
-\newline
-The node embedding approach could be possibly further extended by incorporating time-of-day activity or gas price selection patterns for better clustering performance of predefined address sets.
-\newline
-Specifically looking at node embedding algorithms, we found the Role2Vec algorithm to be the most effective, finding the ground truth pair within the five nearest neighbors in 71 percent.
-
-Results/ Evaluation ...
-
-Clustering based on distance threshold, clusters dependent on this threshold...
-
-Visualizations ...
-
-Somethin about bots ...
-
-Still a lot of natural activity on Decentraland and open infrastructure allows us to analyze it in detail as in this paper, exciting to analyze other things, endless possibilities.
-Address clustering will  make further advancements.
+This thesis aimed to determine how many unique entities correspond to the 473,927 addresses observed in Decentraland from July 16, 2022, to April 23, 2023. \newline
+By focusing on Ethereum and Polygon on-chain data, we narrowed the set down to 137,544 addresses.
+The required data was efficiently sourced by gathering all transactions and token transfers related to the addresses via Etherscan.
+Furthermore, with the help of ENS, we found a way to detect address pairs that have a very high probability of being controlled by the same user.
+These address pairs served as our ground truth when evaluating the node embedding algorithms.
+\newline
+We discussed several existing clustering heuristics and evaluated their suitability in our context.
+Among these heuristics, two were found to be appropriate for clustering a pre-defined set of addresses with the available data: self-authorization \citep{FV:17} and graph representation learning \citep{Beres2020}.
+We modified the graph representation learning approach for our research goal.
+%to align with our research goals, this is the first attempt to utilize intra-set asset transfers in constructing the network graph
+To the best of our knowledge, we are the first to employ intra-set asset transfers for constructing the network graph.
+Moreover, we introduced a novel clustering heuristic that identifies uncompensated transfers of high-value NFTs, particularly LAND.
+\newline
+Due to its general applicability, graph representation learning proved to be the most successful clustering heuristic, while the other two heuristics yielded far fewer address clusters.
+In our exploration of node embedding algorithms, the Role2Vec algorithm stood out, correctly identifying the ground truth pair within the five nearest neighbors in 71 percent of the cases.
+\newline
+From the 137,544 addresses transacting on Polygon or Ethereum, we identified an estimated 115,643 as active Decentraland users.
+A subset of these entities, representing 7.3\%, operated through multiple addresses.
+Notably, the largest address cluster we observed was an entity with 500 distinct addresses.
+Based on our analysis, we believe this entity is likely a bot targeting Decentraland NFT airdrops, with intentions to resell them later.
+\newline
+To enhance clustering performance, node embeddings could incorporate time-of-day activity and gas price selection patterns.
+This approach holds significant promise for future research in entity identification.
+\newline
+A significant challenge with graph representation learning is the formation of clusters after node embedding.
+In our study, we relied on a Euclidean distance threshold for this purpose.
+However, the resulting number and size of clusters are highly sensitive to the precise selection of this threshold.
+\newline
+Notably, our approach is versatile and can be applied to other predefined address sets.
+This adaptability is particularly significant given the increasing importance of determining the true number of users in various protocols, especially in areas like Decentralized Finance and on-chain governance.
+\newline
+Although we were able to detect entity clusters, Decentraland still exhibits a lot of natural activity.
+Its open infrastructure presents vast opportunities for in-depth analysis of the virtual world, as demonstrated in this thesis.
+\newline
+Address clustering will continue to make further advancements.
+From a user perspective, it is crucial that privacy-enhancing protocols continue to evolve and gain large-scale adoption.
+Additionally, education on preserving privacy when transacting on blockchains becomes increasingly important.
+
+ %The major drawback of graph representation learning is the cluster formation after performing the node embedding.
+In our case, we utilize a Euclidean distance threshold for this task.
+However, the number of clusters and their size is very senstive to the exact choice of this threshold value.
+\newline
+%Address clustering will make further advancements.
 From a user perspective it is important that privacy enhancing protocols are also further developed and users educated how to preserve privacy when transacting on blockchains.
 / in the context of blockchains
-
-%1. Public blockchain -> all data available -> allows us to analyse it and find information
-%2. Clustering heuristics for account-based blockchains using on-chain data and on specific predefined address set
-%3. sehr vielversprechend
-%4. From the various methods Role2Vec best
-%5. Summarize Final results
-%6. For researchers -> extend this approach -> apply it to other address sets -> add activity patterns ->
-%7. Sth about bots
-
-%Clustering heuristics -> specific on-chain events, user patterns, graph representation learning
-%All blockchain transaction and token transfer data is publicly available. This allows us to apply various heuristics to cluster addresses belonging to the same entity by exploiting activity patterns.
 

### 2023-08-23 paper.tex
Intro adjustment and other minor changes

@@
 As a result, most methods are heuristic.
-%The majority of these methods are heuristic which often makes them difficult to evaluate due to the absence of any ground truth.
-\newline On one hand, identifying addresses that belong to the same real-world entity is beneficial as it allows for better evaluation of network properties concerning usage, distribution of wealth, and detecting fraudulent activities \citep{FV:17}.
+\newline
+On one hand, identifying addresses that belong to the same real-world entity is beneficial as it allows for better evaluation of network properties concerning usage, distribution of wealth, and detecting fraudulent activities \citep{FV:17}.
 For instance, if a user distributes their voting power across various addresses, they might manipulate an on-chain voting process that seems fair at the outset.
 \newline
-Conversely, the lack of privacy is also detrimental to most financial use cases. As a response, multiple privacy-enhancing tools and protocols have been proposed to obfuscate transaction tracing. 
+Conversely, the lack of privacy is also detrimental to most financial use cases.
+If someone obtains information that allows them to link a blockchain address to an entity, they may effectively observe that entity’s entire transaction history and associated activity.
+Even if the entity uses multiple addresses, any link between these addresses may expose the fact that they belong to the same person.
+As a response, multiple privacy-enhancing tools and protocols have been proposed to obfuscate transaction tracing. 
 Nonetheless, these protocols have yet to be widely adopted, and careless user behavior can undermine the privacy guarantees they offer. \newline
-With these considerations in mind, the topic of privacy, or lack thereof, will remain significant for future blockchain development and research.
-%If someone obtains information that allows them to link a blockchain address to an entity, they may effectively observe that entity’s entire transaction history and associated activity.
-Even if the entity uses multiple addresses, any link between these addresses may expose the fact that they belong to the same person.
+With these considerations in mind, the topic of privacy, or lack thereof, is and will remain significant for blockchain development and research.
 
@@
 Several address clustering heuristics in the UTXO setup have been proposed for Bitcoin and its derivatives \citep{Androulaki2013, Meiklejohn2013, Haslhofer2016, jourdan2018, kappos2022}.
-However, these methods are outside the scope of this work and will not discussed.
+However, these methods are outside the scope of this work and will not be discussed.
 \newline
@@
 % Make an assumption that people only use a small set of addresses
+% still nascent
 Clustering heuristics for account-based blockchains were first introduced by \cite{FV:17}.
@@
  As we focus on clustering methods using on-chain data, we exclude addresses that have not been recorded on either Ethereum or Polygon.
-To accomplish this, we used data from Blockscan\footnote{\url{https://blockscan.com/}}.
+To accomplish this, we used information from Blockscan\footnote{\url{https://blockscan.com/}}.
 Overall, 59,651 addresses were recorded on Ethereum, 129,988 on Polygon, with 52,095 addresses appearing on both networks simultaneously.
@@
 \label{sec:intra-set}
-We want to employ entity clustering heuristics to determine the number of entities represented by the remaining 137,544 addresses.
+We want to employ address clustering heuristics to determine the number of entities represented by the remaining 137,544 addresses.
 Or, to phrase it differently, do users interact with Decentraland using multiple EOAs, and can we identify addresses that belong to the same user?
@@
 Furthermore, it allows us to observe and visualize the asset flows between users.
-In total, we have 974,478 intra-set token transfers and 210,548 intra-set native asset transfers/payments (101,621 Matic, 108,927 Ether).
-
+In total, we have 974,478 intra-set token transfers and 210,548 intra-set native asset transfers.
+
+%(101,621 Matic, 108,927 Ether)
 %(logging in to Decentraland with multiple addresses) When it comes to entity clustering, we essentially want to answer the question of how many real-world entities our remaining  137,544 addresses represent.
@@
 Using the library described by \cite{karateclub} requires certain preprocessing steps for the network graph.
-Transactions must be treated as undirected edges and loops (self-transactions) and multi-edges should be removed.
+Transactions must be treated as undirected edges and loops (self-transactions) and multi-edges must be removed.
 Moreover, nodes outside the largest connected component are excluded.
@@
 \subsection{Time-of-day transaction activity and gas price selection}
-Apart from the node embedding methods applied to Ethereum transaction graphs, \cite{Beres2020} suggest employing clustering heuristics based on time-of-day transaction activity and gas price selection patterns.
+Apart from the applying node embedding methods to Ethereum transaction graphs, \cite{Beres2020} suggest employing clustering heuristics based on time-of-day transaction activity and gas price selection patterns.
 \newline
@@
 We applied three node embedding algorithms that delivered robust results in the experiments by \cite{Beres2020} and assessed their effectiveness in detecting ground truth pairs.
-Our results indicate that Role2Vec is the best-performing method, locating the ground truth pair within the five nearest neighbors in 70\% of cases.
+Our results indicate that Role2Vec is the best-performing method, locating the ground truth pair within the ten nearest neighbors in 70\% of cases.
 This diverges from the findings of \cite{Beres2020}, who determined Diff2Vec to be the superior method among the three evaluated.
@@
 Due to its general applicability, graph representation learning proved to be the most successful clustering heuristic, while the other two heuristics yielded far fewer address clusters.
-In our exploration of node embedding algorithms, the Role2Vec algorithm stood out, correctly identifying the ground truth pair within the five nearest neighbors in 71 percent of the cases.
+In our exploration of node embedding algorithms, the Role2Vec algorithm stood out, correctly identifying the ground truth pair within the ten nearest neighbors in 71 percent of the cases.
 \newline

### 2023-08-24 paper.tex
Update until data analysis

@@
 Researchers try to cluster addresses controlled by the same user by analyzing on-chain data and detecting usage patterns.
-The frequent lack of ground truth makes it difficult to evaluate different clustering methods.
+The frequent lack of ground truth makes it challenging to evaluate different clustering methods.
 As a result, most methods are heuristic.
 \newline
-On one hand, identifying addresses that belong to the same real-world entity is beneficial as it allows for better evaluation of network properties concerning usage, distribution of wealth, and detecting fraudulent activities \citep{FV:17}.
-For instance, if a user distributes their voting power across various addresses, they might manipulate an on-chain voting process that seems fair at the outset.
-\newline
-Conversely, the lack of privacy is also detrimental to most financial use cases.
+On the one hand, identifying addresses that belong to the same real-world entity is beneficial as it allows for better evaluation of network properties concerning usage, distribution of wealth, and detecting fraudulent activities \citep{FV:17}.
+For instance, if users distribute their voting power across various addresses, they might manipulate an on-chain voting process that seems fair at the outset.
+\newline
+Conversely, the lack of privacy is detrimental to most financial use cases.
 If someone obtains information that allows them to link a blockchain address to an entity, they may effectively observe that entity’s entire transaction history and associated activity.
@@
 Nonetheless, these protocols have yet to be widely adopted, and careless user behavior can undermine the privacy guarantees they offer. \newline
-With these considerations in mind, the topic of privacy, or lack thereof, is and will remain significant for blockchain development and research.
-
-\textbf{Related work}\\
-Previous work in this field can be broadly distinguished between methods developed for the unspent transaction output (UTXO) model (e.g., Bitcoin and ZCash) and the account-based model (e.g., Ethereum and Polygon).
+With these considerations in mind, privacy, or lack thereof, is and will remain an essential topic for blockchain development and research.
+
+%\textbf{Related work}\\
+Previous work in this field can be broadly categorized into methods developed for blockchains that use the unspent transaction output (UTXO) model, such as Bitcoin, and those that utilize the account-based model, like Ethereum and Polygon.
 While both models share the concept of addresses, the notion of accounts is absent in UTXO-based blockchains.
 The way in which transactions are processed is fundamentally different, and therefore, clustering heuristics are not applicable to both paradigms.
-
+\newline
 Several address clustering heuristics in the UTXO setup have been proposed for Bitcoin and its derivatives \citep{Androulaki2013, Meiklejohn2013, Haslhofer2016, jourdan2018, kappos2022}.
-However, these methods are outside the scope of this work and will not be discussed.
+However, these methods are outside the scope of this work and will not be discussed further.
 \newline
@@
 Subsequent transactions necessarily use the same address again.
-The account-based model essentially relies on address reuse at the protocol level \citep{Beres2020}.
-Consequently, privacy guarantees should be lower as participants typically use a limited set of addresses.
-\newline
-% Make an assumption that people only use a small set of addresses
-% still nascent
-Clustering heuristics for account-based blockchains were first introduced by \cite{FV:17}.
-He proposed and applied heuristics that exploit patterns related to deposit addresses, multiple participation in airdrops, and token authorization mechanisms.
+Therefore, the account-based model essentially relies on address reuse at the protocol level \citep{Beres2020}.
+Consequently, privacy guarantees should be lower as participants typically only use a limited set of addresses.
+\newline
+Yet, despite these inherent characteristics of account-based blockchains, the development and research into address clustering heuristics remain in their infancy. 
+The first heuristics were introduced by \cite{FV:17}, who proposed and applied methods that exploit patterns related to deposit addresses, multiple participation in airdrops, and token authorization mechanisms.
 \newline
@@
 
-\textbf{Our contribution}\\
+%\textbf{Our contribution}\\
 In this work, we perform entity identification on an address set containing 473,927 addresses.
@@
 
+%Previous work in this field can be broadly distinguished between methods developed for the unspent transaction output (UTXO) model (e.g., Bitcoin) and the account-based model (e.g., Ethereum and Polygon).
+
 %%%%%%%%%%%%%%%%%%%%%
@@
 \textit{EOAs} are created and controlled by private keys and can be used to hold the native protocol asset, send and receive transactions, and interact with contract accounts.
-\textit{Contract accounts} are controlled by the contract's code, their state can be modified through transactions sent to the contract and they cannot initiate transactions.
+\textit{Contract accounts} are controlled by the contract's code; their state can be modified through transactions sent to the contract, and they cannot initiate transactions.
 \citep{buterin2014ethereum} \newline Each account has a 20-byte address encoded in hexadecimal.
@@
 \citep{mastering_ethereum} \newline
-The standarization of tokens allows us to listen for ``transfer events``, which are emitted whenever an token changes ownership.
+The standardization of tokens allows us to listen for ``transfer events``, which are emitted whenever a token changes ownership.
 These transfer events include the \textit{sender} and \textit{recipient} address, along with a \textit{token ID} and/or \textit{amount}.
@@
 To achieve this, we often only consider transactions or token transfer events where both the ``\texttt{from}`` (sender) and the ``\texttt{to}`` (recipient) address are within the address set.
-We call this reduced data set ``intra-set asset transfers``.
-Regarding normal transactions, this means that we only keep native asset transfers (payments), as almost all addresses are EOAs.
+We call this reduced data set ``\textit{intra-set asset transfers}``.
+Regarding normal transactions, this means that we only keep native asset transfers (also called payments), as almost all addresses are EOAs.
 \newline
@@
 \newline
-In addition to regular resolution from name to address, ENS also supports ``reverse resolution``, allowing for a mapping from address back to a name (or other metadata).
+In addition to regular resolution from name to address, ENS also supports ``reverse resolution``, allowing for a mapping from address back to a name or other metadata.
 Reverse resolution is accomplished via the %special
@@
 Deposit addresses share the characteristic that they forward the received funds to a major exchange account.
-Two parameters are essential for deposit address detection: the discrepancy between the amount received and forwarded (since the exchange must pay gas fees), and the time lag between receiving and forwarding funds.
+Two parameters are essential for deposit address detection: the discrepancy between the amount received and forwarded (since the exchange must pay for gas fees), and the time lag between receiving and forwarding funds.
 However, our data set only includes the direct transactions or token transfers associated with the addresses.
@@
 He defines multi-participation when two airdrop recipients forward their tokens to a single address.
-Since we do not have a whole view of the airdrop distribution events, we are not able to find them within our data.
+Since we do not have a whole view of the airdrop distribution events, we are not able to identify them within our data.
 One possible approach would include manual selection of known airdrops.
-However, this process takes very long and is not guaranteed to cluster a lot of addresses, since most new airdrop events were made with some kind of sybil-resistance.
+However, this process takes very long and is not guaranteed to cluster a lot of addresses, since most new airdrop events were carried out with some kind of sybil-resistance.
 Nevertheless, to test this approach we searched for addresses that forwarded the UNI airdrop to another address.
@@
 \newline
-\cite{Beres2020} first introduced this approach on a Ethereum transaction graph for the purpose of entity identification to pair Ethereum addresses associated with Tornado cash deposits and withdrawals.
+\cite{Beres2020} first introduced this approach on an Ethereum transaction graph for the purpose of entity identification to pair Ethereum addresses associated with Tornado cash deposits and withdrawals.
 Building on this, \cite{wu2022tutela} refined and expanded one particular node embedding algorithm to deanonymize Ethereum users at scale.
@@
 This approach differs from the methodologies adopted by \cite{Beres2020} and \cite{wu2022tutela}.
-On one hand, \cite{Beres2020} collected all transactions and token transfer events of their address set, but did not refine this data to only include intra-set asset transfers.
-On the other hand, \cite{wu2022tutela} do not operate on a specific address set, but use all Ethereum transactions to build the network graph, ignoring token transfer events.
+On the one hand, \cite{Beres2020} collected all transactions and token transfer events of their address set but did not refine this data to only include intra-set asset transfers.
+On the other hand, \cite{wu2022tutela} do not operate on a specific address set but use all Ethereum transactions to build the network graph, ignoring token transfer events.
 After comparing these two methodologies with ours, we determined that intra-set asset transfers were the most effective for clustering a pre-defined set of addresses.
@@
 \newline
-We focus on the three methods that performed best in \cite{Beres2020} experiments: ``Diff2Vec`` \citep{rozemberczki2020difftovec}, ``Role2Vec`` \citep{ahmed2018roletovec}, and ``Deepwalk`` \citep{perozzi2014}.
-Diff2Vec and DeepWalk are both neighborhood preserving, while Role2Vec is a structural node embedding method.
-Although all of these methods utilize random walks to capture graph information, they differ in their approaches to leveraging these random walks for constructing Euclidean feature vectors.
+We focus on the three methods that performed best in \cite{Beres2020} experiments: ``\textit{Diff2Vec}`` \citep{rozemberczki2020difftovec}, ``\textit{Role2Vec}`` \citep{ahmed2018roletovec}, and ``\textit{Deepwalk}`` \citep{perozzi2014}.
+Diff2Vec and DeepWalk are neighborhood-preserving methods, while Role2Vec is a structural node embedding method.
+Although all methods utilize random walks to capture graph information, their approaches to leveraging these random walks for constructing Euclidean feature vectors differ.
 A detailed explanation of each method is beyond the scope of this thesis.
-The interested reader may consult the originial publications.
+The interested reader may consult the original publications.
 For a concise overview of Diff2Vec, please refer to \cite{wu2022tutela}.
@@
 Using the library described by \cite{karateclub} requires certain preprocessing steps for the network graph.
-Transactions must be treated as undirected edges and loops (self-transactions) and multi-edges must be removed.
+Transactions must be treated as undirected edges and loops (self-transactions), and multi-edges must be removed.
 Moreover, nodes outside the largest connected component are excluded.
@@
 This choice facilitated the application of \cite{rozemberczki2020difftovec}'s library and eliminated the need to create a custom method.
-\newline
-Based on our network graph, we generate 128-dimensional feature vectors for each address and method. \newline
-Given an node embedding, we can search for the closest $k$ vectors to any given vector.
+Based on our network graph, we generate 128-dimensional feature vectors for each address and method.
+\newline
+Given a node embedding, we can search for the closest $k$ vectors to any given vector.
 As in \cite{wu2022tutela}, we accomplish this using FAISS (Facebook AI Similarity Search), developed by \cite{johnson2019faiss}, which always returns a list of $k$ nodes, ranked by their Euclidean distance to the given node\footnote{We set $k = 51566$, the total number of nodes in the network graph}.
@@
 We run each node embedding method ten times and report the average rank of the target address.
-For comparison, we  compute the mean, median and standard deviation of the average rank for each method.
+For comparison, we compute the mean, median, and standard deviation of the average rank for each method.
 
@@
 \subsection{Time-of-day transaction activity and gas price selection}
-Apart from the applying node embedding methods to Ethereum transaction graphs, \cite{Beres2020} suggest employing clustering heuristics based on time-of-day transaction activity and gas price selection patterns.
+Apart from applying node embedding methods to Ethereum transaction graphs, \cite{Beres2020} suggest employing clustering heuristics based on time-of-day transaction activity and gas price selection patterns.
 \newline
@@
 These UNIX timestamps are transformed into hour-of-the-day-based values.
-The authors argue that account owners may expose daily activity patterns and represent addresses by a vector including the mean, median and standard deviation, as well as an activity histogram divided into four to six hour bins \citep{Beres2020}.
-Figure \ref{fig:ToD} illustrates the time-of-day activity histogram and kernel density estimation (KDE) for a selected ENS address pair, divided into two hour intervals.\newline
-Additionaly, the \textit{gas price distribution} heuristic leverages the possibility of users revealing patterns when choosing their gas price.
+The authors argue that account owners may expose daily activity patterns and represent addresses by a vector including the mean, median, and standard deviation, as well as an activity histogram divided into four to six-hour bins \citep{Beres2020}.
+Figure \ref{fig:ToD} illustrates the time-of-day activity histogram and kernel density estimation (KDE) for a selected ENS address pair, divided into two-hour intervals.\newline
+Additionally, the \textit{gas price distribution} heuristic leverages the possibility of users revealing patterns when choosing their gas price.
 Prior to EIP-1559\footnote{\url{https://eips.ethereum.org/EIPS/eip-1559}}, users could set the gas price manually.
 In practice, most wallet user interfaces offered three levels of gas prices: slow, average, and fast.
-Selecting the the fast option would ensure almost immediate inclusion in the blockchain.
+Selecting the fast option would ensure almost immediate inclusion in the blockchain.
 To account for changes in Ethereum traffic volume, the gas price is normalized by the daily network average.
 The combination of gas price levels users select forms their personal gas price profile.
-An account is represented by a vector including the mean, median, and standard deviation and a normalized gas price histogram divided into 50 bins, which they determined to be optimal for clustering performance.
+An account is represented by a vector including the mean, median, and standard deviation and a normalized gas price histogram divided into 50 bins, which they determined optimal for clustering performance.
 \citep{Beres2020} \newline
-We will not employ both methods due to their significantly poorer stand-alone performance compared to node embeddings.
-Nevertheless, we test a two-step approach: In the first step, we implement Diff2Vec to find the 10 nearest neighbors.
+Both methods will not be employed due to their significantly poorer stand-alone performance compared to node embeddings.
+Nevertheless, we test a two-step approach: In the first step, we implement Diff2Vec to find the ten nearest neighbors.
 In the second step, we order the remaining addresses by their Euclidean distance derived from the time-of-day and/or gas price feature vectors.
@@
 \subsection{Tornado cash heuristics}
-\cite{wu2022tutela} propose five heuristics targeted at Tornado cash, highlighting that careless user behavior can still reveal identity, despite using a mixer.
+\cite{wu2022tutela} propose five heuristics targeted at Tornado cash, highlighting that careless user behavior can still reveal identity despite using a mixer.
 The heuristics they identified are as follows: \newline
-``Address match`` refers to instances where individuals use the same address for both depositing and withdrawing from the Tornado pool.
-``Unique gas price`` involves users selecting a distinct gas price for both their deposit and withdrawal transactions (prior to EIP-1559).
-``Linked ETH addresses`` examines whether a deposit address has interacted with a withdrawal address outside of Tornado Cash.
+``Address match`` refers to instances where individuals use the same address to deposit and withdraw from the Tornado pool.
+``Unique gas price`` involves users selecting a distinct gas price for their deposit and withdrawal transactions (prior to EIP-1559).
+``Linked ETH addresses`` examines whether a deposit address interacts with a withdrawal address outside Tornado Cash.
 ``Multiple denomination`` assesses an address' transaction history; two addresses with matching deposit and withdrawal portfolios are considered a pair.
-``Torn minting`` identifies a specific user behavior when withdrawing so-called Anonymity points, an incentive scheme reward for increasing the anonymity set when depositing assets into Tornado cash.
-
-We identified 84 transactions tied to Tornado cash pools, including 72 deposits, 10 withdrawals, and two transactions where an address sent 0.1 Ether to the corresponding pool without invoking the deposit function.
+``Torn minting`` identifies a specific user behavior when withdrawing so-called Anonymity points, an incentive scheme reward for increasing the anonymity set when depositing assets into Tornado cash.\newline
+We identified 84 transactions tied to Tornado cash pools, including 72 deposits, ten withdrawals, and two transactions where an address sent 0.1 Ether to the corresponding pool without invoking the deposit function.
 Despite applying all clustering heuristics except "Torn minting", we found no clusters.
@@
 \subsection{LAND transfers}
-In addition to the existing clustering heuristics, we propose our own heuristic based on transfers of high-value NFTs such as LAND.
+In addition to the existing clustering heuristics, we propose our heuristic based on transfers of high-value NFTs such as LAND.
 We argue that, given the high value of Decentraland's land parcels, there is a strong likelihood that addresses are controlled by the same entity when LAND is transferred without any compensation.
@@
 The primary challenge of this approach is to detect LAND transfers without any compensation.
-To accomplish this, we identify token or native asset transfers that took place within the same transaction as a LAND transfer.
-Upon manually examining various implementations of LAND trades on the most popular NFT marketplace contracts, we noticed a recurring pattern: the user address appears in both the ``from`` and ``to`` fields if a trade takes place.
+To accomplish this, we identify token or native asset transfers within the same transaction as a LAND transfer.
+Upon manually examining various implementations of LAND trades on the most popular NFT marketplace contracts, we noticed a recurring pattern: the user address appears in both the ``from`` and ``to`` fields if a trade occurs.
 Figure \ref{fig:LAND_example} illustrates an example of this pattern.

### 2023-08-24 paper.tex
Update until conclusion

@@
 These include self-authorization, node embedding, and our proposed approach involving LAND transfers.
-%we describe our approach/method and the results.
 
@@
 \textit{Second}, we extract the approved (spender) address, which is always located at the same position within the calldata due to token standardization.
-We then record the spender address in a new field within our dataframe.
+We then record the spender address in a new field within our data frame.
 \textit{Third}, we implement two filters on the approval transactions.
@@
 \newline
-Subsequently, we run ten independent experiments for each method.
+Subsequently, we ran ten independent experiments for each method.
 Our choice of input parameters is identical to \cite{Beres2020}.
-Each experiment returns a node embedding in the form of a matrix with 51,566 rows corresponding to the number of nodes in the graph, and 128 columns, representing the feature vector dimensions.
+Each experiment returns a node embedding in a matrix with 51,566 rows corresponding to the number of nodes in the graph and 128 columns representing the feature vector dimensions.
 \newline
@@
 We achieve this through the FAISS Python library, which is suitable for efficient similarity search and clustering of dense vectors \citep{johnson2019faiss}.\newline
-This enables us to search for our ENS ground truth pairs and report their relative rank.
+This feature enables us to search for our ENS ground truth pairs and report their relative rank.
 The results for each address pair, averaged over ten experiments, are presented in Table \ref{tbl:ENS_Domain_Ranks}.
@@
 Furthermore, Role2Vec found the target address within the ten nearest neighbors in 24 out of 34 cases (71\%).
-Diff2Vec is barely less effective than Role2Vec or DeepWalk, although still generally successful.
-\newline
-Notably, two address pairs are not present within the network graph and therefore display no values.
+Diff2Vec is barely less effective than Role2Vec or DeepWalk, although it is still generally successful.
+\newline
+Notably, two address pairs are absent within the network graph and, therefore, display no values.
 However, they have been included to demonstrate that the intra-set asset transfer approach may only sometimes be applicable to cluster all addresses of a predefined set.
 \newline
-We also need to consider that average rank may not be the most appropriate evaluation metric, particularly when a user controls more than two addresses.
+We must also consider that average rank may not be the most appropriate evaluation metric, particularly when a user controls more than two addresses.
 Suppose a single entity controlling 20 addresses, but only one pair of addresses is detected as ground truth.
-Even if the algorithm finds all 20 addresses within the nearest neighbors but identifies the ground truth pair as the last one, we will score it lower than another algorithm that finds only one of the twenty addresses but within the ten nearest neighbors.
+Even if the algorithm finds all 20 addresses within the nearest neighbors but identifies the ground truth pair as the last one, we will score it lower than another algorithm that finds only one of the twenty addresses within the 10 nearest neighbors.
 
@@
 \newline
-One approach might involve grouping a node's $k$ nearest neighbours to a cluster and subsequently merging clusters until each node is assigned to exactly one cluster.
-However, selecting an appropriate $k$ is challenging, and it is hard to make the case that each address belongs to a cluster of at least $k$.
+One approach might involve grouping a node's $k$ nearest neighbors to a cluster and subsequently merging clusters until each node is assigned to exactly one cluster.
+However, selecting an appropriate $k$ is challenging, and making the case that each address belongs to a cluster of at least $k$ is problematic.
 \newline
@@
 We explore the sensitivity of clusters to various Euclidean distance threshold values.
-Figure \ref{fig:threshold_sensitivity} shows the histogram of cluster sizes and Table \ref{tbl:cluster_table} displays the number of resulting clusters depending on various threshold values.
+Figure \ref{fig:threshold_sensitivity} shows the histogram of cluster sizes, and Table \ref{tbl:cluster_table} displays the number of resulting clusters depending on various threshold values.
 We chose said values after observing the distance between ground truth pairs.
@@
 Regardless of the threshold, the largest cluster has more than 500 addresses.
-Unsurprisingly, higher thresholds result in fewer single-address clusters and more large sized clusters.
-The effect of the threshold is most pronounced for single address clusters, while affecting other cluster sizes much less.
+Unsurprisingly, higher thresholds result in fewer single-address clusters and more large-sized clusters.
+The effect of the threshold is most pronounced for single address clusters while affecting other cluster sizes much less.
 
@@
 \newline
-A few key observations can be made from this network graph.
+A few key observations can be drawn from this network graph.
 In line with our expectations, most LAND transfers involve some form of compensation.
@@
 Lastly, a recurring behavior pattern is observed wherein an individual address purchases LAND and subsequently transfers it to a third address.
-%This could reflect a common strategy among participants in the LAND market.
-
-\begin{figure}[h]
+
+\begin{figure}[h!]
 	\centering
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{../figures/land_network.png}
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=0.9\textwidth]{../figures/land_network.png}
 	\caption{LAND token network}
@@
 \subsection{Combining clustering results}
-To conclude our clustering analysis, we combine the results of self-authorization, learned node embedding and LAND transfer heuristics.
-By doing so, we can cluster 51,581 out of 137,544 (37.5\%) addresses that represent 29,680 entities.
+To conclude our clustering analysis, we combine the results of self-authorization, learned node embedding, and LAND transfer heuristics.
+By doing so, we can cluster 51,581 out of 137,544 (37.5\%) addresses representing 29,680 entities.
 For the remaining addresses, we consider each as an individual entity. 
@@
 Under these assumptions, we estimate 115,643 active users during the time frame studied.
-Out of these, 8,483 entities (7.3\%) interacted with Decentraland through multiple addresses.
+Of these, 8,483 entities (7.3\%) interacted with Decentraland through multiple addresses.
 The largest entity comprises 499 addresses.
@@
 
-Implementing the \textit{self-authorization} heuristic is straightforward, but results in very few identified address clusters.
+Implementing the \textit{self-authorization} heuristic is straightforward but results in very few identified address clusters.
 This is because it requires a highly specific on-chain behavior, which is rarely observed in practice.
 In particular, approvals are seldom used to authorize another externally owned account one might own.
-We also encountered a significant number of false-positives due to non-standard implementations.
+We also encountered a significant number of false positives due to non-standard implementations.
 We are very confident that the large cluster is not controlled by the same entity, and therefore remove it.
@@
 This outcome aligns with findings by \cite{FV:17}, who also observed that the heuristic captures only a small proportion of addresses.
-In his analysis of Ethereum transaction data up to block number 8,500,000 he identified 4,599 entities from 7,107 addresses.
+In his analysis of Ethereum transaction data up to block number 8,500,000, he identified 4,599 entities from 7,107 addresses.
 
@@
 \newline
-Conversely, \cite{wu2022tutela} aim to cluster addresses without a predefined set, therefore using Ethereum transaction data for network graph construction.
+Conversely, \cite{wu2022tutela} aim to cluster addresses without a predefined set, using Ethereum transaction data for network graph construction as a result.
 \cite{Beres2020} try to match deposit and withdrawal addresses for Tornado Cash, relying on all token transfers and transactions to cluster addresses based on similar on-chain behavior.
-Since it is not very common that Tornado cash withdrawal and deposit addresses interact with each other, the approach chosen by \cite{Beres2020} is better suited for their objectives.
-\newline
-Moreover, we validated our approach and found better results in terms of average rank of ground truth address pairs, when building the network graph from intra-set asset transfers compared to using all token transfer events and/or transactions.
-A possible extension would include incorporating edge weights, similar to \cite{wu2022tutela}, however, we refrained from doing this because we would have needed to implement a custom node embedding algorithm.\newline
+Since it is not common that Tornado cash withdrawal and deposit addresses interact with each other, the approach chosen by \cite{Beres2020} is better suited for their objectives.
+\newline
+Moreover, we validated our approach and found better results regarding the average rank of ground truth address pairs when building the network graph from intra-set asset transfers compared to using all token transfer events and/or transactions.
+A possible extension would include incorporating edge weights, similar to \cite{wu2022tutela}; however, we refrained from doing this because we would have needed to implement a custom node embedding algorithm.\newline
 We applied three node embedding algorithms that delivered robust results in the experiments by \cite{Beres2020} and assessed their effectiveness in detecting ground truth pairs.
 Our results indicate that Role2Vec is the best-performing method, locating the ground truth pair within the ten nearest neighbors in 70\% of cases.
-This diverges from the findings of \cite{Beres2020}, who determined Diff2Vec to be the superior method among the three evaluated.
+This result diverges from the findings of \cite{Beres2020}, who determined Diff2Vec to be the superior method among the three evaluated.
 \newline
@@
 DeepWalk and Diff2Vec, both neighborhood-preserving algorithms, mainly capture node proximity.
-As noted by \cite{ahmed2018roletovec}, this does not necessarily imply similarity, especially when addresses frequently interact with each other without being controlled by the same entity.
+As noted by \cite{ahmed2018roletovec}, this does not necessarily imply similarity, especially when addresses frequently interact without being controlled by the same entity.
 In contrast, Role2Vec, a structural node embedding method, identifies nodes with similar roles within the network.
-In our evaluation sample, network position or role may better represent similarity and structural relatedness among nodes.
+In our evaluation sample, network position or role may better represent node similarity and structural relatedness.
 Despite these insights, the differences in results could be specific to the data at hand, given the small sample size, potential evaluation metric flaws, and the overall robust performance of all methods.
 \newline
-Creating clusters out of the node embeddings, enables us to estimate the number of entities represented by the 51,566 addresses.
-Our method involves calculating the Euclidean distance between pairs of feature vectors, specifically using the node embedding matrix generated by Role2Vec.
+Creating clusters out of the node embeddings enables us to estimate the number of entities represented by the 51,566 addresses.
+Our method involves calculating the Euclidean distance between pairs of feature vectors, explicitly using the node embedding matrix generated by Role2Vec.
 Nodes are clustered if their distance falls below a predetermined threshold, and any overlapping clusters are subsequently merged.
@@
 We have provided a sensitivity analysis to illustrate this issue.
-The distances between the feature vectors tend to be quite narrow, with significant variation even among various ground truth pairs' distances.
+The distances between the feature vectors tend to be narrow, with significant variation even among various ground truth pairs' distances.
 Regardless of the threshold value, we were able to locate a cluster of more than 500 addresses.
-Manual inspection revealed that these address show very similar on-chain patterns: They are all exclusively active on Polygon and most of the transfers are mints of Decentraland related NFTs.
+Manual inspection revealed that these addresses show very similar on-chain patterns: They are all exclusively active on Polygon, and most transfers are mints of Decentraland-related NFTs.
 Further, they transfer some NFTs to address \texttt{``0xE2e2F2240a84A61B7dFF50a86ee10d5FaF7faCa8``}.
 The transfers to and from this address are shown in Figure \ref{fig:cluster}.
-Incoming transfers are indicated by green edges, while outgoing transfers are shown by red edges.
+Incoming transfers are indicated by green edges, while red edges show outgoing transfers.
 We hypothesize that the network in question may be operated by a user or even bot that creates multiple distinct addresses and actively engages with Decentraland.
@@
 The \textit{LAND transfer} heuristic is targeted at users revealing address clusters by sending high-value assets to other addresses.
-In this specific case, we use the information that all addresses are related to Decentraland and therefore analyze LAND transfers.
+In this specific case, we use the information that all addresses are related to Decentraland and analyze LAND transfers.
 However, the approach could be applied (more generally) to other NFT collections or large asset transfers in general.
 \newline
-The main assumption behind this approach is that users may want to reorganize their accounts from time to time, mostly to increase security guarantees or spread the risk across multiple accounts.
-As a concrete example, some users may have started with a simple browser-based wallet but as the value of their assets increased and their knowledge grew, they switched to a more secure hardware wallet.
+The main assumption behind this approach is that users may want to reorganize their accounts from time to time, primarily to increase security guarantees or spread the risk across multiple accounts.
+As a concrete example, some users may have started with a simple browser-based wallet, but as the value of their assets increased, and their knowledge grew, they switched to a more secure hardware wallet.
 We detect 161 entities with 413 addresses applying this approach.
-One cluster with 70 address is very likely a not a single entity.
-It includes an address that participated in the intial LAND auction and subsequently distributed LAND.
+One cluster with 70 addresses is likely not a single entity.
+It includes an address that participated in the initial LAND auction and subsequently distributed LAND.
 This may have happened through off-chain compensation.
-The advantage of this method is that it is relatively easy to visualise and understand.
-The disadvantage is that it demands a specific on-chain behaviour and is only scalable with significant effort.
-Additionally, many events that occur off-chain are not detectable in the data, resulting in an increased occurrence of false positives.
+The advantage of this method is that it is relatively easy to visualize and understand.
+The disadvantage is that it demands a specific on-chain behavior and is only scalable with significant effort.
+Additionally, many events that occur off-chain are not detectable in the data, resulting in increased false positives.
 
@@
 Unlike other clustering heuristics, this approach does not rely on specific on-chain behavior patterns or participation in particular events.
-Our implementation generally captures all addresses that have transferred within the address set at least once.
+Our implementation generally captures all addresses that transferred assets within the address set at least once.
 Nevertheless, some clusters may still go undetected, while others may overestimate the number of addresses within a cluster.
-It is important to note that these methods are still only heuristic and testing their efficacy on a large scale is not possible.
-\newline
-Role2Vec performed best for our small test sample, but is not necessarily always be superior to Diff2Vec or DeepWalk.
-Incorporating time-of-day and normalized gas into feature vectors, or refining clusters using a two-step approach, requires further research but could enhance clustering results.
+It is important to note that these methods are still only heuristic and testing their efficacy on a large scale is not feasible.
+\newline
+Role2Vec performed best for our small test sample but may not always superior to Diff2Vec or DeepWalk.
+Incorporating time-of-day and normalized gas into feature vectors or refining clusters using a two-step approach requires further research but could enhance clustering results.
 
@@
 From the 137,544 addresses transacting on Polygon or Ethereum, we identified an estimated 115,643 as active Decentraland users.
-A subset of these entities, representing 7.3\%, operated through multiple addresses.
+A subset of these entities, 8,483 addresses, representing 7.3\%, operated through multiple addresses.
 Notably, the largest address cluster we observed was an entity with 500 distinct addresses.

### 2023-08-24 paper.tex
Add abstract and update figure

@@
 \large{Master Thesis}\\
-\huge Developing Address Clustering Heuristics for Account-Based Blockchain Networks:\\ An Analysis based on a Specific Address Set \\
+\LARGE Developing Address Clustering Heuristics for Account-Based Blockchain Networks:\\ An Analysis based on a Specific Address Set \\
 \Large \vspace{1em}
@@
 \begin{flushleft}
-Supervised by:\\ 
+Supervised by: \\
 Prof. Dr. Fabian Schär \\ 
@@
 \end{center}
-Assentiar consuetae ha opinionum mentemque ob ii.
-Ne conflantur de intelligat et me cohibendam.
-Imaginandi ob to at agnoscerem et mutationum.
-In methodum ob ii at quicquid lectorum.
-Procuravi ha dependent ob evidenter tangantur concipere.
-Immortalem objectivus deo eae rei attingebam ita advertebam quamprimum.
-Typis patet prius qua nia mem ens.
-Suppono sim ita pendere nam agnosci quopiam vestiri spondeo dum.
-Tes illum mundo vetus signa fit talem res his.
+%Privacy, entity clustering, blockchains
+This paper examines heuristics to cluster blockchain addresses using Ethereum and Polygon PoS on-chain data.
+We investigate the number of entities represented by over 470 thousand addresses collected from Decentraland movement data over the course of nine months.
+For this purpose, we assess various existing heuristics, adapt them to our specific research context, and introduce a novel heuristic.
+Our findings suggest that graph representation learning, particularly our variation of node embedding algorithms, to be the most effective approach for clustering a pre-defined address set.
+However, the method does not come without its drawbacks, which is why we discuss extension possibilities for improving clustering performance.
 \\
+
 \vfill
@@
 	\includegraphics[width=0.6\textwidth]{../figures/venn_diagram.png}
-	\caption{Address Subsets Visualized in a Venn Diagram}
+	\caption{Network Specific Address Subsets}
 	\label{fig:Venn}
@@
 	\includegraphics[width=\textwidth]{../figures/land-opensea.png}
-	\caption{LAND trade on Opensea, Source: \href{https://etherscan.io/tx/0x2c2a70114e9080596bf5da6ad9c9b9f6d7e4c85a9d3b06e992f7248f9457a2ec}{Etherscan}}
+	\caption{Example of LAND trade on Opensea, Source: \href{https://etherscan.io/tx/0x2c2a70114e9080596bf5da6ad9c9b9f6d7e4c85a9d3b06e992f7248f9457a2ec}{Etherscan}}
 	\label{fig:LAND_example}
@@
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[width=\textwidth]{../figures/cluster_histogram.png}
-	\caption{Cluster Size Histogram for different distance thresholds}
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=0.9\textwidth]{../figures/cluster_histogram.png}
+	\caption{Cluster Size Histogram for Different Distance Thresholds}
 	\label{fig:threshold_sensitivity}
@@
   \end{tabular}
-  \caption{Clustering results for different threshold values}
+  \caption{Clustering Results for Different Threshold Values}
   \label{tbl:cluster_table}
@@
 	\includegraphics[width=\textwidth]{../figures/cluster-size-distribution.png}
-	\caption{Number of clusters by Cluster Size}
+	\caption{Number of Clusters by Cluster Size}
 	\label{fig:barplot_clusters}
@@
 The required data was efficiently sourced by gathering all transactions and token transfers related to the addresses via Etherscan.
-Furthermore, with the help of ENS, we found a way to detect address pairs that have a very high probability of being controlled by the same user.
+Furthermore, with the help of ENS, we found a way to detect address pairs with a very high probability of being controlled by the same user.
 These address pairs served as our ground truth when evaluating the node embedding algorithms.
@@
 \newline
-From the 137,544 addresses transacting on Polygon or Ethereum, we identified an estimated 115,643 as active Decentraland users.
-A subset of these entities, 8,483 addresses, representing 7.3\%, operated through multiple addresses.
+From the 137,544 addresses transacting on Polygon or Ethereum, we identified an estimated 115,643 active Decentraland users.
+A subset of 8,483 entities, representing 7.3\%, operated through multiple addresses.
 Notably, the largest address cluster we observed was an entity with 500 distinct addresses.
-Based on our analysis, we believe this entity is likely a bot targeting Decentraland NFT airdrops, with intentions to resell them later.
+Based on our analysis, this entity is likely a bot targeting Decentraland NFT airdrops, with intentions to resell them later.
 \newline
@@
 \newline
-A significant challenge with graph representation learning is the formation of clusters after node embedding.
-In our study, we relied on a Euclidean distance threshold for this purpose.
+A significant challenge for graph representation learning is the formation of clusters after node embedding.
+In our study, we relied on an Euclidean distance threshold for this purpose.
 However, the resulting number and size of clusters are highly sensitive to the precise selection of this threshold.

### 2023-08-24 python/combine-clusters.py

@@ -48,7 +48,8 @@ bin_counts = bin_counts.reindex(labels)
 
 # Create a horizontal barplot with a bar for each bin
 plt.figure(figsize=(10, 5))
-ax = sns.barplot(x=bin_counts.values, y=bin_counts.index, color='blue')
+color_palette = sns.color_palette("deep")
+ax = sns.barplot(x=bin_counts.values, y=bin_counts.index, color=color_palette[0], alpha=0.7)
 plt.xlabel('')
 plt.ylabel('Cluster Size', fontsize=14)
 plt.title('Number of Clusters', fontsize=14)

### 2023-08-24 paper.tex
Update Appendix and Title page

@@
 \usepackage{subcaption}
+\usepackage{seqsplit}
 
@@
 %%% Document Specifications %%%
-\title{Template Master's Thesis}
-\author{John Doe}
+\title{Developing Address Clustering Heuristics for Account-Based Blockchain Networks: An Analysis based on a Specific Address Set}
+\author{Dario Thürkauf}
 
@@
 \begin{document}
-%\begin{titlepage}
+\begin{titlepage}
 \begin{center}
@@
 %\noindent\textbf{JEL:} X00, X00, X00
-%\end{titlepage}
+\end{titlepage}
 
@@
 	\includegraphics[width=\textwidth]{../figures/land-opensea.png}
-	\caption{Example of LAND trade on Opensea, Source: \href{https://etherscan.io/tx/0x2c2a70114e9080596bf5da6ad9c9b9f6d7e4c85a9d3b06e992f7248f9457a2ec}{Etherscan}}
+	\caption{LAND trade on Opensea, Source: \href{https://etherscan.io/tx/0x2c2a70114e9080596bf5da6ad9c9b9f6d7e4c85a9d3b06e992f7248f9457a2ec}{Etherscan}}
 	\label{fig:LAND_example}
@@
   \end{tabular}
-  \caption{Average Rank of ENS Domain Names for Different Embedding Methods}
+  \caption{Average Rank of Target Address}
   \label{tbl:ENS_Domain_Ranks}
@@
 	\includegraphics[width=0.5\textwidth]{../figures/land_clusters.png}
-	\caption{Resulting LAND clusters, with largest cluster marked in green}
+	\caption{LAND clusters, largest cluster marked in green}
 	\label{fig:LAND_clusters}
@@
 	\centering
-	\includegraphics[width=0.65\textwidth]{../figures/network_visualization_0xe2e.png}
+	\includegraphics[width=0.8\textwidth]{../figures/network_visualization_0xe2e.png}
 	\caption{Token Transfer Graph for \texttt{0xE2e2F$\dots$faCa8}}
@@
 
+%\subsection{List of Figures}
+
+%\subsection{List of Tables}
+
 \subsection{Database Schema}
@@
   \tiny
-  \begin{tabular}{ll p{4cm} l}
+  \begin{tabular}{ll p{4cm} p{5.5cm}}
     \hline
@@
  \\
-    (16.1M rows) & \texttt{hash} & Transaction hash & 0x8d9490e9f0992e68490cfcb126e76290eca3bf668a... \\
+    (16.1M rows) & \texttt{hash} & Transaction hash & 0x8d9490e9f0992e68490cfcb126e76290eca3bf... \\
      & \texttt{timeStamp} & Timestamp in seconds from the UNIX epoch &  1657777314\\
@@
      & \texttt{value} & The amount of Ether/Matic to send to the destination & 500 \\
-     & \texttt{input} & Calldata & 0x095ea7b30000000000000000000000001111111254fb6c44bac0bed2854e76f90643097dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff \\
+     & \texttt{input} & Calldata & \seqsplit{0x095ea7b30000000000000000000000001111111254fb6c44bac0bed2854e76f90643097dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff} \\
      & \texttt{functionName} & added by Etherscan & approve(address spender, uint256 rawAmount) \\
@@
      & \texttt{chainName} & see above &  see above \\
-     & \texttt{isSet} & Indicator if from or to address are from address set &  from or to \\
+     & \texttt{isSet} & Indicator if `from` or `to` address are from address set &  from or to \\
      & \texttt{userAddress} & Address of interested user & 0x000000085d9a759bb5c3d459d638739c0f48deb0\\
@@
   \end{tabular}
-  \caption{Database/data set Description}
+  %\caption{Database/data set Description}
 \end{table}
-
 %Distinction: Transaction is a message sent from an externally owned account
+
+\subsection{Github Repos}
 

### 2023-08-24 python/cluster-node-embedding.py
Improve naming of files

@@ -82,7 +82,7 @@ for cluster_id, nodes in cluster_df.iterrows():
 
 new_cluster_df = pd.DataFrame(cluster_list, columns=['ClusterID', 'Address'])
 print(new_cluster_df)
-new_cluster_df.to_csv('../data/clusters_R2V_0_5.csv', index=False)
+new_cluster_df.to_csv('../data/clusters/clusters_role2vec_05.csv', index=False)
 
 
 # Show clusters with sizes greater than 50

### 2023-08-24 python/combine-clusters.py

@@ -3,7 +3,7 @@ import matplotlib.pyplot as plt
 import seaborn as sns
 
 # Create the three dataframes
-df1 = pd.read_csv('../data/clusters/clusters_R2V_0_5.csv')
+df1 = pd.read_csv('../data/clusters/clusters_role2vec_05.csv')
 df2 = pd.read_csv('../data/clusters/clusters_selfAuthorization.csv')
 df3 = pd.read_csv('../data/clusters/clusters_LAND.csv', usecols=['ClusterID', 'Address'])
 

### 2023-08-24 python/histogram_node_embedding_cluster.py

@@ -1,6 +1,6 @@
 from utils import *
 
-all_transfers_df = pd.read_csv('../data/all_intra_transfers.csv', index_col=[0], low_memory=False)
+all_transfers_df = pd.read_csv('../data/intra_all_transfers.csv', index_col=[0], low_memory=False)
 
 # Create network graph
 G = nx.from_pandas_edgelist(all_transfers_df, 'from', 'to', create_using=nx.MultiDiGraph())

### 2023-08-24 paper.tex
rename figure
Remove old comments

@@
 
-%Check for each address in the list if the address points to an human-readable name.
-(reverse mapping must be set/configured) From the web3.py documentation \url{https://web3py.readthedocs.io/en/stable/ens_overview.html } %The ens module is included with web3.py.
-It provides an interface to look up domains and addresses, add resolver records, or get and set metadata.
-%If two addresses point to the same ENS name we consider them belonging to the same entity. 
-%Normally, one .eth domain cannot point/map to multiple Ethereum addresses. Forward resolution. This is likely due to the owner change and the record not updated.
-%Only the forward resolution from the name to the address is changed.
-The reverse record resolution from the old address to the name is still there.
-For an visual explanation please see Figure \ref{fig:ENS}.
+%From the web3.py documentation \url{https://web3py.readthedocs.io/en/stable/ens_overview.html }
+%The ens module is included with web3.py. It provides an interface to look up domains and addresses, add resolver records, or get and set metadata.
 %Anyone who owns a domain at any level may configure subdomains - for themselves or others - as desired.
 For instance, if Alice owns 'alice.eth', she can create 'pay.alice.eth' and configure it as she wishes.
-%Currently, all the subdomains or non .eth domains are not NFTs, unless the domain registrar itself supports NFT such as (dcl.eth, and .kred).
-%If the owner sets a reverse resolution set with his new address, we have two addresses pointing to the same ens name. 
-%While 'regular' resolution involves mapping from a name to an address, reverse resolution maps from an address back to a name - or other metadata.
-ENS supports reverse resolution to allow applications to display ENS names in place of hexadecimal addresses.
-Before this can be done, the owner of the address has to configure reverse resolution for their address.
-%In spirit, it is similar to the well-known Domain Name Service (DNS). However, in ENS the registry is implemented in Ethereum smart contracts.
-%Therefore, ENS provides a more user-friendly way of transferring assets on Ethereum, where users can use ENS names as recipient addresses instead of the error-prone hexadecimal Ethereum addresses.
-%Resolving a name is a two-step process: First, ask the registry what resolver is responsible for the name, and second, ask that resolver for the answer to your query.\newline
 
@@
 For comparison, we compute the mean, median, and standard deviation of the average rank for each method.
-
-\iffalse
 %write here that we tested different data sets to create the network graph but intra-set asset transfers performed best for our task.
-The intuition of Diff2Vec is to summarize a node by its neighborhood through a diffusion-like random process.
-Specifically, there are four steps to Diff2Vec: 1) Generating a diffusion graph, 2) sampling a node sequence, 3) extracting features, 4) learning a neural network embedding
-\fi
 
@@
 	\centering
-	\includegraphics[width=\textwidth]{../figures/land-opensea.png}
+	\includegraphics[width=\textwidth]{../figures/etherscan-opensea.png}
 	\caption{LAND trade on Opensea, Source: \href{https://etherscan.io/tx/0x2c2a70114e9080596bf5da6ad9c9b9f6d7e4c85a9d3b06e992f7248f9457a2ec}{Etherscan}}
@@
 \section{Discussion}
-
-%The results chapter or section simply and objectively reports what you found, without speculating on why you found these results. 
-%The discussion
-%... interprets the meaning of the results, puts them in context, and explains why they matter.
-%... is an in-depth exploration of the results, going into detail about the meaning of your findings and citing relevant sources to put them in context.
-%... Try to explain "What do your results mean?", and how they relate to the literature,
-%... provides the explanation and interpretation of results or findings by comparing with the findings in prior studies.
-
 Throughout our analysis, we successfully applied three heuristics to cluster our address set while making use of on-chain data.
@@
 \section{Conclusion}
-
-%...Re-state the main points in a new concise way that you want your readers to remember.
-%...write the output of the work/ investigations in summarized form
-%...intended to help the reader understand why your research should matter to them after they have finished reading the paper.
-%...not merely a summary of your points or a re-statement of your research problem but a synthesis of key points.
-For most essays, one well-developed paragraph is sufficient for a conclusion, although in some cases, a two-or-three paragraph conclusion may be required.
-
 This thesis aimed to determine how many unique entities correspond to the 473,927 addresses observed in Decentraland from July 16, 2022, to April 23, 2023. \newline
@@
 %\subsection{List of Figures}
-
 %\subsection{List of Tables}
@@
 
-%% Table
 \begin{table}[h!]
@@
 \end{document}
-
-%%% Table
-%\begin{table}[h!]
-%  \center
-%  \begin{tabular}{lcc}
-%    \hline\hline
-%    Header & Header & Header \\ \hline
-%    Entry 1 & $0 \leq x<1$ & $\alpha$\\
-%    Entry 2 & $x=1$ & $\beta$\\
-%    Entry 3 & $x>1$ & $\gamma$\\
-%    \hline\hline
-%  \end{tabular}
-%  \caption{This is a table}
-%  \label{tbl:test}
-%\end{table}
-%%%

### 2023-08-25 python/utils.py
Remove old function from utils.py

@@ -172,28 +172,4 @@ class DistCalculation:
         else:
             return None, None
 
-    def foo(self, address1, address2):
-        """
-        returns the rank of a target vector with respect to a query vector in a nearest neighbor search.
-        Args:
-            address1 (str): Address corresponding to the query vector
-            address2 (str): Address corresponding to the target vector
-        Returns:
-            tuple: The rank of the target vector and the corresponding distance. If either address is not found in the node_map, it returns (None, None).
-        """
-        address1, address2 = address1.lower(), address2.lower()
-        if address1 in self.node_map and address2 in self.node_map:
-            query_idx = self.node_map[address1]
-            target_idx = self.node_map[address2]
-
-            distances, indices = self.get_dist_idx(query_idx)
-
-            if len(indices) > 0 and target_idx in indices:
-                trg_idx = np.where(indices == target_idx)[0]
-                return trg_idx.item() + 1, distances[trg_idx].item()
-            else:
-                return None, None
-        else:
-            return None, None
-
 

### 2023-08-25 python/data-visualization/network-visualizer.py
Change network-visualizer directory

@@ -56,9 +56,6 @@ class NetworkVisualizer:
 
 
 if __name__ == "__main__":
-    #addresses = ["0x85e5472752a6f00775faca4d5179bde1081571b0", "0xbf886e3069d0dfd64e384c93da322f775faa8876"]
-    #addresses = ['0xb4955ba9d1fda0c45e1eaa9c5c103d79b9622413']
-    #addresses = ['0x59d2c715aB5bEecA6649b8d4B5F45072EDC37073']
     addresses = ['0xE2e2F2240a84A61B7dFF50a86ee10d5FaF7faCa8']
     network_visualizer = NetworkVisualizer(addresses)
     data = network_visualizer.get_data()

### 2023-08-25 python/data-visualization/histogram_node_embedding_cluster.py
Add utils to data-visualization folder and update histogram_node_embeddings.py

@@ -1,6 +1,6 @@
 from utils import *
 
-all_transfers_df = pd.read_csv('../data/intra_all_transfers.csv', index_col=[0], low_memory=False)
+all_transfers_df = pd.read_csv('../../data/intra_all_transfers.csv', index_col=[0], low_memory=False)
 
 # Create network graph
 G = nx.from_pandas_edgelist(all_transfers_df, 'from', 'to', create_using=nx.MultiDiGraph())
@@ -20,7 +20,7 @@ ordered_addresses = [idx_map[idx] for idx in range(len(node_map))]
 print(f'Nodes: {len(G_cc.nodes())}\nEdges: {len(G_cc.edges())}')
 
 # Get Role2Vec embeddings
-emb_r2v_df = pd.read_csv('../data/embeddings/role2vec.csv', index_col='address')
+emb_r2v_df = pd.read_csv('../../data/embeddings/role2vec.csv', index_col='address')
 embeddings_r2v = emb_r2v_df.values
 faiss_index_r2v = DistCalculation(embeddings_r2v, node_map)
 

### 2023-08-25 python/data-visualization/utils.py

@@ -1,0 +1,175 @@
+# Import packages
+import pandas as pd
+from karateclub import Diff2Vec, Role2Vec, DeepWalk
+import networkx as nx
+import matplotlib.pyplot as plt
+import numpy as np
+import seaborn as sns
+from tqdm import tqdm
+
+
+# Functions
+def compute_weights(df):  ### evtl direkt mit undirected graph arbeiten
+    # Sort from and to addresses lexicographically
+    df['from'], df['to'] = np.where(df['from'] > df['to'], [df['to'], df['from']], [df['from'], df['to']])
+    # Group by 'from' and 'to', and count the number of interactions
+    grouped_df = df.groupby(['from', 'to']).size().reset_index(name='weight')
+    # grouped_df = grouped_df.rename(columns={"from": "address1", "to": "address2"})
+    return grouped_df
+
+
+def clean_graph(G, k=None):
+    """Convert to undirected graph and remove self loops"""
+    G_undir = G.to_undirected()
+    G_tmp = nx.Graph()
+    G_tmp.add_edges_from(G_undir.edges())
+    G_tmp.remove_edges_from(nx.selfloop_edges(G_tmp))
+    # remove low degree nodes
+    if k is not None:
+        G_tmp = nx.k_core(G_tmp, k=2)
+    return G_tmp
+
+
+def recode_graph(G):
+    """Rename nodes to work with Diff2Vec"""
+    N = G.number_of_nodes()
+    node_map = dict(zip(G.nodes(), range(N)))
+    edges_addr = list(G.edges())
+    edges_idx = [(node_map[src], node_map[trg]) for src, trg in edges_addr]
+    G_tmp = nx.Graph()
+    G_tmp.add_edges_from(edges_idx)
+    return G_tmp, node_map
+
+
+def fit_model(G, model, ordered_addresses):
+    """
+    Fit the input model on a graph and get the node embeddings.
+    Returns a tuple where the first element is the node embeddings (numpy array) and the second element is a DataFrame containing the node embeddings with addresses as indices.
+    """
+    model.fit(G)
+    embeddings = model.get_embedding()
+    emb_df = pd.DataFrame(embeddings)
+    emb_df["address"] = ordered_addresses
+    emb_df = emb_df.set_index('address')
+    return embeddings, emb_df
+
+
+def address_txs(address_str):
+    """Get all intra-set transfers/transactions related to an address"""
[…]

### 2023-08-25 python/data-visualization/activity-by-chain.py
Move activity by chain to visualization folder

@@ -3,11 +3,11 @@ import pandas as pd
 import matplotlib.pyplot as plt
 
 # Get all transfers as a pandas dataframe except the '_id', 'userAddress' and 'isSet' column
-df_transfer = pd.read_csv('../data/raw_transfer_events.csv', usecols=lambda x: x not in ['_id', 'userAddress', 'isSet'])
+df_transfer = pd.read_csv('../../data/raw_transfer_events.csv', usecols=lambda x: x not in ['_id', 'userAddress', 'isSet'])
 
 # Get all transactions as a pandas dataframe except the '_id' column
-df_transactions_eth = pd.read_csv('../data/raw_ethereum_transactions.csv', usecols=lambda x: x not in ['_id'])
-df_transactions_polygon = pd.read_csv('../data/raw_polygon_transactions.csv', usecols=lambda x: x not in ['_id'])
+df_transactions_eth = pd.read_csv('../../data/raw_ethereum_transactions.csv', usecols=lambda x: x not in ['_id'])
+df_transactions_polygon = pd.read_csv('../../data/raw_polygon_transactions.csv', usecols=lambda x: x not in ['_id'])
 df_tx = pd.concat([df_transactions_eth, df_transactions_polygon])
 
 # Drop duplicates
@@ -67,5 +67,5 @@ plt.ylim(bottom=-10)
 plt.xlim(left=df.timeStamp.min(), right=df.timeStamp.max())
 plt.xlabel("")
 plt.ylabel("")
-plt.savefig('../figures/transfers_tx_by_chain.png', dpi=300, bbox_inches='tight')
+plt.savefig('../../figures/transfers_tx_by_chain.png', dpi=300, bbox_inches='tight')
 plt.show()

### 2023-08-25 python/combine-clusters.py
Import utils instead of all packages separately

@@ -1,6 +1,4 @@
-import pandas as pd
-import matplotlib.pyplot as plt
-import seaborn as sns
+from utils import *
 
 # Create the three dataframes
 df1 = pd.read_csv('../data/clusters/clusters_role2vec_05.csv')

### 2023-08-25 python/data-visualization/activity-by-chain.py

@@ -1,6 +1,4 @@
-import seaborn as sns
-import pandas as pd
-import matplotlib.pyplot as plt
+from utils import *
 
 # Get all transfers as a pandas dataframe except the '_id', 'userAddress' and 'isSet' column
 df_transfer = pd.read_csv('../../data/raw_transfer_events.csv', usecols=lambda x: x not in ['_id', 'userAddress', 'isSet'])

### 2023-08-25 python/data-visualization/daily-activity-pattern.py

@@ -1,8 +1,4 @@
-import pandas as pd
-import seaborn as sns
-import matplotlib.pyplot as plt
-import numpy as np
-
+from utils import *
 
 def format_x_axis(ax, hour_bins):
     """Formats the x-axis of the time histogram."""

### 2023-08-25 python/data-visualization/network-visualizer.py

@@ -1,7 +1,4 @@
-from pymongo import MongoClient
-import pandas as pd
-import networkx as nx
-import matplotlib.pyplot as plt
+from utils import *
 
 class NetworkVisualizer:
 

### 2023-08-25 python/data-visualization/venn-diagram.py

@@ -1,6 +1,5 @@
-import pandas as pd
+from utils import *
 from matplotlib_venn import venn2
-import matplotlib.pyplot as plt
 
 df = pd.read_csv('../../data/subsets.csv', index_col=[0])
 

### 2023-08-25 python/self-authorization.py

@@ -1,7 +1,6 @@
+from utils import *
 from pymongo import MongoClient
-import pandas as pd
 import re
-import networkx as nx
 
 # Connect to db collection
 client = MongoClient('mongodb://localhost:27017/')

### 2023-08-25 python/data-visualization/histogram-node-embedding-clusters.py
Minor code updates

@@ -83,5 +83,5 @@ plt.ylim([0, 15000])
 plt.legend()
 plt.grid(axis='y', linestyle='--', alpha=0.7)
 plt.tight_layout()
-plt.savefig('../figures/cluster_histogram.png')
+plt.savefig('../../figures/cluster_histogram.png')
 plt.show()

### 2023-08-25 python/utils.py

@@ -111,9 +111,9 @@ def format_x_axis(ax, hour_bins):
 
 
 
-############################
-### Distance Calculation ###
-############################
+##################################
+### Distance Calculation Class ###
+##################################
 
 class DistCalculation:
     def __init__(self, X, node_map):

### 2023-08-25 python/utils.py
Update utils.py
Remove functions

@@ -7,17 +7,6 @@ import numpy as np
 import seaborn as sns
 from tqdm import tqdm
 
-
-# Functions
-def compute_weights(df):  ### evtl direkt mit undirected graph arbeiten
-    # Sort from and to addresses lexicographically
-    df['from'], df['to'] = np.where(df['from'] > df['to'], [df['to'], df['from']], [df['from'], df['to']])
-    # Group by 'from' and 'to', and count the number of interactions
-    grouped_df = df.groupby(['from', 'to']).size().reset_index(name='weight')
-    # grouped_df = grouped_df.rename(columns={"from": "address1", "to": "address2"})
-    return grouped_df
-
-
 def clean_graph(G, k=None):
     """Convert to undirected graph and remove self loops"""
     G_undir = G.to_undirected()
@@ -29,7 +18,6 @@ def clean_graph(G, k=None):
         G_tmp = nx.k_core(G_tmp, k=2)
     return G_tmp
 
-
 def recode_graph(G):
     """Rename nodes to work with Diff2Vec"""
     N = G.number_of_nodes()
@@ -39,7 +27,6 @@ def recode_graph(G):
     G_tmp = nx.Graph()
     G_tmp.add_edges_from(edges_idx)
     return G_tmp, node_map
-
 
 def fit_model(G, model, ordered_addresses):
     """
@@ -53,7 +40,6 @@ def fit_model(G, model, ordered_addresses):
     emb_df = emb_df.set_index('address')
     return embeddings, emb_df
 
-
 def address_txs(address_str):
     """Get all intra-set transfers/transactions related to an address"""
     transfer_df = pd.read_csv('../data/token_transfers.csv', index_col=[0])
@@ -62,53 +48,6 @@ def address_txs(address_str):
     address = str(address_str).lower()
     txs = all_df[(all_df["from"] == address) | (all_df["to"] == address)]
     return txs.sort_values("timeStamp")
-
-
-def show_patterns(events_df, addresses, hour_bins=24, figsize=(15, 15), show_kde=True):
-    """Show side channels distribution of the given addresses"""
-    addresses = [addr.lower() for addr in addresses]
-    events_df['timeStamp'] = pd.to_datetime(events_df['timeStamp'], unit='s')
-    events_df['hour'] = events_df['timeStamp'].dt.hour * 3600 + events_df['timeStamp'].dt.minute * 60 + events_df[
-        'timeStamp'].dt.second
-    sns.set_theme(context='paper')
-
[…]

### 2023-08-25 python/data-visualization/utils.py
Update 2nd utils file

@@ -8,16 +8,6 @@ import seaborn as sns
 from tqdm import tqdm
 
 
-# Functions
-def compute_weights(df):  ### evtl direkt mit undirected graph arbeiten
-    # Sort from and to addresses lexicographically
-    df['from'], df['to'] = np.where(df['from'] > df['to'], [df['to'], df['from']], [df['from'], df['to']])
-    # Group by 'from' and 'to', and count the number of interactions
-    grouped_df = df.groupby(['from', 'to']).size().reset_index(name='weight')
-    # grouped_df = grouped_df.rename(columns={"from": "address1", "to": "address2"})
-    return grouped_df
-
-
 def clean_graph(G, k=None):
     """Convert to undirected graph and remove self loops"""
     G_undir = G.to_undirected()
@@ -31,7 +21,7 @@ def clean_graph(G, k=None):
 
 
 def recode_graph(G):
-    """Rename nodes to work with Diff2Vec"""
+    """Rename nodes to work with Node Embedding models"""
     N = G.number_of_nodes()
     node_map = dict(zip(G.nodes(), range(N)))
     edges_addr = list(G.edges())
@@ -55,60 +45,13 @@ def fit_model(G, model, ordered_addresses):
 
 
 def address_txs(address_str):
-    """Get all intra-set transfers/transactions related to an address"""
+    """Get all intra-set asset transfers related to an address"""
     transfer_df = pd.read_csv('../data/token_transfers.csv', index_col=[0])
     transaction_df = pd.read_csv('../data/native_transfers.csv', index_col=[0])
     all_df = pd.concat([transaction_df, transfer_df], ignore_index=True)
     address = str(address_str).lower()
     txs = all_df[(all_df["from"] == address) | (all_df["to"] == address)]
     return txs.sort_values("timeStamp")
-
-
-def show_patterns(events_df, addresses, hour_bins=24, figsize=(15, 15), show_kde=True):
-    """Show side channels distribution of the given addresses"""
-    addresses = [addr.lower() for addr in addresses]
-    events_df['timeStamp'] = pd.to_datetime(events_df['timeStamp'], unit='s')
-    events_df['hour'] = events_df['timeStamp'].dt.hour * 3600 + events_df['timeStamp'].dt.minute * 60 + events_df[
-        'timeStamp'].dt.second
-    sns.set_theme(context='paper')
-
[…]

### 2023-08-25 python/data-visualization/utils.py
Update function in utils

@@ -6,6 +6,7 @@ import matplotlib.pyplot as plt
 import numpy as np
 import seaborn as sns
 from tqdm import tqdm
+from pymongo import MongoClient
 
 
 def clean_graph(G, k=None):
@@ -44,14 +45,19 @@ def fit_model(G, model, ordered_addresses):
     return embeddings, emb_df
 
 
-def address_txs(address_str):
-    """Get all intra-set asset transfers related to an address"""
-    transfer_df = pd.read_csv('../data/token_transfers.csv', index_col=[0])
-    transaction_df = pd.read_csv('../data/native_transfers.csv', index_col=[0])
-    all_df = pd.concat([transaction_df, transfer_df], ignore_index=True)
-    address = str(address_str).lower()
-    txs = all_df[(all_df["from"] == address) | (all_df["to"] == address)]
-    return txs.sort_values("timeStamp")
+def address_txs(address_list):
+    """
+    Fetches transactions from the 'transactions' collection where any provided address
+    is in the 'from' field.
+    :param address_list: List of Ethereum addresses in string format.
+    :return: A pandas DataFrame containing the transactions.
+    """
+    client = MongoClient('mongodb://localhost:27017/')
+    db = client['address-clustering']
+    transactions = db['transactions']
+
+    return pd.DataFrame(list(transactions.find({"from": {"$in": address_list}})))
+
 
 
 ############################

### 2023-08-25 python/data-visualization/timeOfDay-activity-pattern.py
Update ToD script

@@ -8,8 +8,7 @@ def format_x_axis(ax, hour_bins):
     x_labels = [f'{int(tick / 3600)}' for tick in x_ticks]
     ax.set_xticklabels(x_labels)
 
-
-def show_patterns(events_df, addresses, ens_name, hour_bins=24, figsize=(15, 15), show_kde=True):
+def show_ToD_pattern(events_df, addresses, ens_name, hour_bins=24, figsize=(15, 15), show_kde=True):
     """Show side channels distribution of the given addresses"""
     addresses = [addr.lower() for addr in addresses]
     events_df['timeStamp'] = pd.to_datetime(events_df['timeStamp'], unit='s')
@@ -46,12 +45,26 @@ def show_patterns(events_df, addresses, ens_name, hour_bins=24, figsize=(15, 15)
     return fig, (ax_hist, ax_kde)
 
 
-all_transfers_df = pd.read_csv('../data/all_intra_transfers.csv', index_col=[0])
-ens_pairs = pd.read_csv('../data/ens_pairs.csv', index_col=[0])
+def get_addresses(ens_name, ens_pairs):
+    # Extract addresses corresponding to the queried ENS name
+    query_result = ens_pairs[ens_pairs['ens_name'] == ens_name]
+    if query_result.empty:
+        print(f"No addresses found for {ens_name}")
+        return
+    else:
+        return query_result.iloc[0]['addr1'], query_result.iloc[0]['addr2']
 
-# Specify the addresses to be compared
-addresses = ['0xa5dbd5f2f45cec05ace6c08f0b75bec711ea9517','0xf1289a44a9e7f75809de380ffa261f6095387c72']
 
-show_patterns(all_transfers_df, addresses, 'erikarand.eth', hour_bins=12, show_kde=True, figsize=(15, 10))
-plt.savefig('../figures/time-of-day-activity.png', bbox_inches='tight', dpi=500)
+# ENS Pairs dataset
+ens_pairs = pd.read_csv('../../data/ens_pairs.csv')
+
+# ENS Name to query
+ens_name = 'erikarand.eth'
+# Get addresses corresponding to the queried ENS name
+addresses = get_addresses(ens_name, ens_pairs)
+# Get transactions corresponding to addresses
+transactions_df = address_txs(addresses)
+
+show_ToD_pattern(transactions_df, addresses, ens_name, hour_bins=12, show_kde=True, figsize=(15, 10))
[…]

### 2023-08-25 python/utils.py
Remove old function

@@ -40,15 +40,6 @@ def fit_model(G, model, ordered_addresses):
     emb_df = emb_df.set_index('address')
     return embeddings, emb_df
 
-def address_txs(address_str):
-    """Get all intra-set transfers/transactions related to an address"""
-    transfer_df = pd.read_csv('../data/token_transfers.csv', index_col=[0])
-    transaction_df = pd.read_csv('../data/native_transfers.csv', index_col=[0])
-    all_df = pd.concat([transaction_df, transfer_df], ignore_index=True)
-    address = str(address_str).lower()
-    txs = all_df[(all_df["from"] == address) | (all_df["to"] == address)]
-    return txs.sort_values("timeStamp")
-
 
 ##################################
 ### Distance Calculation Class ###

### 2023-08-25 python/cluster-node-embedding.py
Add script description

@@ -1,6 +1,22 @@
+"""
+This script processes intra-set asset transfer data, representing it as a network graph, and subsequently
+builds clusters out of the graph based on node embeddings derived from techniques like Diff2Vec, Role2Vec,
+and DeepWalk.
+
+Main Steps:
+1. Load transaction data and transform it into a network graph.
+2. Clean and preprocess the graph to keep the largest connected component.
+3. Recode the graph's nodes for efficient referencing.
+4. Load node embeddings (Diff2Vec, Role2Vec, DeepWalk) from CSVs.
+5. Initialize a FAISS index for each embedding to compute distances quickly.
+6. Apply distance threshold and merge overlapping clusters
+7. Convert and save the resulting clusters to a CSV format.
+"""
+
 from utils import *
 
-all_transfers_df = pd.read_csv('../data/all_intra_transfers.csv', index_col=[0], low_memory=False)
+# Load data
+all_transfers_df = pd.read_csv('../data/intra_all_transfers.csv', index_col=[0], low_memory=False)
 
 # Create network graph
 G = nx.from_pandas_edgelist(all_transfers_df, 'from', 'to', create_using=nx.MultiDiGraph())
@@ -10,21 +26,13 @@ G_cc = G.subgraph(largest_cc)
 G_cc, node_map = recode_graph(G_cc) # Recode the graph's nodes, node_map maps from address to index
 idx_map = dict(zip(node_map.values(),node_map.keys())) # Create reverse map (from indices to addresses)
 ordered_addresses = [idx_map[idx] for idx in range(len(node_map))]
-
 print(f'Nodes: {len(G_cc.nodes())}\nEdges: {len(G_cc.edges())}')
 
-#Diff2Vec
-emb_d2v_df = pd.read_csv('../data/embeddings/diff2vec.csv', index_col='address')
-embeddings_d2v = emb_d2v_df.values
-faiss_index_d2v = DistCalculation(embeddings_d2v, node_map)
-#Role2Vec
+# Load node embedding generated by Role2Vec
 emb_r2v_df = pd.read_csv('../data/embeddings/role2vec.csv', index_col='address')
 embeddings_r2v = emb_r2v_df.values
+# Create FAISS index for computing distances efficiently
 faiss_index_r2v = DistCalculation(embeddings_r2v, node_map)
-#Deepwalk
-emb_dw_df = pd.read_csv('../data/embeddings/deepWalk.csv', index_col='address')
[…]

### 2023-08-25 paper.tex
Update abstract

@@
 \end{center}
-%Privacy, entity clustering, blockchains
-This paper examines heuristics to cluster blockchain addresses using Ethereum and Polygon PoS on-chain data.
-We investigate the number of entities represented by over 470 thousand addresses collected from Decentraland movement data over the course of nine months.
-For this purpose, we assess various existing heuristics, adapt them to our specific research context, and introduce a novel heuristic.
-Our findings suggest that graph representation learning, particularly our variation of node embedding algorithms, to be the most effective approach for clustering a pre-defined address set.
-However, the method does not come without its drawbacks, which is why we discuss extension possibilities for improving clustering performance.
+Given the negligible cost of creating blockchain addresses, the notion that one address equates to one user is flawed.
+Therefore, Blockchain Address Clustering emerges as a key tool for estimating the actual number of users.
+This paper examines heuristics to cluster addresses using Ethereum and Polygon PoS on-chain data, analyzing over 470,000 addresses collected from Decentraland over the course of nine months.
+We assess various existing heuristics, adapt them to our specific research context, and also introduce a novel heuristic.
+Our findings suggest that graph representation learning, particularly our variation of a node embedding algorithm, is the most effective approach for clustering a pre-defined address set.
+However, the method does not come without its drawbacks, which is why we propose possible extensions for improving clustering performance.
 \\

### 2023-08-26 paper.tex
Remove comments and update introduction

@@
 
-Public permissionless blockchains such as Bitcoin \citep{nakamotoBitcoin2008} and Ethereum \citep{buterin2014ethereum} allow users %individuals
- to participate with multiple pseudonymous addresses, the creation of which is virtually cost-free.
+Public permissionless blockchains such as Bitcoin \citep{nakamotoBitcoin2008} and Ethereum \citep{buterin2014ethereum} allow users to participate with multiple pseudonymous addresses, the creation of which is virtually cost-free.
 Contrary to popular belief, these blockchains are entirely transparent.
@@
 This circumstance has opened up a nascent scientific field dealing with entity identification within blockchain networks.
-Researchers try to cluster addresses controlled by the same user by analyzing on-chain data and detecting usage patterns.
+Researchers try to cluster addresses controlled by the same entity by analyzing on-chain data and detecting usage patterns.
 The frequent lack of ground truth makes it challenging to evaluate different clustering methods.
@@
 Conversely, the lack of privacy is detrimental to most financial use cases.
-If someone obtains information that allows them to link a blockchain address to an entity, they may effectively observe that entity’s entire transaction history and associated activity.
-Even if the entity uses multiple addresses, any link between these addresses may expose the fact that they belong to the same person.
-As a response, multiple privacy-enhancing tools and protocols have been proposed to obfuscate transaction tracing. 
+If someone links an address to an entity, they can observe all its transactions and activities.
+Using multiple addresses does not ensure privacy, as any connection between them can reveal that they belong to the same individual.
+\citep{nadler2023tornado} \newline
+As a response, various privacy-enhancing tools and protocols have been proposed to obfuscate transaction tracing. 
 Nonetheless, these protocols have yet to be widely adopted, and careless user behavior can undermine the privacy guarantees they offer. \newline
 With these considerations in mind, privacy, or lack thereof, is and will remain an essential topic for blockchain development and research.
-
-%\textbf{Related work}\\
+%If someone obtains information that allows them to link an address to an entity, they may effectively observe that entity’s entire transaction history and associated activity.
+Even if the entity uses multiple addresses, any link between these addresses may expose the fact that they belong to the same person.
+
+%\textbf{Related work}
 Previous work in this field can be broadly categorized into methods developed for blockchains that use the unspent transaction output (UTXO) model, such as Bitcoin, and those that utilize the account-based model, like Ethereum and Polygon.
@@
 \newline
-\cite{Beres2020} propose more universally applicable methods, arguing that Victor’s heuristics, while powerful, assume participation in certain on-chain events.
+\cite{Beres2020} propose more universally applicable methods, arguing that Victor’s heuristics assume participation in certain on-chain events.
 Their approach interprets transactions or token transfers as network graphs, with addresses as nodes and asset transfers as edges.
-They quantitatively compare graph-representation learning algorithms (a subset of machine learning) and propose further user profiling techniques based on time-of-day activity and transaction fee patterns.
+They quantitatively compare graph-representation learning algorithms, a subset of machine learning, and propose further user profiling techniques based on time-of-day activity and transaction fee patterns.
 Using ENS address pairs as ground truth, the authors rigorously test their methods and apply their findings to significantly reduce the privacy guarantees of \textit{Tornado Cash}, a non-custodial privacy-enhancing protocol on Ethereum.
@@
 
-%\textbf{Our contribution}\\
+%\textbf{Our contribution}
 In this work, we perform entity identification on an address set containing 473,927 addresses.
@@
 The fifth section applies the clustering heuristics described in section 4, after which we discuss the results of our analysis and summarize our findings in sections 6 and 7.
-
-%Previous work in this field can be broadly distinguished between methods developed for the unspent transaction output (UTXO) model (e.g., Bitcoin) and the account-based model (e.g., Ethereum and Polygon).
 
@@
 \citep{matic_whitepaper}
-%A high-level programming language is typically used to write smart contracts, and a compiler to convert them into bytecode \citep{mastering_ethereum}
 
@@
 These methods are discussed in more detail in section 4.
-%it is more difficult to link a withdrawal address to a specific depositor address)
 %making use of address re-use, transaction activity, transaction cost choice, or more complex transaction graph and network analyses.
@@
 \section{Data Collection and Preparation} 
-The starting point for our work was a data set comprising 473,927 distinct Web3 addresses. %The original data set comprised 473,927 distinct (Web3) addresses.
+The starting point for our work was a data set comprising 473,927 distinct Web3 addresses.
  As we focus on clustering methods using on-chain data, we exclude addresses that have not been recorded on either Ethereum or Polygon.
@@
 
-\iffalse
-%Transfer Events: 30,689,978
-%Transfer Events Ethereum: 7,832,778
-%Transfer Events Polygon: 22,857,200
-%Transactions = 16,092,531
-%Transactions Ethereum = 8,448,584
-%Transactions Polygon = 7,643,947
-Figure X visualizes the number of daily transactions and token transfers for each chain.
-\begin{figure}[h!]
-	\centering
-	\includegraphics[width=\textwidth]{../figures/transfers_tx_by_chain.png}
-	\caption{Monthly Transactions and Token Transfers by chain}
-	\label{fig:Data}
-\end{figure} 
-\fi
-
 \subsection{Intra-set asset transfers}
@@
 In total, we have 974,478 intra-set token transfers and 210,548 intra-set native asset transfers.
-
-%(101,621 Matic, 108,927 Ether)
-%(logging in to Decentraland with multiple addresses) When it comes to entity clustering, we essentially want to answer the question of how many real-world entities our remaining  137,544 addresses represent.
-%filter our transactions and token transfers to entries where both the 'from' and the 'to' are within this narrowed pool of addresses.
-We define this as intra-set asset transfers.
-For the transactions, this means that we only consider native asset (Ether or matic) transfers.
-%between two EOAs
-%we focus on on-chain data (and not user location or avatar data), allowing us to exclude addresses that have not transacted or interacted with any token on Ethereum or Polygon. 
-%As mentioned in the introduction, the goal of this paper is to cluster addresses belongig to the same entity that were recorded/active in Decentraland during the 9-month period.
-Therefore, we disregard addresses outside of this set.
-Also, since we only look at on-chain data, we cannot cluster addresses without activity on Polygon or Ethereum.
-Doing these two reductions, there are  141, 591 'clusterable' addresses remaining.
-%Since all of our addresses are EOAs (some multisig smart contract wallets).
+%101,621 Matic, 108,927 Ether
 
@@
 \newline
-\textit{Resolvers} are responsible for %(the actual process of)
- translating names into addresses.
+\textit{Resolvers} are responsible for translating names into addresses.
 Any contract that adheres to the relevant standards may act as a resolver.
@@
 	\includegraphics[width=0.8\textwidth]{../figures/time-of-day-activity.png}
-	\caption{Time-of-day activity histogram and KDE for a selected ENS address pair}
+	\caption{Time-of-day activity histogram and KDE for a selected ENS address pair, own illustration based on \cite{Beres2020}}
 	\label{fig:ToD}

### 2023-08-26 paper.tex
Remove comment and minor adjustment

@@
 Since all the addresses' transactions are available in our data set, we can easily employ this heuristic.
-
-\iffalse
-For the ERC-20 standard: \texttt{approve(address spender, uint256 amount)}
-For the ERC-721 standard: \texttt{approve(address to, uint256 tokenId)} and \texttt{setApprovalForAll(address operator, bool approved)}\\
-For the ERC-1155 standard: \texttt{setApprovalForAll(address operator, bool approved)}
-\fi
 
@@
 From a user perspective, it is crucial that privacy-enhancing protocols continue to evolve and gain large-scale adoption.
-Additionally, education on preserving privacy when transacting on blockchains becomes increasingly important.
+Additionally, education on preserving privacy when transacting on blockchains becomes an increasingly important.
 

### 2023-08-26 paper.tex
Incorporate manual revision 1

@@
 Therefore, Blockchain Address Clustering emerges as a key tool for estimating the actual number of users.
-This paper examines heuristics to cluster addresses using Ethereum and Polygon PoS on-chain data, analyzing over 470,000 addresses collected from Decentraland over the course of nine months.
+This paper examines heuristics to cluster addresses using Ethereum and Polygon PoS data, analyzing over 470,000 addresses collected from Decentraland over the course of nine months.
 We assess various existing heuristics, adapt them to our specific research context, and also introduce a novel heuristic.
-Our findings suggest that graph representation learning, particularly our variation of a node embedding algorithm, is the most effective approach for clustering a pre-defined address set.
+Our findings suggest that graph representation learning, particularly our variation of a node embedding algorithm, is the most effective approach for clustering a predefined address set.
 However, the method does not come without its drawbacks, which is why we propose possible extensions for improving clustering performance.
@@
 All transactions are publicly observable and stored as part of the blockchain's history.
-This circumstance has opened up a nascent scientific field dealing with entity identification within blockchain networks.
+This circumstance has opened up a nascent scientific field dealing with entity identification within blockchains.
 Researchers try to cluster addresses controlled by the same entity by analyzing on-chain data and detecting usage patterns.
@@
 Conversely, the lack of privacy is detrimental to most financial use cases.
-If someone links an address to an entity, they can observe all its transactions and activities.
+If someone links an address to an entity, they can observe all its transactions and associated activities.
 Using multiple addresses does not ensure privacy, as any connection between them can reveal that they belong to the same individual.
@@
 Several address clustering heuristics in the UTXO setup have been proposed for Bitcoin and its derivatives \citep{Androulaki2013, Meiklejohn2013, Haslhofer2016, jourdan2018, kappos2022}.
-However, these methods are outside the scope of this work and will not be discussed further.
+However, these methods are outside the scope of this thesis and will not be discussed further.
 \newline
@@
 \cite{wu2022tutela} extend on one of \cite{Beres2020} graph representation learning algorithms and apply it at scale.
-Further, they also propose a set of new clustering heuristics targeting Tornado Cash,  showing that careless user behavior can still reveal identity.
+Further, they propose a set of new clustering heuristics targeting Tornado Cash,  showing that careless user behavior can still reveal identity.
 Based on those heuristics, they developed an application to measure the anonymity of an Ethereum address.
@@
 \newline
-Broadening the scope of entity identification, \cite{victorlüders2019} study the largest Ethereum ERC-20 token networks from a graph perspective.
+Broadening the scope of entity identification, \cite{victorlüders2019} study the largest fungible token networks on Ethereum from a graph perspective.
 Similarly, \cite{casalebrunet2021} apply network graph analysis to various non-fungible token (NFT) ecosystems.
-Both find that many networks follow a star or a hub-and-spoke pattern, similar to social network interaction graphs.
-Moreover, \cite{Payette2017} propose a segmentation of the Ethereum address space into four distinct behavior groups sharing similar attributes while applying k-means clustering.
+Both find that many networks follow either a star or a hub-and-spoke pattern, similar to social network interaction graphs.
+Moreover, \cite{Payette2017} propose a segmentation of the Ethereum address space into four distinct behavior groups sharing similar attributes, while applying k-means clustering.
 \newline
@@
 For EOAs, this address is based on the last 20 bytes of the Keccak-256 hash of the ECDSA public key.
-For contract accounts, it is usually the last 20 bytes of the Keccak-256 hash of the RLP encoding of the sender address and account nonce.
+For contract accounts, it is usually the last 20 bytes of the Keccak-256 hash derived from the sender's address and account nonce.
 \citep{GW:14}
@@
 \textit{First}, its open architecture allows compiling snapshots of user activity, including the users' location within the metaverse and Web3 address.
-Using this capability, \cite{metaverse-retailing2023} captured snapshots of avatar locations over a nine-month period and provided the Web3 addresses collected for this thesis.\newline
+Using this capability, \cite{metaverse-retailing2023} captured snapshots of avatar locations over a nine-month period and provided the collected addresses for this thesis.\newline
 \textit{Second}, users who connect their Web3 account can own various digital assets, such as monetary units, land parcels, and avatar collectibles (e.g., wearables, emotes, and names).
@@
 Moreover, the Decentraland core developers provide a smart-contract-based marketplace where users can buy or trade LAND or other in-game collectibles.
-%The term metaverse refers to Neal Stephenson’s 1992 novel Snow Crash and describes an immersive virtual world that is populated by humans-as-avatars.
 
@@
 \citep{nadler2023tornado} \newline
-In contrast, non-custodial crypto asset mixers (e.g., Tornado Cash) replace the trusted mixing party with a publicly verifiable smart contract.
+In contrast, non-custodial crypto asset mixers, such as Tornado Cash, replace the trusted mixing party with a publicly verifiable smart contract.
 They rely on cryptographic schemes that allow anyone to prove and independently verify the validity of a withdrawal without disclosing the link to a specific deposit.
@@
 The set of all deposits that a particular withdrawal could be originated from is defined as the \textit{anonymity set}.
-In theory, a larger anonymity set will provide a higher level of privacy since any withdrawal address could be linked to more deposit addresses. However, in practice, this does not always hold.
-Some users reveal the link between their withdrawal and deposit addresses, which also affects the privacy of other depositors, for example, by withdrawing from the pool with the same address they deposited or directly sending funds between the two addresses.
+In theory, a larger anonymity set will provide a higher level of privacy since any withdrawal address could be linked to more deposit addresses.
+However, in practice, this principle does not always hold.
+Some users reveal the link between their withdrawal and deposit addresses, for example, by withdrawing from the pool with the same address they deposited or directly sending funds between the two addresses.
+This behavior also affects the privacy of other depositors.
 According to \cite{nadler2023tornado}, careless use of the protocol, testing transactions, or external incentive mechanisms might be reasons for this behavior.
@@
 The absence of account indexing in Ethereum or Polygon poses a challenge for retrieving all past transactions and token transfers of a specific address, as it requires scanning through all blocks and token transfer events emitted by designated token contracts.
-Fortunately, Etherscan offers an API Endpoint Module for ``Accounts`` that facilitates the retrieval of transactions and token transfer events for a given address.
+Fortunately, Etherscan offers an API Endpoint for ``Accounts`` that facilitates the retrieval of transactions and token transfer events for a given address.
 By using our network-specific address subsets, we were able to significantly decrease the number of required API calls.
@@
 \label{sec:ens}
-Similarly to \cite{Beres2020}, we use Ethereum Name Service (ENS) identifiers as ground truth information to evaluate some of the clustering methods.\newline
+Similarly to \cite{Beres2020}, we use Ethereum Name Service (ENS) identifiers as ground truth information to evaluate clustering methods.\newline
 \textit{ENS} is a naming system that relies on the Ethereum smart contracts.
@@
 The registry allows the owner of a domain to make changes to that data.
-\citep{ENSdocs} %Domain owners may set the resolver for the domain.
-\newline
 \textit{Resolvers} are responsible for translating names into addresses.
@@
 The process of resolving a name involves two steps: \textit{First}, the registry must be queried to find out which resolver is responsible for the name, and \textit{second}, that resolver must be asked for the response to the query.
-\newline
+\citep{ENSdocs} \newline
 In addition to regular resolution from name to address, ENS also supports ``reverse resolution``, allowing for a mapping from address back to a name or other metadata.
@@
 If this special case occurs, we assume that both addresses belong to the same entity.
-%We did not observe cases where someone set a reverse record to a completely unrelated address (e.g. alice.eth)
 
@@
 		\end{tikzpicture}
-		\caption{Changing the record to another address does not change the old reverse resolution (Simplified Schematic Representation)}
+		\caption{Simplified Schematic Representation of a Record Change to Another Address}
 		\label{fig:ENS}
@@
 We applied the following methodology to find ground truth pairs: \textit{First}, we gathered all addresses that interacted with ENS to reduce the amount of name look-ups.
-\textit{Second}, we iterated over each address and checked if it reverse-resolved to an ENS domain\footnote{This was done via the ENS module within web3.py \url{https://web3py.readthedocs.io/en/stable/ens_overview.html}, which provides an interface to look up domains and addresses.}.
+\textit{Second}, we iterated over all addresses and checked if they reverse-resolved to an ENS domain\footnote{This was done via the ENS module within web3.py \url{https://web3py.readthedocs.io/en/stable/ens_overview.html}, which provides an interface to look up domains and addresses.}.
 If so, we logged the ENS domain and address in a CSV file.
@@
 The ``self authorization`` heuristic, proposed by \cite{FV:17}, suggests that users might authorize another address they own, possibly for risk distribution across several addresses or for testing purposes.
-\newline
 Since all the addresses' transactions are available in our data set, we can easily employ this heuristic.
@@
 Two parameters are essential for deposit address detection: the discrepancy between the amount received and forwarded (since the exchange must pay for gas fees), and the time lag between receiving and forwarding funds.
-However, our data set only includes the direct transactions or token transfers associated with the addresses.
-The transactions between deposit and main exchange address are absent.
-Consequently, this clustering heuristic is not applicable %with our data
- and it would require significantly more effort for gathering the required data.
+However, our data set only includes the transactions or token transfers associated with the addresses.
+The transactions between deposit and exchange address are absent.
+Consequently, this clustering heuristic is not applicable and would require significantly more effort for gathering the required data.
 
@@
 However, \cite{FV:17} argues that managing the tokens on all of these addresses is impractical, which is why they are often aggregated into one address.
-He finds around 500 same-source, fixed amount token distribution events with at least 1,000 recipients while also taking into account the block difference between the individual aidrop token transfers.
-He defines multi-participation when two airdrop recipients forward their tokens to a single address.
+He found around 500 same-source, fixed amount token distribution events with at least 1,000 recipients while also taking into account the block difference between the individual aidrop token transfers.
+He defined multi-participation when two airdrop recipients forward their tokens to a single address.
 Since we do not have a whole view of the airdrop distribution events, we are not able to identify them within our data.
 One possible approach would include manual selection of known airdrops.
-However, this process takes very long and is not guaranteed to cluster a lot of addresses, since most new airdrop events were carried out with some kind of sybil-resistance.
+However, this process takes a long time and is not guaranteed to cluster many addresses, since more recent airdrop events were mostly carried out with some kind of sybil-resistance.
 Nevertheless, to test this approach we searched for addresses that forwarded the UNI airdrop to another address.
@@
 \label{sec:node}
-According to \cite{Beres2020}, \textit{node embedding} methods form a class of graph representation learning\footnote{Sometimes also referred to as ``network representation learning``} methods that map graph nodes to vectors in a low-dimensional vector space.
+According to \cite{Beres2020}, \textit{node embedding} algorithms form a class of graph representation learning\footnote{Sometimes also referred to as ``network representation learning``} methods that map graph nodes to vectors in a low-dimensional vector space.
 These methods aim to represent vertices with similar neighborhood structure by vectors that are close in the vector space.
@@
 \newline
-The foundation for these node-embedding methods is an undirected graph where nodes are composed of distinct addresses, and an edge is placed between two nodes if there is a transaction between them.
+The foundation for these node-embedding algorithms is an undirected graph where nodes are composed of distinct addresses, and an edge is placed between two nodes if there is a transaction between them.
 \newline
 To construct the network graph, we use the intra-set asset transfers described in section \ref{sec:intra-set}.
-This approach differs from the methodologies adopted by \cite{Beres2020} and \cite{wu2022tutela}.
+Our approach differs from the methodologies adopted by \cite{Beres2020} and \cite{wu2022tutela}.
 On the one hand, \cite{Beres2020} collected all transactions and token transfer events of their address set but did not refine this data to only include intra-set asset transfers.
 On the other hand, \cite{wu2022tutela} do not operate on a specific address set but use all Ethereum transactions to build the network graph, ignoring token transfer events.
-After comparing these two methodologies with ours, we determined that intra-set asset transfers were the most effective for clustering a pre-defined set of addresses.
+After comparing these two methodologies with ours, we determined that intra-set asset transfers were the most effective for clustering a predefined set of addresses.
 %using node-embedding methods.
 \newline
-Using the network graph, node embedding methods seek to learn a function that projects a node to a $d$-dimensional vector representation (also called feature vector).
+Using the network graph, node embedding algorithms seek to learn a function that projects a node to a $d$-dimensional vector representation (also called feature vector).
 This is a way of simplifying the graph information by associating each node with a point in the Euclidean space.
-Various node embedding methods have been developed and applied to different domains.
+Various node embedding algorithms have been developed and applied to different domains.
 \citep{rozemberczki2020difftovec} \newline
-The intuition behind node-embedding approaches is that addresses which interact with the same set of addresses within the network graph should be close in Euclidean distance.
+The intuition behind node embeddings is that addresses which interact with the same set of addresses within the network graph should be close in Euclidean distance.
 \cite{Beres2020} cites two main reasons for this.
-Firstly, users with multiple accounts often interact with the same addresses or services from most of them.
-Secondly, when users move funds between their personal addresses, they may unintentionally reveal their address clusters.
-\newline
-\cite{karateclub} provide a variety of node embedding methods as a Python library\footnote{\url{https://github.com/benedekrozemberczki/karateclub}}.
+\textit{First}, users with multiple accounts often interact with the same addresses or services from most of them.
+\textit{Second}, when users move funds between their personal addresses, they may unintentionally reveal their address clusters.
+\newline
+\cite{karateclub} provide a variety of node embedding algorithms as a Python library\footnote{\url{https://github.com/benedekrozemberczki/karateclub}}.
 They categorize the methods into neighborhood (proximity) preserving and structural.
 \newline
-We focus on the three methods that performed best in \cite{Beres2020} experiments: ``\textit{Diff2Vec}`` \citep{rozemberczki2020difftovec}, ``\textit{Role2Vec}`` \citep{ahmed2018roletovec}, and ``\textit{Deepwalk}`` \citep{perozzi2014}.
+We focus on the three methods that performed best in \cite{Beres2020} experiments: ``\textit{Diff2Vec}`` \citep{rozemberczki2020difftovec}, ``\textit{Role2Vec}`` \citep{ahmed2018roletovec}, and ``\textit{DeepWalk}`` \citep{perozzi2014}.
 Diff2Vec and DeepWalk are neighborhood-preserving methods, while Role2Vec is a structural node embedding method.
 Although all methods utilize random walks to capture graph information, their approaches to leveraging these random walks for constructing Euclidean feature vectors differ.
-A detailed explanation of each method is beyond the scope of this thesis.
+A detailed explanation of each algorithm is beyond the scope of this thesis.
 The interested reader may consult the original publications.
@@
 With our intra-set asset transfer data (\ref{sec:intra-set}) and ENS address pairs (\ref{sec:ens}), we were able to apply and evaluate the node embedding methods described above.
-Using the library described by \cite{karateclub} requires certain preprocessing steps for the network graph.
-Transactions must be treated as undirected edges and loops (self-transactions), and multi-edges must be removed.
+To use the library described by \cite{karateclub}, certain preprocessing steps for the network graph are required.
+Transactions must be treated as undirected edges, loops (self-transactions) and multi-edges must be removed.
 Moreover, nodes outside the largest connected component are excluded.
@@
 For instance, if Alice sent Bob Ether three times and Bob sent Alice Ether two times, the edge weight would correspond to five.
-This choice facilitated the application of \cite{rozemberczki2020difftovec}'s library and eliminated the need to create a custom method.
+This choice facilitated the application of \cite{rozemberczki2020difftovec}'s library and eliminated the need to develop a custom method.
 Based on our network graph, we generate 128-dimensional feature vectors for each address and method.
@@
 \newline
-To evaluate the three node embedding algorithms, we use our ENS address pairs as ground truth.
+For the evaluation of the three node embedding algorithms, we use our ENS address pairs as ground truth.
 We run each node embedding method ten times and report the average rank of the target address.
 For comparison, we compute the mean, median, and standard deviation of the average rank for each method.
-%write here that we tested different data sets to create the network graph but intra-set asset transfers performed best for our task.
 
@@
 The heuristics they identified are as follows: \newline
-``Address match`` refers to instances where individuals use the same address to deposit and withdraw from the Tornado pool.
-``Unique gas price`` involves users selecting a distinct gas price for their deposit and withdrawal transactions (prior to EIP-1559).
-``Linked ETH addresses`` examines whether a deposit address interacts with a withdrawal address outside Tornado Cash.
-``Multiple denomination`` assesses an address' transaction history; two addresses with matching deposit and withdrawal portfolios are considered a pair.
-``Torn minting`` identifies a specific user behavior when withdrawing so-called Anonymity points, an incentive scheme reward for increasing the anonymity set when depositing assets into Tornado cash.\newline
+\textit{Address match} refers to instances where individuals use the same address to deposit and withdraw from the Tornado pool.
+\textit{Unique gas price} involves users selecting a distinct gas price for their deposit and withdrawal transactions (prior to EIP-1559).
+\textit{Linked ETH addresses} examines whether a deposit address interacts with a withdrawal address outside Tornado Cash.
+\textit{Multiple denomination} assesses an address' transaction history; two addresses with matching deposit and withdrawal portfolios are considered a pair.
+\textit{Torn minting} identifies a specific user behavior when withdrawing so-called Anonymity points, an incentive scheme reward for increasing the anonymity set when depositing assets into Tornado cash.\newline
 We identified 84 transactions tied to Tornado cash pools, including 72 deposits, ten withdrawals, and two transactions where an address sent 0.1 Ether to the corresponding pool without invoking the deposit function.
@@
 \newline
-Instead, we choose to build clusters based on the Euclidean distance.
-All neighbors of a node below a certain threshold are considered a cluster.
+Instead, we choose to build clusters based on Euclidean distance, where all neighbors of a node below a certain threshold are clustered.
 Afterward, we merge overlapping clusters; for instance, if node A is clustered with nodes B and C, and node C is clustered with nodes A and X, we form a cluster comprising A, B, C, and X.
@@
 If the same user address appears as the sender and recipient, we mark the transaction as a purchase.
-Finally, we filter out purchases and create address clusters based on the remaining LAND transfers.
+Finally, we filter for purchases and create address clusters based on the remaining LAND transfers.
 
@@
 Upon analysis, we were able to group these addresses into 161 distinct clusters.
-The distribution of these clusters is shown in Figure \ref{fig:LAND_clusters}.
+Figure \ref{fig:LAND_clusters} visualizes the clusters in a network graph.
 Notably, the majority of clusters consist of two or three addresses.
@@
 This outcome aligns with findings by \cite{FV:17}, who also observed that the heuristic captures only a small proportion of addresses.
-In his analysis of Ethereum transaction data up to block number 8,500,000, he identified 4,599 entities from 7,107 addresses.
+In his analysis of Ethereum transaction data up to block number \texttt{8,500,000}, he identified 4,599 entities from 7,107 addresses.
 
@@
 In this specific case, we use the information that all addresses are related to Decentraland and analyze LAND transfers.
-However, the approach could be applied (more generally) to other NFT collections or large asset transfers in general.
+However, the approach could be applied to other NFT collections or large asset transfers in general.
 \newline
@@
 Our implementation generally captures all addresses that transferred assets within the address set at least once.
-Nevertheless, some clusters may still go undetected, while others may overestimate the number of addresses within a cluster.
-It is important to note that these methods are still only heuristic and testing their efficacy on a large scale is not feasible.
+Nevertheless, some clusters may still go undetected, while others may be overestimated.
+It is important to note that these methods are heuristic, and testing their efficacy on a large scale is not feasible.
 \newline
@@
 By focusing on Ethereum and Polygon on-chain data, we narrowed the set down to 137,544 addresses.
-The required data was efficiently sourced by gathering all transactions and token transfers related to the addresses via Etherscan.
+The required data was efficiently sourced by gathering all transactions and token transfers related to the addresses via Etherscan and Polygonscan.
 Furthermore, with the help of ENS, we found a way to detect address pairs with a very high probability of being controlled by the same user.
@@
 To enhance clustering performance, node embeddings could incorporate time-of-day activity and gas price selection patterns.
-This approach holds significant promise for future research in entity identification.
+This approach holds considerable promise for future research in entity identification.
 \newline
@@
 \newline
-Notably, our approach is versatile and can be applied to other predefined address sets.
+Notably, our approach is versatile and can be applied to other large predefined address sets.
 This adaptability is particularly significant given the increasing importance of determining the true number of users in various protocols, especially in areas like Decentralized Finance and on-chain governance.

### 2023-08-26 paper.tex
Solve remaining issues

@@
 On the one hand, identifying addresses that belong to the same real-world entity is beneficial as it allows for better evaluation of network properties concerning usage, distribution of wealth, and detecting fraudulent activities \citep{FV:17}.
-For instance, if users distribute their voting power across various addresses, they might manipulate an on-chain voting process that seems fair at the outset.
+For instance, distributing voting power across various addresses could allow a user to manipulate an on-chain voting process that seems fair at the outset.
 \newline
@@
 To achieve this, we often only consider transactions or token transfer events where both the ``\texttt{from}`` (sender) and the ``\texttt{to}`` (recipient) address are within the address set.
-We call this reduced data set ``\textit{intra-set asset transfers}``.
+We call this reduced data set \textit{intra-set asset transfers}.
 Regarding normal transactions, this means that we only keep native asset transfers (also called payments), as almost all addresses are EOAs.
@@
 Airdrops are popular token distribution mechanisms, and recipients are mostly chosen based on past protocol activity.
-Probably the most well known example is Uniswap's UNI airdrop, where each address that interacted with the protocol until a specified cutoff date received a fixed amount of 400 UNI tokens\footnote{\url{https://blog.uniswap.org/uni}}.
+Probably the most well known example is Uniswap's UNI airdrop, where each address that ever called the Uniswap V1 or V2 contracts until a specified cutoff date received a fixed amount of 400 UNI tokens\footnote{\url{https://blog.uniswap.org/uni}}.
 Especially in the early days of airdrops, these distribution mechanisms were not Sybil-resistant, leading to people creating multiple addresses in anticipation of an airdrop.
@@
 \citep{rozemberczki2020difftovec} \newline
-The intuition behind node embeddings is that addresses which interact with the same set of addresses within the network graph should be close in Euclidean distance.
+The intuition behind node embeddings is that addresses interacting with the same set of addresses within the network graph should be close in Euclidean distance.
 \cite{Beres2020} cites two main reasons for this.
@@
 \newline
-We focus on the three methods that performed best in \cite{Beres2020} experiments: ``\textit{Diff2Vec}`` \citep{rozemberczki2020difftovec}, ``\textit{Role2Vec}`` \citep{ahmed2018roletovec}, and ``\textit{DeepWalk}`` \citep{perozzi2014}.
+We focus on the three methods that performed best in \cite{Beres2020} experiments: \textit{Diff2Vec} \citep{rozemberczki2020difftovec}, \textit{Role2Vec} \citep{ahmed2018roletovec}, and \textit{DeepWalk} \citep{perozzi2014}.
 Diff2Vec and DeepWalk are neighborhood-preserving methods, while Role2Vec is a structural node embedding method.
@@
 \newline
-For the evaluation of the three node embedding algorithms, we use our ENS address pairs as ground truth.
+For evaluation of the three node embedding algorithms, we use our ENS address pairs as ground truth.
 We run each node embedding method ten times and report the average rank of the target address.
@@
 We identified 84 transactions tied to Tornado cash pools, including 72 deposits, ten withdrawals, and two transactions where an address sent 0.1 Ether to the corresponding pool without invoking the deposit function.
-Despite applying all clustering heuristics except "Torn minting", we found no clusters.
+Despite applying all clustering heuristics except Torn minting, we found no clusters.
 
@@
 However, they have been included to demonstrate that the intra-set asset transfer approach may only sometimes be applicable to cluster all addresses of a predefined set.
-\newline
-We must also consider that average rank may not be the most appropriate evaluation metric, particularly when a user controls more than two addresses.
-Suppose a single entity controlling 20 addresses, but only one pair of addresses is detected as ground truth.
-Even if the algorithm finds all 20 addresses within the nearest neighbors but identifies the ground truth pair as the last one, we will score it lower than another algorithm that finds only one of the twenty addresses within the 10 nearest neighbors.
 
@@
 Despite these insights, the differences in results could be specific to the data at hand, given the small sample size, potential evaluation metric flaws, and the overall robust performance of all methods.
+\newline %biased sample
+Additionally, our evaluation sample may be biased, as one could argue that users changing the address associated with their ENS domain name while also keeping the reverse records are not primarily concerned with preserving privacy.
+\newline
+We also need to consider that average rank may not be the most appropriate evaluation metric, particularly when a user controls more than two addresses.
+Suppose a single entity controlling 20 addresses, but only one pair of addresses is detected as ground truth.
+Even if the algorithm finds all 20 addresses within the nearest neighbors but identifies the ground truth pair as the last one, we will score it lower than another algorithm that finds only one of the twenty addresses within the 10 nearest neighbors.
 \newline
@@
 The main assumption behind this approach is that users may want to reorganize their accounts from time to time, primarily to increase security guarantees or spread the risk across multiple accounts.
-As a concrete example, some users may have started with a simple browser-based wallet, but as the value of their assets increased, and their knowledge grew, they switched to a more secure hardware wallet.
+As a concrete example, some users may have started with a simple browser-based wallet, but as their assets appreciated in value, they transitioned to a more secure hardware wallet.
 We detect 161 entities with 413 addresses applying this approach.

### 2023-08-27 python/combine-clusters.py
Add documentation and references to scripts

@@ -1,3 +1,16 @@
+'''
+This script is used for processing and analyzing the three clusters resulting from Node Embedding,
+Self-Authorization and LAND Transfers.
+It combines these clusters into a single dataframe, updating the cluster IDs to ensure uniqueness across the combined set.
+Next, it identifies and resolves overlapping clusters by updating the cluster IDs in the concatenated
+dataframe based on overlapping addresses. Duplicate rows are then removed, and the dataframe is sorted
+by 'ClusterID' and the index is reset.
+
+The script then calculates the number of addresses in each cluster and identifies the number of clusters
+containing more than one address. Following this, it categorizes the clusters into different size bins
+and plots the distribution of cluster sizes as a bar plot.
+'''
+
 from utils import *
 
 # Create the three dataframes

### 2023-08-27 python/self-authorization.py

@@ -1,3 +1,23 @@
+'''
+This script is designed to filter and analyze Ethereum transaction data to identify 'self-authorization' events,
+where an Ethereum address approves another address to spend its tokens. The script first filters the transactions
+to only keep those where the 'input' field starts with the function signature of an approval function.
+
+The script then extracts the spender address from the transaction 'input' data and filters the transactions
+to only keep those where the spender is within the address set.
+Further filtering is applied to only keep transactions where the sender is different from the spender.
+
+The filtered transactions are then used to build a directed graph, where an edge from address A to address B
+indicates that address A has approved address B. Connected components of the graph are then identified as clusters,
+and each address is assigned a cluster ID.
+
+Finally, the largest cluster is removed, and the remaining clusters are saved to a CSV file.
+
+Overall, this script is used to identify self-authorization events in Ethereum transaction data and cluster addresses
+based on these events.
+'''
+
+
 from utils import *
 from pymongo import MongoClient
 import re

### 2023-08-27 python/utils.py

@@ -7,6 +7,8 @@ import numpy as np
 import seaborn as sns
 from tqdm import tqdm
 
+# This function is based on the 'ethereum-privacy' package available at:
+# https://github.com/ferencberes/ethereum-privacy/blob/master/ethprivacy/node_embeddings.py
 def clean_graph(G, k=None):
     """Convert to undirected graph and remove self loops"""
     G_undir = G.to_undirected()
@@ -18,6 +20,8 @@ def clean_graph(G, k=None):
         G_tmp = nx.k_core(G_tmp, k=2)
     return G_tmp
 
+# This function is based on the 'ethereum-privacy' package available at:
+# https://github.com/ferencberes/ethereum-privacy/blob/master/ethprivacy/node_embeddings.py
 def recode_graph(G):
     """Rename nodes to work with Diff2Vec"""
     N = G.number_of_nodes()
@@ -45,6 +49,11 @@ def fit_model(G, model, ordered_addresses):
 ### Distance Calculation Class ###
 ##################################
 
+# This class is based on the 'ethereum-privacy' package available at:
+# https://github.com/ferencberes/ethereum-privacy/blob/master/ethprivacy/distance_calculation.py
+# It also uses the 'faiss' library for efficient similarity search and clustering of dense vectors.
+# 'faiss' is a library developed by Facebook AI Research.
+# More information about 'faiss' can be found at: https://github.com/facebookresearch/faiss
 class DistCalculation:
     def __init__(self, X, node_map):
         """

### 2023-08-27 paper.tex
Update abstract, titles and figure captions

@@
 This paper examines heuristics to cluster addresses using Ethereum and Polygon PoS data, analyzing over 470,000 addresses collected from Decentraland over the course of nine months.
-We assess various existing heuristics, adapt them to our specific research context, and also introduce a novel heuristic.
-Our findings suggest that graph representation learning, particularly our variation of a node embedding algorithm, is the most effective approach for clustering a predefined address set.
+We assess various existing heuristics, adapt them to our specific research context, and also introduce a new heuristic.
+Our findings suggest that graph representation learning, particularly the application of an existing node embedding algorithm to an asset transfer network graph, is the most effective approach for clustering a predefined address set.
 However, the method does not come without its drawbacks, which is why we propose possible extensions for improving clustering performance.
-\\
+\\ %intra-set
 
@@
 
-\subsection{Non-custodial crypto asset mixers}
+\subsection{Non-Custodial Crypto Asset Mixers}
 According to \cite{nadler2023tornado}, crypto-asset mixers are currently the most widely used approach to achieve privacy on public blockchains.
@@
 
-\subsection{Intra-set asset transfers}
+\subsection{Intra-Set Asset Transfers}
 \label{sec:intra-set}
@@
 
-\subsection{ENS address pairs}
+\subsection{ENS Address Pairs}
 \label{sec:ens}
@@
 
-\subsection{Self-authorization} 
+\subsection{Self-Authorization} 
 	All three token standards require functions to allow another address to transfer tokens on behalf of the actual owner.
@@
 
-\subsection{Deposit address reuse}
+\subsection{Deposit Address Reuse}
 The concept of deposit address reuse was first introduced and systematically utilized by \cite{FV:17} and subsequently adoped by \cite{wu2022tutela}.
@@
 
-\subsection{Airdrop multi participation}
+\subsection{Airdrop Multi Participation}
 Airdrops are popular token distribution mechanisms, and recipients are mostly chosen based on past protocol activity.
@@
 
-\subsection{Graph representation learning}
+\subsection{Graph Representation Learning}
 \label{sec:node}
@@
 
-\subsection{Time-of-day transaction activity and gas price selection}
+\subsection{Time-of-Day Transaction Activity and Gas Price Selection}
 Apart from applying node embedding methods to Ethereum transaction graphs, \cite{Beres2020} suggest employing clustering heuristics based on time-of-day transaction activity and gas price selection patterns.
@@
 	\includegraphics[width=0.8\textwidth]{../figures/time-of-day-activity.png}
-	\caption{Time-of-day activity histogram and KDE for a selected ENS address pair, own illustration based on \cite{Beres2020}}
+	\caption{Time-of-Day Activity Histogram and KDE for a Selected ENS Address Pair (Based on \cite{Beres2020})}
 	\label{fig:ToD}
@@
 
-\subsection{Tornado cash heuristics}
+\subsection{Tornado Cash Heuristics}
 \cite{wu2022tutela} propose five heuristics targeted at Tornado cash, highlighting that careless user behavior can still reveal identity despite using a mixer.
@@
 
-\subsection{LAND transfers}
+\subsection{LAND Transfers}
 In addition to the existing clustering heuristics, we propose our heuristic based on transfers of high-value NFTs such as LAND.
@@
 	\includegraphics[width=\textwidth]{../figures/etherscan-opensea.png}
-	\caption{LAND trade on Opensea, Source: \href{https://etherscan.io/tx/0x2c2a70114e9080596bf5da6ad9c9b9f6d7e4c85a9d3b06e992f7248f9457a2ec}{Etherscan}}
+	\caption{Example of LAND Trade on Opensea, Source: \href{https://etherscan.io/tx/0x2c2a70114e9080596bf5da6ad9c9b9f6d7e4c85a9d3b06e992f7248f9457a2ec}{Etherscan}}
 	\label{fig:LAND_example}
@@
 
-\subsection{Self-authorization}
+\subsection{Self-Authorization}
 We analyze the addresses' transaction data to find self-authorizations, focusing on the transaction's ``calldata``.
@@
 
-\subsection{Node embeddings}
+\subsection{Node Embeddings}
 Our analysis of node embedding methods starts with a network graph built from intra-set asset transfers.
@@
 
-\subsection{LAND transfers}
+\subsection{LAND Transfers}
 To implement the LAND transfer clustering heuristic, we select all transaction hashes of LAND transfers between two Decentraland addresses.
@@
 	\includegraphics[width=0.5\textwidth]{../figures/land_clusters.png}
-	\caption{LAND clusters, largest cluster marked in green}
+	\caption{LAND Entity Clusters (largest cluster marked in green)}
 	\label{fig:LAND_clusters}
@@
 	\includegraphics[width=0.9\textwidth]{../figures/land_network.png}
-	\caption{LAND token network}
+	\caption{LAND Transfer Network of Address Set}
 	\label{fig:LAND_network}
@@
 
-\subsection{Combining clustering results}
+\subsection{Combining Clustering Results}
 To conclude our clustering analysis, we combine the results of self-authorization, learned node embedding, and LAND transfer heuristics.

### 2023-08-27 python/utils.py
Update references

@@ -51,8 +51,7 @@ def fit_model(G, model, ordered_addresses):
 
 # This class is based on the 'ethereum-privacy' package available at:
 # https://github.com/ferencberes/ethereum-privacy/blob/master/ethprivacy/distance_calculation.py
-# It also uses the 'faiss' library for efficient similarity search and clustering of dense vectors.
-# 'faiss' is a library developed by Facebook AI Research.
+# It also uses the 'faiss' library developed by Facebook AI Research for efficient similarity search and clustering of dense vectors.
 # More information about 'faiss' can be found at: https://github.com/facebookresearch/faiss
 class DistCalculation:
     def __init__(self, X, node_map):

### 2023-08-27 paper.tex
Update Appendix

@@
 
-%\subsection{List of Figures}
-%\subsection{List of Tables}
-
 \subsection{Database Schema}
@@
  \\
-    (16.1M rows) & \texttt{hash} & Transaction hash & 0x8d9490e9f0992e68490cfcb126e76290eca3bf... \\
+    (16.1M rows) & \texttt{hash} & Transaction hash & \seqsplit{0x8d9490e9f0992e68490cfcb126e76290eca3bf668a9ba0295d563e0553ed657d} \\
      & \texttt{timeStamp} & Timestamp in seconds from the UNIX epoch &  1657777314\\
@@
      & \texttt{nonce} &   &   \\
-     & \texttt{from} & Address initiating the transaction &   \\
-     & \texttt{to} & The destination address (either native asset transfer or function call) &  \\
-     & \texttt{value} & The amount of Ether/Matic to send to the destination & 500 \\
+     & \texttt{from} & Address initiating the transaction & \seqsplit{0xbf9645420578f66d29145dbe5c4a0ba6a85e7121}  \\
+     & \texttt{to} & The destination address (either native asset transfer or function call) & \seqsplit{0x000000000d5a50614bcdf08700fe6ceb1c7dad4b} \\
+     & \texttt{value} & The amount of Ether/Matic to send to the destination address & 500 \\
      & \texttt{input} & Calldata & \seqsplit{0x095ea7b30000000000000000000000001111111254fb6c44bac0bed2854e76f90643097dffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffffff} \\
@@
      & \texttt{nonce} &  see above & see above \\
-     & \texttt{from} &  Sender address & see above \\
-     & \texttt{to} &  Recipient address & see above \\
+     & \texttt{from} &  Sender address (zero address for mints) & \seqsplit{0x0000000000000000000000000000000000000000} \\
+     & \texttt{to} &  Recipient address & \seqsplit{0x000000000d5a50614bcdf08700fe6ceb1c7dad4b} \\
      & \texttt{value} & Amount of tokens transferred in Wei, only for fungible or semi-fungible tokens & 10000000000000000 or NaN (ERC-721) \\
-     & \texttt{tokenID} &  Identifier of the NFT or semi-fungible token &  or NaN (ERC20) \\
+     & \texttt{tokenID} &  Identifier of the NFT or semi-fungible token &  1314 or NaN (ERC20) \\
      & \texttt{contractAddress} & The token contract address &  0xc02aaa39b223fe8d0a0e5c4f27ead9083c756cc2 \\
@@
 
-\subsection{Github Repos}
+\subsection{Github Repositories}
+
+The code, figures, and data sets used for this thesis are hosted on Github. The repository is organized into the following directories:
+
+\begin{itemize}
+	\item \texttt{python}: Contains all the source code used for data collection, analysis, and visualization.
+	\item \texttt{figures}: Contains all the figures and plots generated during the analysis.
+	\item \texttt{data}: Contains the small data sets used for the analysis.
+\end{itemize}
+
+For the complete repository including a documentation of each file and its purpose, please visit the following link:
+
+\texttt{\url{https://github.com/dariothuerkauf/address-clustering}}
+
+For raw data not available in the repository, please contact the authors directly.
+
+A early proof-of-concept for a generalized address clustering Python module can be found under the following link:
+
+\texttt{\url{}}
 

### 2023-08-27 paper.tex
Update paper

@@
 %\textbf{Related work}
-Previous work in this field can be broadly categorized into methods developed for blockchains that use the unspent transaction output (UTXO) model, such as Bitcoin, and those that utilize the account-based model, like Ethereum and Polygon.
+Previous work in this field can be broadly categorized into methods developed for blockchains that use the unspent transaction output (UTXO) model, such as Bitcoin, and those that utilize the account-based model, like Ethereum and Polygon PoS.
 While both models share the concept of addresses, the notion of accounts is absent in UTXO-based blockchains.
@@
 
-\subsection{Ethereum, Polygon and the EVM}
-Ethereum and Polygon are both smart contract-based account-model blockchains. They share the same execution logic - the Ethereum Virtual Machine (EVM).
+\subsection{Ethereum, Polygon PoS and the EVM}
+Ethereum and Polygon PoS are both smart contract-based account-model blockchains. They share the same execution logic - the Ethereum Virtual Machine (EVM).
 The EVM provides a standardized framework for contract execution, ensuring that smart contracts produce deterministic results across all nodes in the network \citep{GW:14}.
 The EVM is independent of the underlying blockchain protocol, allowing other blockchain implementations to adopt this standardized framework for contract execution.\newline
-\textit{Polygon} is a so-called sidechain and aims to address the scalability limitations of Ethereum.
+\textit{Polygon PoS} (referred to as \textit{Polygon}) is a so-called sidechain and aims to address the scalability limitations of Ethereum.
 The adoption of the EVM means that both blockchains share the same user address schemes.
@@
 Initially, Decentraland launched with two native tokens.
-\textit{LAND}, an NFT compliant with ERC-721, manages the ownership of land parcels in Decentraland.
+\textit{LAND}, a NFT compliant with ERC-721, manages the ownership of land parcels in Decentraland.
 \textit{MANA}, a fungible token compliant with ERC-20, is the in-world currency used to purchase digital goods and services.
@@
 While the amount of transactions is similar between the two networks, Polygon has roughly three times more transfer events.
-\newline The output was stored in separate CSV files and also imported into a MongoDB\footnote{\url{https://www.mongodb.com/}} database.
+\newline The output was stored in separate CSV files and imported into a MongoDB\footnote{\url{https://www.mongodb.com/}} database.
 The database contains distinct collections for transactions and transfers.
@@
 \newline
-The ``self authorization`` heuristic, proposed by \cite{FV:17}, suggests that users might authorize another address they own, possibly for risk distribution across several addresses or for testing purposes.
+The \textit{self authorization} heuristic, proposed by \cite{FV:17}, suggests that users might authorize another address they own, possibly for risk distribution across several addresses or for testing purposes.
 Since all the addresses' transactions are available in our data set, we can easily employ this heuristic.
@@
 Deposit addresses share the characteristic that they forward the received funds to a major exchange account.
-Two parameters are essential for deposit address detection: the discrepancy between the amount received and forwarded (since the exchange must pay for gas fees), and the time lag between receiving and forwarding funds.
+Two parameters are essential for deposit address detection: the discrepancy between the amount received and forwarded, as the exchange must pay for gas fees, and the time lag between receiving and forwarding funds.
 However, our data set only includes the transactions or token transfers associated with the addresses.
@@
 One possible approach would include manual selection of known airdrops.
-However, this process takes a long time and is not guaranteed to cluster many addresses, since more recent airdrop events were mostly carried out with some kind of sybil-resistance.
+However, this process takes a long time and is not guaranteed to cluster many addresses, since more recent airdrop events were mostly carried out with some kind of Sybil-resistance.
 Nevertheless, to test this approach we searched for addresses that forwarded the UNI airdrop to another address.
@@
 	\includegraphics[width=0.8\textwidth]{../figures/time-of-day-activity.png}
-	\caption{Time-of-Day Activity Histogram and KDE for a Selected ENS Address Pair (Based on \cite{Beres2020})}
+	\caption{Time-of-Day Activity Histogram and KDE for a Selected ENS Address Pair, Own Illustration Based on \cite{Beres2020}}
 	\label{fig:ToD}
@@
 To accomplish this, we identify token or native asset transfers within the same transaction as a LAND transfer.
-Upon manually examining various implementations of LAND trades on the most popular NFT marketplace contracts, we noticed a recurring pattern: the user address appears in both the ``from`` and ``to`` fields if a trade occurs.
+Upon manually examining various implementations of LAND trades on the most popular NFT marketplace contracts, we noticed a recurring pattern: the user address appears in both the \texttt{``from``} and \texttt{``to``} fields if a trade occurs.
 Figure \ref{fig:LAND_example} illustrates an example of this pattern.
@@
 Notably, two address pairs are absent within the network graph and, therefore, display no values.
-However, they have been included to demonstrate that the intra-set asset transfer approach may only sometimes be applicable to cluster all addresses of a predefined set.
+However, they have been included to demonstrate that the intra-set asset transfer approach may not always be applicable to cluster all addresses of a predefined set.
 
@@
 In line with our expectations, most LAND transfers involve some form of compensation.
-Moreover, certain nodes play a central role in LAND trading, indicated by their high connectivity within the network.
+Moreover, certain nodes play a central role in LAND trading activity, indicated by their high connectivity within the network.
 Lastly, a recurring behavior pattern is observed wherein an individual address purchases LAND and subsequently transfers it to a third address.
@@
 We discussed several existing clustering heuristics and evaluated their suitability in our context.
-Among these heuristics, two were found to be appropriate for clustering a pre-defined set of addresses with the available data: self-authorization \citep{FV:17} and graph representation learning \citep{Beres2020}.
+Among these heuristics, two were found to be appropriate for clustering a predefined set of addresses with the available data: self-authorization \citep{FV:17} and graph representation learning \citep{Beres2020}.
 We modified the graph representation learning approach for our research goal.
@@
 Notably, our approach is versatile and can be applied to other large predefined address sets.
-This adaptability is particularly significant given the increasing importance of determining the true number of users in various protocols, especially in areas like Decentralized Finance and on-chain governance.
+This adaptability is particularly significant given the increasing importance of determining the true number of users in various blockchain applications, especially in areas like Decentralized Finance or on-chain governance.
 \newline

### 2023-08-27 paper.tex
Update Appendix

@@
 
-A early proof-of-concept for a generalized address clustering Python module can be found under the following link:
-
-\texttt{\url{}}
+An early version of a generalized address clustering Python module can be found at:
+
+\texttt{\url{https://github.com/dariothuerkauf/intra-set-address-clustering}}
+
+This module fetches the required data from Etherscan and Polygonscan when given a set of addresses as input, applies the Role2Vec algorithm to the resulting intra-set asset transfer data, and then constructs the clusters using a Euclidean Distance threshold.
+Please note that this module is still under development.
 

### 2023-08-28 python/data-visualization/activity-by-chain.py
Update comments

@@ -1,3 +1,5 @@
+# Not used in paper
+
 from utils import *
 
 # Get all transfers as a pandas dataframe except the '_id', 'userAddress' and 'isSet' column

### 2023-08-28 paper.tex
Final small updates

@@
 		\end{tikzpicture}
-		\caption{Simplified Schematic Representation of a Record Change to Another Address}
+		\caption{Simplified Schematic Representation of an ENS Record Change to Another Address}
 		\label{fig:ENS}
@@
 \newline
-To use the Python library developed by \cite{karateclub}, we remove multi-edges and loops (transfers with the same sender and recipient address) and only consider nodes within the largest connected component.
+To use the Python library developed by \cite{karateclub}, we remove multi-edges and loops (i.e., transfers with the same sender and recipient address) and only consider nodes within the largest connected component.
 The resulting network graph includes 51,566 nodes and 249,302 edges.
@@
      & \texttt{gasPrice} & The price of gas the originator is willing to pay &  12449848873 \\
-     & \texttt{nonce} &   &   \\
+     & \texttt{nonce} & Scalar value equal to the number of transaction sent from an EOA or, in the case of contract accounts, the number of contract-creations made by this account  & 23 \\
      & \texttt{from} & Address initiating the transaction & \seqsplit{0xbf9645420578f66d29145dbe5c4a0ba6a85e7121}  \\
@@
      & \texttt{isSet} & Indicator if `from` or `to` address are from address set &  from or to \\
-     & \texttt{userAddress} & Address of interested user & 0x000000085d9a759bb5c3d459d638739c0f48deb0\\
+     & \texttt{userAddress} & Address of user in set & 0x000000085d9a759bb5c3d459d638739c0f48deb0\\
     \hline
@@
 	\item \texttt{python}: Contains all the source code used for data collection, analysis, and visualization.
-	\item \texttt{figures}: Contains all the figures and plots generated during the analysis.
+	\item \texttt{figures}: Contains the figures and plots generated during the analysis. Network Graphs can be viewed as an interactive HTML file.
 	\item \texttt{data}: Contains the small data sets used for the analysis.

### 2023-09-23 paper.tex
Minor correction
Update paper

@@
 Using multiple addresses does not ensure privacy, as any connection between them can reveal that they belong to the same individual.
-\citep{nadler2023tornado} \newline
+\citep{Beres2020, nadler2023tornado} \newline
 As a response, various privacy-enhancing tools and protocols have been proposed to obfuscate transaction tracing. 
@@
 Account-based blockchains usually distinguish between externally owned accounts (EOAs) and contract accounts (smart contracts).
-\textit{EOAs} are created and controlled by private keys and can be used to hold the native protocol asset, send and receive transactions, and interact with contract accounts.
+\textit{EOAs} derived and controlled by private keys and can be used to hold the native protocol asset, send and receive transactions, and interact with contract accounts.
 \textit{Contract accounts} are controlled by the contract's code; their state can be modified through transactions sent to the contract, and they cannot initiate transactions.
@@
 For EOAs, this address is based on the last 20 bytes of the Keccak-256 hash of the ECDSA public key.
-For contract accounts, it is usually the last 20 bytes of the Keccak-256 hash derived from the sender's address and account nonce.
+For contract accounts, the address is usually the last 20 bytes of the Keccak-256 hash derived from the sender's address and account nonce.
 \citep{GW:14}
@@
 \subsection{Tokens and Token Standards}
-\cite{roth2019tokenization} define \textit{tokens} as rivalrous, digital units of value that represent ownership of an asset or utility.
+Tokens are rivalrous, digital units of value \citep{roth2019tokenization} and may represent virtually any kind of asset or promise \citep{Rosenfeld2013}.
 Smart contracts are the primary method of creating tokens on EVM-based blockchains.
@@
 Any smart contract containing these elements can be interpreted as a token contract.
-\citep{roth2019tokenization} \newline
+\newline
 \textit{Token standards} specify basic interfaces that allow for interoperability between smart contracts.
@@
 \textit{Second}, users who connect their Web3 account can own various digital assets, such as monetary units, land parcels, and avatar collectibles (e.g., wearables, emotes, and names).
-Smart contracts on Ethereum and Polygon track and manage the ownership of these assets \citep{goldbergschaer2023}.
+Smart contracts on Ethereum and Polygon track and manage the ownership of these assets.
 This allows us to analyze the entire transaction history and derive information about the avatars' economic activity.
@@
 
-\subsection{Non-Custodial Crypto Asset Mixers}
-According to \cite{nadler2023tornado}, crypto-asset mixers are currently the most widely used approach to achieve privacy on public blockchains.
-At a high level, we can distinguish between custodial and non-custodial crypto-asset mixers.
+\subsection{Privacy-enhancing Protocols}
+Crypto-asset mixers are currently the most widely used approach to achieve privacy on public blockchains \citep{nadler2023tornado}.
+At a high level, they are categorized into a custodial and a non-custodial setup.
 \newline
@@
 This approach is fully trust-based, as the service provider has complete control over the assets and access to the identifying data.
-\citep{nadler2023tornado} \newline
-In contrast, non-custodial crypto asset mixers, such as Tornado Cash, replace the trusted mixing party with a publicly verifiable smart contract.
+\citep{wu2022tutela, nadler2023tornado} \newline
+In contrast, non-custodial crypto asset mixers (or privacy-enhancing protocols), such as Tornado Cash, replace the trusted mixing party with a publicly verifiable smart contract.
 They rely on cryptographic schemes that allow anyone to prove and independently verify the validity of a withdrawal without disclosing the link to a specific deposit.
@@
 \citep{nadler2023tornado} \newline
-In a nutshell, the mixer works in the following way: Various entities deposit the same amount of a specific crypto asset to a mixer address acting as a pool.
+In a nutshell, the mixer works in the following way: Various entities deposit the same amount of a specific crypto asset to a Tornado Cash smart contract acting as a pool.
 Anyone who has contributed to the pool may then generate a new address and withdraw their funds without revealing the link between the deposit and withdrawal addresses.
-This is achieved using zkSNARKs (zero-knowledge, succinct, non-interactive argument of knowledge).
+This feature is achieved using zkSNARKs (zero-knowledge, succinct, non-interactive argument of knowledge).
 Each depositor inserts a hash value in a Merkle tree.
+%Subsequently, users can withdraw their assets from the mixer whenever they consider that the size of the anonymity set is satisfactory.
  At the time of withdrawal, each legitimate withdrawer can prove unlinkably with a zero-knowledge proof that they know the pre-image of a previously inserted hash leaf in the Merkle tree.
-%Subsequently, users can withdraw their assets from the mixer whenever they consider that the size of the anonymity set is satisfactory.
-For a more detailed description of how Tornado Cash works, see \cite{nadler2023tornado} or \cite{Beres2020}. \newline
+For a detailed technical description of the Tornado Cash protocol, see \cite{khovratovich2019tornado} or \cite{pertsev2019tornado}.
+\newline
 In the context of this thesis, it is sufficient to know that third parties can still observe the addresses that have deposited to and withdrawn from the pool.
@@
 This behavior also affects the privacy of other depositors.
-According to \cite{nadler2023tornado}, careless use of the protocol, testing transactions, or external incentive mechanisms might be reasons for this behavior.
+Careless use of the protocol, testing transactions, or external incentive mechanisms might be reasons for this behavior.
 \newline
@@
     \hline
-	\textbf{ENS domain name} & \textbf{Diff2Vec} & \textbf{Role2Vec} & \textbf{DeepWalk} \\
+	User & \textbf{Diff2Vec} & \textbf{Role2Vec} & \textbf{DeepWalk} \\
 	\hline
-	anisofim.eth & 2.5 & 6.2 & 2.7 \\
-	arisalzberg.eth & 577.3 & 33.3 & 58.8 \\
-	atearnz.eth & 2.8 & 2.5 & 3.3 \\
-	awedjob.eth & 106.8 & 71.1 & 20.1 \\
-	captvicky.eth & - & - & - \\
-	disruptor.eth & 11.1 & 3.0 & 1.4 \\
-	dragonkiller.eth & 30.7 & 1.0 & 1.0 \\
-	eibriel.eth & 44.3 & 91.2 & 545.4 \\
-	epdrabbit.eth & 16.3 & 10.4 & 4.1 \\
-	erikarand.eth & 1.0 & 1.0 & 1.0 \\
-	hyperspek.eth & 129.1 & 10.0 & 605.4 \\
-	jamesmillerblog.eth & - & - & - \\
-	jasonhsu.eth & 1.0 & 1.0 & 1.8 \\
-	joeyz.eth & 1.9 & 1.0 & 1.0 \\
-	keastie.eth & 10.4 & 1.0 & 18.2 \\
-	linkg.eth & 4.0 & 1.0 & 10.3 \\
-	lulox.eth & 4.2 & 1.5 & 27.2 \\
-	maruudn.eth & 5.7 & 5.6 & 108.5 \\
-	maryana.eth & 52.3 & 373.8 & 9.0 \\
-	meanboss.eth & 9.0 & 9.0 & 51.8 \\
-	metatiger.dcl.eth & 474.2 & 86.7 & 2.4 \\
-	mgdivingnz.eth & 1.7 & 5.0 & 1.0 \\
-	mrcryp.eth & 2.7 & 1.0 & 2.3 \\
-	nicebhaiya.eth & 1.3 & 3.4 & 2.4 \\
-	niceguy.eth & 1.0 & 1.0 & 2.2 \\
-	ornellaweb3.eth & 3.7 & 2.0 & 284.0 \\
-	pinkboots.eth & 16.9 & 14.4 & 2.2 \\
-	remx.eth & 3.6 & 2.6 & 1.7 \\
-	rileybeans.eth & 1.5 & 2.0 & 1.6 \\
-	robertjames.eth & 2.7 & 1.0 & 1.1 \\
-	rsantos.eth & 2.0 & 13.6 & 101.2 \\
-	sannin.eth & 64.8 & 1.1 & 1.6 \\
-	smileface.eth & 3.0 & 19.3 & 1.7 \\
-	theartcollection.eth & 11.0 & 5.6 & 3.4 \\
-	turkii13.eth & 52.1 & 68.9 & 47.3 \\
-	tweetious.eth & 10.3 & 4.0 & 227.0 \\
+    1 & 2.5 & 6.2 & 2.7 \\
+    2 & 577.3 & 33.3 & 58.8 \\
+    3 & 2.8 & 2.5 & 3.3 \\
+    4 & 106.8 & 71.1 & 20.1 \\
+    5 & - & - & - \\
+    6 & 11.1 & 3.0 & 1.4 \\
+    7 & 30.7 & 1.0 & 1.0 \\
+    8 & 44.3 & 91.2 & 545.4 \\
+    9 & 16.3 & 10.4 & 4.1 \\
+    10 & 1.0 & 1.0 & 1.0 \\
+    11 & 129.1 & 10.0 & 605.4 \\
+    12 & - & - & - \\
+    13 & 1.0 & 1.0 & 1.8 \\
+    14 & 1.9 & 1.0 & 1.0 \\
+    15 & 10.4 & 1.0 & 18.2 \\
+    16 & 4.0 & 1.0 & 10.3 \\
+    17 & 4.2 & 1.5 & 27.2 \\
+    18 & 5.7 & 5.6 & 108.5 \\
+    19 & 52.3 & 373.8 & 9.0 \\
+    20 & 9.0 & 9.0 & 51.8 \\
+    21 & 474.2 & 86.7 & 2.4 \\
+    22 & 1.7 & 5.0 & 1.0 \\
+    23 & 2.7 & 1.0 & 2.3 \\
+    24 & 1.3 & 3.4 & 2.4 \\
+    25 & 1.0 & 1.0 & 2.2 \\
+    26 & 3.7 & 2.0 & 284.0 \\
+    27 & 16.9 & 14.4 & 2.2 \\
+    28 & 3.6 & 2.6 & 1.7 \\
+    29 & 1.5 & 2.0 & 1.6 \\
+    30 & 2.7 & 1.0 & 1.1 \\
+    31 & 2.0 & 13.6 & 101.2 \\
+    32 & 64.8 & 1.1 & 1.6 \\
+    33 & 3.0 & 19.3 & 1.7 \\
+    34 & 11.0 & 5.6 & 3.4 \\
+    35 & 52.1 & 68.9 & 47.3 \\
+    36 & 10.3 & 4.0 & 227.0 \\
     \hline
@@
     Median & 4.2 & 3.4 & 3.3 \\
-    Standard deviation & 120.504 & 68.814 &  139.932\\
-    Within 5 nearest neighbors & 17 (0.5) & 19 (0.56) & 20 (0.59) \\
-    Within 10 nearest neighbors & 19 (0.56) & 24 (0.71) & 21 (0.62)\\
+    Standard Deviation & 120.504 & 68.814 &  139.932\\
+    Within 5 nearest & 17 (0.5) & 19 (0.56) & 20 (0.59) \\
+    Within 10 nearest & 19 (0.56) & 24 (0.71) & 21 (0.62)\\
     \hline
@@
 \subsection{LAND Transfers}
-To implement the LAND transfer clustering heuristic, we select all transaction hashes of LAND transfers between two Decentraland addresses.
+To implement the LAND transfer clustering heuristic, we select all transaction hashes of LAND transfers that occurred between two Decentraland addresses.
 Next, we gather all token and native asset transfers associated with the selected transaction hashes.
@@
 If the same user address appears as the sender and recipient, we mark the transaction as a purchase.
-Finally, we filter for purchases and create address clusters based on the remaining LAND transfers.
-
-A total of 740 LAND transfers were recorded, involving 413 unique addresses.
-Of these transfers, none involved any form of compensation within the same transaction.
-Upon analysis, we were able to group these addresses into 161 distinct clusters.
-Figure \ref{fig:LAND_clusters} visualizes the clusters in a network graph.
-Notably, the majority of clusters consist of two or three addresses.
-However, one cluster stands out, containing a significantly higher count of 71 addresses.
-This prominent cluster has been marked in green for ease of identification.
-\newline
-LAND transfers between Decentraland addresses can also be visualized as a token network graph, as shown in Figure \ref{fig:LAND_network}.
-In this graph, red edges signify simple transfers, whereas blue edges represent LAND transfers made as part of a trade.
+Finally, we filter out purchases cluster addresses that sent each other LAND without compensation.
+\newline
+A total of 2159 intra-set LAND transfers were recorded, of those, 740 (X \%) were without compensation.
+We were able to group the 413 unique addresses from these uncompensated transfers into 161 distinct clusters.
+Notably, the majority of clusters consist of two or three addresses. However, one cluster stands out, containing a significantly higher count of 71 addresses. \newline 
+Figure \ref{fig:LAND_network} visualizes LAND transfers between Decentraland addresses as a token network graph.
+In this graph, red edges signify non-compensated transfers, whereas blue edges represent LAND transfers made as part of a trade/purchase.
 Notably, the 71-address cluster previously mentioned is visible on the top-right of the largest connected component.
@@
 
-\begin{figure}[h!]
-	\centering
-	\includegraphics[width=0.5\textwidth]{../figures/land_clusters.png}
-	\caption{LAND Entity Clusters (largest cluster marked in green)}
-	\label{fig:LAND_clusters}
-\end{figure}
+%\begin{figure}[h!]
+%	\centering
+%	\includegraphics[width=0.5\textwidth]{../figures/land_clusters.png}
+%	\caption{LAND Entity Clusters (largest cluster marked in green)}
+%	\label{fig:LAND_clusters}
+%\end{figure}
 
@@
 Despite these insights, the differences in results could be specific to the data at hand, given the small sample size, potential evaluation metric flaws, and the overall robust performance of all methods.
-\newline %biased sample
+\newline
 Additionally, our evaluation sample may be biased, as one could argue that users changing the address associated with their ENS domain name while also keeping the reverse records are not primarily concerned with preserving privacy.
@@
 From a user perspective, it is crucial that privacy-enhancing protocols continue to evolve and gain large-scale adoption.
-Additionally, education on preserving privacy when transacting on blockchains becomes an increasingly important.
-
- %The major drawback of graph representation learning is the cluster formation after performing the node embedding.
-In our case, we utilize a Euclidean distance threshold for this task.
-However, the number of clusters and their size is very senstive to the exact choice of this threshold value.
-\newline
-%Address clustering will make further advancements.
-From a user perspective it is important that privacy enhancing protocols are also further developed and users educated how to preserve privacy when transacting on blockchains.
-/ in the context of blockchains
+Additionally, education on preserving privacy when transacting on blockchains becomes an increasingly important topic.
 

### 2023-09-29 paper.tex
Neutral formatting, minor adjustments

@@
 \vspace{1em}
-\large{Master Thesis}\\
-\LARGE Developing Address Clustering Heuristics for Account-Based Blockchain Networks:\\ An Analysis based on a Specific Address Set \\
-\Large \vspace{1em}
-Dario Thürkauf
-\end{center}
-
+%\large{Master Thesis}\\
+\Large Address Clustering Heuristics for Account-Based Blockchain Networks: An Analysis based on a Decentraland User Address Set \\
+\large \vspace{1em}
+Dario Thürkauf \\
 \vspace{1em}
 \normalsize
-\begin{flushleft}
-Supervised by: \\
-Prof. Dr. Fabian Schär \\ 
+PhD candidate, Center for Innovative Finance, University of Basel\\
+\vspace{1.5em}
+Supervised by \\
+\large Prof. Dr. Fabian Schär\\
+\vspace{1em}
+\normalsize
 Professor for Distributed Ledger Technologies and Fintech \\
 Center for Innovative Finance, University of Basel
-\end{flushleft}
-
-\vspace{1em}
+\end{center}
+
+\normalsize
+%\begin{flushleft}
+%Supervised by: \\
+%Prof. Dr. Fabian Schär \\ 
+%Professor for Distributed Ledger Technologies and Fintech \\
+%Center for Innovative Finance, University of Basel
+%\end{flushleft}
+
 \onehalfspacing
@@
 \vfill
-\textbf{Keywords:} Blockchain, Accounts, Clustering Heuristics, Entity Identification, Graph Representation Learning.\\
+\textbf{Keywords:} Blockchain, Web3, Accounts, Clustering Heuristics, Entity Identification, Graph Representation Learning.\\
 %\noindent\textbf{JEL:} X00, X00, X00
@@
 
-\pagenumbering{gobble}
-
-\newpage
-\pagenumbering{Roman}
-\tableofcontents
-
-\vfill
-\begin{center}
-\includegraphics[width=4cm]{../figures/logo_cif.png}
-\end{center}
-\newpage
-\singlespacing
+%\pagenumbering{gobble}
+
+%\pagenumbering{Roman}
+%\tableofcontents
+
+%\singlespacing
 %\vspace{-1.5cm}
-\section*{Declaration of Independent Authorship}
-I attest with my signature that I have written this work independently and without outside help.
+%\section*{Declaration of Independent Authorship}
+%I attest with my signature that I have written this work independently and without outside help.
 I also attest that the information concerning the sources used in this work is true and complete in every respect.
 All sources that have been quoted or paraphrased have been marked accordingly.
-Additionally, I affirm that any text passages written with the help of AI-supported technology are marked as such, including a reference to the AI-supported program used.
+%Additionally, I affirm that any text passages written with the help of AI-supported technology are marked as such, including a reference to the AI-supported program used.
 This paper may be checked for plagiarism and use of AI-supported technology using the appropriate software.
 I understand that unethical conduct may lead to a grade of 1 or ``fail`` or expulsion from the study program.\\
-
-Dario Thürkauf
-
-\begin{figure}[h!]
-	\centering
-	\hspace{-10cm}
-	\includegraphics[width=3cm]{../figures/signature.jpeg}
-\end{figure}
+%
+%Dario Thürkauf
+%\begin{figure}[h!]
+%	\centering
+%	\hspace{-10cm}
+%	\includegraphics[width=3cm]{../figures/signature.jpeg}
+%\end{figure}
 %%%%%%%%%%%%%%%%%%%%
@@
 Several address clustering heuristics in the UTXO setup have been proposed for Bitcoin and its derivatives \citep{Androulaki2013, Meiklejohn2013, Haslhofer2016, jourdan2018, kappos2022}.
-However, these methods are outside the scope of this thesis and will not be discussed further.
+However, these methods are outside the scope of this work and will not be discussed further.
 \newline
@@
 Both find that many networks follow either a star or a hub-and-spoke pattern, similar to social network interaction graphs.
-Moreover, \cite{Payette2017} propose a segmentation of the Ethereum address space into four distinct behavior groups sharing similar attributes, while applying k-means clustering.
+Moreover, using k-means clustering, \cite{Payette2017} propose a segmentation of the Ethereum address space into four distinct behavior groups sharing similar attributes.
 \newline
@@
 
-%\textbf{Our contribution}
 In this work, we perform entity identification on an address set containing 473,927 addresses.
@@
 As of our knowledge, we are the first to cluster addresses within a predefined set on a large scale.
-%Anwenden/discuss/anpassen/erweitern and evaluate existing heuristics to my specific address set.
 
@@
 Account-based blockchains usually distinguish between externally owned accounts (EOAs) and contract accounts (smart contracts).
-\textit{EOAs} derived and controlled by private keys and can be used to hold the native protocol asset, send and receive transactions, and interact with contract accounts.
+\textit{EOAs} are derived from private keys and can be used to hold the native protocol asset, send and receive transactions, and interact with contract accounts.
 \textit{Contract accounts} are controlled by the contract's code; their state can be modified through transactions sent to the contract, and they cannot initiate transactions.
@@
 \textit{First}, its open architecture allows compiling snapshots of user activity, including the users' location within the metaverse and Web3 address.
-Using this capability, \cite{metaverse-retailing2023} captured snapshots of avatar locations over a nine-month period and provided the collected addresses for this thesis.\newline
+Using this capability, \cite{metaverse-retailing2023} captured snapshots of avatar locations over a nine-month period and provided the collected addresses for this work.\newline
 \textit{Second}, users who connect their Web3 account can own various digital assets, such as monetary units, land parcels, and avatar collectibles (e.g., wearables, emotes, and names).
@@
 The majority of purchases and trades are settled in MANA.
-\newline
 Moreover, the Decentraland core developers provide a smart-contract-based marketplace where users can buy or trade LAND or other in-game collectibles.
@@
 \subsection{Privacy-enhancing Protocols}
-Crypto-asset mixers are currently the most widely used approach to achieve privacy on public blockchains \citep{nadler2023tornado}.
-At a high level, they are categorized into a custodial and a non-custodial setup.
-\newline
+%Crypto-asset mixers are currently the most widely used approach to achieve privacy on public blockchains \citep{nadler2023tornado}. 
+At a high level, privacy-enhancing services or protocols are categorized into a custodial and a non-custodial setup.
 In the custodial setup, users send their assets to a centralized service provider's public deposit address.
@@
 This approach is fully trust-based, as the service provider has complete control over the assets and access to the identifying data.
-\citep{wu2022tutela, nadler2023tornado} \newline
-In contrast, non-custodial crypto asset mixers (or privacy-enhancing protocols), such as Tornado Cash, replace the trusted mixing party with a publicly verifiable smart contract.
+\citep{Beres2020, wu2022tutela, nadler2023tornado} \newline
+In contrast, non-custodial privacy-enhancing protocols, such as Tornado Cash, replace the trusted mixing party with a publicly verifiable smart contract.
 They rely on cryptographic schemes that allow anyone to prove and independently verify the validity of a withdrawal without disclosing the link to a specific deposit.
@@
 This feature is achieved using zkSNARKs (zero-knowledge, succinct, non-interactive argument of knowledge).
-Each depositor inserts a hash value in a Merkle tree.
-%Subsequently, users can withdraw their assets from the mixer whenever they consider that the size of the anonymity set is satisfactory.
+Each depositor inserts a hash value in a Merkle tree. Subsequently, users can withdraw their assets from the mixer whenever they consider that the size of the anonymity set is satisfactory.
  At the time of withdrawal, each legitimate withdrawer can prove unlinkably with a zero-knowledge proof that they know the pre-image of a previously inserted hash leaf in the Merkle tree.
@@
 \newline
-In the context of this thesis, it is sufficient to know that third parties can still observe the addresses that have deposited to and withdrawn from the pool.
+In the context of this work, it is sufficient to know that third parties can still observe the addresses that have deposited to and withdrawn from the pool.
 The set of all deposits that a particular withdrawal could be originated from is defined as the \textit{anonymity set}.
@@
 These methods are discussed in more detail in section 4.
-%In theory, a larger anonymity set will provide a higher level of privacy as third parties will not be able to link a specific depositor address to a specific withdrawal address.
-However, this is not always the case.
-For example, some users (might) withdraw from the pool with the same address as they deposited.
-According to \cite{nadler2023tornado}, careless use of the protocol, testing transactions or external incentive mechanisms might be reasons for this behaviour.
-\newline
-%In addition, \cite{Beres2020} and \cite{wu2022tutela} propose approaches to de-anonymize Tornado cash transactions using various clustering heuristics.
-These methods are discussed in more detail in section 4.
-%making use of address re-use, transaction activity, transaction cost choice, or more complex transaction graph and network analyses.
 
@@
 Although all methods utilize random walks to capture graph information, their approaches to leveraging these random walks for constructing Euclidean feature vectors differ.
-A detailed explanation of each algorithm is beyond the scope of this thesis.
+A detailed explanation of each algorithm is beyond the scope of this work.
 The interested reader may consult the original publications.
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{../figures/time-of-day-activity.png}
+	\includegraphics[width=0.9\textwidth]{../figures/time-of-day-activity.png}
 	\caption{Time-of-Day Activity Histogram and KDE for a Selected ENS Address Pair, Own Illustration Based on \cite{Beres2020}}
@@
     \hline
-	User & \textbf{Diff2Vec} & \textbf{Role2Vec} & \textbf{DeepWalk} \\
+	\textbf{User} & \textbf{Diff2Vec} & \textbf{Role2Vec} & \textbf{DeepWalk} \\
 	\hline
@@
 We group the data by transaction hash and examine each transfer's sender (\texttt{from}) and recipient (\texttt{to}) address.
-If the same user address appears as the sender and recipient, we mark the transaction as a purchase.
-Finally, we filter out purchases cluster addresses that sent each other LAND without compensation.
+If the same address appears as the sender and recipient, we mark the transaction as a purchase.
+Finally, we exclude purchases and build clusters for addresses that sent each other LAND without compensation.
 \newline
@@
 We were able to group the 413 unique addresses from these uncompensated transfers into 161 distinct clusters.
-Notably, the majority of clusters consist of two or three addresses. However, one cluster stands out, containing a significantly higher count of 71 addresses. \newline 
+Notably, the majority of clusters consist of two or three addresses. However, one cluster counting 71 addresses stands out. \newline 
 Figure \ref{fig:LAND_network} visualizes LAND transfers between Decentraland addresses as a token network graph.
@@
 \section{Conclusion}
-This thesis aimed to determine how many unique entities correspond to the 473,927 addresses observed in Decentraland from July 16, 2022, to April 23, 2023. \newline
+This work aimed to determine how many unique entities correspond to the 473,927 addresses observed in Decentraland from July 16, 2022, to April 23, 2023. \newline
 By focusing on Ethereum and Polygon on-chain data, we narrowed the set down to 137,544 addresses.
@@
 Although we were able to detect entity clusters, Decentraland still exhibits a lot of natural activity.
-Its open infrastructure presents vast opportunities for in-depth analysis of the virtual world, as demonstrated in this thesis.
+Its open infrastructure presents vast opportunities for in-depth analysis of the virtual world, as demonstrated in this work.
 \newline
@@
 Additionally, education on preserving privacy when transacting on blockchains becomes an increasingly important topic.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+%%% Acknowledgements %%%
+%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\section*{Acknowledgements}
+I would like to thank Prof.
+Dr.
+Fabian Schär for his advice and support throughout the thesis and the opportunity to delve into this intriguing topic.
+My gratitude also extends to Mitchell Goldberg for his valuable inputs and discussions.
+Last but not least, a special thanks to Willy Thürkauf for his proof-reading.
 
@@
 
-For raw data not available in the repository, please contact the authors directly.
-
-An early version of a generalized address clustering Python module can be found at:
-
-\texttt{\url{https://github.com/dariothuerkauf/intra-set-address-clustering}}
-
-This module fetches the required data from Etherscan and Polygonscan when given a set of addresses as input, applies the Role2Vec algorithm to the resulting intra-set asset transfer data, and then constructs the clusters using a Euclidean Distance threshold.
+%For raw data not available in the repository, please contact the authors directly.
+%
+%An early version of a generalized address clustering Python module can be found at:
+%
+%\texttt{\url{https://github.com/dariothuerkauf/intra-set-address-clustering}}
+%
+%This module fetches the required data from Etherscan and Polygonscan when given a set of addresses as input, applies the Role2Vec algorithm to the resulting intra-set asset transfer data, and then constructs the clusters using a Euclidean Distance threshold.
 Please note that this module is still under development.

### 2023-09-29 paper.tex
Update paper to compile in VSC

@@
 %%% Document Specifications %%%
-\title{Developing Address Clustering Heuristics for Account-Based Blockchain Networks: An Analysis based on a Specific Address Set}
+\title{Address Clustering Heuristics for Account-Based Blockchain Networks: An Analysis based on a Specific Address Set}
 \author{Dario Thürkauf}
@@
 As suggested by \cite{nakamotoBitcoin2008} in the Bitcoin whitepaper, most Bitcoin wallet implementations use a new key pair for each transaction to keep them from being linked to a common owner.
-Unlike the UTXO model, native transactions in account-based blockchains can only move funds between a single sender and receiver, and the ``change`` remains in the sender account.
+Unlike the UTXO model, native transactions in account-based blockchains can only move funds between a single sender and receiver, and the ''change'' remains in the sender account.
 Subsequent transactions necessarily use the same address again.
@@
 When a transaction completes, it produces a transaction receipt that contains log entries providing information about the actions that occurred during its execution.
-Solidity\footnote{Solidity is the dominant high-level programming language for smart contracts targeting the EVM.} high-level objects called ``Events`` construct these logs, which can be queried from a full node and are stored separately from the state.
+Solidity\footnote{Solidity is the dominant high-level programming language for smart contracts targeting the EVM.} high-level objects called ''Events'' construct these logs, which can be queried from a full node and are stored separately from the state.
 \citep{mastering_ethereum} \newline
-The standardization of tokens allows us to listen for ``transfer events``, which are emitted whenever a token changes ownership.
+The standardization of tokens allows us to listen for ''transfer events'', which are emitted whenever a token changes ownership.
 These transfer events include the \textit{sender} and \textit{recipient} address, along with a \textit{token ID} and/or \textit{amount}.
@@
 Overall, 59,651 addresses were recorded on Ethereum, 129,988 on Polygon, with 52,095 addresses appearing on both networks simultaneously.
-The set of ``clusterable`` addresses therefore counts 137,544 addresses.
+The set of ''clusterable'' addresses therefore counts 137,544 addresses.
 The subsets are visualized as a Venn diagram in Figure \ref{fig:Venn}.
@@
 	\centering
-	\includegraphics[width=0.6\textwidth]{../figures/venn_diagram.png}
+	\includegraphics[width=0.6\textwidth]{./figures/venn_diagram.png}
 	\caption{Network Specific Address Subsets}
@@
 The absence of account indexing in Ethereum or Polygon poses a challenge for retrieving all past transactions and token transfers of a specific address, as it requires scanning through all blocks and token transfer events emitted by designated token contracts.
-Fortunately, Etherscan offers an API Endpoint for ``Accounts`` that facilitates the retrieval of transactions and token transfer events for a given address.
+Fortunately, Etherscan offers an API Endpoint for ''Accounts'' that facilitates the retrieval of transactions and token transfer events for a given address.
 By using our network-specific address subsets, we were able to significantly decrease the number of required API calls.
@@
 \newline
-To achieve this, we often only consider transactions or token transfer events where both the ``\texttt{from}`` (sender) and the ``\texttt{to}`` (recipient) address are within the address set.
+To achieve this, we often only consider transactions or token transfer events where both the ''\texttt{from}'' (sender) and the ''\texttt{to}'' (recipient) address are within the address set.
 We call this reduced data set \textit{intra-set asset transfers}.
@@
 \newline
-The \textit{ENS registry} consists of a single smart contract\footnote{The registry contract is ERC-721 compliant, which means that .eth registrations can be transferred in the same way as other NFTs.} that maintains a list of all domains and subdomains, recording the ``owner`` and ``resolver`` for each.
+The \textit{ENS registry} consists of a single smart contract\footnote{The registry contract is ERC-721 compliant, which means that .eth registrations can be transferred in the same way as other NFTs.} that maintains a list of all domains and subdomains, recording the ''owner'' and ''resolver'' for each.
 The registry allows the owner of a domain to make changes to that data.
@@
 \citep{ENSdocs} \newline
-In addition to regular resolution from name to address, ENS also supports ``reverse resolution``, allowing for a mapping from address back to a name or other metadata.
+In addition to regular resolution from name to address, ENS also supports ''reverse resolution'', allowing for a mapping from address back to a name or other metadata.
 Reverse resolution is accomplished via the %special
@@
 \label{sec:node}
-According to \cite{Beres2020}, \textit{node embedding} algorithms form a class of graph representation learning\footnote{Sometimes also referred to as ``network representation learning``} methods that map graph nodes to vectors in a low-dimensional vector space.
+According to \cite{Beres2020}, \textit{node embedding} algorithms form a class of graph representation learning\footnote{Sometimes also referred to as ''network representation learning''} methods that map graph nodes to vectors in a low-dimensional vector space.
 These methods aim to represent vertices with similar neighborhood structure by vectors that are close in the vector space.
@@
 	\centering
-	\includegraphics[width=0.9\textwidth]{../figures/time-of-day-activity.png}
+	\includegraphics[width=0.9\textwidth]{./figures/time-of-day-activity.png}
 	\caption{Time-of-Day Activity Histogram and KDE for a Selected ENS Address Pair, Own Illustration Based on \cite{Beres2020}}
@@
 To accomplish this, we identify token or native asset transfers within the same transaction as a LAND transfer.
-Upon manually examining various implementations of LAND trades on the most popular NFT marketplace contracts, we noticed a recurring pattern: the user address appears in both the \texttt{``from``} and \texttt{``to``} fields if a trade occurs.
+Upon manually examining various implementations of LAND trades on the most popular NFT marketplace contracts, we noticed a recurring pattern: the user address appears in both the \texttt{''from''} and \texttt{''to''} fields if a trade occurs.
 Figure \ref{fig:LAND_example} illustrates an example of this pattern.
@@
 	\centering
-	\includegraphics[width=\textwidth]{../figures/etherscan-opensea.png}
+	\includegraphics[width=\textwidth]{./figures/etherscan-opensea.png}
 	\caption{Example of LAND Trade on Opensea, Source: \href{https://etherscan.io/tx/0x2c2a70114e9080596bf5da6ad9c9b9f6d7e4c85a9d3b06e992f7248f9457a2ec}{Etherscan}}
@@
 \subsection{Self-Authorization}
-We analyze the addresses' transaction data to find self-authorizations, focusing on the transaction's ``calldata``.
+We analyze the addresses' transaction data to find self-authorizations, focusing on the transaction's ''calldata''.
 The first four bytes of the calldata represent the function selector, which unambiguously specifies the smart contract function the transaction originator wants to invoke.
@@
 After manual inspection, we excluded a cluster containing 80 addresses with all approvals issued by the same address for the same token contract.
-The token contract represents a collection of wearable NFTs on Polygon called ``Renaissance King by René Mäkelä`` and may use an uncommon or potentially even faulty token minting scheme.
+The token contract represents a collection of wearable NFTs on Polygon called ''Renaissance King by René Mäkelä'' and may use an uncommon or potentially even faulty token minting scheme.
 Ultimately, we discovered 35 addresses associated with 15 distinct entities.
@@
 	\centering
-	\includegraphics[width=0.9\textwidth]{../figures/cluster_histogram.png}
+	\includegraphics[width=0.9\textwidth]{./figures/cluster_histogram.png}
 	\caption{Cluster Size Histogram for Different Distance Thresholds}
@@
 	\centering
-	\includegraphics[width=0.9\textwidth]{../figures/land_network.png}
+	\includegraphics[width=0.9\textwidth]{./figures/land_network.png}
 	\caption{LAND Transfer Network of Address Set}
@@
 	\centering
-	\includegraphics[width=\textwidth]{../figures/cluster-size-distribution.png}
+	\includegraphics[width=\textwidth]{./figures/cluster-size-distribution.png}
 	\caption{Number of Clusters by Cluster Size}
@@
 Manual inspection revealed that these addresses show very similar on-chain patterns: They are all exclusively active on Polygon, and most transfers are mints of Decentraland-related NFTs.
-Further, they transfer some NFTs to address \texttt{``0xE2e2F2240a84A61B7dFF50a86ee10d5FaF7faCa8``}.
+Further, they transfer some NFTs to address \texttt{''0xE2e2F2240a84A61B7dFF50a86ee10d5FaF7faCa8''}.
 The transfers to and from this address are shown in Figure \ref{fig:cluster}.
@@
 	\centering
-	\includegraphics[width=0.8\textwidth]{../figures/network_visualization_0xe2e.png}
+	\includegraphics[width=0.8\textwidth]{./figures/network_visualization_0xe2e.png}
 	\caption{Token Transfer Graph for \texttt{0xE2e2F$\dots$faCa8}}

### 2023-09-29 paper.tex
Update title
Update Title page

@@
 %%% Document Specifications %%%
-\title{Address Clustering Heuristics for Account-Based Blockchain Networks: An Analysis based on a Specific Address Set}
+\title{Address Clustering Heuristics for Account-Based Blockchain Networks: An Analysis based on a Decentraland User Set}
 \author{Dario Thürkauf}
@@
 %\large{Master Thesis}\\
-\Large Address Clustering Heuristics for Account-Based Blockchain Networks: An Analysis based on a Decentraland User Address Set \\
+\Large Address Clustering Heuristics for Account-Based Blockchain Networks: An Analysis based on a Decentraland User Set \\
 \large \vspace{1em}
@@
 PhD candidate, Center for Innovative Finance, University of Basel\\
-\vspace{1.5em}
-Supervised by \\
+\vspace{1em}
+Supervised by \\ \vspace{1em}
 \large Prof. Dr. Fabian Schär\\

### 2023-10-31 paper.tex
Minor change
Change text for single authorship

@@
 \Large Address Clustering Heuristics for Account-Based Blockchain Networks: An Analysis based on a Decentraland User Set \\
-\large \vspace{1em}
+\large \vspace{2em}
 Dario Thürkauf \\
@@
 PhD candidate, Center for Innovative Finance, University of Basel\\
-\vspace{1em}
-Supervised by \\ \vspace{1em}
-\large Prof. Dr. Fabian Schär\\
-\vspace{1em}
-\normalsize
-Professor for Distributed Ledger Technologies and Fintech \\
-Center for Innovative Finance, University of Basel
+\vspace{2em}
 \end{center}
@@
 This paper examines heuristics to cluster addresses using Ethereum and Polygon PoS data, analyzing over 470,000 addresses collected from Decentraland over the course of nine months.
-We assess various existing heuristics, adapt them to our specific research context, and also introduce a new heuristic.
-Our findings suggest that graph representation learning, particularly the application of an existing node embedding algorithm to an asset transfer network graph, is the most effective approach for clustering a predefined address set.
-However, the method does not come without its drawbacks, which is why we propose possible extensions for improving clustering performance.
+I assess various existing heuristics, adapt them to our specific research context, and also introduce a new heuristic.
+The findings suggest that graph representation learning, particularly the application of an existing node embedding algorithm to an asset transfer network graph, is the most effective approach for clustering a predefined address set.
+However, the method does not come without its drawbacks, which is why I propose possible extensions for improving clustering performance.
 \\ %intra-set
@@
 
-In this work, we perform entity identification on an address set containing 473,927 addresses.
+In this work, I perform entity identification on an address set containing 473,927 addresses.
 To obtain these addresses, a separate project collected snapshots of avatar activity in Decentraland over nine months from July 2022 to April 2023.
@@
 \newline
-We test the applicability of existing heuristics, and if feasible, their efficacy in detecting entities using multiple addresses is evaluated.
+I test the applicability of existing heuristics, and if feasible, their efficacy in detecting entities using multiple addresses is evaluated.
 The main objective is to estimate the number of real-world entities these addresses represent.
 The clustering of addresses is limited to this set only, without considering any addresses outside of it, e.g., that were not registered in Decentraland during the given time frame.
-Furthermore, we introduce our heuristic for identifying address clusters and evaluate its suitability for implementation in other contexts.
-As of our knowledge, we are the first to cluster addresses within a predefined set on a large scale.
-
-The remainder of this paper is structured as follows: In Section 2, we provide a brief overview of the basic concepts necessary to understand the setup, including Ethereum accounts, tokens, Decentraland, and privacy-enhancing protocols.
+Furthermore, I introduce my heuristic for identifying address clusters and evaluate its suitability for implementation in other contexts.
+As of my knowledge, this work is the first to cluster addresses within a predefined set on a large scale.
+
+The remainder of this paper is structured as follows: In Section 2, I provide a brief overview of the basic concepts necessary to understand the setup, including Ethereum accounts, tokens, Decentraland, and privacy-enhancing protocols.
 Section 3 describes our methodology for data collection and preparation.
 The fourth section provides a detailed explanation of various clustering heuristics.
-The fifth section applies the clustering heuristics described in section 4, after which we discuss the results of our analysis and summarize our findings in sections 6 and 7.
+The fifth section applies the clustering heuristics described in section 4, after which I discuss the results of our analysis and summarize our findings in sections 6 and 7.
 
@@
 The starting point for our work was a data set comprising 473,927 distinct Web3 addresses.
- As we focus on clustering methods using on-chain data, we exclude addresses that have not been recorded on either Ethereum or Polygon.
-To accomplish this, we used information from Blockscan\footnote{\url{https://blockscan.com/}}.
+Focusing on clustering methods using on-chain data, I exclude addresses that have not been recorded on either Ethereum or Polygon.
+To accomplish this, information from Blockscan\footnote{\url{https://blockscan.com/}} was used.
 Overall, 59,651 addresses were recorded on Ethereum, 129,988 on Polygon, with 52,095 addresses appearing on both networks simultaneously.
@@
 Fortunately, Etherscan offers an API Endpoint for ''Accounts'' that facilitates the retrieval of transactions and token transfer events for a given address.
-By using our network-specific address subsets, we were able to significantly decrease the number of required API calls.
-We gathered all transactions and token transfers up until block number \texttt{17,670,000} on Ethereum (July 11, 2023) and \texttt{44,990,000} on Polygon (July 12, 2023).
-In total, we collected over 30 million %30,689,978
+By using our network-specific address subsets, I was able to significantly decrease the number of required API calls.
+I gathered all transactions and token transfers up until block number \texttt{17,670,000} on Ethereum (July 11, 2023) and \texttt{44,990,000} on Polygon (July 12, 2023).
+In total, I collected over 30 million %30,689,978
 token transfer events and more than 16 million %16,092,531
@@
 \label{sec:intra-set}
-We want to employ address clustering heuristics to determine the number of entities represented by the remaining 137,544 addresses.
-Or, to phrase it differently, do users interact with Decentraland using multiple EOAs, and can we identify addresses that belong to the same user?
-\newline
-To achieve this, we often only consider transactions or token transfer events where both the ''\texttt{from}'' (sender) and the ''\texttt{to}'' (recipient) address are within the address set.
-We call this reduced data set \textit{intra-set asset transfers}.
-Regarding normal transactions, this means that we only keep native asset transfers (also called payments), as almost all addresses are EOAs.
+I want to employ address clustering heuristics to determine the number of entities represented by the remaining 137,544 addresses.
+%Or, to phrase it differently, do users interact with Decentraland using multiple EOAs, and can identify addresses that belong to the same user?
+\newline
+To achieve this, I often only consider transactions or token transfer events where both the ''\texttt{from}'' (sender) and the ''\texttt{to}'' (recipient) address are within the address set.
+I call this reduced data set \textit{intra-set asset transfers}.
+Regarding normal transactions, this means that only native asset transfers (also called payments) are kept, as almost all addresses are EOAs.
 \newline
 The intra-set asset transfer data set is mainly used to generate the network graphs (see Section \ref{sec:node}).
-When clustering addresses using graph-based approaches, this has the advantage that we do not need to differentiate between EOA and smart contract account later on.
+When clustering addresses using graph-based approaches, this has the advantage that I do not need to differentiate between EOA and smart contract account later on.
 Furthermore, it allows us to observe and visualize the asset flows between users.
-In total, we have 974,478 intra-set token transfers and 210,548 intra-set native asset transfers.
+In total, there are 974,478 intra-set token transfers and 210,548 intra-set native asset transfers.
 %101,621 Matic, 108,927 Ether
@@
 \label{sec:ens}
-Similarly to \cite{Beres2020}, we use Ethereum Name Service (ENS) identifiers as ground truth information to evaluate clustering methods.\newline
+Similarly to \cite{Beres2020}, I use Ethereum Name Service (ENS) identifiers as ground truth information to evaluate clustering methods.\newline
 \textit{ENS} is a naming system that relies on the Ethereum smart contracts.
@@
 As a domain can only point to one address at the time, the previous mapping from \texttt{`foo.eth`} to the old address is deleted.
-However, \texttt{`ABC....addr.reverse`} still points to \texttt{`foo.eth`} and when we query the name corresponding to \texttt{`0xABC...`} and \texttt{`0xDEF...`}, both will return \texttt{`foo.eth`}.
-If this special case occurs, we assume that both addresses belong to the same entity.
+However, \texttt{`ABC....addr.reverse`} still points to \texttt{`foo.eth`} and querying the name corresponding to \texttt{`0xABC...`} and \texttt{`0xDEF...`}, will return \texttt{`foo.eth`}.
+If this special case occurs, I assume that both addresses belong to the same entity.
 
@@
 
-We applied the following methodology to find ground truth pairs: \textit{First}, we gathered all addresses that interacted with ENS to reduce the amount of name look-ups.
-\textit{Second}, we iterated over all addresses and checked if they reverse-resolved to an ENS domain\footnote{This was done via the ENS module within web3.py \url{https://web3py.readthedocs.io/en/stable/ens_overview.html}, which provides an interface to look up domains and addresses.}.
-If so, we logged the ENS domain and address in a CSV file.
-\textit{Third}, using our new list, we identified if two addresses referenced the same ENS domain.
-If matched, we recorded both addresses alongside the ENS domain.
-\newline
-From this, we identified 11,440 reverse records and 40 pairs of addresses pointing to the same ENS name, which we utilized as our ground truth to evaluate various clustering heuristics.
+I applied the following methodology to find ground truth pairs: \textit{First}, I gathered all addresses that interacted with ENS to reduce the amount of name look-ups.
+\textit{Second}, I iterated over all addresses and checked if they reverse-resolved to an ENS domain\footnote{This was done via the ENS module within web3.py \url{https://web3py.readthedocs.io/en/stable/ens_overview.html}, which provides an interface to look up domains and addresses.}.
+If so, I logged the ENS domain and address in a CSV file.
+\textit{Third}, using our new list, I identified if two addresses referenced the same ENS domain.
+If matched, I recorded both addresses alongside the ENS domain.
+\newline
+From this, I identified 11,440 reverse records and 40 pairs of addresses pointing to the same ENS name, which I utilized as our ground truth to evaluate various clustering heuristics.
 Although this sample is relatively small, it allows us to assess and draw conclusions about the effectiveness of the methods.
@@
 \section{Clustering Heuristics}
-In this section, we present an overview of clustering heuristics in the context of account-based blockchains and on-chain data.
-We will provide a detailed explanation of the mechanics and rationale behind the heuristic and assess its applicability to our case.
-In Section 5, we will implement and evaluate the heuristics we determine to be suitable for our objectives.
+In this section, I present an overview of clustering heuristics in the context of account-based blockchains and on-chain data.
+I will provide a detailed explanation of the mechanics and rationale behind the heuristic and assess its applicability to our case.
+In Section 5, I will implement and evaluate the heuristics I determine to be suitable for our objectives.
 
@@
 The \textit{self authorization} heuristic, proposed by \cite{FV:17}, suggests that users might authorize another address they own, possibly for risk distribution across several addresses or for testing purposes.
-Since all the addresses' transactions are available in our data set, we can easily employ this heuristic.
+Since all the addresses' transactions are available in our data set, I can easily employ this heuristic.
 
@@
 He defined multi-participation when two airdrop recipients forward their tokens to a single address.
-Since we do not have a whole view of the airdrop distribution events, we are not able to identify them within our data.
+Since the whole view of the airdrop distribution events is not available, I am not able to identify them within our data.
 One possible approach would include manual selection of known airdrops.
 However, this process takes a long time and is not guaranteed to cluster many addresses, since more recent airdrop events were mostly carried out with some kind of Sybil-resistance.
-Nevertheless, to test this approach we searched for addresses that forwarded the UNI airdrop to another address.
-We found eight such transfers, but none involved two addresses sending funds to a third address.
+Nevertheless, to test this approach I searched for addresses that forwarded the UNI airdrop to another address.
+I found eight such transfers, but none involved two addresses sending funds to a third address.
 
@@
 \newline
-To construct the network graph, we use the intra-set asset transfers described in section \ref{sec:intra-set}.
+To construct the network graph, I use the intra-set asset transfers described in section \ref{sec:intra-set}.
 Our approach differs from the methodologies adopted by \cite{Beres2020} and \cite{wu2022tutela}.
@@
 On the other hand, \cite{wu2022tutela} do not operate on a specific address set but use all Ethereum transactions to build the network graph, ignoring token transfer events.
-After comparing these two methodologies with ours, we determined that intra-set asset transfers were the most effective for clustering a predefined set of addresses.
+After comparing these two methodologies with ours, I determined that intra-set asset transfers were the most effective for clustering a predefined set of addresses.
 %using node-embedding methods.
@@
 \newline
-We focus on the three methods that performed best in \cite{Beres2020} experiments: \textit{Diff2Vec} \citep{rozemberczki2020difftovec}, \textit{Role2Vec} \citep{ahmed2018roletovec}, and \textit{DeepWalk} \citep{perozzi2014}.
+I focus on the three methods that performed best in \cite{Beres2020} experiments: \textit{Diff2Vec} \citep{rozemberczki2020difftovec}, \textit{Role2Vec} \citep{ahmed2018roletovec}, and \textit{DeepWalk} \citep{perozzi2014}.
 Diff2Vec and DeepWalk are neighborhood-preserving methods, while Role2Vec is a structural node embedding method.
@@
 \newline
-With our intra-set asset transfer data (\ref{sec:intra-set}) and ENS address pairs (\ref{sec:ens}), we were able to apply and evaluate the node embedding methods described above.
+With our intra-set asset transfer data (\ref{sec:intra-set}) and ENS address pairs (\ref{sec:ens}), I was able to apply and evaluate the node embedding methods described above.
 To use the library described by \cite{karateclub}, certain preprocessing steps for the network graph are required.
@@
 \newline
-It is worth noting that unlike \cite{wu2022tutela}, we decided not to include edge weights.
+It is worth noting that unlike \cite{wu2022tutela}, I decided not to include edge weights.
 For instance, if Alice sent Bob Ether three times and Bob sent Alice Ether two times, the edge weight would correspond to five.
 This choice facilitated the application of \cite{rozemberczki2020difftovec}'s library and eliminated the need to develop a custom method.
-Based on our network graph, we generate 128-dimensional feature vectors for each address and method.
-\newline
-Given a node embedding, we can search for the closest $k$ vectors to any given vector.
-As in \cite{wu2022tutela}, we accomplish this using FAISS (Facebook AI Similarity Search), developed by \cite{johnson2019faiss}, which always returns a list of $k$ nodes, ranked by their Euclidean distance to the given node\footnote{We set $k = 51566$, the total number of nodes in the network graph}.
-\newline
-For evaluation of the three node embedding algorithms, we use our ENS address pairs as ground truth.
-We run each node embedding method ten times and report the average rank of the target address.
-For comparison, we compute the mean, median, and standard deviation of the average rank for each method.
+Based on our network graph, I generate 128-dimensional feature vectors for each address and method.
+\newline
+Given a node embedding, I can search for the closest $k$ vectors to any given vector.
+As in \cite{wu2022tutela}, I accomplish this using FAISS (Facebook AI Similarity Search), developed by \cite{johnson2019faiss}, which always returns a list of $k$ nodes, ranked by their Euclidean distance to the given node\footnote{I set $k = 51566$, the total number of nodes in the network graph}.
+\newline
+For evaluation of the three node embedding algorithms, I use our ENS address pairs as ground truth.
+I run each node embedding method ten times and report the average rank of the target address.
+For comparison, I compute the mean, median, and standard deviation of the average rank for each method.
 
@@
 Both methods will not be employed due to their significantly poorer stand-alone performance compared to node embeddings.
-Nevertheless, we test a two-step approach: In the first step, we implement Diff2Vec to find the ten nearest neighbors.
-In the second step, we order the remaining addresses by their Euclidean distance derived from the time-of-day and/or gas price feature vectors.
-We analyze the impact of this two-step approach on the average rank of a target address.
+Nevertheless, I test a two-step approach: In the first step, I implement Diff2Vec to find the ten nearest neighbors.
+In the second step, I order the remaining addresses by their Euclidean distance derived from the time-of-day and/or gas price feature vectors.
+I analyze the impact of this two-step approach on the average rank of a target address.
 
@@
 \textit{Torn minting} identifies a specific user behavior when withdrawing so-called Anonymity points, an incentive scheme reward for increasing the anonymity set when depositing assets into Tornado cash.\newline
-We identified 84 transactions tied to Tornado cash pools, including 72 deposits, ten withdrawals, and two transactions where an address sent 0.1 Ether to the corresponding pool without invoking the deposit function.
-Despite applying all clustering heuristics except Torn minting, we found no clusters.
+I identified 84 transactions tied to Tornado cash pools, including 72 deposits, ten withdrawals, and two transactions where an address sent 0.1 Ether to the corresponding pool without invoking the deposit function.
+Despite applying all clustering heuristics except Torn minting, no clusters were found.
 
 \subsection{LAND Transfers}
-In addition to the existing clustering heuristics, we propose our heuristic based on transfers of high-value NFTs such as LAND.
-We argue that, given the high value of Decentraland's land parcels, there is a strong likelihood that addresses are controlled by the same entity when LAND is transferred without any compensation.
+In addition to the existing clustering heuristics, I propose our heuristic based on transfers of high-value NFTs such as LAND.
+I argue that, given the high value of Decentraland's land parcels, there is a strong likelihood that addresses are controlled by the same entity when LAND is transferred without any compensation.
 Users might perform such transfers to rearrange their LAND holdings, e.g., by upgrading to a more secure wallet.
@@
 The primary challenge of this approach is to detect LAND transfers without any compensation.
-To accomplish this, we identify token or native asset transfers within the same transaction as a LAND transfer.
-Upon manually examining various implementations of LAND trades on the most popular NFT marketplace contracts, we noticed a recurring pattern: the user address appears in both the \texttt{''from''} and \texttt{''to''} fields if a trade occurs.
+To accomplish this, I identify token or native asset transfers within the same transaction as a LAND transfer.
+Upon manually examining various implementations of LAND trades on the most popular NFT marketplace contracts, I noticed a recurring pattern: the user address appears in both the \texttt{''from''} and \texttt{''to''} fields if a trade occurs.
 Figure \ref{fig:LAND_example} illustrates an example of this pattern.
@@
 \subsection{Self-Authorization}
-We analyze the addresses' transaction data to find self-authorizations, focusing on the transaction's ''calldata''.
+I analyze the addresses' transaction data to find self-authorizations, focusing on the transaction's ''calldata''.
 The first four bytes of the calldata represent the function selector, which unambiguously specifies the smart contract function the transaction originator wants to invoke.
 \newline
-\textit{First}, we identify all transactions that begin with a function signature related to the approval functions corresponding to ERC-20, ERC-721, and ERC-1155 token standards.
-\textit{Second}, we extract the approved (spender) address, which is always located at the same position within the calldata due to token standardization.
-We then record the spender address in a new field within our data frame.
-\textit{Third}, we implement two filters on the approval transactions.
+\textit{First}, I identify all transactions that begin with a function signature related to the approval functions corresponding to ERC-20, ERC-721, and ERC-1155 token standards.
+\textit{Second}, I extract the approved (spender) address, which is always located at the same position within the calldata due to token standardization.
+I then record the spender address in a new field within our data frame.
+\textit{Third}, I implement two filters on the approval transactions.
 The first filter checks if the spender address is part of our address set, and the second ensures that the spender address is different from the address initiating the transaction, which may occur due to a user interface bug or testing transactions.
-\textit{Fourth}, we group the remaining approvals by the initiating address and form the clusters.
-
-We identified 16 clusters across 126 self-authorizing transactions, comprising 115 distinct addresses.
-After manual inspection, we excluded a cluster containing 80 addresses with all approvals issued by the same address for the same token contract.
+\textit{Fourth}, I group the remaining approvals by the initiating address and form the clusters.
+
+I identified 16 clusters across 126 self-authorizing transactions, comprising 115 distinct addresses.
+After manual inspection, I excluded a cluster containing 80 addresses with all approvals issued by the same address for the same token contract.
 The token contract represents a collection of wearable NFTs on Polygon called ''Renaissance King by René Mäkelä'' and may use an uncommon or potentially even faulty token minting scheme.
-Ultimately, we discovered 35 addresses associated with 15 distinct entities.
+Ultimately, I discovered 35 addresses associated with 15 distinct entities.
 
@@
 Our analysis of node embedding methods starts with a network graph built from intra-set asset transfers.
-We treat addresses as nodes and add undirected edges between them if they interacted with each other.
-\newline
-To use the Python library developed by \cite{karateclub}, we remove multi-edges and loops (i.e., transfers with the same sender and recipient address) and only consider nodes within the largest connected component.
+I treat addresses as nodes and add undirected edges between them if they interacted with each other.
+\newline
+To use the Python library developed by \cite{karateclub}, I remove multi-edges and loops (i.e., transfers with the same sender and recipient address) and only consider nodes within the largest connected component.
 The resulting network graph includes 51,566 nodes and 249,302 edges.
-As previously stated, we utilize the Diff2Vec, Role2Vec, and DeepWalk methods from the library.
-\newline
-Subsequently, we ran ten independent experiments for each method.
+As previously stated, I utilize the Diff2Vec, Role2Vec, and DeepWalk methods from the library.
+\newline
+Subsequently, I ran ten independent experiments for each method.
 Our choice of input parameters is identical to \cite{Beres2020}.
@@
 \newline
-For any node within the embedding, we can easily order all other nodes by the Euclidean distance.
-We achieve this through the FAISS Python library, which is suitable for efficient similarity search and clustering of dense vectors \citep{johnson2019faiss}.\newline
+For any node within the embedding, I can easily order all other nodes by the Euclidean distance.
+I achieve this through the FAISS Python library, which is suitable for efficient similarity search and clustering of dense vectors \citep{johnson2019faiss}.\newline
 This feature enables us to search for our ENS ground truth pairs and report their relative rank.
 The results for each address pair, averaged over ten experiments, are presented in Table \ref{tbl:ENS_Domain_Ranks}.
-Additionally, we calculated the mean, median, standard deviation, and the rate of the target address appearing within the five or ten nearest neighbors for each method.
+Additionally, I calculated the mean, median, standard deviation, and the rate of the target address appearing within the five or ten nearest neighbors for each method.
 
@@
 \newline
-A total of 2159 intra-set LAND transfers were recorded, of those, 740 (X \%) were without compensation.
+A total of 2159 intra-set LAND transfers were recorded, of those, 677 (X \%) were without compensation.
 We were able to group the 413 unique addresses from these uncompensated transfers into 161 distinct clusters.
@@
 
-\subsection{Github Repositories}
+\subsection{Github Repository}
 

### 2023-11-07 paper.tex
Rewrite Abstract and Introduction

@@
 This paper examines heuristics to cluster addresses using Ethereum and Polygon PoS data, analyzing over 470,000 addresses collected from Decentraland over the course of nine months.
-I assess various existing heuristics, adapt them to our specific research context, and also introduce a new heuristic.
+Various existing heuristics are assessed, adapted to the the specific research context, and a new heuristic is introduced.
 The findings suggest that graph representation learning, particularly the application of an existing node embedding algorithm to an asset transfer network graph, is the most effective approach for clustering a predefined address set.
-However, the method does not come without its drawbacks, which is why I propose possible extensions for improving clustering performance.
+However, the method does not come without its drawbacks, which is why possible extensions for improving clustering performance are proposed.
 \\ %intra-set

### 2023-11-07 paper.tex
Update Section 2 and 3

@@
 Both find that many networks follow either a star or a hub-and-spoke pattern, similar to social network interaction graphs.
-Moreover, using k-means clustering, \cite{Payette2017} propose a segmentation of the Ethereum address space into four distinct behavior groups sharing similar attributes.
-\newline
+Moreover, \cite{Payette2017} propose a partition of the Ethereum address space into four distinct behavior groups sharing similar attributes while applying k-means clustering.\newline
 Rather than treating users as entities and analyzing on-chain data, \cite{yu2023} propose a novel approach for correlation analysis by exploiting network information.
@@
 The clustering of addresses is limited to this set only, without considering any addresses outside of it, e.g., that were not registered in Decentraland during the given time frame.
-Furthermore, I introduce my heuristic for identifying address clusters and evaluate its suitability for implementation in other contexts.
+Furthermore, I introduce a new heuristic for identifying address clusters and evaluate its suitability for implementation in other contexts.
 As of my knowledge, this work is the first to cluster addresses within a predefined set on a large scale.
 
-The remainder of this paper is structured as follows: In Section 2, I provide a brief overview of the basic concepts necessary to understand the setup, including Ethereum accounts, tokens, Decentraland, and privacy-enhancing protocols.
+The remainder of this paper is structured as follows: Section 2 presents a brief overview of the basic concepts necessary to understand the setup, including Ethereum accounts, tokens, Decentraland, and privacy-enhancing protocols.
 Section 3 describes our methodology for data collection and preparation.
@@
 \section{Data Collection and Preparation} 
-The starting point for our work was a data set comprising 473,927 distinct Web3 addresses.
+The starting point for this work was a data set comprising 473,927 distinct Web3 addresses.
 Focusing on clustering methods using on-chain data, I exclude addresses that have not been recorded on either Ethereum or Polygon.
-To accomplish this, information from Blockscan\footnote{\url{https://blockscan.com/}} was used.
+To accomplish this, I used data from Blockscan\footnote{\url{https://blockscan.com/}}.
 Overall, 59,651 addresses were recorded on Ethereum, 129,988 on Polygon, with 52,095 addresses appearing on both networks simultaneously.
@@
 Fortunately, Etherscan offers an API Endpoint for ''Accounts'' that facilitates the retrieval of transactions and token transfer events for a given address.
-By using our network-specific address subsets, I was able to significantly decrease the number of required API calls.
+By using the network-specific address subsets, I was able to significantly decrease the number of required API calls.
 I gathered all transactions and token transfers up until block number \texttt{17,670,000} on Ethereum (July 11, 2023) and \texttt{44,990,000} on Polygon (July 12, 2023).
-In total, I collected over 30 million %30,689,978
-token transfer events and more than 16 million %16,092,531
+In total, I found over 30 million token transfer events and more than 16 million
  normal transactions.
@@
 For additional information on the data fields of each collection, see Appendix \ref{sec:database}.
+%30,689,978 %16,092,531
 
@@
 %Or, to phrase it differently, do users interact with Decentraland using multiple EOAs, and can identify addresses that belong to the same user?
-\newline
-To achieve this, I often only consider transactions or token transfer events where both the ''\texttt{from}'' (sender) and the ''\texttt{to}'' (recipient) address are within the address set.
+To achieve this, I often reduce the data set to only consider transactions or token transfer events where both the ''\texttt{from}'' (sender) and the ''\texttt{to}'' (recipient) address are within the address set.
 I call this reduced data set \textit{intra-set asset transfers}.
-Regarding normal transactions, this means that only native asset transfers (also called payments) are kept, as almost all addresses are EOAs.
+Regarding normal transactions, this means that only native asset transfers (also referred to as payments) are kept, as almost all addresses are EOAs.
 \newline
 The intra-set asset transfer data set is mainly used to generate the network graphs (see Section \ref{sec:node}). 
-When clustering addresses using graph-based approaches, this has the advantage that I do not need to differentiate between EOA and smart contract account later on.
+When clustering addresses through graph-based approaches, this has the advantage that contract accounts without a logical owner do not need to be excluded later on.
 Furthermore, it allows us to observe and visualize the asset flows between users.
@@
 
-Figure \ref{fig:ENS} illustrates the mechanism that allowed us to generate ground truth pairs in a simplified way: Initially, the domain name \texttt{`foo.eth`} resolves to address \texttt{`0xABC...`}.
+Figure \ref{fig:ENS} illustrates the mechanism that allowed to generate ground truth pairs in a simplified way: Initially, the domain name \texttt{`foo.eth`} resolves to address \texttt{`0xABC...`}.
 The owner has also set a reverse resolution for this address, indicated by the the edge from the address to the domain name.
@@
 
-I applied the following methodology to find ground truth pairs: \textit{First}, I gathered all addresses that interacted with ENS to reduce the amount of name look-ups.
+I applied the following methodology to discover ground truth pairs: \textit{First}, I gathered all addresses that interacted with ENS to reduce the amount of name look-ups.
 \textit{Second}, I iterated over all addresses and checked if they reverse-resolved to an ENS domain\footnote{This was done via the ENS module within web3.py \url{https://web3py.readthedocs.io/en/stable/ens_overview.html}, which provides an interface to look up domains and addresses.}.
-If so, I logged the ENS domain and address in a CSV file.
-\textit{Third}, using our new list, I identified if two addresses referenced the same ENS domain.
+If this was the case, the ENS domain and address were stored in a CSV file.
+\textit{Third}, I identified if two addresses referenced the same ENS domain.
 If matched, I recorded both addresses alongside the ENS domain.
 \newline
-From this, I identified 11,440 reverse records and 40 pairs of addresses pointing to the same ENS name, which I utilized as our ground truth to evaluate various clustering heuristics.
-Although this sample is relatively small, it allows us to assess and draw conclusions about the effectiveness of the methods.
+11,440 reverse records and 40 pairs of addresses pointing to the same name were identified and utilized as ground truth to evaluate various clustering heuristics.
+Although this sample is relatively small, it allows me to compare and draw conclusions about the effectiveness of the methods.
 

### 2023-11-07 paper.tex
Update section 4 clustering heursitics

@@
 In this section, I present an overview of clustering heuristics in the context of account-based blockchains and on-chain data.
-I will provide a detailed explanation of the mechanics and rationale behind the heuristic and assess its applicability to our case.
-In Section 5, I will implement and evaluate the heuristics I determine to be suitable for our objectives.
+I will provide a detailed explanation of the mechanics and rationale behind the heuristic and assess its applicability.
+In Section 5, I will implement and evaluate the heuristics I determine to be suitable for this work.
 
@@
 The \textit{self authorization} heuristic, proposed by \cite{FV:17}, suggests that users might authorize another address they own, possibly for risk distribution across several addresses or for testing purposes.
-Since all the addresses' transactions are available in our data set, I can easily employ this heuristic.
+Since all the addresses' transactions are available in our data set, this heuristic can be easily employed.
 
@@
 This heuristic relies on the prevalent practice of crypto exchanges generating unique deposit addresses for each user.
-These addresses then forward the funds to an exchange's main address.
+The deposit addresses then forward the funds to an exchange's main address.
 It is highly likely that multiple addresses sending funds to the same deposit address are controlled by the same entity.
@@
 One possible approach would include manual selection of known airdrops.
-However, this process takes a long time and is not guaranteed to cluster many addresses, since more recent airdrop events were mostly carried out with some kind of Sybil-resistance.
+However, this process is cumbersome and not guaranteed to cluster many addresses, since more recent airdrop events were mostly carried out with some kind of Sybil-resistance.
 Nevertheless, to test this approach I searched for addresses that forwarded the UNI airdrop to another address.
-I found eight such transfers, but none involved two addresses sending funds to a third address.
+Eight such transfers were found, but none involved two addresses sending funds to a third address.
 
@@
 To construct the network graph, I use the intra-set asset transfers described in section \ref{sec:intra-set}.
-Our approach differs from the methodologies adopted by \cite{Beres2020} and \cite{wu2022tutela}.
+My approach differs from the methodologies adopted by \cite{Beres2020} and \cite{wu2022tutela}.
 On the one hand, \cite{Beres2020} collected all transactions and token transfer events of their address set but did not refine this data to only include intra-set asset transfers.
 On the other hand, \cite{wu2022tutela} do not operate on a specific address set but use all Ethereum transactions to build the network graph, ignoring token transfer events.
-After comparing these two methodologies with ours, I determined that intra-set asset transfers were the most effective for clustering a predefined set of addresses.
-%using node-embedding methods.
+Comparing these two methodologies with mine, I found the intra-set asset transfers to be the most effective for clustering the address set examined in this work.
+%through node-embedding algorithms in my case
+%a predefined set of addresses through node-embedding algorithms.
 \newline
@@
 I focus on the three methods that performed best in \cite{Beres2020} experiments: \textit{Diff2Vec} \citep{rozemberczki2020difftovec}, \textit{Role2Vec} \citep{ahmed2018roletovec}, and \textit{DeepWalk} \citep{perozzi2014}.
-Diff2Vec and DeepWalk are neighborhood-preserving methods, while Role2Vec is a structural node embedding method.
+Diff2Vec and DeepWalk are neighborhood-preserving methods, while Role2Vec is a structural node embedding algorithm.
 Although all methods utilize random walks to capture graph information, their approaches to leveraging these random walks for constructing Euclidean feature vectors differ.
@@
 This choice facilitated the application of \cite{rozemberczki2020difftovec}'s library and eliminated the need to develop a custom method.
-Based on our network graph, I generate 128-dimensional feature vectors for each address and method.
+Based on the network graph, I generate 128-dimensional feature vectors for each address and method.
 \newline
@@
 \newline
-For evaluation of the three node embedding algorithms, I use our ENS address pairs as ground truth.
+For evaluation of the three node embedding algorithms, I use the ENS address pairs as ground truth.
 I run each node embedding method ten times and report the average rank of the target address.
@@
 \subsection{LAND Transfers}
-In addition to the existing clustering heuristics, I propose our heuristic based on transfers of high-value NFTs such as LAND.
+In addition to the existing clustering heuristics, I propose a heuristic based on transfers of high-value NFTs such as LAND.
 I argue that, given the high value of Decentraland's land parcels, there is a strong likelihood that addresses are controlled by the same entity when LAND is transferred without any compensation.
@@
 The primary challenge of this approach is to detect LAND transfers without any compensation.
-To accomplish this, I identify token or native asset transfers within the same transaction as a LAND transfer.
+To accomplish this, token or native asset transfers within the same transaction as a LAND transfer are identified.
 Upon manually examining various implementations of LAND trades on the most popular NFT marketplace contracts, I noticed a recurring pattern: the user address appears in both the \texttt{''from''} and \texttt{''to''} fields if a trade occurs.

### 2023-11-07 paper.tex
Update section 5-7

@@
 \section{Data Analysis}
-This section analyzes clustering heuristics applicable to our address set using the collected data.
-These include self-authorization, node embedding, and our proposed approach involving LAND transfers.
+This section analyzes clustering heuristics applicable to the address set using the collected data.
+These include self-authorization, node embedding, and the proposed approach involving LAND transfers.
 
@@
 \textit{Second}, I extract the approved (spender) address, which is always located at the same position within the calldata due to token standardization.
-I then record the spender address in a new field within our data frame.
+The spender address is recorded in a new field within the data frame.
 \textit{Third}, I implement two filters on the approval transactions.
-The first filter checks if the spender address is part of our address set, and the second ensures that the spender address is different from the address initiating the transaction, which may occur due to a user interface bug or testing transactions.
+The first filter checks if the spender address is part of the address set, and the second ensures that the spender address is different from the address initiating the transaction, which may occur due to a user interface bug or testing transactions.
 \textit{Fourth}, I group the remaining approvals by the initiating address and form the clusters.
@@
 \subsection{Node Embeddings}
-Our analysis of node embedding methods starts with a network graph built from intra-set asset transfers.
-I treat addresses as nodes and add undirected edges between them if they interacted with each other.
+The analysis of node embedding methods starts with a network graph built from intra-set asset transfers.
+Addresses are treated as nodes and undirected edges are added if they interacted with each other.
 \newline
@@
 Subsequently, I ran ten independent experiments for each method.
-Our choice of input parameters is identical to \cite{Beres2020}.
+The choice of input parameters is identical to \cite{Beres2020}.
 Each experiment returns a node embedding in a matrix with 51,566 rows corresponding to the number of nodes in the graph and 128 columns representing the feature vector dimensions.
@@
 I achieve this through the FAISS Python library, which is suitable for efficient similarity search and clustering of dense vectors \citep{johnson2019faiss}.\newline
-This feature enables us to search for our ENS ground truth pairs and report their relative rank.
+This enables searching for the ENS ground truth pairs and reporting their relative rank.
 The results for each address pair, averaged over ten experiments, are presented in Table \ref{tbl:ENS_Domain_Ranks}.
@@
 \newline
-Notably, two address pairs are absent within the network graph and, therefore, display no values.
-However, they have been included to demonstrate that the intra-set asset transfer approach may not always be applicable to cluster all addresses of a predefined set.
 
@@
   \end{tabular}
-  \caption{Average Rank of Target Address}
+  \caption{Average Rank of Target Address. Two address pairs are not part of the largest connected component within the network graph and therefore display no values.}
   \label{tbl:ENS_Domain_Ranks}
@@
 
-After evaluating the different node embedding methods, we want to cluster the addresses to assess the number of entities represented by the 51,566 nodes in the network.
-We use the node embedding generated by Role2Vec.
+After evaluating the different node embedding methods, I cluster the addresses to assess the number of entities represented by the 51,566 nodes in the network.
+The node embeddings generated by Role2Vec are used.
 \newline
@@
 \newline
-Instead, we choose to build clusters based on Euclidean distance, where all neighbors of a node below a certain threshold are clustered.
-Afterward, we merge overlapping clusters; for instance, if node A is clustered with nodes B and C, and node C is clustered with nodes A and X, we form a cluster comprising A, B, C, and X.
-\newline
-We explore the sensitivity of clusters to various Euclidean distance threshold values.
+Instead, I choose to build clusters based on Euclidean distance, where all neighbors of a node below a certain threshold are clustered.
+Afterward, the overlapping clusters are merged; for instance, if node A is clustered with nodes B and C, and node C is clustered with nodes A and X, a cluster comprising A, B, C, and X is formed.
+\newline
+I explore the sensitivity of clusters to various Euclidean distance threshold values.
 Figure \ref{fig:threshold_sensitivity} shows the histogram of cluster sizes, and Table \ref{tbl:cluster_table} displays the number of resulting clusters depending on various threshold values.
-We chose said values after observing the distance between ground truth pairs.
-For better visibility, we only display clusters below 20 addresses in Figure \ref{fig:threshold_sensitivity}.
-At thresholds of 0.6, 0.7, and 0.8, we find 23,608, 18,592, and 14,793 clusters, respectively.
+I chose said values after observing the distance between ground truth pairs.
+For better visibility, only clusters below 20 addresses are displayed in Figure \ref{fig:threshold_sensitivity}.
+At thresholds of 0.6, 0.7, and 0.8, I find 23,608, 18,592, and 14,793 clusters, respectively.
 Regardless of the threshold, the largest cluster has more than 500 addresses.
-Unsurprisingly, higher thresholds result in fewer single-address clusters and more large-sized clusters.
+By design, higher thresholds result in fewer single-address clusters and more large-sized clusters.
 The effect of the threshold is most pronounced for single address clusters while affecting other cluster sizes much less.
@@
 \subsection{LAND Transfers}
-To implement the LAND transfer clustering heuristic, we select all transaction hashes of LAND transfers that occurred between two Decentraland addresses.
-Next, we gather all token and native asset transfers associated with the selected transaction hashes.
-We group the data by transaction hash and examine each transfer's sender (\texttt{from}) and recipient (\texttt{to}) address.
-If the same address appears as the sender and recipient, we mark the transaction as a purchase.
-Finally, we exclude purchases and build clusters for addresses that sent each other LAND without compensation.
+To implement the LAND transfer clustering heuristic, I select all transaction hashes of LAND transfers that occurred between two Decentraland addresses.
+Next, I gather all token and native asset transfers associated with the selected transaction hashes.
+The data is grouped by transaction hash and each transfer's sender (\texttt{from}) and recipient (\texttt{to}) address is examined.
+If the same address appears as the sender and recipient, I mark the transaction as a purchase.
+Finally, purchases are excluded and clusters for addresses that sent each other LAND without compensation are built.
 \newline
@@
 \subsection{Combining Clustering Results}
-To conclude our clustering analysis, we combine the results of self-authorization, learned node embedding, and LAND transfer heuristics.
-By doing so, we can cluster 51,581 out of 137,544 (37.5\%) addresses representing 29,680 entities.
-For the remaining addresses, we consider each as an individual entity. 
-We applied a strict distance threshold of 0.5 for clustering embeddings generated by Role2Vec and excluded the 80-address cluster identified in self-authorization.
-Under these assumptions, we estimate 115,643 active users during the time frame studied.
+To conclude the clustering analysis, the results of self-authorization, learned node embedding, and LAND transfer heuristics are combined.
+By doing so, I can cluster 51,581 out of 137,544 (37.5\%) addresses representing 29,680 entities.
+For the remaining addresses, I consider each as an individual entity. 
+I applied a strict distance threshold of 0.5 for clustering embeddings generated by Role2Vec and excluded the 80-address cluster identified in self-authorization.
+Under these assumptions, I estimate 115,643 active users during the time frame studied.
 Of these, 8,483 entities (7.3\%) interacted with Decentraland through multiple addresses.
 The largest entity comprises 499 addresses.
-We plot the distribution of cluster sizes in Figure \ref{fig:barplot_clusters}.
+The distribution of the cluster sizes for different thresholds is shown in Figure \ref{fig:barplot_clusters}.
 
@@
 \section{Discussion}
-Throughout our analysis, we successfully applied three heuristics to cluster our address set while making use of on-chain data.
-In the following discussion, we will examine each of the approaches step-by-step.
+Throughout the analysis, I successfully applied three heuristics to cluster our address set while making use of on-chain data.
+In the following discussion, I will examine each of the approaches step-by-step.
 
 Implementing the \textit{self-authorization} heuristic is straightforward but results in very few identified address clusters.
-This is because it requires a highly specific on-chain behavior, which is rarely observed in practice.
+This heuristic demands a highly specific on-chain behavior, which is rarely observed in practice.
 In particular, approvals are seldom used to authorize another externally owned account one might own.
-We also encountered a significant number of false positives due to non-standard implementations.
-We are very confident that the large cluster is not controlled by the same entity, and therefore remove it.
-After excluding these instances, we identified a total of 15 entities consisting of 35 addresses.
+I also encountered a significant number of false positives due to non-standard implementations.
+I am very confident that the large cluster is not controlled by the same entity, and therefore remove it.
+After excluding these instances, I identified a total of 15 entities consisting of 35 addresses.
 This outcome aligns with findings by \cite{FV:17}, who also observed that the heuristic captures only a small proportion of addresses.
@@
 
-Address clustering through \textit{graph representation learning} proved to be the most effective approach in our analysis.
+Address clustering through \textit{graph representation learning} proved to be the most effective approach in my analysis.
 Unlike methods that require participation in specific on-chain events, node embedding algorithms examine the entire asset transfer network between addresses, making it broadly applicable.
 \newline
-Our implementation of node embedding methods differs from previous approaches by \cite{Beres2020} and \cite{wu2022tutela}, the main reason being different settings and research questions.
-We construct the network graph based on asset transfers within our address set and simultaneously analyze Polygon and Ethereum data.
+The implementation of the node embedding methods differs from previous approaches by \cite{Beres2020} and \cite{wu2022tutela}, the main reason being different settings and research questions.
+I construct the network graph based on asset transfers within our address set and simultaneously analyze Polygon and Ethereum data.
 \newline
@@
 \newline
-Moreover, we validated our approach and found better results regarding the average rank of ground truth address pairs when building the network graph from intra-set asset transfers compared to using all token transfer events and/or transactions.
-A possible extension would include incorporating edge weights, similar to \cite{wu2022tutela}; however, we refrained from doing this because we would have needed to implement a custom node embedding algorithm.\newline
-We applied three node embedding algorithms that delivered robust results in the experiments by \cite{Beres2020} and assessed their effectiveness in detecting ground truth pairs.
-Our results indicate that Role2Vec is the best-performing method, locating the ground truth pair within the ten nearest neighbors in 70\% of cases.
+Moreover, I validated the approach and found better results regarding the average rank of ground truth address pairs when building the network graph from intra-set asset transfers compared to using all token transfer events and/or transactions.
+A possible extension would include incorporating edge weights, similar to \cite{wu2022tutela}; however, I refrained from doing this because the implementation a custom node embedding algorithm would have been necessary.\newline
+I applied three node embedding algorithms that delivered robust results in the experiments by \cite{Beres2020} and assessed their effectiveness in detecting ground truth pairs.
+The results indicate that Role2Vec is the best-performing method, locating the ground truth pair within the ten nearest neighbors in 70\% of cases.
 This result diverges from the findings of \cite{Beres2020}, who determined Diff2Vec to be the superior method among the three evaluated.
@@
 In contrast, Role2Vec, a structural node embedding method, identifies nodes with similar roles within the network.
-In our evaluation sample, network position or role may better represent node similarity and structural relatedness.
+In my evaluation sample, network position or role may better represent node similarity and structural relatedness.
 Despite these insights, the differences in results could be specific to the data at hand, given the small sample size, potential evaluation metric flaws, and the overall robust performance of all methods.
 \newline
-Additionally, our evaluation sample may be biased, as one could argue that users changing the address associated with their ENS domain name while also keeping the reverse records are not primarily concerned with preserving privacy.
-\newline
-We also need to consider that average rank may not be the most appropriate evaluation metric, particularly when a user controls more than two addresses.
+Additionally, the evaluation sample may be biased, as one could argue that users changing the address associated with their ENS domain name while also keeping the reverse records are not primarily concerned with preserving privacy.
+\newline
+It should also be noted that average rank may not be the most appropriate evaluation metric, particularly when a user controls more than two addresses.
 Suppose a single entity controlling 20 addresses, but only one pair of addresses is detected as ground truth.
@@
 \newline
-Creating clusters out of the node embeddings enables us to estimate the number of entities represented by the 51,566 addresses.
-Our method involves calculating the Euclidean distance between pairs of feature vectors, explicitly using the node embedding matrix generated by Role2Vec.
+Creating clusters out of the node embeddings enables an estimation of the number of entities represented by the 51,566 addresses.
+The method involves calculating the Euclidean distance between pairs of feature vectors, explicitly using the node embedding matrix generated by Role2Vec.
 Nodes are clustered if their distance falls below a predetermined threshold, and any overlapping clusters are subsequently merged.
 \newline
-While our clustering method may not be ideal, it is probably more effective than clustering a fixed number of $k$ neighbors for each node.
-We observed that the number of clusters and their size is highly sensitive to the chosen distance threshold, making it challenging to assess the accuracy of these clusters.
-We have provided a sensitivity analysis to illustrate this issue.
+While the clustering method may not be ideal, it is probably more effective than clustering a fixed number of $k$ neighbors for each node.
+I observed that the number of clusters and their size is highly sensitive to the chosen distance threshold, making it challenging to assess the accuracy of these clusters.
+I have provided a sensitivity analysis to illustrate this issue.
 The distances between the feature vectors tend to be narrow, with significant variation even among various ground truth pairs' distances.
-Regardless of the threshold value, we were able to locate a cluster of more than 500 addresses.
+Regardless of the threshold value, a cluster of more than 500 addresses persisted.
 Manual inspection revealed that these addresses show very similar on-chain patterns: They are all exclusively active on Polygon, and most transfers are mints of Decentraland-related NFTs.
-Further, they transfer some NFTs to address \texttt{''0xE2e2F2240a84A61B7dFF50a86ee10d5FaF7faCa8''}.
+Further, they transfer some NFTs to address \texttt{''0xE2e2F224\dots''}.
 The transfers to and from this address are shown in Figure \ref{fig:cluster}.
 Incoming transfers are indicated by green edges, while red edges show outgoing transfers.
-We hypothesize that the network in question may be operated by a user or even bot that creates multiple distinct addresses and actively engages with Decentraland.
-It seems likely that this bot may target specific locations or events where NFTs are (automatically) air-dropped to avatars in presence.
-If the NFTs hold value, the bot may then aggregate them to the main address and sell them on the Decentraland marketplace.
-This hypothesis could be verified with the Decentraland movement data.
+I hypothesize that the network in question may be operated by a user or even bot that creates multiple distinct addresses and actively engages with Decentraland.
+It seems likely that this user may target specific locations or events where NFTs can be collected or are (automatically) air-dropped to avatars in presence.
+If the NFTs hold value, the user may then aggregate them to the main address and sell them on the Decentraland marketplace.
+This hypothesis could be verified using Decentraland movement data.
 \newline
@@
 \newline
-Finally, we explored potential enhancements to the graph representation learning method, such as incorporating time-of-day-activity and/or gas price selection information into the feature vectors generated by Role2Vec.
+Finally, I explored potential enhancements to the graph representation learning method, such as incorporating time-of-day-activity and/or gas price selection information into the feature vectors generated by Role2Vec.
 Unfortunately, these modifications did not lead to any significant improvements.
@@
 	\includegraphics[width=0.8\textwidth]{./figures/network_visualization_0xe2e.png}
-	\caption{Token Transfer Graph for \texttt{0xE2e2F$\dots$faCa8}}
+	\caption{Token Transfer Graph for \texttt{0xE2e2F24$\dots$faCa8}}
 	\label{fig:cluster}
@@
 The \textit{LAND transfer} heuristic is targeted at users revealing address clusters by sending high-value assets to other addresses.
-In this specific case, we use the information that all addresses are related to Decentraland and analyze LAND transfers.
+In this specific case, I use the information that all addresses are related to Decentraland and analyze LAND transfers.
 However, the approach could be applied to other NFT collections or large asset transfers in general.
@@
 
-Ultimately, we combined the results for each clustering heuristic mentioned above.
-Consequently, we managed to cluster 51,518 addresses, corresponding to 29,680 distinct entities.
-When adding the unclustered addresses, we identified 115,643 active users during the nine months, with 8,483 entities interacting through multiple addresses.
-\newline
-These results, however, are heavily influenced by the assumptions we made.
-We were conservative by setting a low distance threshold and treating all other addresses as individual entities.
+Ultimately, I combined the results for each clustering heuristic mentioned above.
+Consequently, I managed to cluster 51,518 addresses, corresponding to 29,680 distinct entities.
+When adding the unclustered addresses, 115,643 active users were identified during the nine months, with 8,483 entities interacting through multiple addresses.
+\newline
+These results, however, are heavily influenced by the assumptions made.
+I was conservative by setting a low distance threshold and treating all other addresses as individual entities.
 Raising the threshold would result in larger clusters and fewer entities.
@@
 Unlike other clustering heuristics, this approach does not rely on specific on-chain behavior patterns or participation in particular events.
-Our implementation generally captures all addresses that transferred assets within the address set at least once.
+My implementation generally captures all addresses that transferred assets within the address set at least once.
 Nevertheless, some clusters may still go undetected, while others may be overestimated.
@@
 This work aimed to determine how many unique entities correspond to the 473,927 addresses observed in Decentraland from July 16, 2022, to April 23, 2023. \newline
-By focusing on Ethereum and Polygon on-chain data, we narrowed the set down to 137,544 addresses.
+By focusing on Ethereum and Polygon on-chain data, I narrowed the set down to 137,544 addresses.
 The required data was efficiently sourced by gathering all transactions and token transfers related to the addresses via Etherscan and Polygonscan.
-Furthermore, with the help of ENS, we found a way to detect address pairs with a very high probability of being controlled by the same user.
+Furthermore, with the help of ENS, I found a way to detect address pairs with a very high probability of being controlled by the same user.
 These address pairs served as our ground truth when evaluating the node embedding algorithms.
 \newline
-We discussed several existing clustering heuristics and evaluated their suitability in our context.
+I discussed several existing clustering heuristics and evaluated their suitability for this context.
 Among these heuristics, two were found to be appropriate for clustering a predefined set of addresses with the available data: self-authorization \citep{FV:17} and graph representation learning \citep{Beres2020}.
-We modified the graph representation learning approach for our research goal.
+I modified the graph representation learning approach for our research goal.
 %to align with our research goals, this is the first attempt to utilize intra-set asset transfers in constructing the network graph
-To the best of our knowledge, we are the first to employ intra-set asset transfers for constructing the network graph.
-Moreover, we introduced a novel clustering heuristic that identifies uncompensated transfers of high-value NFTs, particularly LAND.
+To the best of my knowledge, this is the first approach of employing intra-set asset transfers for constructing the network graph.
+Moreover, I introduced a novel clustering heuristic that identifies uncompensated transfers of high-value NFTs, particularly LAND.
 \newline
 Due to its general applicability, graph representation learning proved to be the most successful clustering heuristic, while the other two heuristics yielded far fewer address clusters.
-In our exploration of node embedding algorithms, the Role2Vec algorithm stood out, correctly identifying the ground truth pair within the ten nearest neighbors in 71 percent of the cases.
-\newline
-From the 137,544 addresses transacting on Polygon or Ethereum, we identified an estimated 115,643 active Decentraland users.
+In my exploration of node embedding algorithms, the Role2Vec algorithm stood out, correctly identifying the ground truth pair within the ten nearest neighbors in 71 percent of the cases.
+\newline
+From the 137,544 addresses transacting on Polygon or Ethereum, I identified an estimated 115,643 active Decentraland users.
 A subset of 8,483 entities, representing 7.3\%, operated through multiple addresses.
-Notably, the largest address cluster we observed was an entity with 500 distinct addresses.
-Based on our analysis, this entity is likely a bot targeting Decentraland NFT airdrops, with intentions to resell them later.
+Notably, the largest address cluster I observed was an entity with 500 distinct addresses.
+Based on the analysis, this entity may represent a bot targeting Decentraland NFT airdrops, with intentions to resell them later.
 \newline
@@
 A significant challenge for graph representation learning is the formation of clusters after node embedding.
-In our study, we relied on an Euclidean distance threshold for this purpose.
+In this study, I relied on an Euclidean distance threshold for this purpose.
 However, the resulting number and size of clusters are highly sensitive to the precise selection of this threshold.
 \newline
-Notably, our approach is versatile and can be applied to other large predefined address sets.
+Notably, the discussed approach is versatile and can be applied to other large predefined address sets.
 This adaptability is particularly significant given the increasing importance of determining the true number of users in various blockchain applications, especially in areas like Decentralized Finance or on-chain governance.
 \newline
-Although we were able to detect entity clusters, Decentraland still exhibits a lot of natural activity.
+Although I was able to detect entity clusters, Decentraland still exhibits a lot of natural activity.
 Its open infrastructure presents vast opportunities for in-depth analysis of the virtual world, as demonstrated in this work.
@@
 My gratitude also extends to Mitchell Goldberg for his valuable inputs and discussions.
-Last but not least, a special thanks to Willy Thürkauf for his proof-reading.
 
